### 2022-12-02 Documentation/Relatorio_2/Conclusion/Conclusion.tex
new project organization

\section{Conclusion}

For further steps the following tasks will be done:

- make experiments with different time windows. This will help to see the time needed for the system to stabilize.

- change power supply and oscilloscope libraries to an updated version wich covers both hardwares.

- correct and upgrade plots to make a better sense of the data.

- Include DHT11 temperature and humidity sensor to the setup.

- Thread sincronization in the main routine.

### 2022-12-02 Documentation/Relatorio_2/Development/Development.tex
new project organization

\section{Development}

\subsection*{3.1 Peripherals integration}

Doing experiments we discovered that the frequency of the pump machine internal motors was
creating an interference in the flowrate. Therefore compromising the stabilization in cone jet mode.
A solution for that was to increase the flowrate wich smooths this pumping noise. For that was also necessary
to increase the nozzle diameter to balance with all other variables from the experiment.

\subsection*{3.2 Experiment 1}

\begin{figure}[H]
    \center
    \includegraphics[width=18cm]{images/images_folder_2/img1.png}
    \caption{Data acquired in the experiment 1 - liquid: Water AND alcohol}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{images/images_folder_2/img2.png}
    \caption{Dripping sample}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=15cm]{images/images_folder_2/img3.png}
    \caption{Cone jet sample}
\end{figure}

\begin{multicols}{3}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph1.png}
        \caption{mean current X voltage}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph2.png}
        \caption{deviation/mean}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph3.png}
        \caption{mean/median}
    \end{figure}

\end{multicols}

\subsection*{3.3 Experiment 2}

\begin{figure}[H]
    \center
    \includegraphics[width=18cm]{images/images_folder_3/data3.png}
    \caption{Data acquired in the experiment 2 - pure ethanol}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{images/images_folder_3/data3current.png}
    \caption{current graph with classification}
\end{figure}

\begin{multicols}{3}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph1.png}
        \caption{current mean X voltage}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph2.png}
        \caption{deviation/mean}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph3.png}
        \caption{mean/median}
    \end{figure}

\end{multicols}

\subsection*{3.4 Experiment 3}

\begin{figure}[H]
    \center
    \includegraphics[width=18cm]{images/images_folder_3/data4.png}
    \caption{Data acquired in the experiment 3 - pure ethanol}
\end{figure}

\begin{multicols}{3}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph1.png}
        \caption{current mean X voltage}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph2.png}
        \caption{deviation/mean}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph3.png}
        \caption{mean/median}
    \end{figure}

\end{multicols}

### 2022-12-02 Documentation/Relatorio_2/Summary/Summary.tex
new project organization

\section{Summary}

        Electrohydrodynamic Atomization (EHDA), also known as Electrospray (ES), is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.
EHDA surveys have contributed as an important tool for the development of water technology (thermal desalination and metal recovery), material sciences (nanofibers and nano spheres fabrication, metal recovery, selective membranes, and batteries), and biomedical application (droplet encapsulation).
Besides that, the project is merged with the Energy Transition strategy and Innovation Agenda Agriculture, Water, and Food, Key Enabling Technologies (KETs). 
Although, there are EHDA applications in industry, stabilizing the cone-jet spray mode is done empirically and based on mean current measurements.

The electric current flowing transported by the spray reveals characteristic shapes for different spray modes.
Those shapes cannot simply be summarized by its mean value. In figure one we can see an example of cone-jet mode electrospray.

\begin{figure}[H]
    \center
    \includegraphics[width=8cm]{images/electrospray.png}
    \label{img1}
    \caption{EHDA}
\end{figure}

Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task.

Industrial applications demand automated stabilization of a spray mode.
This can be achieved by a closed-loop control system.
Automated classification of the spray mode is a crucial part of a control system same as the development of an appropriate control algorithm. 
Signal processing implementations of previous projects of the NHL Stenden Water Technology group are showing good classification results.
Further research is necessary to improve the classification accuracy and research and implementation of a suitable classification algorithm. 
Because of that, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to match analysis possibilities with knowledge and infrastructure availability.

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
    \caption{System Architecture}
\end{figure}

\begin{multicols}{2}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/conejetexample.png}
        \caption{cone jet mode}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=5cm]{images/images_folder_3/multijetexample.png}
        \caption{multi jet mode}
    \end{figure}

\end{multicols}

### 2022-12-02 Documentation/literature review/main.tex
new project organization

\documentclass[10pt]{article}
\usepackage{multicol}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}%
\usepackage{microtype} 			% para melhorias de justificação
\usepackage[backend=biber]{biblatex}
\usepackage{newclude}
\addbibresource{refs.bib}

\author{João Pedro Miranda Marques - 2017050495}

\begin{document}

\include{front_cover/front_cover}

Electrohydrodynamic Atomization (EHDA), also known as Electrospray (ES), is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.
The electric current flowing transported by the spray reveals characteristic shapes for different spray modes.
Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
Industrial applications demand automated stabilization of a spray mode.
This can be achieved by a closed-loop control system. This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control
the variables to stabilize in the desired mode. In the figure we can see how EHDA experiment works.

\begin{figure}[H]
    \center
    \includegraphics[width=8cm]{images/electrospray.png}
    \label{img1}
    \caption{EHDA example}
\end{figure}

This project was inspired by the research \emph{A generic electrospray classification} \cite*[]{Sjaaks}.
In this paper the author studied the current signal through the high voltage circuit in the EHDA experiment.
This signal is highly correlated with the spraying dynamics because the current is flowing with the liquid charges sprayed.
The author analysed this current data grouping samples in a time window. With observation in the data and the process he could
notice that the dynamic mode of the spray can be classified using statistical measurements of the signal. In his research the author 
emphasised the separability in the data using the relations between mean, median and standart deviation of the signal. This paper is important
for this project because the author explored the classification with non visual data. By the other side, the author focused his research in statistical values
in the time domain. In the project we can explore more the data characteristics in the frequency domain.

Another project is the \emph{experimental investigation of scaling laws for electrospraying: dieletric constant effect}\cite*[]{Chen_Pui}.
Where the author study about the quemical properties of the liquid being sprayed that can actually interfere in the dynamics of the process. 
In the paper the author emphasised about the liquid dieletric constant. For us this paper is interesting because we can understand better which liquid
has a better margin of operation in cone jet mode for example. What is missing in his article is that it is not mentioning all the variables that can interfere in the 
electrospray dynamics, which would be important to know.

\pagebreak
\printbibliography
\end{document}

### 2022-12-02 Documentation/modelo_PFC_latex/Resultados/Resultados (Alexandre Mesquita's conflicted copy 2019-02-22).tex
new project organization

\chapter{Resultados}

Para a execução do projeto, algumas etapas de desenvolvimento tiveram de ser seguidas: familiarização com o sistema, estudo dos módulos envolvidos, leitura dos requisitos, elaboração de documento descrevendo todo o processo de implementação e relacionamento com os diversos módulos, implementação e testes.

\section{Atividades do Projeto}
\label{metodo3}

\section {Requisitos do Sistema}
\label{req}

\section{Desenvolvimeto e Implementação}

A Tabela \ref{tab:tabela} apresenta as atividades executadas.

\begin{table}
\centering
%Note os alinhamentos diferentes em cada coluna
\begin{tabular}{|c|r|l|}\hline
		Atividade 1 & aa  & ab  \\ 
					 & a & b \\ \hline
		Ativ. 2  & aa & ab \\			
					 &  a & b \\ \hline
		\end{tabular}
	\caption{Exemplo de tabela - Coloque toda informação sobre a tabela aqui}
	\label{tab:tabela}
\end{table}

\section{Testes}

\section{Análise dos Resultados}

Apresente os resultados sem adulterações e faça análises objetivas. Pense na melhor maneira de apresentar os resultados graficamente. Se os gráficos são difíceis de interpretar, talvez tabelas sejam uma forma melhor de apresentar resultados. Não apresente dados (gráficos e tabelas) se não há uma conclusão interessante a ser tirada. Lembre-se de ser conciso.

\emph{Não se esqueça das unidades!} Pense que \emph{a priori} todo número deve ter uma unidade. Não escreva as unidades em itálico (no ambiente matemático) e tome cuidado para diferenciar maiúsculas e minúsculas. Um exemplo é escrever $22$ [kN] e não $22 KN$ (Kelvin vezes Newton!).

Ao apresentar resultados experimentais, tome o cuidado para também apresentar o cálculo das incertezas sempre que forem significativas. Ao fazer conclusões, sempre considere se o tamanho da sua amostra é grande o suficiente do ponto de vista estatístico.

\section{Resumo do Capítulo}
\label{sec:resumoo4}
Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!

\section{Formato, expressões matemáticas e o \LaTeX}

\subsection{O \LaTeX}

O {\LaTeX}  é o método preferencial de preparação de documentos para textos técnicos nas ciências exatas. O {\LaTeX} permite não só lidar com equações de uma forma mais prática que em editores de texto, mas também facilita a formatação de documentos e tem um desempenho marcadamente superior a editores de texto na preparação de documentos longos como monografias.

Documentos em {\LaTeX} são escritos em um ou mais arquivos de texto com extensão .tex. Após a escrita, o .tex é \emph{compilado} para gerar arquivos nos formatos .pdf, .dvi ou .ps. Hoje há duas distribuições padrão para o \LaTeX. Sistemas Windows usam o {Mik\TeX} e sistemas Unix usam o \TeX Live. Além das distribuições, muitos usuários utilizam \emph{front-ends} que facilitam a edição do texto, a compilação e a instalação de pacotes.

Os pacotes necessários para compilar o presente documento devem ser encontrados numa instalação completa dessas distribuições. Se tiver dificuldades com os pacotes, você pode instalá-los manualmente ou tentar alterar o código para usar versões antigas dos mesmos.

A compilação pode ser feita pelos comandos \textsf{latex} ou \textsf{pdflatex}, invocados pela linha de comando ou pelo \emph{front-end}. Note que será necessário empregar o comando \textbf{mais de uma vez} para que as referências cruzadas saiam corretas.

Como discutido na Seção \ref{sec:revisão}, uma ferramenta útil para gerenciar as citações em {\LaTeX} é o Bib\TeX. Para gerar uma lista bibliográfica a partir do arquivo .bib, este arquivo deve ser indicado no arquivo .tex. Em seguida devem-se executar os comandos \textsf{pdflatex}, \textsf{bibtex} e \textsf{pdflatex} novamente sempre usando o .tex como argumento. Note que os comandos são executados nesta ordem e de forma repetida para que as referências cruzadas sejam geradas corretamente.

A fonte \textsf{Times}, indicada pela resolução do PFC e usada neste documento, não possui uma das aparências mais agradáveis, especialmente para os símbolos matemáticos. Se preferir símbolos matemáticos mais harmoniosos, remova a inclusão da fonte \textsf{newtxmath} no cabeçalho do .tex.

Nesta seção você deve encontrar exemplos dos comandos mais usados em \LaTeX. Outros exemplos e manuais podem ser encontrados na internet com facilidade.

\subsection{Expressões Matemáticas}

Ao escrever expressões matemáticas, defina todas as variáveis antes de usá-las ou imediatamente depois da expressão. Deixar de fazê-lo torna seu texto ilegível. Segue um exemplo.

Seja o par $(a_1,a_2)\in \mathbb{R}^2$. Para $s\in\mathbb{C}$, definimos a função $f(s)$ como
\[%cria equações sem numeração
f(s)\triangleq \frac{a_1 s+a_2}{s^2+2\zeta\omega_n s+\omega_n^2}
\enspace,
\]
onde os escalares $\zeta,\omega_n>0$ são constantes.

Note que não foi necessário atribuir valores às variáveis neste momento. Repare também como devemos \textbf{usar pontuação} (vírgula) nas equações, tratando-as como parte da frase. Usamos o símbolo $\triangleq$ ou $:=$ para deixar explícito que se trata de uma definição. Ser claro nesse aspecto facilita o entendimento do leitor.

A equação acima não foi numerada porque não será citada no texto. Vejamos um exemplo com numeração.

A função $f(\cdot)$ possui um zero em $-a_2/a_1$ (ou $-\frac{a_2}{a_1}$) e, para $\zeta<1$, possui polos complexos $p_{1,2}$ dados por
\begin{equation}
\label{eq:polos}
p_{1,2}=\omega_n \left(-\zeta\pm j\sqrt{1-\zeta^2}\right)
\enspace.
\end{equation}
Agora podemos citar os polos dados pela Equação (\ref{eq:polos}) (aqui adotamos a convenção de citar sempre com o número entre parênteses precedido da palavra Equação). Note como usamos um comando especial na Equação (\ref{eq:polos}) para garantir o ajuste automático do tamanho dos parênteses.

Vejamos agora como criar equações alinhadas. Considere o sistema dinâmico dado pelas equações diferenciais:

\begin{align}
\dot{x}_1 & = \cos(x_2)\cdot\ln(1/x_1)+\tan(u) \label{eq:x1dot} \\
\dot{x}_2 & = e^{-x_1-x_2} \nonumber \\
& y  = \min\{x_1,x_2\}  \label{eq:saida}
\enspace,
\end{align}
onde $x(t)=[x_1(t) ~ x_2(t)]'$, $t>0$, é a variável de estado do sistema, $u(t)$ é o sinal de entrada e $y(t)$ é o sinal de saída do sistema. Note no .tex que o caracter de tabulação \textsf{\&} foi usado para indicar o ponto de alinhamento horizontal das equações. Além disso, para ilustrar o uso do \LaTeX, retiramos a numeração da segunda equação e citamos as equações separadamente.

Nas Equações (\ref{eq:x1dot}) e (\ref{eq:saida}), aparecem operadores como $\min$, $\ln$, $\cos$ e $\tan$. A convenção aqui é que \textbf{variáveis devem ser escritas em itálico e operadores não}. Por essa razão todas as expressões matemáticas devem ser escritas no ambiente matemático (entre cifrão) mesmo quando for possível usar texto comum. Isso garante a consistência das fontes utilizadas (nem sempre a fonte do ambiente matemático é a mesma fonte do texto).

Para escrever matrizes, podemos fazer por exemplo:
\[
\sum_{n=0}^{\infty}z^{-n}\left[\begin{array}{cc}
\lambda & 1 \\
0 & \lambda
\end{array}\right]^n=
\left[\begin{array}{cc}
\frac{z}{z-\lambda} & \frac{z}{(z-\lambda)^2} \\
0 & \frac{z}{z-\lambda}
\end{array}\right]
,~\forall \lambda<|z|
\enspace.
\]

Para escrever uma expressão com múltiplos casos, podemos fazer, para um inteiro $N$ positivo,
\[
g[n]=
\left\{
\begin{array}{ll}
0,& \mbox{se }~ n\leq 0 \\
n,& \mbox{se }~ n=1,2,\ldots,N-1 \\
N,& \mbox{se }~ n\mod N = 0 \\
0,& \mbox{caso contrário}\enspace.
\end{array}
\right.
\]

\textbf{Nunca reaproveite símbolos} matemáticos, isto é, nunca use o mesmo símbolo para designar variáveis diferentes.

Para um exemplo com múltiplas linhas de expressão matemática: tem-se que, para $a\neq 0$,

\begin{equation}
\begin{split}
ax^2+bx+c &= 0 \\
& \Rightarrow a(x^2+bx/a+c/a) =0 \Rightarrow a((x+b/(2a))^2+c/a-b^2/(4a^2))=0  \\
& \Rightarrow (x+b/(2a))^2=(b^2-4ac)/(4a^2) \\
& \Rightarrow (x+b/(2a))=\pm\sqrt{b^2-4ac}/(2a) \\
& \Rightarrow x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}
\enspace.
\end{split}
\end{equation}

Note a argumentação lógica aqui. Não estamos dizendo que o valor de $x$ é dado pela última linha. Estamos dizendo que a hipótese da primeira linha juntamente com a hipótese $a\neq 0$ implicam os referidos valores de $x$. \textbf{Um erro comum dos alunos ao escrever é não distinguir a veracidade das implicações com a veracidade das hipóteses}.

\clearpage

### 2022-12-02 configuration_FUG.py

@@ -1,166 +1,0 @@
-
-# package needed to list available COM ports
-import serial.tools.list_ports
-# package needed for sleep
-import time
-import re
-import sys
-
-
-def FUG_initialize(com_port_idx):
-    # print out user information
-    # get available COM ports and store as list
-    com_ports = list(serial.tools.list_ports.comports())
-    # get number of available COM ports
-    no_com_ports = len(com_ports)
-
-    if no_com_ports > 0:
-        print("Total no. of available COM ports: " + str(no_com_ports))
-        # show all available COM ports
-        for idx, curr in enumerate(com_ports):
-            print("  " + str(idx) + ".)  " + curr.description)
-
-        if com_port_idx > no_com_ports or com_port_idx < 0:
-            print("[FUG] Incorrect value for COM port! Enter a Number (0 - " + str(no_com_ports - 1) + ")")
-            return None
-
-        # configure the COM port to talk to. Default values: 115200,8,N,1
-        com_port = serial.Serial(
-            port=com_ports[com_port_idx].device,  # chosen COM port
-            baudrate=115200,  # 115200
-            bytesize=serial.EIGHTBITS,  # 8
-            parity=serial.PARITY_NONE,  # N
-            stopbits=serial.STOPBITS_ONE,  # 1
-            timeout=0
-        )
-        try:
-            if com_port.is_open:
-                com_port.flushInput()
-                com_port.flushOutput()
-                print('[FUG] FUG initialized!')
-                print("[FUG] FUG Opened Port: " + com_ports[com_port_idx].device)
-                return com_port
-        except Exception as e:
-            print('[FUG] Error FUG_initialize()')
-            print('[FUG] Exception: ' + e.message)
-            return e.message
-            sys.exit(1)
-
-    else:
-        print('[FUG] Error FUG_initialize()')
-        return None
-
-
-
-
-# cmd, list of commands expected
-def FUG_sendcommands(com_port, cmd):
-    # cmd = ['I 6e-4', 'S0R 250', 'U 5e3', 'F1']
-    # cmd = ['I 6e-4', 'S0R 50', 'U 1e4']
-    # cmd = ['F0'] turn it off
-    # cmd = ['>M0?'] readback the actual voltage
-    responses = []
-    try:
-        for command in cmd:
-            # print("cmd:" + command)
[…]

### 2022-12-02 configuration_influxDB.py

@@ -1,86 +1,0 @@
-"""
-TITLE: Code for testing Influx database usage with grafana GUI
-AUTHOR: 乔昂  @jueta
-DATE: 21/10/2022
-FRAMEWORK: influxDB v2
-"""
-
-import influxdb_client
-from influxdb_client.client.write_api import SYNCHRONOUS
-import numpy as np
-import datetime
-import time
-
-
-# *************************************
-#       DATABASE CONFIGURATION
-# *************************************
-
-# token = os.environ.get("INFLUXDB_TOKEN")
-token = "X0wU2OIZbscp32eFh2fFfV83RKKd4hDV27wtj8OlRfBE7wm0scW1ntb63FleGF55a7es4IP3FFQ35ZsqFzLzRg=="
-print(token)
-org = "jpmm2209@gmail.com"
-url = "https://europe-west1-1.gcp.cloud2.influxdata.com"
-
-client = influxdb_client.InfluxDBClient(url=url, token=token, org=org)
-
-bucket = "test2"
-
-write_api = client.write_api(write_options=SYNCHRONOUS)
-
-
-# *************************************
-#      			 FUNCTIONS
-# *************************************
-
-# Logs the data to your InfluxDB
-def send_to_influxdb(id, mean, std, voltage_PS, timestamp, classification, temperature, humidity):
-    
-    json_body = [
-        {"measurement": "HighVoltage",
-         "tags": {
-             "classification": classification,
-        },
-         "time": timestamp,
-         "fields": {
-             "running_id": id,
-             "std_current": std,
-             "voltage_PS": voltage_PS,
-             "temperature": temperature,
-             "humidity": humidity
-        }
-        }
-    ]
-    try:
-        write_api.write(bucket='test2', record=json_body)
-        print("JSON Sent!")
-    except:
-        print("Package Lost!")  
-
-
-# *************************************
-#      	MAIN for testing purpose
-# *************************************
-
-
-# def main():
-
-
-#     for i in range(100):
-#         send_to_influxdb(
-#             id='01',
-#             mean= 1 + 1 * np.random.random(),
-#             std= 1 + 2 * np.random.random(),
-#             voltage_PS= 5 + 5 * np.random.random(),
-#             timestamp=datetime.datetime.utcnow(),
-#             classification=np.random.randint(0,5),
-#             temperature=20 + 10 * np.random.random(),
-#             humidity=80 + 20 * np.random.random()
-#         )
[…]

### 2022-12-02 electrospray.py

@@ -1,403 +1,0 @@
-import logging
-import numpy as np
-import csv
-import json
-from scipy.signal import argrelextrema
-from scipy import signal
-from scipy.signal import hilbert
-from scipy.signal import butter, lfilter
-
-
-class ElectrosprayConfig:
-    def __init__(self, file_setup, file_liquid):
-        self.file_setup = file_setup
-        self.file_liquid = file_liquid
-        self.ki = 6.46  # no units
-
-    def __repr__(self):
-        """dictionary = {
-            "electrical conductivity": str(self.k_electrical_conductivity),
-            "flow rate": str(self.q_flow_rate),
-            "voltage": str(self.voltage),
-            "setup": str(self.json_setup_obj)
-        }
-        return "config: %s " % (json.dumps(dictionary))"""
-        d = dict(
-            config=dict(comment=str(self.current_comment),
-                        flow_rate_min=str(self.flow_rate_min), type_of_measurement=str(self.typeofmeasurement)))
-        return json.dumps(d, sort_keys=True)
-
-    def load_json_config_setup(self):
-
-        print("load_json_config_setup")
-        # print(self.file_setup)
-        
-        with open(self.file_setup, 'r') as file:
-            # First we load existing data into a dict.
-            self.json_setup_obj = json.load(file)
-            # print(type(self.json_setup_obj))
-
-        """with open(self.file_setup) as json_file:
-            self.json_setup_obj = json.load(json_file)"""
-
-    def load_json_config_liquid(self):
-
-        print("load_json_config_liquid")
-        # print(self.file_liquid)
-
-        with open(self.file_liquid, 'r') as file:
-            # First we load existing data into a dict.
-            self.json_liquid_obj = json.load(file)
-            # print(type(self.json_liquid_obj))
-
-        """with open(self.file_liquid) as json_file:
-            self.json_liquid_obj = json.load(json_file) # dictionary"""
-
-    def get_json_liquid(self):
-        return self.json_liquid_obj
-
-    def get_json_setup(self):
-        return self.json_setup_obj
-
-    def set_comment_current(self, current_comment):
-        self.current_comment = current_comment
-
-    def set_type_of_measurement(self, typeofmeasurement):
-        self.type_of_measurement = typeofmeasurement
-
-    def get_dict_config(self):
-        dictionary = {
-            "voltage regime": self.type_of_measurement
-        }
[…]

### 2022-12-02 literature/monicas/histogramliquid.py

@@ -1,342 +1,0 @@
-import io
-import pandas as pd
-import matplotlib.pyplot as plt
-from matplotlib import ticker
-from scipy import stats
-from scipy.signal import butter, lfilter
-from scipy.stats import norm
-
-import json
-import os
-import matplotlib.pyplot as plt
-from matplotlib.patches import Rectangle
-import numpy as np
-import re
-import seaborn as sns
-from scipy.stats import norm
-import math
-import pandas as pd
-import matplotlib.cm as cm
-from PIL import Image
-from io import BytesIO
-
-from scipy.stats import norm
-
-mean_value_array = []
-med_value_array = []
-flow_rate_chen_pui = [[]]
-flow_rate_actual_array = [[]]
-flow_rate_array = [[]]
-stddev_value_array = [[]]
-fourier_peaks_array = [[]]
-maximum_variation_distance_array = [[]]
-data_each_shape = [[]]
-mean_each_shape = [[]]
-sjaak_verified = [[]]
-x_ganan_calvo = [[]]
-I_Ig_ganan_calvo = [[]]
-sjaak_std_mean_array = [[]]
-sjaak_mean_median_array = [[]]
-sjaak_verified_false = [[]]
-sjaak_verified_true = [[]]
-electrical_conductivity_array = [[]]
-mean_histogram = [[]]
-
-rho = [0]
-electrical_conductivity = [0]
-permitivity = [0]
-surface_tension = [0]
-dielectric_const = [0]
-min_fr_chen_pui = [0]
-
-name = []
-slope = []
-all_data = []
-sjaak_std_mean = []
-sjaak_avg_development_relaxation_ratios = []
-sjaak_mean_median = []
-
-sjaak_std_mean_array_total = []
-sjaak_mean_median_array_total = []
-mean_div_max_variation_array = []
-variance_div_deviation_array = []
-height_div_pos_array = []
-pos_array = []
-height_array = []
-mean_freq_array = []
-freq_values = []
-mean_freq_values = []
-variance_value_array = []
-med_value_array = []
-
-record_last_index_value = 0
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-ki = 6.46
-index = 0
-index_aux = 0
-# path = 'C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles'
-
-path = 'E:/2022json/'
-directory_contents = os.listdir(path)
-print(directory_contents)
[…]

### 2022-12-02 literature/monicas/plot_italy.py

@@ -1,206 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-from matplotlib.widgets import Slider, Button
-import json
-import os
-import matplotlib.pyplot as plt
-from scipy import signal
-from matplotlib.patches import Rectangle
-import numpy as np
-import re
-import seaborn as sns
-from scipy.stats import norm
-import math
-import pandas as pd
-import matplotlib.cm as cm
-from PIL import Image
-from io import BytesIO
-
-from scipy.stats import norm
-data_index = 0
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-#0 - 5000 hz
-
-#absolute value: cumsum 0 -5000 hz
-"""
-make another plot 0 - 50k
-
-we want to ccumulate until a certain point
-we dont want the index - bc is DC
-
-fft for cone jet is empty except for the dc frequency
-"""
-
-index = 0
-index_aux = 0
-path = "E:/2022JSONCORRECT/"
-#path = "C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/"
-filename = "rampsetup7ethyleneglycol_all shapes_1.222232e-09m3_s.json"
-
-#filename = "rampsetup7ethyleneglycol_CONE JET REGION_1.222232e-09m3_s.json"
-directory_contents = os.listdir(path)
-
-data = []
-
-mean_div_max_variation_array = []
-variance_div_deviation_array = []
-
-voltage_PS_array = []
-current_PS_array = []
-spray_mode_array = []
-mean_value_array = []
-flow_rate_actual = 0
-med_array = []
-flow_rate_actual_array = []
-flow_rate_array = []
-stddev_array = []
-fourier_peaks_array = []
-maximum_variation_distance_array = []
-rms_array = []
-data_each_flow_rate = []
-mean_each_flow_rate = []
-electrical_conductivity_array = []
-mean_array = []
-tuple_mean_and_flowrate = []
-data_array = []
-name_list = []
-
-plt.rcParams["figure.autolayout"] = True
-
-def calculate_for_json_with_all_shapes(data_dict, index):
-    global flow_rate_actual
-    # for i in range(10, 60):
-    for i in range(3, len(data_dict['processing'])):
-        # datapoints = (data_dict['measurements'][i]['data [nA]'])
-        # data_points_np = np.array(datapoints)
-        current_PS = (data_dict['measurements'][i]['current PS'])
[…]

### 2022-12-02 literature/monicas/plot_italy_SJAAKVARIABLES.py

@@ -1,131 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-from matplotlib.widgets import Slider, Button
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import itertools
-import math
-font = {'weight' : 'bold',
-        'size' : 18}
-
-plt.rc('font', **font)
-
-data_index = 0
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-#0 - 5000 hz
-
-index = 0
-index_aux = 0
-# path = "E:/2022jsonauxethanol/"
-#path = "E:/summer22water60alcohol40/"
-#path = "E:/summer22propanol/"
-path = "E:/summer22ethanol/"
-#path = "E:/summer22propanol/"
-#path = "C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/"
-directory_contents = os.listdir(path)
-#directory_contents = "stepsetup92propanol_all shapes_1.94446e-08m3_s.json"
-data = []
-
-mean_div_max_variation_array = []
-variance_div_deviation_array = []
-
-voltage_PS_array = []
-current_PS_array = []
-spray_mode_array = []
-mean_value_array = []
-flow_rate_actual = 0
-med_array = []
-flow_rate_actual_array = []
-flow_rate_array = []
-stddev_array = []
-fourier_peaks_array = []
-maximum_variation_distance_array = []
-rms_array = []
-data_each_flow_rate = []
-mean_each_flow_rate = []
-electrical_conductivity_array = []
-mean_array = []
-tuple_mean_and_flowrate = []
-data_array = []
-name_list = []
-sjaak_std_div_mean = []
-sjaak_mean_div_median = []
-
-plot_markers = itertools.cycle((',', '+', '^', 'o', '*', '>', '2', '1', '<', '3', '+', 's', '4'))
-plot_colors = itertools.cycle(('orange', 'firebrick', 'hotpink', 'aqua', 'purple', 'red', 'yellowgreen', 'lightseagreen', 'blueviolet', 'darkcyan', 'green', 'black'))
-plot_lines = []
-
-def calculate_for_json_with_all_shapes(data_dict):
-    # for i in range(10, 60):
-    global flow_rate_actual_array
-    flow_rate_actual = (data_dict['measurements'][10]['flow rate [m3/s]'])
-    print(flow_rate_actual)
-    #flow_rate_actual_array.append(str(round(float(flow_rate_actual), 2)) + "[m3/s]")
[…]

### 2022-12-02 literature/monicas/plotfolhaconejet_italy.py

@@ -1,154 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-from matplotlib.widgets import Slider, Button
-import json
-import os
-import matplotlib.pyplot as plt
-from scipy import signal
-from matplotlib.patches import Rectangle
-import numpy as np
-import re
-import seaborn as sns
-from scipy.stats import norm
-import math
-import pandas as pd
-import matplotlib.cm as cm
-from PIL import Image
-from io import BytesIO
-
-from scipy.stats import norm
-data_index = 0
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-#0 - 5000 hz
-
-#absolute value: cumsum 0 -5000 hz
-"""
-make another plot 0 - 50k
-
-we want to ccumulate until a certain point
-we dont want the index - bc is DC
-
-fft for cone jet is empty except for the dc frequency
-"""
-index = 0
-index_aux = 0
-path = "E:/2022JSONTESTSEG/"
-#path = "E:/2022jsonauxethanol/"
-#path = "C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/"
-directory_contents = os.listdir(path)
-
-data = []
-
-mean_div_max_variation_array = []
-variance_div_deviation_array = []
-
-voltage_PS_array = []
-current_PS_array = []
-spray_mode_array = []
-mean_value_array = []
-flow_rate_actual = 0
-med_array = []
-flow_rate_actual_array = []
-flow_rate_array = []
-stddev_array = []
-fourier_peaks_array = []
-maximum_variation_distance_array = []
-rms_array = []
-data_each_flow_rate = []
-mean_each_flow_rate = []
-electrical_conductivity_array = []
-mean_array = []
-tuple_mean_and_flowrate = []
-data_array = []
-name_list = []
-sjaak_std_div_mean = []
-sjaak_mean_div_median = []
-
-plt.rcParams["figure.autolayout"] = True
-
-def calculate_for_json_with_all_shapes(data_dict):
-    # for i in range(10, 60):
-    for i in range(0, len(data_dict['processing'])):
-        # datapoints = (data_dict['measurements'][i]['data [nA]'])
-        # data_points_np = np.array(datapoints)
-        current_PS = data_dict['measurements'][i]['current PS']
-        voltage_PS = data_dict['measurements'][i]['voltage']
[…]

### 2022-12-02 literature/monicas/validation.py

@@ -1,325 +1,0 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-from scipy import stats
-from scipy.signal import butter, lfilter
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import re
-import math
-
-import matplotlib.cm as cm
-
-all_data = []
-mean_value_array = []
-med_value_array = []
-flow_rate_chen_pui = []
-flow_rate_actual_array = []
-flow_rate_array = []
-I_actual_array = []
-stddev_value_array = []
-alpha_chen_pui = []
-I_emitted_chen_pui = []
-sjaak_verified = []
-sjaak_verified_false = 0
-sjaak_verified_true = 0
-x_ganan_calvo = []
-I_Ig_ganan_calvo = []
-sjaak_std_mean_array = []
-sjaak_mean_median_array = []
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-number_subplots = 5
-ki = 6.46
-
-path = '/E:/2022JSONTESTSEG/'
-directory_contents = os.listdir(path)
-print(directory_contents)
-current_shapes = ["no voltage no fr", "no voltage", "dripping", "intermittent", "cone jet", "multijet", "streamer onset"]
-
-for i in directory_contents:
-    res = re.search("cone jet", i)
-    if res == None:
-
-
-        continue
-    else:
-        print(i)
-        with open('C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/'+i) as json_file:
-            data_dict = json.load(json_file)
-
-            manual_shape = data_dict['config']['liquid']['actual measurement']['current shape manual']
-            print("\nmanual shape:", manual_shape)
-
-            current_comment = data_dict['config']['liquid']['actual measurement']['current comment']
-            res = re.search("unstable", current_comment)
-
-            if res == None:
-                name = data_dict['config']['liquid']['name']
-
-                # flow_rate_actual = data_dict['config']['liquid']['actual measurement']['flow rate']
-                electrical_conductivity = data_dict['config']['liquid']['actual measurement']['electrical conductivity']*10 # ToDo: take off this *10 for the next measurements
-                min_fr_chen_pui = data_dict['config']['liquid']['actual measurement']['flow rate chen pui']
-                rho = data_dict['config']['liquid']['density']
-                permitivity = data_dict['config']['liquid']['vacuum permitivity']
-
[…]

### 2022-12-02 literature/monicas/validation_classification_conejet.py

@@ -1,579 +1,0 @@
-import io
-import pandas as pd
-import matplotlib.pyplot as plt
-from scipy import stats
-from scipy.signal import butter, lfilter
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import re
-import math
-import pandas as pd
-import matplotlib.cm as cm
-from PIL import Image
-from io import BytesIO
-
-save_path = """E:/2022json/"""
-file_name = "teste"
-completeName = os.path.join(save_path, file_name)
-
-mean_value_array = [[]]
-med_value_array = [[]]
-flow_rate_chen_pui = [[]]
-flow_rate_actual_array = [[]]
-flow_rate_array = [[]]
-stddev_value_array = [[]]
-alpha_chen_pui = [[]]
-I_emitted_chen_pui = [[]]
-sjaak_verified = [[]]
-x_ganan_calvo = [[]]
-I_Ig_ganan_calvo = [[]]
-sjaak_std_mean_array = [[]]
-sjaak_mean_median_array = [[]]
-sjaak_verified_false = [[]]
-sjaak_verified_true = [[]]
-electrical_conductivity_array = [[]]
-rho = [0]
-electrical_conductivity = [0]
-permitivity = [0]
-surface_tension = [0]
-dielectric_const = [0]
-min_fr_chen_pui = [0]
-
-name = []
-slope = []
-all_data = []
-sjaak_std_mean = []
-sjaak_avg_development_relaxation_ratios = []
-sjaak_mean_median = []
-
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-ki = 6.46
-index = 0
-index_aux = 0
-path = 'C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/'
-directory_contents = os.listdir(path)
-print(directory_contents)
-current_shapes = ["no voltage no fr", "no voltage", "dripping", "intermittent", "cone jet", "multijet",
-                  "streamer onset"]
-
-for i in directory_contents:
-    res = re.search("cone jet", i)
-    if res == None:
-        continue
-    else:
-        print(i)
-        with open(path + i) as json_file:
-            data_dict = json.load(json_file)
-            manual_shape = data_dict['config']['liquid']['actual measurement']['current shape manual']
-            print("\nmanual shape:", manual_shape)
-            current_comment = data_dict['config']['liquid']['actual measurement']['current comment']
-            res = re.search("unstable", current_comment)
[…]

### 2022-12-02 literature/monicas/validation_matrix.py

@@ -1,488 +1,0 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-from scipy import stats
-from scipy.signal import butter, lfilter
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import re
-import math
-
-import matplotlib.cm as cm
-
-mean_value_array = [[]]
-med_value_array = [[]]
-flow_rate_chen_pui = [[]]
-flow_rate_actual_array = [[]]
-flow_rate_array = [[]]
-stddev_value_array = [[]]
-alpha_chen_pui = [[]]
-I_emitted_chen_pui = [[]]
-sjaak_verified = [[]]
-x_ganan_calvo = [[]]
-I_Ig_ganan_calvo = [[]]
-sjaak_std_mean_array = [[]]
-sjaak_mean_median_array = [[]]
-sjaak_verified_false = [[]]
-sjaak_verified_true = [[]]
-electrical_conductivity_array = [[]]
-rho = [0]
-electrical_conductivity = [0]
-permitivity = [0]
-surface_tension = [0]
-dielectric_const = [0]
-min_fr_chen_pui = [0]
-
-name = []
-slope = []
-all_data = []
-sjaak_std_mean = []
-sjaak_avg_development_relaxation_ratios = []
-sjaak_mean_median = []
-"""beta_ganan_calvo = []
-alphap_ganan_calvo = []
-I_ganan_calvo = []
-Ig_ganan_calvo = []"""
-
-sampling_frequency = 1e5
-time_step = 1 / sampling_frequency
-ki = 6.46
-index = 0
-index_aux = 0
-path = 'C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/'
-directory_contents = os.listdir(path)
-print(directory_contents)
-current_shapes = ["no voltage no fr", "no voltage", "dripping", "intermittent", "cone jet", "multijet",
-                  "streamer onset"]
-
-for i in directory_contents:
-    res = re.search("cone jet", i)
-    if res == None:
-        continue
-    else:
-        print(i)
-        with open(path + i) as json_file:
-            data_dict = json.load(json_file)
-            manual_shape = data_dict['config']['liquid']['actual measurement']['current shape manual']
-            print("\nmanual shape:", manual_shape)
-            current_comment = data_dict['config']['liquid']['actual measurement']['current comment']
-            res = re.search("unstable", current_comment)
-            electrical_conductivity = data_dict['config']['liquid']['actual measurement'][
[…]

### 2022-12-02 literature/peripherals/Arduino_camera_trigger/src/cameraTrigger.cpp

@@ -1,38 +1,0 @@
-/*
-	Arduino code for Triggering the Photon Camera from serial interface.
-	AUTHOR: 乔昂
-	DATE: 26/10/2022
-*/
-
-#include <Arduino.h>
-
-void setup()
-{
-	pinMode(8, OUTPUT);
-	digitalWrite(8, LOW);
-	Serial.begin(9600);
-}
-
-void loop()
-{
-	if (Serial.available() > 0)
-	{
-		int value = Serial.readString().toInt();
-		if (value == 1)
-		{
-			digitalWrite(8, HIGH);
-			delay(1);
-			digitalWrite(8, LOW);
-			delay(50);
-			digitalWrite(8, HIGH);
-			delay(1);
-			digitalWrite(8, LOW);
-			Serial.print("Start Reccording!");
-		}
-		else
-		{
-			Serial.print("Arduino Wrong Value Received: ");
-			Serial.print(value);
-		}
-	}
-}

### 2022-12-02 literature/peripherals/pyphotron/setup.py

@@ -1,43 +1,0 @@
-import os
-import struct
-import numpy as np
-
-from setuptools import setup, find_packages, Extension
-from Cython.Build import cythonize
-
-from pyphotron.utils import write_codes
-write_codes()  # Write the file with the error codes (required before install)
-
-requirements = [
-    'numpy'
-]
-
-sdk_root = '.'
-lib_dir = os.path.abspath(os.path.normpath(os.path.join(sdk_root, 'Lib\\64bit(x64)')))
-include_dir = os.path.abspath(os.path.normpath(os.path.join(sdk_root, 'Include')))
-
-assert os.path.exists(lib_dir), "Library directory '{}' missing".format(lib_dir)
-assert os.path.exists(include_dir), "Include directory '{}' missing".format(lib_dir)
-assert 8 * struct.calcsize("P") == 64, 'Not running 64 bit python'
-
-
-photron_camera_extension = Extension(
-    name='pyphotron.pyphotron_pdclib',
-    sources=['pyphotron/pyphotron_pdclib.pyx'],
-    include_dirs=[include_dir, np.get_include()],
-    libraries=['PDCLIB'],
-    library_dirs=[lib_dir],
-    extra_compile_args=['/Gz', '/fp:precise', '/Zc:wchar_t', '/Zc:forScope', '/Zc:inline'],
-    extra_link_args=['/DEBUG', '/MACHINE:X64'], #'/VERBOSE'],
-)
-setup(
-    name='pyphotron',
-    version='0.0.1',
-    description='Python bindings for the Photron PDC library',
-    install_requires=requirements,
-    packages=find_packages(exclude=('config', 'doc', 'tests*')),
-    ext_modules=cythonize( [photron_camera_extension], language_level=3, ),
-    requires=['Cython'],
-    author='crousseau',
-    # zip_safe=False,  # TODO: remove ?
-)

### 2022-12-02 literature/peripherals/serial_GSM/AT_gsm.py

@@ -1,15 +1,0 @@
-import time
-import serial
-import sys
-import RPi.GPIO as GPIO
-
-SERIAL_PORT ="/dev/ttyS0"
-
-ser = serial.Serial (SERIAL_PORT, baudrate = 9600, timeout=5)
-ser.write("AT")
-print("dialing")
-time.sleep(10)
-ser.write("ATD9443680313;\r ")
-print("dialing")
-time.sleep(10)
-ser.write("ATH\r ")

### 2022-12-02 literature/peripherals/serial_GSM/USBtoUART_test.ino.py

@@ -1,18 +1,0 @@
-
-import serial
-import time
-
-# make sure the 'COM#' is set according the Windows Device Manager
-ser = serial.Serial('COM8', 115200, timeout=1)
-time.sleep(2)
-
-for i in range(50):
-    line = ser.readline()   # read a byte
-    if line:
-        string = line.decode()  # convert the byte string to a unicode string
-        num = int(string) # convert the unicode string to an int
-        print(num)
-
-ser.close()
-
-# https://www.youtube.com/watch?v=KOig5ndq2ek&ab_channel=CytronTechnologies

### 2022-12-02 literature/peripherals/serial_GSM/testSIM4G.sh

@@ -1,559 +1,0 @@
-#!/bin/bash
-############################################################################
-# ModemStat -- Version 2.0.2
-#
-# Runs a series of diagnostic tests on the modem to determine what the
-#
-# - Signal strength is
-# - Network registration state
-# - SIM state (Pin Lock / Blocked / other error )
-# - Service level available and Selected (GPRS/3G/etc..)
-# - Modem Type / IMEI / SIM Nunber/ Firmware version
-#
-# Copyright (c) 2016-2021 Andrew O'Connell and others
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-#
-# THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
-# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
-# MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
-# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE
-# LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION
[…]

### 2022-12-02 literature/peripherals/serial_pump/serial_test_pump.py

@@ -1,77 +1,0 @@
-import time
-import serial
-
-"""
-VER The pump type and software version
-DIA Diameter of the syringe or tubing - Use quick set area to set syringe 
-DIR The current pumping direction.
-PHN The current phase number
-RAT The current pumping rate.
-FUN The current pump function.
-DIS The Infusion and Withdrawal counter values from the pump.
-AL Alarms on/off use manual command
-00AL1 will turn alarms on for the pump at address 0
-PF Power fail on/off 
-TRG Trigger type
-DIN Digital input state 
-ROM Pump motor operating TTL out signal
-LOC Keypad lockout 
-BUZ Buzzer on/off
-SAF Safe mode on/off 
-BP Keypad beeping on/off
-IN2 Digital input #2 
-IN4 Digital input #3
-IN4 Digital input #4 
-IN6 Digital input #6
-"""
-repeat = "VER"
-
-
-command_sequence = ["00PHN", "00STP", "*BUZ12", "0BUZ12", "00RUN", "00VOL", "00DIR", "00RAT",
-                    "00FUN", "00TIM", "00PHN", "00STP"]
-
-command_sequence_run = ["00PHN", "00STP", "*BUZ12", "0BUZ12", "00RUN", "00VOL", "00DIR", "00RAT",
-                    "00FUN", "00TIM", "00PHN", ]
-
-command_sequence_verify_how_much_dispensed = ["00PHN", "00STP", "*BUZ12", "0BUZ12", "00RUN", "00VOL", "00DIR", "00RAT",
-                    "00FUN", "00TIM", "00PHN", "00STP"]
-
-command_sequence_stop = ["00STP"]
-
-command_diameter_double_check = ["00dia1.3", "00.dia"] # response should be 00S1.300
-
-command_sequence_defining_step_rate = ["dia 1.3", "al 1", "bp 1", "PF 0", "phase START",
-                                       "fun rat", "rat5uh", "vol1", "00dir", "dir inf",
-                                       "phase", "fun rat", "rat5.5uh", "vol 5", "dir inf",
-                                       "phase", "fun stp"]
-com_port = serial.Serial(
-    port="COM6",  # chosen COM port
-    baudrate=19200,  #
-    bytesize=serial.EIGHTBITS,  # 8
-    parity=serial.PARITY_NONE,  # N
-    stopbits=serial.STOPBITS_ONE,  # 1
-    timeout = 1
-)
-print("name: " + com_port.name)
-
[…]

### 2022-12-02 literature/peripherals/serial_sensor_dht11/serial_dht11_test_2.py

@@ -1,189 +1,0 @@
-#############################################
-#    Retrieving the data from a DHT sensor
-#    connected to an Arduino Uno board
-# by A.LINA June 2014
-#############################################
-
-import os
-import re
-import matplotlib.pyplot as plt
-import threading as thr
-import serial as srl
-import time
-
-ArduinoPort = "/dev/tty.usbmodem1451"
-ArduinoSerial = None
-DataTime = None
-ArduinoDataH = None
-ArduinoDataT = None
-
-
-def InitSerial():
-    global ArduinoSerial
-
-    ArduinoSerial = srl.Serial(ArduinoPort,
-                               baudrate=9600,
-                               bytesize=srl.EIGHTBITS,
-                               parity=srl.PARITY_NONE,
-                               stopbits=srl.STOPBITS_ONE,
-                               timeout=2,
-                               xonxoff=0,
-                               rtscts=0)
-
-    time.sleep(2)
-    ArduinoSerial.baudrate = 9600
-    print("Open serial communication with Arduino")
-    print(ArduinoSerial)
-    print("======================================")
-    return ArduinoSerial.isOpen()
-
-
-def SetSamplingRate(SamplingRate):
-    if (ArduinoSerial.isOpen()):
-        ArduinoSerial.readline()
-        temp = str(20000 + SamplingRate);
-        ArduinoSerial.write(temp.encode('utf-8'))
-
-
-def StartSendData():
-    if (ArduinoSerial.isOpen()):
-        ArduinoSerial.readline()
-        temp = str(10001);
-        ArduinoSerial.write(temp.encode('utf-8'))
-
-
-def StopSendData():
-    if (ArduinoSerial.isOpen()):
-        ArduinoSerial.readline()
-        temp = str(10000);
-        ArduinoSerial.write(temp.encode('utf-8'))
-
-
-def GetData(DurationSec):
-    global ArduinoDataH, ArduinoDataT, DataTime
-
-    DataTime = []
-    ArduinoDataH = []
-    ArduinoDataT = []
-    Inc = 0
-
-    InitTime = time.time()
-
-    # dummy read to flush the port
-    ArduinoSerial.readline()
-
-    while ((time.time() - InitTime) < DurationSec):
-        print
[…]

### 2022-12-02 literature/peripherals/tiepie/OscilloscopeBlock.py

@@ -1,123 +1,0 @@
-# OscilloscopeBlock.py
-#
-# This example performs a block mode measurement and writes the data to OscilloscopeBlock.csv.
-#
-# Find more information on http://www.tiepie.com/LibTiePie .
-
-from __future__ import print_function
-import time
-import os
-import sys
-import libtiepie
-from printinfo import *
-
-# Print library info:
-print_library_info()
-
-# Enable network search:
-libtiepie.network.auto_detect_enabled = True
-
-# Search for devices:
-libtiepie.device_list.update()
-
-# Try to open an oscilloscope with block measurement support:
-scp = None
-for item in libtiepie.device_list:
-    if item.can_open(libtiepie.DEVICETYPE_OSCILLOSCOPE):
-        scp = item.open_oscilloscope()
-        if scp.measure_modes & libtiepie.MM_BLOCK:
-            break
-        else:
-            scp = None
-
-if scp:
-    try:
-        # Set measure mode:
-        scp.measure_mode = libtiepie.MM_BLOCK
-
-        # Set sample frequency:
-        scp.sample_frequency = 1e6  # 1 MHz
-
-        # Set record length:
-        scp.record_length = 10000  # 10000 samples
-
-        # Set pre sample ratio:
-        scp.pre_sample_ratio = 0  # 0 %
-
-        # For all channels:
-        for ch in scp.channels:
-            # Enable channel to measure it:
-            ch.enabled = True
-
-            # Set range:
-            ch.range = 8  # 8 V
-
-            # Set coupling:
-            ch.coupling = libtiepie.CK_DCV  # DC Volt
-
-        # Set trigger timeout:
-        scp.trigger_time_out = 100e-3  # 100 ms
-
-        # Disable all channel trigger sources:
-        for ch in scp.channels:
-            ch.trigger.enabled = False
-
-        # Setup channel trigger:
-        ch = scp.channels[0]  # Ch 1
-
-        # Enable trigger source:
-        ch.trigger.enabled = True
-
-        # Kind:
-        ch.trigger.kind = libtiepie.TK_RISINGEDGE  # Rising edge
-
-        # Level:
-        ch.trigger.levels[0] = 0.5  # 50 %
-
-        # Hysteresis:
-        ch.trigger.hystereses[0] = 0.05  # 5 %
-
-        # Print oscilloscope info:
-        print_device_info(scp)
-
-        # Start measurement:
-        scp.start()
-
-        # Wait for measurement to complete:
-        while not scp.is_data_ready:
[…]

### 2022-12-02 literature/peripherals/tiepie/OscilloscopeBlock_CH1_influx.py

@@ -1,185 +1,0 @@
-# OscilloscopeBlock.py
-#
-# This example performs a block mode measurement and writes the data to OscilloscopeBlock.csv.
-#
-# Find more information on http://www.tiepie.com/LibTiePie .
-
-from __future__ import print_function
-import time
-import _datetime
-import os
-import sys
-import libtiepie
-from printinfo import *
-import numpy as np
-import datetime
-from influxdb import InfluxDBClient
-
-def send_to_influxdb(measurement, mean, std, voltage_PS, timestamp, classification, temperature, humidity):
-    json_body = [
-        {"measurement": measurement,
-         "tags": {
-             "classification": classification,
-         },
-         "time": timestamp,
-         "fields": {
-             "std_current": std,
-             "voltage_PS": voltage_PS,
-             "temperature": temperature,
-             "humidity": humidity
-         }
-         }
-    ]
-
-    payload = [{
-        "mean_current": mean,
-
-        "time and date": timestamp,
-        "classification": classification,
-        "sensor": {
-            "temperature": temperature,
-            "humidity": humidity
-        }
-    }]
-    # client.write_points(payload)
-    client.write_points(json_body)
-
-
-
-# Print library info:
-print_library_info()
-
-# Enable network search:
-libtiepie.network.auto_detect_enabled = True
-
-# Search for devices:
-libtiepie.device_list.update()
-
-# Try to open an oscilloscope with block measurement support:
-scp = None
-for item in libtiepie.device_list:
-    if item.can_open(libtiepie.DEVICETYPE_OSCILLOSCOPE):
-        scp = item.open_oscilloscope()
-        """if scp.measure_modes & libtiepie.MM_BLOCK:
-            break
-        else:
-            scp = None
-        """
-
-if scp:
-    try:
-        # Set measure mode:
-        scp.measure_mode = libtiepie.MM_BLOCK
-
-        # Set sample frequency:
-        scp.sample_frequency = 1e5  # 1 MHz
-
-        # Set record length:
-        scp.record_length = 10000  # TODO: 50000 samples
-
-        # Set pre sample ratio:
-        scp.pre_sample_ratio = 0  # 0 %
-
-        # For 1 channel:
-        scp.channels[0].enabled = True
-        scp.channels[0].range = 8  # in V
-        scp.channels[0].coupling = libtiepie.CK_DCV # DC Volt
-        scp.channels[0].trigger.enabled = True
[…]

### 2022-12-02 mainElectrospray.py

@@ -1,254 +1,0 @@
-import threading
-import sys
-import queue
-import classification_electrospray
-from printinfo import *
-import matplotlib.pyplot as plt
-from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig
-from validation_electrospray import ElectrosprayValidation
-from classification_electrospray import ElectrosprayClassification
-from configuration_FUG import *
-import cameraTrigger
-import data_acquisition
-import plotting 
-import data_processing
-import os
-import json
-import logging
-
-
-
-# # # **************************************
-# # #                 MAIN
-# # # **************************************
-if __name__ == '__main__':
-
-
-# # # **************************************
-# # #         INITIAL CONFIGURATION
-# # # **************************************
-
-    finish_event = threading.Event()  # when Power Supply finish the finish_event will be set
-
-    # LOGGING CONFIG
-    LOG_FILENAME = r'logging_test.out'
-    logging.basicConfig(filename=LOG_FILENAME, encoding='utf-8',
-                        format='%(asctime)s %(message)s', level=logging.INFO)
-    logging.info('Started')
-
-    sampling_frequency = 1e5  # 100000
-    array_electrospray_measurements = []
-    array_electrospray_processing = []
-
-    name_setup = "setup12"
-    setup = "setup/nozzle/" + name_setup
-    name_liquid = "ethanol" # ["ethyleneglycolHNO3", "ethanol", water60alcohol40, 2propanol]
-    liquid = "setup/liquid/" + name_liquid
-    current_shape_comment = "difficult cone jet stabilization"
-   
-    FLAG_PLOT = True
-    plt.style.use('seaborn-colorblind')
-    plt.ion()
-
-    electrospray_config_liquid_setup_obj = ElectrosprayConfig(setup + ".json", liquid + ".json")
-    electrospray_config_liquid_setup_obj.load_json_config_liquid()
-    electrospray_config_liquid_setup_obj.load_json_config_setup()
-    electrospray_validation = ElectrosprayValidation(name_liquid)
-    electrospray_classification = classification_electrospray.ElectrosprayClassification(name_liquid)
-    electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
-    electrospray_config_setup = electrospray_config_liquid_setup_obj.get_json_setup()
-    impedance = electrospray_config_setup["osc_impedance"]
-    typeofmeasurement = electrospray_config_setup["typeofmeasurement"]
-    Q = electrospray_config_setup["flow_rate"]  # flow rate  uL/h
[…]

### 2022-12-02 plotting.py

@@ -1,139 +1,0 @@
-from simple_pid import PID
-import os
-import re
-import numpy as np
-import json
-import logging
-import pylab
-import numpy as np
-import plotting
-import libtiepie
-from configuration_FUG import *
-import configuration_tiepie
-from scipy.signal import butter, lfilter
-from time import gmtime, strftime
-from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig, ElectrosprayMeasurements
-from validation_electrospray import ElectrosprayValidation
-from classification_electrospray import ElectrosprayClassification
-import matplotlib.pyplot as plt
-
-
-
-
-def real_time_plot(data_processed_queue, finish_event, fig, ax, ln0, ln1, ln2, bg):
-    # real time plotting loop event for iterable plotting
-
-    while not finish_event.is_set() or not data_processed_queue.empty():
-
-        print('[PLOTTING] plot finish_event')
-        message = data_processed_queue.get()
-
-        electrospray_data, datapoints_filtered, time_step, electrospray_processing, txt_sjaak_str, txt_monica_str, txt_max_peaks = message
-        logging.info(
-            "Consumer got message: %s (data_processed_queue size=%d)", message, data_processed_queue.qsize()
-            )
-        logging.info("Consumer received data_processed_queue. Exiting")
-
-        try:
-
-            # reset the background back in the canvas state, screen unchange
-            fig.canvas.restore_region(bg)
-
-            ln0.set_ydata(electrospray_data.data)
-            ln1.set_ydata(electrospray_processing.datapoints_filtered)
-            ln2.set_ydata(
-                (electrospray_processing.fourier_transform[0:500]))
-            ax[0].legend(bbox_to_anchor=(1.05, 1),
-                         loc='upper left', borderaxespad=0.)
-
-            # re-render the artist, updating the canvas state, but not the screen
-            ax[0].draw_artist(ln0)
-            ax[1].draw_artist(ln1)
-            ax[2].draw_artist(ln2)
-
-            fig.canvas.manager.set_window_title('Sjaak: ' + txt_sjaak_str + 'monnica' + txt_monica_str + '; Peaks:' + txt_max_peaks +
-                                                " voltage_PS= " + str(electrospray_data.voltage) + " current_PS= " + str(
[…]

### 2022-12-02 software/cameraTrigger.py

@@ -1,0 +1,79 @@
+#  *************************************
+# 	Camera trigger send code for arduino
+# 	AUTHOR: 乔昂
+# 	DATE: 26/10/2022
+#  *************************************
+
+import serial.tools.list_ports
+import time
+
+
+def activateTrigger(com_port_idx,finish_event, typeofmeasurement, number_camera_partitions):
+    # Function to trigger Photron PFV4 with arduino Hardware Trigger INPUT
+    # This functions needs at least 3 seconds in between each use so that the communication with arduino works.
+
+
+    time_between_videos  = ((typeofmeasurement['voltage_stop'] - typeofmeasurement['voltage_start']) / typeofmeasurement['step_size']) * typeofmeasurement['step_time'] / number_camera_partitions
+
+    print("[CAMERA THREAD] Time Between Videos: ", time_between_videos)
+
+
+    com_ports = list(serial.tools.list_ports.comports())
+    com_port = serial.Serial(
+        port=com_ports[com_port_idx].device,
+        baudrate=9600,
+        timeout=0.1
+    )
+
+    # # get number of available COM ports
+    # no_com_ports = len(com_ports)
+    #
+    # if no_com_ports > 0:
+    #     print("Total no. of available COM ports: " + str(no_com_ports))
+    #     # show all available COM ports
+    #     for idx, curr in enumerate(com_ports):
+    #         print("  " + str(idx) + ".)  " + curr.description)
+    #
+    #     if com_port_idx > no_com_ports or com_port_idx < 0:
+    #         print("Incorrect value for COM port! Enter a Number (0 - " + str(no_com_ports - 1) + ")")
+    #         return None
+    #
+    #
+
+    if com_port.is_open:
+        print("Arduino Port: " + com_ports[com_port_idx].device)
+        print("Arduino Camera Trigger Connected!")
+    else:
+        print("ERROR: Communication to Arduino/camera failed!")
+
+    #  THREAD LOOP
+    i = 1
+    for i in range(0, number_camera_partitions + 1):
+
+        if com_port.is_open:
+            com_port.flushInput()
+            com_port.flushOutput()
+            time.sleep(1)
+            print("Camera Trigger", i)
+            com_port.write(bytes('1', 'utf-8'))
+            time.sleep(2)
+            # Fazer algoritmo de checar response
+            response = com_port.readline()
+            print(response.decode())
+            i += 1
+        else:
[…]

### 2022-12-02 software/classification_electrospray.py

@@ -1,0 +1,256 @@
+import itertools
+import os
+import re
+from typing import TextIO
+import logging
+import numpy as np
+import json
+import math
+
+
+class ElectrosprayClassification:
+    def __init__(self, name_liquid):
+        self.name_liquid = name_liquid
+        self.all_data = []
+        self.sjaak_std_mean_array = []
+        self.sjaak_mean_median_array = []
+        self.med_value_array = []
+        self.mean_value_array = []
+        self.sjaak_verified = []
+        self.sjaak_verified_false = []
+        self.sjaak_verified_true = []
+
+        self.data_points_list = 0
+        self.electrical_conductivity = 0
+        self.surface_tension = 0
+        self.dieletric_const = 0
+        self.electrical_conductivity = 0
+        self.permitivity = 0
+        self.rho = 0
+        self.density = 0
+
+
+    def do_sjaak(self, mean, median, stddeviation, psd_values, variance):
+        self.med_value_array.append(median)
+        sjaak_classification_txt = ""
+
+        if mean != 0:
+            self.sjaak_std_mean = (stddeviation / mean)
+            # print("std/mean = %f ;" % (self.sjaak_std_mean))
+        else:
+            self.sjaak_std_mean = 0
+        self.sjaak_std_mean_array.append(self.sjaak_std_mean)
+
+        if median != 0:
+            self.sjaak_mean_median = (mean / median)
+            # print('sjaak_mean_median: ', self.sjaak_mean_median)
+        else:
+            self.sjaak_mean_median = 0
+        self.sjaak_mean_median_array.append(self.sjaak_mean_median)
+
+        # classification for dripping
+        # if mean <= 5:
+        if self.sjaak_std_mean > 2.5:
+            sjaak_classification_txt = "dripping 1 "
+            if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
+                # logging.info("Dripping Sjaak")
+                # print("classification dripping confirmed!")
+                sjaak_classification_txt = "dripping"
+
+        # classification for intermittent
+        # if mean > 5:
+        if (self.sjaak_std_mean) < 2.5 and self.sjaak_std_mean > 0.5:
+            # print("intermittent Sjaak!")
+            sjaak_classification_txt = "intermittent 1"
[…]

### 2022-12-02 software/configuration_FUG.py

@@ -1,0 +1,166 @@
+
+# package needed to list available COM ports
+import serial.tools.list_ports
+# package needed for sleep
+import time
+import re
+import sys
+
+
+def FUG_initialize(com_port_idx):
+    # print out user information
+    # get available COM ports and store as list
+    com_ports = list(serial.tools.list_ports.comports())
+    # get number of available COM ports
+    no_com_ports = len(com_ports)
+
+    if no_com_ports > 0:
+        print("Total no. of available COM ports: " + str(no_com_ports))
+        # show all available COM ports
+        for idx, curr in enumerate(com_ports):
+            print("  " + str(idx) + ".)  " + curr.description)
+
+        if com_port_idx > no_com_ports or com_port_idx < 0:
+            print("[FUG] Incorrect value for COM port! Enter a Number (0 - " + str(no_com_ports - 1) + ")")
+            return None
+
+        # configure the COM port to talk to. Default values: 115200,8,N,1
+        com_port = serial.Serial(
+            port=com_ports[com_port_idx].device,  # chosen COM port
+            baudrate=115200,  # 115200
+            bytesize=serial.EIGHTBITS,  # 8
+            parity=serial.PARITY_NONE,  # N
+            stopbits=serial.STOPBITS_ONE,  # 1
+            timeout=0
+        )
+        try:
+            if com_port.is_open:
+                com_port.flushInput()
+                com_port.flushOutput()
+                print('[FUG] FUG initialized!')
+                print("[FUG] FUG Opened Port: " + com_ports[com_port_idx].device)
+                return com_port
+        except Exception as e:
+            print('[FUG] Error FUG_initialize()')
+            print('[FUG] Exception: ' + e.message)
+            return e.message
+            sys.exit(1)
+
+    else:
+        print('[FUG] Error FUG_initialize()')
+        return None
+
+
+
+
+# cmd, list of commands expected
+def FUG_sendcommands(com_port, cmd):
+    # cmd = ['I 6e-4', 'S0R 250', 'U 5e3', 'F1']
+    # cmd = ['I 6e-4', 'S0R 50', 'U 1e4']
+    # cmd = ['F0'] turn it off
+    # cmd = ['>M0?'] readback the actual voltage
+    responses = []
+    try:
+        for command in cmd:
+            # print("cmd:" + command)
[…]

### 2022-12-02 software/configuration_influxDB.py

@@ -1,0 +1,86 @@
+"""
+TITLE: Code for testing Influx database usage with grafana GUI
+AUTHOR: 乔昂  @jueta
+DATE: 21/10/2022
+FRAMEWORK: influxDB v2
+"""
+
+import influxdb_client
+from influxdb_client.client.write_api import SYNCHRONOUS
+import numpy as np
+import datetime
+import time
+
+
+# *************************************
+#       DATABASE CONFIGURATION
+# *************************************
+
+# token = os.environ.get("INFLUXDB_TOKEN")
+token = "X0wU2OIZbscp32eFh2fFfV83RKKd4hDV27wtj8OlRfBE7wm0scW1ntb63FleGF55a7es4IP3FFQ35ZsqFzLzRg=="
+print(token)
+org = "jpmm2209@gmail.com"
+url = "https://europe-west1-1.gcp.cloud2.influxdata.com"
+
+client = influxdb_client.InfluxDBClient(url=url, token=token, org=org)
+
+bucket = "test2"
+
+write_api = client.write_api(write_options=SYNCHRONOUS)
+
+
+# *************************************
+#      			 FUNCTIONS
+# *************************************
+
+# Logs the data to your InfluxDB
+def send_to_influxdb(id, mean, std, voltage_PS, timestamp, classification, temperature, humidity):
+    
+    json_body = [
+        {"measurement": "HighVoltage",
+         "tags": {
+             "classification": classification,
+        },
+         "time": timestamp,
+         "fields": {
+             "running_id": id,
+             "std_current": std,
+             "voltage_PS": voltage_PS,
+             "temperature": temperature,
+             "humidity": humidity
+        }
+        }
+    ]
+    try:
+        write_api.write(bucket='test2', record=json_body)
+        print("JSON Sent!")
+    except:
+        print("Package Lost!")  
+
+
+# *************************************
+#      	MAIN for testing purpose
+# *************************************
+
+
+# def main():
+
+
+#     for i in range(100):
+#         send_to_influxdb(
+#             id='01',
+#             mean= 1 + 1 * np.random.random(),
+#             std= 1 + 2 * np.random.random(),
+#             voltage_PS= 5 + 5 * np.random.random(),
+#             timestamp=datetime.datetime.utcnow(),
+#             classification=np.random.randint(0,5),
+#             temperature=20 + 10 * np.random.random(),
+#             humidity=80 + 20 * np.random.random()
+#         )
[…]

### 2022-12-02 software/configuration_tiepie.py

@@ -1,0 +1,34 @@
+import libtiepie
+
+def config_TiePieScope(scp, sampling_frequency):
+    # ToDo set input to single ended or differential
+    # in oscilloscopechannel.py _get_is_differential or _get_impedance ... investigate further
+    """print("SCP is differential: %s" % scp.channels[0].is_differential)
+    print("SCP impedance: %s" % scp.channels[0].impedance)
+    print("SCP is safe_ground: %s" % scp.channels[0].safe_ground_enabled)"""
+    # !!!! input impedance by default is 2MOhm ... is in differential mode
+    scp.measure_mode = libtiepie.MM_BLOCK
+    scp.sample_frequency = sampling_frequency
+    scp.record_length = 50000  # 10000 samples
+    scp.pre_sample_ratio = 0  # 0 %
+    scp.channels[0].enabled = True
+    scp.channels[0].range = 4  # range in V
+    # ToDo using autoranging would be an advantage?
+    scp.channels[0].coupling = libtiepie.CK_DCV  # DC Volt
+    scp.channels[0].trigger.enabled = True
+    scp.channels[0].trigger.kind = libtiepie.TK_RISINGEDGE
+    scp.channels[1].enabled = False
+    scp.channels[2].enabled = False
+    scp.channels[3].enabled = False
+    scp.trigger_time_out = 100e-3  # 100 ms
+    # Disable all channel trigger sources:
+    for ch in scp.channels:
+        ch.trigger.enabled = False
+    # Setup channel trigger:
+    ch = scp.channels[0]  # Ch 1
+    # Enable trigger source:
+    ch.trigger.enabled = True
+    ch.trigger.kind = libtiepie.TK_RISINGEDGE  # Rising edge
+    ch.trigger.levels[0] = 0.5  # 50 %
+    ch.trigger.hystereses[0] = 0.05  # 5 %
+    return scp

### 2022-12-02 software/electrospray.py

@@ -1,0 +1,403 @@
+import logging
+import numpy as np
+import csv
+import json
+from scipy.signal import argrelextrema
+from scipy import signal
+from scipy.signal import hilbert
+from scipy.signal import butter, lfilter
+
+
+class ElectrosprayConfig:
+    def __init__(self, file_setup, file_liquid):
+        self.file_setup = file_setup
+        self.file_liquid = file_liquid
+        self.ki = 6.46  # no units
+
+    def __repr__(self):
+        """dictionary = {
+            "electrical conductivity": str(self.k_electrical_conductivity),
+            "flow rate": str(self.q_flow_rate),
+            "voltage": str(self.voltage),
+            "setup": str(self.json_setup_obj)
+        }
+        return "config: %s " % (json.dumps(dictionary))"""
+        d = dict(
+            config=dict(comment=str(self.current_comment),
+                        flow_rate_min=str(self.flow_rate_min), type_of_measurement=str(self.typeofmeasurement)))
+        return json.dumps(d, sort_keys=True)
+
+    def load_json_config_setup(self):
+
+        print("load_json_config_setup")
+        # print(self.file_setup)
+        
+        with open(self.file_setup, 'r') as file:
+            # First we load existing data into a dict.
+            self.json_setup_obj = json.load(file)
+            # print(type(self.json_setup_obj))
+
+        """with open(self.file_setup) as json_file:
+            self.json_setup_obj = json.load(json_file)"""
+
+    def load_json_config_liquid(self):
+
+        print("load_json_config_liquid")
+        # print(self.file_liquid)
+
+        with open(self.file_liquid, 'r') as file:
+            # First we load existing data into a dict.
+            self.json_liquid_obj = json.load(file)
+            # print(type(self.json_liquid_obj))
+
+        """with open(self.file_liquid) as json_file:
+            self.json_liquid_obj = json.load(json_file) # dictionary"""
+
+    def get_json_liquid(self):
+        return self.json_liquid_obj
+
+    def get_json_setup(self):
+        return self.json_setup_obj
+
+    def set_comment_current(self, current_comment):
+        self.current_comment = current_comment
+
+    def set_type_of_measurement(self, typeofmeasurement):
+        self.type_of_measurement = typeofmeasurement
+
+    def get_dict_config(self):
+        dictionary = {
+            "voltage regime": self.type_of_measurement
+        }
[…]

### 2022-12-02 software/literature/influx_db/sync_db.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python3
+
+import datetime
+from influxdb import InfluxDBClient
+import numpy as np
+
+# todo: separate this func sync to the send
+def connect_send_to_influxdb(id, mean, std, voltage_PS, timestamp, classification, datapoints, temperature, humidity):
+    # sync InfluxDB
+
+    host = 'localhost'  # Change this as necessary
+    # port = 25826
+    port = 8086
+    username = 'admin'  # Change this as necessary
+    password = 'admin1234'  # Change this as necessary
+    db = 'testdb'  # Change this as necessary
+
+    # InfluxDB client to write to
+
+    client = InfluxDBClient(host, port)
+    client = InfluxDBClient(host, port, username, password)
+    client.switch_database(db)
+
+    json_body = [
+        {"measurement": "tiepie-rpi",
+         "tags": {
+             "classification": classification,
+         },
+         "time": timestamp,
+         "fields": {
+             "running_id": id,
+             "std_current": std,
+             "mean_current": mean,
+             "voltage_PS": voltage_PS,
+             "datapoints": datapoints,
+             "temperature": temperature,
+             "humidity": humidity
+         }
+         }
+    ]
+    client.write_points(json_body)
+    return json_body
+
+"""
+
+for i in range(10):
+    measurement = i
+    var = np.random.randint(100, size=100)
+    mean_val = np.mean(var)
+    std_val = np.std(var)
+    voltage_PS_val = int(np.random.randint(10000, size=1))
+    timestamp_val = datetime.datetime.utcnow()
+    class_val = possible_class[int(np.random.randint(low=0, high=3, size=1))]
+    temperature_val = 10 * np.random.random()
+    humidity_val = 20 * np.random.random()
+    # send_to_influxdb(i, mean_val, std_val, voltage_PS_val, timestamp_val, class_val, temperature_val, humidity_val)
+    send_to_influxdb(i, mean_val, std_val, voltage_PS_val, timestamp_val, class_val, temperature_val, humidity_val)
+"""

### 2022-12-02 software/literature/monicas/classification_dripping.py

@@ -1,0 +1,506 @@
+import io
+import pandas as pd
+import matplotlib.pyplot as plt
+from scipy import stats
+from scipy.signal import butter, lfilter
+import json
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+import math
+import pandas as pd
+import matplotlib.cm as cm
+from PIL import Image
+from io import BytesIO
+
+save_path = """E:/2022json/"""
+file_name = "teste"
+completeName = os.path.join(save_path, file_name)
+
+mean_value_array = [[]]
+med_value_array = [[]]
+flow_rate_chen_pui = [[]]
+flow_rate_actual_array = [[]]
+flow_rate_array = [[]]
+stddev_value_array = [[]]
+alpha_chen_pui = [[]]
+I_emitted_chen_pui = [[]]
+sjaak_verified = [[]]
+x_ganan_calvo = [[]]
+I_Ig_ganan_calvo = [[]]
+sjaak_std_mean_array = [[]]
+sjaak_mean_median_array = [[]]
+sjaak_verified_false = [[]]
+sjaak_verified_true = [[]]
+electrical_conductivity_array = [[]]
+rho = [0]
+electrical_conductivity = [0]
+permitivity = [0]
+surface_tension = [0]
+dielectric_const = [0]
+min_fr_chen_pui = [0]
+
+name = []
+slope = []
+all_data = []
+sjaak_std_mean = []
+sjaak_avg_development_relaxation_ratios = []
+sjaak_mean_median = []
+record_last_index_value = 0
+sampling_frequency = 1e5
+time_step = 1 / sampling_frequency
+ki = 6.46
+index = 0
+index_aux = 0
+path = '/jsonfiles/'
+directory_contents = os.listdir(path)
+print(directory_contents)
+current_shapes = ["no voltage no fr", "no voltage", "dripping", "intermittent", "multijet",
+                  "streamer onset"]
+
+
+
+for i in directory_contents:
+    res = re.search(current_shapes[2], i)
+    if res == None:
+        continue
+    else:
+        print(i)
+        with open('C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/' + i) as json_file:
+            data_dict = json.load(json_file)
+            manual_shape = data_dict['config']['liquid']['actual measurement']['current shape manual']
+            print("\nmanual shape:", manual_shape)
+            current_comment = data_dict['config']['liquid']['actual measurement']['current comment']
+            res = re.search("unstable", current_comment)
[…]

### 2022-12-02 software/literature/monicas/plot_italy_SJAAKVARIABLES.py

@@ -1,0 +1,131 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.widgets import Slider, Button
+import json
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import itertools
+import math
+font = {'weight' : 'bold',
+        'size' : 18}
+
+plt.rc('font', **font)
+
+data_index = 0
+sampling_frequency = 1e5
+time_step = 1 / sampling_frequency
+#0 - 5000 hz
+
+index = 0
+index_aux = 0
+# path = "E:/2022jsonauxethanol/"
+#path = "E:/summer22water60alcohol40/"
+#path = "E:/summer22propanol/"
+path = "E:/summer22ethanol/"
+#path = "E:/summer22propanol/"
+#path = "C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles/"
+directory_contents = os.listdir(path)
+#directory_contents = "stepsetup92propanol_all shapes_1.94446e-08m3_s.json"
+data = []
+
+mean_div_max_variation_array = []
+variance_div_deviation_array = []
+
+voltage_PS_array = []
+current_PS_array = []
+spray_mode_array = []
+mean_value_array = []
+flow_rate_actual = 0
+med_array = []
+flow_rate_actual_array = []
+flow_rate_array = []
+stddev_array = []
+fourier_peaks_array = []
+maximum_variation_distance_array = []
+rms_array = []
+data_each_flow_rate = []
+mean_each_flow_rate = []
+electrical_conductivity_array = []
+mean_array = []
+tuple_mean_and_flowrate = []
+data_array = []
+name_list = []
+sjaak_std_div_mean = []
+sjaak_mean_div_median = []
+
+plot_markers = itertools.cycle((',', '+', '^', 'o', '*', '>', '2', '1', '<', '3', '+', 's', '4'))
+plot_colors = itertools.cycle(('orange', 'firebrick', 'hotpink', 'aqua', 'purple', 'red', 'yellowgreen', 'lightseagreen', 'blueviolet', 'darkcyan', 'green', 'black'))
+plot_lines = []
+
+def calculate_for_json_with_all_shapes(data_dict):
+    # for i in range(10, 60):
+    global flow_rate_actual_array
+    flow_rate_actual = (data_dict['measurements'][10]['flow rate [m3/s]'])
+    print(flow_rate_actual)
+    #flow_rate_actual_array.append(str(round(float(flow_rate_actual), 2)) + "[m3/s]")
[…]

### 2022-12-02 software/literature/monicas/validation_working_italy.py

@@ -1,0 +1,257 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+from scipy import stats
+from scipy.signal import butter, lfilter
+import json
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+import math
+import matplotlib.cm as cm
+
+data_index = 0
+sampling_frequency = 1e5
+time_step = 1 / sampling_frequency
+
+mean_value_array = [[]]
+med_value_array = [[]]
+flow_rate_chen_pui = [[]]
+flow_rate_actual_array = [[]]
+flow_rate_array = [[]]
+stddev_value_array = [[]]
+alpha_chen_pui = [[]]
+I_emitted_chen_pui = [[]]
+sjaak_verified = [[]]
+x_ganan_calvo = [[]]
+I_Ig_ganan_calvo = [[]]
+sjaak_std_mean_array = [[]]
+sjaak_mean_median_array = [[]]
+sjaak_verified_false = [[]]
+sjaak_verified_true = [[]]
+electrical_conductivity_array = [[]]
+rho = [0]
+electrical_conductivity = [0]
+permitivity = [0]
+surface_tension = [0]
+dielectric_const = [0]
+min_fr_chen_pui = [0]
+
+name = []
+slope = []
+all_data = []
+sjaak_std_mean = []
+sjaak_avg_development_relaxation_ratios = []
+sjaak_mean_median = []
+"""beta_ganan_calvo = []
+alphap_ganan_calvo = []
+I_ganan_calvo = []
+Ig_ganan_calvo = []
+
+we want to ccumulate until a certain point
+we dont want the index - bc is DC
+
+088-1236860
+
+fft for cone jet is empty except for the dc frequency
+"""
+ki = 6.46
+index = 0
+index_aux = 0
+path = 'E:/2022JSONCORRECT/'
+directory_contents = os.listdir(path)
+print(directory_contents)
+current_shapes = ["no voltage no fr", "no voltage", "dripping", "intermittent", "cone jet", "multijet",
+                  "streamer onset"]
+
+record_last_index_value = 0
+def calculate_for_json_with_all_shapes(data_dict, index):
+    # for i in range(10, 60):
+    rho = data_dict['config']['liquid']['density']
+    permitivity = data_dict['config']['liquid']['vacuum permitivity']
+    density = data_dict['config']['liquid']['density']
+    electrical_conductivity = data_dict['config']['liquid']['electrical conductivity']
[…]

### 2022-12-02 software/literature/peripherals/serial_FUG/hvl_fug_lib_ex.py

@@ -1,0 +1,74 @@
+#  Copyright (c) 2020-2022 ETH Zurich, SIS ID and HVL D-ITET
+#
+"""
+Example script for the device FuG
+"""
+
+import logging
+from time import sleep
+import serial
+from hvl_ccb.dev import FuG, FuGDigitalVal, FuGError
+
+
+logging.basicConfig(level=logging.INFO)
+
+# create device object
+hv = FuG({"port": "COM9"})
+
+# start the device
+hv.start(max_voltage=1e3, max_current=10e-3)
+
+# give the device some time to apply hv.set_number_of_recordings()
+# that was called during hv.start()
+sleep(0.5)
+
+# print the nominal voltage and current
+print(
+    f"This power supply can apply {hv.max_voltage_hardware} V "
+    f"and {hv.max_current_hardware} A"
+)
+print(f"In this setup the limits are at {hv.max_voltage} V and {hv.max_current} A")
+
+
+# apply a current limitation
+hv.current = 3.5e-3
+
+sleep(0.5)
+
+# turn on the output
+hv.on = FuGDigitalVal.YES
+sleep(0.5)
+
+# Try to apply a voltage which is to high
+try:
+    hv.voltage = 50000000
+except FuGError:
+    print(f"You can't set a voltage higher than {hv.max_voltage} V.")
+
+# apply a (normal) voltage
+setVoltage = 250
+hv.voltage = setVoltage
+
+sleep(0.5)  # give the device some time to apply the voltage
+
+# check the set voltage
+commandVoltage = hv.voltage.actualsetvalue
+
+print("Charging...")
+
+# measure the output voltage
+max_n = 25
+while hv.current_monitor.value >= 1e-3 and max_n >= 0:
+    print(f"still charging: {hv.voltage_monitor.value} V")
+    max_n -= 1
+    sleep(1)
+
+
+# print the result
+print(
+    f"I wanted to set {setVoltage} V, the command set {commandVoltage} V, "
+    f"and I finally measured {hv.voltage_monitor.value} V"
+)
+
+# stop the device (this also turns off the output)
+hv.stop()

### 2022-12-02 software/mainElectrospray.py

@@ -1,0 +1,254 @@
+import threading
+import sys
+import queue
+import classification_electrospray
+from printinfo import *
+import matplotlib.pyplot as plt
+from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig
+from validation_electrospray import ElectrosprayValidation
+from classification_electrospray import ElectrosprayClassification
+from configuration_FUG import *
+import cameraTrigger
+import data_acquisition
+import plotting 
+import data_processing
+import os
+import json
+import logging
+
+
+
+# # # **************************************
+# # #                 MAIN
+# # # **************************************
+if __name__ == '__main__':
+
+
+# # # **************************************
+# # #         INITIAL CONFIGURATION
+# # # **************************************
+
+    finish_event = threading.Event()  # when Power Supply finish the finish_event will be set
+
+    # LOGGING CONFIG
+    LOG_FILENAME = r'logging_test.out'
+    logging.basicConfig(filename=LOG_FILENAME, encoding='utf-8',
+                        format='%(asctime)s %(message)s', level=logging.INFO)
+    logging.info('Started')
+
+    sampling_frequency = 1e5  # 100000
+    array_electrospray_measurements = []
+    array_electrospray_processing = []
+
+    name_setup = "setup12"
+    setup = "setup/nozzle/" + name_setup
+    name_liquid = "ethanol" # ["ethyleneglycolHNO3", "ethanol", water60alcohol40, 2propanol]
+    liquid = "setup/liquid/" + name_liquid
+    current_shape_comment = "difficult cone jet stabilization"
+   
+    FLAG_PLOT = True
+    plt.style.use('seaborn-colorblind')
+    plt.ion()
+
+    electrospray_config_liquid_setup_obj = ElectrosprayConfig(setup + ".json", liquid + ".json")
+    electrospray_config_liquid_setup_obj.load_json_config_liquid()
+    electrospray_config_liquid_setup_obj.load_json_config_setup()
+    electrospray_validation = ElectrosprayValidation(name_liquid)
+    electrospray_classification = classification_electrospray.ElectrosprayClassification(name_liquid)
+    electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
+    electrospray_config_setup = electrospray_config_liquid_setup_obj.get_json_setup()
+    impedance = electrospray_config_setup["osc_impedance"]
+    typeofmeasurement = electrospray_config_setup["typeofmeasurement"]
+    Q = electrospray_config_setup["flow_rate"]  # flow rate  uL/h
[…]

### 2022-12-02 software/plotting.py

@@ -1,0 +1,139 @@
+from simple_pid import PID
+import os
+import re
+import numpy as np
+import json
+import logging
+import pylab
+import numpy as np
+import plotting
+import libtiepie
+from configuration_FUG import *
+import configuration_tiepie
+from scipy.signal import butter, lfilter
+from time import gmtime, strftime
+from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig, ElectrosprayMeasurements
+from validation_electrospray import ElectrosprayValidation
+from classification_electrospray import ElectrosprayClassification
+import matplotlib.pyplot as plt
+
+
+
+
+def real_time_plot(data_processed_queue, finish_event, fig, ax, ln0, ln1, ln2, bg):
+    # real time plotting loop event for iterable plotting
+
+    while not finish_event.is_set() or not data_processed_queue.empty():
+
+        print('[PLOTTING] plot finish_event')
+        message = data_processed_queue.get()
+
+        electrospray_data, datapoints_filtered, time_step, electrospray_processing, txt_sjaak_str, txt_monica_str, txt_max_peaks = message
+        logging.info(
+            "Consumer got message: %s (data_processed_queue size=%d)", message, data_processed_queue.qsize()
+            )
+        logging.info("Consumer received data_processed_queue. Exiting")
+
+        try:
+
+            # reset the background back in the canvas state, screen unchange
+            fig.canvas.restore_region(bg)
+
+            ln0.set_ydata(electrospray_data.data)
+            ln1.set_ydata(electrospray_processing.datapoints_filtered)
+            ln2.set_ydata(
+                (electrospray_processing.fourier_transform[0:500]))
+            ax[0].legend(bbox_to_anchor=(1.05, 1),
+                         loc='upper left', borderaxespad=0.)
+
+            # re-render the artist, updating the canvas state, but not the screen
+            ax[0].draw_artist(ln0)
+            ax[1].draw_artist(ln1)
+            ax[2].draw_artist(ln2)
+
+            fig.canvas.manager.set_window_title('Sjaak: ' + txt_sjaak_str + 'monnica' + txt_monica_str + '; Peaks:' + txt_max_peaks +
+                                                " voltage_PS= " + str(electrospray_data.voltage) + " current_PS= " + str(
[…]

### 2022-12-02 software/raspberry_electrospray.py

@@ -1,0 +1,394 @@
+from __future__ import print_function
+
+import codecs
+import time
+import threading
+import sys
+import libtiepie
+
+import classification_electrospray
+from printinfo import *
+from scipy.signal import butter, lfilter
+from scipy import signal
+from time import gmtime, strftime
+import csv
+import configparser
+
+from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig, ElectrosprayMeasurements
+from classification_electrospray import ElectrosprayClassification
+# from aux_functions_electrospray import *
+from configuration_FUG import *
+import configuration_tiepie
+import configuration_influxDB
+
+import os
+import re
+import numpy as np
+import json
+import logging
+import threading
+import numpy as np
+
+
+event = threading.Event()
+
+
+from threading import Thread
+# fig = pylab.gcf()
+
+# LOGGING CONFIG
+LOG_FILENAME = r'logging_test.out'
+logging.basicConfig(filename=LOG_FILENAME, encoding='utf-8', format='%(asctime)s %(message)s', level=logging.INFO)
+logging.info('Started')
+
+multiplier_for_nA = 500
+sampling_frequency = 1e5
+
+a_electrospray_measurements = []
+a_electrospray_measurements_data = []
+a_electrospray_processing = []
+a_statistics = []
+append_array_measurements = []
+
+d_electrospray_measurements = {}
+d_electrospray_measurements_data = {}
+d_electrospray_processing = {}
+d_statistics = {}
+
+
+
+# *************************************
+#       INITIAL CONFIGURATION 
+# *************************************
+
+#  VAR_BIN_CONFIG = input("Would you like to save data? [True/False] ")
+VAR_BIN_CONFIG = False
+SAVE_DB = True
+SAVE_DATA = VAR_BIN_CONFIG
+SAVE_PROCESSING = VAR_BIN_CONFIG
+SAVE_CONFIG = VAR_BIN_CONFIG
+SAVE_JSON = VAR_BIN_CONFIG
+append_array_data = VAR_BIN_CONFIG
+append_array_processing = VAR_BIN_CONFIG
+
+
+
+# **************************************
+#    LIQUID AND SETUP INITIAL CONFIG
+# **************************************
+
+MODERAMP = True  # else go in steps
+number_measurements = 45 # maybe change to 100 (45 looks to be a good size for saving)
[…]

### 2022-12-02 software/tests/TieBlock.py

@@ -1,0 +1,282 @@
+# OscilloscopeBlock.py
+#
+# This example performs a block mode measurement and writes the data to OscilloscopeBlock.csv.
+#
+# Find more information on http://www.tiepie.com/LibTiePie .
+
+from __future__ import print_function
+import time
+import os
+import sys
+import libtiepie
+from printinfo import *
+import matplotlib.pyplot as plt
+import matplotlib
+import matplotlib.animation as animation
+import numpy as np
+from datetime import datetime
+from scipy.signal import butter, lfilter
+from threading import Thread
+from threading import Condition, Lock
+import json
+import statistics
+import networkx as nx
+from matplotlib.animation import FuncAnimation, PillowWriter
+
+# matplotlib.use('Qt5Agg')
+
+
+def animate2(i, data):
+    axs[0].clear()
+
+    # axs[0].plot(data[0:i, 0], data[0:i, 1])
+    # https://www.geeksforgeeks.org/using-matplotlib-for-animations/
+    # axs[0].plot(np.arange(0, len(datapoints), 1), datapoints)
+    # axs[0].grid()
+
+
+def connection_wifi_tiepie():
+    # scan available Wifi networks
+    os.system('cmd /c "netsh wlan show networks"')
+
+    # input Wifi name
+    name_of_router = str('TiePie-WS6D-37427')
+
+    try:
+        # connect to the given wifi network
+        os.system(f'''cmd /c "netsh wlan connect name={name_of_router}"''')
+    except KeyboardInterrupt as e:
+        print("\nExiting...")
+
+
+if __name__ == "__main__":
+    # connection_wifi()
+    sampling_frequency = 1e5
+
+    # Print library info:
+    print_library_info()
+
+    # Enable network search:
+    libtiepie.network.auto_detect_enabled = True
+
+    # Search for devices:
+    libtiepie.device_list.update()
+
+    # lock = threading.RLock()
+    # condition = Condition()
+    # condition.acquire()  # da a chave para essa thread
+    # try:
+
+    """
+    if len(libtiepie.device_list) > 0:
+        print()
+        print('Available devices:')
+
+        for item in libtiepie.device_list:
+            print('  Name: ' + item.name)
+            print('    Serial number  : ' + str(item.serial_number))
+            print('    Available types: ' + libtiepie.device_type_str(item.types))
+    else:
+        print('No devices found!')"""
+
+    # finally:
+        # condition.release()  # tira a chave para essa thread """
+
[…]

### 2022-12-02 software/tests/readtuple.py

@@ -1,0 +1,19 @@
+import io
+import pandas as pd
+import matplotlib.pyplot as plt
+from scipy import stats
+from scipy.signal import butter, lfilter
+import json
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+import math
+import pandas as pd
+import matplotlib.cm as cm
+from PIL import Image
+from io import BytesIO
+
+save_path = """E:/2022json/"""
+file_name = "teste"
+completeName = os.path.join(save_path, file_name)

### 2022-12-02 software/tests/searchfiles.py

@@ -1,0 +1,25 @@
+import json
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+path = 'C:/Users/hvvhl/Desktop/joao/EHDA_library/jsonfiles'
+
+directory_contents = os.listdir(path)
+
+print(directory_contents)
+
+
+for i in directory_contents:
+    res = re.search("cone jet", i)
+    if res == None:
+        continue
+    else:
+        print(i)
+
+        """print("*******")
+        with open(filename) as jsonFile:
+            # data1 = jsonFile.read()
+            # data = json.loads(data1)
+            jsonObject = json.load(jsonFile)
+            print(type(jsonObject))"""

### 2022-12-02 tests/TieBlock.py

@@ -1,282 +1,0 @@
-# OscilloscopeBlock.py
-#
-# This example performs a block mode measurement and writes the data to OscilloscopeBlock.csv.
-#
-# Find more information on http://www.tiepie.com/LibTiePie .
-
-from __future__ import print_function
-import time
-import os
-import sys
-import libtiepie
-from printinfo import *
-import matplotlib.pyplot as plt
-import matplotlib
-import matplotlib.animation as animation
-import numpy as np
-from datetime import datetime
-from scipy.signal import butter, lfilter
-from threading import Thread
-from threading import Condition, Lock
-import json
-import statistics
-import networkx as nx
-from matplotlib.animation import FuncAnimation, PillowWriter
-
-# matplotlib.use('Qt5Agg')
-
-
-def animate2(i, data):
-    axs[0].clear()
-
-    # axs[0].plot(data[0:i, 0], data[0:i, 1])
-    # https://www.geeksforgeeks.org/using-matplotlib-for-animations/
-    # axs[0].plot(np.arange(0, len(datapoints), 1), datapoints)
-    # axs[0].grid()
-
-
-def connection_wifi_tiepie():
-    # scan available Wifi networks
-    os.system('cmd /c "netsh wlan show networks"')
-
-    # input Wifi name
-    name_of_router = str('TiePie-WS6D-37427')
-
-    try:
-        # connect to the given wifi network
-        os.system(f'''cmd /c "netsh wlan connect name={name_of_router}"''')
-    except KeyboardInterrupt as e:
-        print("\nExiting...")
-
-
-if __name__ == "__main__":
-    # connection_wifi()
-    sampling_frequency = 1e5
-
-    # Print library info:
-    print_library_info()
-
-    # Enable network search:
-    libtiepie.network.auto_detect_enabled = True
-
-    # Search for devices:
-    libtiepie.device_list.update()
-
-    # lock = threading.RLock()
-    # condition = Condition()
-    # condition.acquire()  # da a chave para essa thread
-    # try:
-
-    """
-    if len(libtiepie.device_list) > 0:
-        print()
-        print('Available devices:')
-
-        for item in libtiepie.device_list:
-            print('  Name: ' + item.name)
-            print('    Serial number  : ' + str(item.serial_number))
-            print('    Available types: ' + libtiepie.device_type_str(item.types))
-    else:
-        print('No devices found!')"""
-
-    # finally:
-        # condition.release()  # tira a chave para essa thread """
-
[…]

### 2022-12-02 tests/logic.py

@@ -1,293 +1,0 @@
-"""Propositional Logic: states a fact;
-	logical symbols => represent facts. (S, R, Q)
-	Connectives symbols => to relates the fact (not, and or)
-	Implications => implies only if the second condition to be true.
-	Biconditional => if only and only be true.
-	model => assign a fact to each symbol either true or false.
-	entailment => alpha entails beta; means that both are true
-	infernce => dreving new sentence from old.
-
-Algorithms:
-	Model Check:
-		Enumerate through all the possible models.
-		KB = True and query = True.
-	Inference Rule:
-		set premis and reach the conclusion.
-
-	Important concepts.
-	And Elimination:
-	Double Negation Eimination
-	inpication elimination: if then => or.
-	biconditionl elimination.
-	Demorgans law:
-	moving negation inside.
-	Distributive property."""
-
-class Sentence():
-    def evaluate(self, model):
-        """Evaluates the logical sentence."""
-        raise Exception("nothing to evaluate")
-
-    def formula(self):
-        return ""
-
-    def symbols(self):
-        """Returns a set of all symbols in the logical sentence."""
-        return set()
-
-    @classmethod
-    def validate(cls, sentence):
-        if not isinstance(sentence, Sentence):
-            raise TypeError("must be a logical sentence")
-
-    @classmethod
-    def parenthesize(cls, s):
-        """Parenthesizes an expression if not already parenthesized."""
-
-        def balanced(s):
-            """Checks if a string has balanced parentheses."""
-            count = 0
-            for c in s:
-                if c == "(":
-                    count += 1
-                elif c == ")":
-                    if count <= 0:
-                        return False
-                    count -= 1
-            return count == 0
-
-        if not len(s) or s.isalpha() or (
-                s[0] == "(" and s[-1] == ")" and balanced(s[1:-1])
-        ):
-            return s
-        else:
-            return f"({s})"
-
-
-class Symbol(Sentence):
-    """	logical symbols => represent facts. (S, R, Q)"""
-
-    def __init__(self, name):
-        self.name = name
-
-    def __eq__(self, other):
-        return isinstance(other, Symbol) and self.name == other.name
-
-    def __hash__(self):
-        return hash(("symbol", self.name))
-
-    def __repr__(self):
-        return self.name
-
-    def evaluate(self, model):
-        try:
-            return bool(model[self.name])
-        except KeyError:
-            raise Exception(f"variable {self.name} not in model")
-
[…]

### 2022-12-02 tests/readtuple.py

@@ -1,19 +1,0 @@
-import io
-import pandas as pd
-import matplotlib.pyplot as plt
-from scipy import stats
-from scipy.signal import butter, lfilter
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import re
-import math
-import pandas as pd
-import matplotlib.cm as cm
-from PIL import Image
-from io import BytesIO
-
-save_path = """E:/2022json/"""
-file_name = "teste"
-completeName = os.path.join(save_path, file_name)

### 2022-12-02 tests/testsaveobject.py

@@ -1,202 +1,0 @@
-# save numpy array as csv file
-from numpy import asarray
-from numpy import savetxt
-import csv
-import json
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import re
-import pandas as pd
-from pandas.io.json import json_normalize
-from functools import reduce
-from IPython.display import display, HTML
-
-class Dog:
-
-    teste_var: int
-    tricks = []             # mistaken use of a class variable
-
-    def __init__(self, name):
-        self.name = name
-
-    def __repr__(self):
-        return (json.dumps((self.name) + " " + str(self.teste_var)))
-
-    def test_self(self):
-        self.teste_var = 666
-
-    def get_teste_var(self):
-        return self.teste_var
-
-    def add_trick(self, trick):
-        self.tricks.append(trick)
-
-    def get_dog_name(self):
-        return self.name
-
-    def save_new(self):
-        """save class as self.name.txt"""
-        data = []
-        txt_file = open("E:/"+self.name+'.txt','w')
-        json_file = open("E:/"+self.name+'.json','w')
-        csv_file = open("E:/"+self.name+'.csv','w')
-        csv_file.write('Sample')
-        json_file.write('Sample')
-        dictionary = {
-            "name": "sathiyajith",
-            "rollno": 56,
-            "cgpa": 8.6,
-            "phonenumber": "9976770500",
-            "tricks": self.tricks
-        }
-        """
-        for i in self.tricks:
-            csv_file.write(';'+str(i))
-            data.append(i)
-
-        dictionary["data"] = data"""
-        json_object = json.dumps(dictionary, indent=5)
-        json_file.write(json_object)
-        txt_file.write(str(dictionary))
-
-    def load_setup(self, filename, dictionary):
-
-        with open(filename, 'r+') as file:
-            # First we load existing data into a dict.
-            file_data = json.load(file)
-            # Join new_data with file_data inside emp_details
-            file_data["liquid"].append(dictionary)
-            # Sets file's current position at offset.
-            file.seek(0)
-            # convert back to json.
-            json.dump(file_data, file, indent=4)
-
-    def close_setup(self):
-        self.jsonFile.close()
-
-class Food:
-    def __init__(self, object):
-        self.name = object.name
-
-    def print_food(self):
-        print(self.name)
-
-
-
-
-
-
-
-def pretty_json(data):
[…]

### 2022-12-02 Documentation/Relatorio_2/Conclusion/Conclusion.tex
Documentation

@@
 
-For further steps the following tasks will be done:
+In this step of the project the python code was upgraded to optimize the data acquiring, processing and saving. Also 
+started structuring the software to fit our control model. Initial experiments was made in order to evaluate the algorithm 
+performance and intuitivity. With the data collect in those first experiments we can notice that:
 
-- make experiments with different time windows. This will help to see the time needed for the system to stabilize.
+- The algorithm is not capable of separating cone jet mode and multi jet mode.
 
-- change power supply and oscilloscope libraries to an updated version wich covers both hardwares.
+- The algorithm is not capable of sepaating intermittend and dripping.
 
-- correct and upgrade plots to make a better sense of the data.
+- It has noise in the current values which are not discovered yet.
 
-- Include DHT11 temperature and humidity sensor to the setup.
+As the method proposed by Sjaak\cite*[]{Sjaaks} classifies each spraying mode using deviation/mean and mean/median relations,
+we can se in Figure 14 that the colors are well separated by certain deviation/mean range.
 
-- Thread sincronization in the main routine.
+For next steps experiments will be done varying the step size and step time of the power supply to get a better undertanding in how
+the change in dynamics behave. It is already known that it needs an adapting time to stabilize in a certain spraying mode. The next step
+will try to measure and understand this time. It is also known that the system has an histeses when changing between spraying modes. This is also
+another target for further studies.

### 2022-12-07 data_analysis/data_analysis.py
data analysis from experiments set

@@ -17,18 +17,23 @@ from scipy.signal import butter, lfilter
 # warnings.filterwarnings('ignore')
 sampling_frequency = 1e5
 
-file_path1 = "joaoData/"
+file_path1 = "joaoData/experiments_05_12/"
 
-file_name1 = "data1"
-file_name2 = "data2"
-file_name3 = "data3"
-file_name4 = "data4"
+file_name1 = "exp1"
+file_name2 = "exp2"
+file_name3 = "exp3"
+file_name4 = "exp4"
+file_name5 = "exp5"
+file_name6 = "exp6"
+file_name7 = "exp7"
+file_name8 = "exp8"
+file_name9 = "exp9"
 
 easygui.msgbox("欢迎")
 
 msg ="What experiment do you want to run?"
 title = "EDHA - JSON data"
-choices = [file_name1, file_name2, file_name3, file_name4]
+choices = [file_name1, file_name2, file_name3, file_name4, file_name5, file_name6, file_name7, file_name8, file_name9]
 exp_choice = easygui.choicebox(msg, title, choices)
 
 
@@ -143,9 +148,8 @@ else:
     fig, axs = plt.subplots(5, 1)
 
     axs[0].set(ylabel='ccurent nA')
-    axs[0].plot(data_sample.index/sampling_frequency, data_sample['data-0'])
+    axs[0].plot((data_sample.index/sampling_frequency)/60, data_sample['data-0'])
     axs[0].grid()
-    axs[0].legend(loc="upper right")
 
     axs[1].set(ylabel='voltage (V)')
     axs[1].set_yticks(np.arange(0, 5000, 10))

### 2022-12-07 data_analysis/voltage_graph.py

@@ -12,24 +12,11 @@ from sklearn.utils import column_or_1d
 import numpy as np
 from scipy.signal import butter, lfilter
 
-# warnings.filterwarnings('ignore')
-sampling_frequency = 1e5
 
 
-with open("joaoData/" + "data2" + ".json", 'r') as data_file:    
-    data = json.loads(data_file.read())  
+df = pd.read_pickle("exp7.pkl")
 
-data_measurements = pd.json_normalize(data, record_path=['measurements'])
-data_processing = pd.json_normalize(data, record_path=['processing'])
-df = pd.concat([data_measurements, data_processing], axis=1)
-
-print(df.info())
-
-fig, axs = plt.subplots(2, 2)
-# plt.title()
-axs[0].set(ylabel='mean curent nA',  xlabel='Voltage')
-axs[0].scatter(df['voltage'], df['mean'])
-# axs[0].set_xticks(np.arange(3000, 11000, 100))
-axs[0].grid()
+import seaborn as sns
+sns.scatterplot('voltage', 'data [nA]', data=df, hue='spray mode.Sjaak')
 
 plt.show()

### 2022-12-07 Documentation/Relatorio_2/Development/Development.tex

@@
-\section{Development}
+\section{Metodology and Results}
 
-\subsection*{3.1 Peripherals integration}
+\subsection*{3.1 Setup and Routine Algorithm Optimization}
 
-Doing experiments we discovered that the frequency of the pump machine internal motors was
+    About the python algorithm to turn the experiment autonomous it was made a study and modelling of the software architecture to optimize it 
+    for further control loop application to be implemented.
+    From the changes made until now it highlights:
+
+    - Integrate high speed camera to the experiment routine.
+
+    - Remodel the software to support threads in order to separate the sensoring and controlling routines.
+
+    - Reduce the data collected size.
+
+    - Synchronize the power supply step commands and voltage sensoring.
+
+    - Reestructure the setup file in order to make it more intuitive to use the experiment.
+
+    - Improvements in code organization and readability.
+
+    About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to make the experiment 
+    the most stable and easy to reach cone-jet mode as possible.
+    For example, while doing experiments we discovered that the frequency of the pump machine internal motors was
     creating an interference in the flowrate. Therefore compromising the stabilization in cone jet mode.
@@
 
+    This first experiment was made using the setup:
+
+    - liquid: water60alcohol40
+
+    - flow rate min: 1.45 mL/hr
+
+    - config: nozzle to plate
+
+    - nozzle to plate or ring distance: 1.5 cm
+
+    - nozzle diameter: 0.136 mm
+
+    In Figure 5 we can see 5 graphs:
+
+    1 - current values measured by the oscilloscope. As it is a lot of data it is compressed in the figure.
+
+    2 - Voltage step sequency in order to evaluate the dynamics in each high voltage level.
+
+    3,4,5 - Statistical values measured by each window of 0.5s of data collected. This values will be used in the classification algorithm.
+    Those values are already classified by colour and the legend is showed below.
+
+    LEGEND:
+
+    - Green = Dripping
+
+    - Blue =  Intermittend
+
+    - Red = Cone Jet mode
+
+    - Purple = Streamer Onset (high current values)
+
+    - Black = Undefined
+
     \begin{figure}[H]
         \center
-    \includegraphics[width=18cm]{images/images_folder_2/img1.png}
+        \includegraphics[width=17cm]{images/images_folder_2/img1.png}
         \caption{Data acquired in the experiment 1 - liquid: Water AND alcohol}
     \end{figure}
+
+    In Figure 6 and 7 we can see one data window sample of dripping and one of cone jet dynamics. There are two graphs. The first one its
+    the current datapoints filtered by a ideal low pass butterworth filter. In the second graph we can see the module of the fast fourier transform real values.
+
+    We can see in Figure 6 that there were two droplets expelled by the nozzle. This can be seen as the two signal waves in the current value and the amount of frequencies seen in the second graph.
 
@@
 
+    We can see in Figure 7 that the current signal is more stable and also with an offset current arround 100nA showing that the spray is in cone jet mode.
+Also seen as the 0 Hz DC component value in the frequency domain graph.
+
     \begin{figure}[H]
         \center
-    \includegraphics[width=15cm]{images/images_folder_2/img3.png}
+        \includegraphics[width=12cm]{images/images_folder_2/img3.png}
         \caption{Cone jet sample}
     \end{figure}
+
+    Other interesting grahps exposed in Sjaaks\cite*[]{Sjaaks} paper is correlating statistical values relations to each voltage step and classification.
+This is also good to evaluate the separability of each classification method.
+    Those graphs can be seen in Figures 8, 9 and 10.
 
@@
 
+In this experiment the liquid was changed in order to have a bigger voltage range in the cone jet mode. Which is the most valuable mode in this project.
+
+    - liquid: ethanol pure
+
+    - flow rate min: 1.5 mL/hr
+
+    - camera to nozzle distance: 16.5 cm
+
+    - config: nozzle to plate
+
+    - nozzle to plate or ring distance: 1.5 cm
+
+    - nozzle diameter: 0.136 mm
+
+    - type of measurement:
+
+        * voltage start: 3000 V
+
+        * voltage stop: 10000 V
+
+        * step size: 100 V
+
+        * step time: 5 s
+
+    In Figure 11, the data is well classified but it also have a noise in the system that can been seen in the peak current values.
+    Those peaks can be seen in all the voltage ranges in this experiment and also have similar distances in beetween the peaks. This is probably caused by
+    external interference but it is still not certain what is it about.
+
     \begin{figure}[H]
         \center
-    \includegraphics[width=18cm]{images/images_folder_3/data3.png}
+        \includegraphics[width=17cm]{images/images_folder_3/data3.png}
         \caption{Data acquired in the experiment 2 - pure ethanol}
@@
 
+    The Figure 12 shows the same current x time graph but with a zoom in y axis in order to see the signal steps in the experiment.
+It is also classified by the same color legend as all graphs in this overview.
+
     \begin{figure}[H]
         \center
-    \includegraphics[width=12cm]{images/images_folder_3/data3current.png}
+        \includegraphics[width=15cm]{images/images_folder_3/data3current.png}
         \caption{current graph with classification}
     \end{figure}
+
+    The Figures 13, 14 and 15 shows graphs with statistical realations in the data.
 
@@
 
+    - liquid: ethanol pure
+
+    - flow rate min: 1.5 mL/hr
+
+    - camera to nozzle distance: 16.5 cm
+
+    - config: nozzle to plate
+
+    - nozzle to plate or ring distance: 1.5 cm
+
+    - nozzle diameter: 0.136 mm
+
+    - type of measurement:
+
+        * voltage start: 3000 V
+
+        * voltage stop: 11000 V
+
+        * step size: 50 V
+
+        * step time: 1 s
+
     \begin{figure}[H]
         \center
-    \includegraphics[width=18cm]{images/images_folder_3/data4.png}
+        \includegraphics[width=17cm]{images/images_folder_3/data4.png}
         \caption{Data acquired in the experiment 3 - pure ethanol}

### 2022-12-07 Documentation/modelo_PFC_latex/DescricaoProcesso/DescricaoProcesso.tex

\chapter[Descrição do Processo]{Descrição do Problema/Processo ou O Processo de Fazer Alguma Coisa}
\label{chap:descricaoproblema}
%Note que, como nome do capítulo é muito longo, fornecemos um nome abreviado uso no cabeçalho

Se desejar, uma visão geral do capítulo pode ser colocada antes da primeira seção. Este é o capítulo de descrição do processo e formulação do problema. Tendo em vista que se trata de uma monografia de engenharia de controle e automação, em muitos casos será fundamental a apresentação dos sensores e atuadores do processo.

\section{Processo de Fazer Alguma Coisa}
\label{sec:hist}

Cada seção inicia pela descrição do seu conteúdo e pode terminar com um parágrafo de conexão com a seção seguinte.

Antes de formular o problema, \textbf{não se esqueça de fazer todas as definições necessárias}. Também devem-se detalhar os aspectos complementares da abordagem: se estamos estudando um aspeto particular do problema, se a resposta encontrada é universal ou dependente de simplificações e hipóteses prévias.

\section{Instrumentação do Processo}
\label{sec:instrumentação}

Descreva a aparelhagem e o equipamento utilizados bem como a ligação entre os diversos componentes. Nesta seção e, ao longo de todo o texto, você deve dar detalhes suficientes para que qualquer pessoa consiga reproduzir seus experimentos.

Contudo, \textbf{não disperse o leitor com detalhes irrelevantes} ou aspectos
demasiado técnicos ou formais. Reserve tais detalhes para um
apêndice.

Como uma imagem vale mais que mil palavras, e como usar mil palavras prejudicaria a clareza do texto, ilustramos o processo com a Figura \ref{fig:processo}. Lembrar que toda figura deve ser comentada no texto, você nunca deve colocar figuras que fiquem ``soltas'' no texto.

\begin{figure}[thpb]
  \centering
  \resizebox{120mm}{!}{\includegraphics{DescricaoProcesso/Figuras/FiguraProcesso.pdf}}
  \caption{Aqui escrevemos \textbf{toda} informação pertinente à figura. Ou seja, este texto deve ser uma descrição auto-contida da figura, não sendo necessário recorrer ao corpo de texto para saber detalhes sobre a mesma. \emph{Fonte:} Citar fonte se figura 	não for elaborada pelo autor e \textbf{pedir permissão para usar!}}
  \label{fig:processo}
\end{figure}

\section{Situação Atual/Estado da Arte/Revisão da Literatura}
\label{sec:revisão}

Este é o espaço para uma revisão detalhada do enquadramento do problema. Isso inclui descrever a situação atual do processo, aquilo que foi feito até então dentro da empresa/laboratório, e aquilo que se pode chamar de ``Estado da Arte'', ou seja, uma apresentação do conhecimento preexistente
sobre o tema do projeto.

A elaboração desta seção tipicamente demanda uma boa revisão da literatura. Deve haver, quando aplicável uma análise das soluções potencialmente concorrentes, elencando vantagens e desvantagens.

\subsection{Como Elaborar uma Revisão da Literatura}

Ao selecionar referências, devem-se preferir referências de veículos confiáveis, que tenham por exemplo processo de revisão por pares. Portanto, dá-se preferência a artigos em periódicos e livros, em seguida teses e dissertações, artigos em anais de congresso e por fim relatórios. Evitar citar páginas da internet por oferecem menor garantia da informação nelas contida.

Pesquise sua bibliografia em bases confiáveis como o \textsf{Web of Science}, \textsf{Scopus}, ou o \textsf{Google Scholar}. \textbf{Não use uma ferramenta de busca comum!} (elas não foram feitas pensando no \emph{ranking} de textos científicos) Use o número de citações de uma dada referência como um indicador de sua qualidade. Explore os artigos que citam a referência estudada bem como os artigos que ela cita.

Prefira as referências mais recentes quando se tratar de um assunto na fronteira do conhecimento ou de tecnologia de ponta. Quando se tratar de um assunto já consolidado, prefira citar livros ou artigos com muitas citações.

Evite citar informações de segunda-mão e procure na medida do possível rastrear a fonte original. Contudo, em situações em que a fonte original é de acesso mais difícil, seja por ter tido publicação limitada como no caso de relatórios ou por não ser em língua inglesa ou portuguesa, é preferível a citação de segunda-mão em um veículo mais acessível.

Para gerenciar suas referências, use uma ferramenta de software como o \textsf{Mendeley}, que permite gerar arquivos .bib para uso em {\LaTeX} ou simplesmente gerar a lista de referências para uso direto em editores de texto. Em \LaTeX, mais especificamente Bib\TeX, a lista de referências é criada a partir de um arquivo .bib, que é uma espécie de banco de informações bibliográficas em que cada entrada é uma referência associada a uma chave para citação. A lista criada incluirá apenas as referências citadas ao longo do texto, mesmo que haja mais referências no arquivo .bib. As informações bibliográficas no formato Bib\TeX também podem ser obtidas para cada referência em ferramentas como o \textsf{Google Scholar} e então coladas no arquivo .bib.

Na Seção \ref{sec:comocitar} discutiremos como e quando as citações devem ser usadas.

\section{Resumo do Capítulo}

Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!

\clearpage

### 2022-12-07 Documentation/modelo_PFC_latex/Metodologia/Metodologia.tex

\chapter{Metodologia}
\label{chap:metodologia}

Este capítulo deve descrever os métodos utilizados no projeto. As teorias e ferramentas utilizadas, assim como as ações executadas, devem ser escritas de forma clara e precisa, sem deixar espaço para ambiguidades. Tenha em mente que \textbf{o objetivo aqui é dar credibilidade ao seu trabalho e permitir que ele possa ser reproduzido por quem tenha interesse (algumas vezes por você mesmo!)}.

É natural que este capítulo contenha uma revisão bibliográfica mais detalhada das técnicas utilizadas. O ideal é que o capítulo seja auto-contido, de modo que o leitor não necessite recorrer às referências para entender seu trabalho ou reproduzi-lo.

Ao apresentar os métodos, será importante justificar devidamente as opções tomadas e discutir as alternativas disponíveis e os critérios que o levaram à escolha do método.

No restante do capítulo, apresentamos um pequeno manual de escrita técnica.

\section{Técnica 1 - Organização do texto}
\label{sec:metodo1}

Procure \textbf{definir a estrutura} de seu texto \textbf{antes de começar a escrever}. Isso evitará que as ideias apareçam foram de ordem. A falta de organização é uma das características mais comuns de textos difíceis de ler.

Nunca invoque conceitos ou objetos antes de defini-los. Procure fornecer o máximo de informação \emph{a priori} possível. Evite referências para frente no texto.

Para evitar que o leitor se perca, antes de iniciar um trecho longo de texto que contenha ideias diversas, \textbf{adiante para o leitor o que será feito}, aonde se quer chegar. Ao fim do trecho, declare explicitamente que chegou à conclusão que desejava. Esta técnica vale especialmente para seções e capítulos do texto.

\section{Técnica 2 - Estilo}
\label{sec:estilo}

O texto técnico deve ser preciso, claro, sem ambiguidades, objetivo e conciso. Mesmo com esse rigor, não deixe de prender a atenção do leitor. Lembre-se de que o início e o fim de cada parágrafo, de cada frase, são as partes mais importantes e onde você deve colocar maior ênfase.

\subsection{Precisão}

Use as palavras corretas! Não escreva redondo se é esférico. Não escreva igual se é aproximado. Não escreva sistema se é função de transferência. Não escreva grande, pequeno, máximo, mínimo, ótimo, se não há uma escala que defina tais conceitos.

Prefira usar números que deem uma noção de escala a usar adjetivos difíceis de precisar.

Seja específico e evite generalidades. Por exemplo, em vez de dizer ``O processo 1 é um processo de alto custo'', devemos ser mais precisos com relação à natureza do custo e dizer ``O processo 1 possui custo operacional elevado com relação a processos tradicionais tais como o processo 2''.

\subsection{Clareza}

Não deixe margem para dúvidas! Para reduzir a possibilidade de confusão na leitura do seu texto, \textbf{evite frases longas}. Nunca escreva frases com mais de $20$ palavras. Procure escrever na média $12$ palavras por frase. Evite palavras compridas ou que possam ser consideradas difíceis.

Não deixe ideias subentendidas! Não assuma que seu leitor pensa como você e vai saber do que você está falando. Explicite todos os passos de seu raciocínio lógico. Pular passos de raciocínio é uma das causas mais comuns de confusão na leitura. Não seja preguiçoso neste quesito.

Novamente, defina todos os conceitos antes de fazer uso deles.

Não deixe o sujeito verbal subentendido. Para evitar ambiguidades, tome cuidado ao usar pronomes como ``esse, este, isso, ele''. É preferível repetir um nome a deixar margem para dúvidas. Por exemplo, após a primeira frase deste parágrafo poderíamos dizer de forma não tão clara: ``Esta é uma causa de confusão na escrita.''; ou poderíamos dizer de forma mais clara: ``Essa falta de informação é uma causa de confusão na escrita.''

Não há problemas em haver repetições em textos técnicos. O mais importante é a clareza, a inexistência de ambiguidades, não a beleza. Se acha que uma determinada frase pode ser confusa ou se alguma ideia parece difícil de explicar, repita a mesma ideia em outras palavras ou, melhor ainda, dê um exemplo.

Por fim, domine o significado das palavras utilizadas para evitar ambiguidades. Se uma palavra pode ter mais de um significado em determinada frase, tente trocá-la por outra que não deixe dúvidas. Mais importante ainda, não use palavras sobre cuja definição você não tem certeza.

\subsection{Ojetividade}

O texto técnico deve ser direto ao ponto, sem rodeios, e livre de opiniões. Evite apartes, evite divagações e discussões irrelevantes com relação ao tema principal.

\textbf{Nunca use hipérboles}. Cuidado com termos como ``otimizar, muito grande, enorme, muito bom''.  Usar números sempre que possível para quantificar conceitos, sejam eles precisos ou apenas uma estimativa. Em especial deve-se tomar cuidado com as palavras ``muito'' e ``muitos''.

O tom deve ser impessoal, apresentando apenas fatos e não opiniões. Em português, a voz passiva é um instrumento comum para se obter um tom impessoal. Contudo, sempre que possível, tente usar a voz ativa ou a voz passiva sintética para deixar o texto mais fluido e claro.

Palavras abstratas deixam a escrita vaga. Prefira palavras concretas, fortes, isto é, palavras que tenham um único significado. Sempre que possível substitua múltiplas palavras por uma única. Por exemplo, na frase ``A máquina processou as amostras'' temos duas palavras genéricas: máquina e processar. A mesma ideia seria mais objetiva se expressa como ``A centrífuga girou as amostras''.

Controle seu tom. \textbf{Não use linguagem coloquial. Não use clichês}. Não use de arrogância: ``obviamente, como é sabido, é claro que''.

\subsection{Concisão}

O texto técnico deve ser tão curto quanto possível, sem prejuízo de sua clareza e precisão. Não use palavras a mais, não inclua expressões irrelevantes ou supérfluas. Não escreva simplesmente para encher as páginas. Se um assunto não é relevante para a compreensão do seu trabalho, corte-o, mova-o para um apêndice ou aponte uma referência.

Evite redundâncias como ``opinião pessoal'' e ``garantia absoluta''.

\section{Vícios comuns}

\begin{itemize}
\item Estrangeirismos: ``\emph{performance}'', ``\emph{mutatis mutandis}''. Se necessário, coloque o termo estrangeiro em itálico e dê uma tradução entre parênteses.

\item Usar linguagem rebuscada. Lembre-se de que a linguagem técnica deve ser clara, precisa e objetiva.

\item Alternar o tempo verbal entre passado e presente. Seja consistente e escreva apenas no passado ou no presente.

\item Iniciar uma frase com verbo porque o sujeito está implícito na frase anterior. Deixe sempre o sujeito explícito.

\item Inserir referências no meio de uma frase. Isso quebra o fluxo da leitura. Coloque a citação no fim da frase.

\item \textbf{Usar siglas sem antes defini-las}. Sempre escreva a sigla por extenso \emph{na primeira vez} que ela aparece no texto. Por exemplo, ``este é um texto de Projeto Final de Curso (PFC)''.

\item Escrever ``como sabemos'', ``como é sabido'', ``por razões óbvias'', ``é evidente que'', ``talvez seja verdade que''. Estes termos significam apenas que você não sabe explicar o que está afirmando.

\item Usar definições \emph{por exemplo}, isto é, apresentar a definição de um conceito ou termo por meio de um exemplo. Primeiro defina o conceito, depois exemplifique.

\end{itemize}

\section{Boas práticas}

\begin{itemize}
\item Sempre que introduzir novos termos e conceitos, destaque-os em itálico para que o leitor saiba que se trata de uma definição e para que ele ache a definição com facilidade quando for necessário rastreá-la no texto.
\item Releia o que escreve a cada parágrafo. Releia rapidamente cada seção para verificar o encadeamento de ideias.
\item Corte palavras sempre que possível.
\item Nunca assuma que o leitor entenderá o que você escrever. Esforce-se para fazê-lo entender.
\item Use um corretor ortográfico.
\item Peça que alguém leia seu texto.
\end{itemize}

\section{Uso de referências}
\label{sec:comocitar}

Uma afirmação incluída num texto técnico se enquadra em um de três casos: a) seu conteúdo é de conhecimento geral dentro da área do texto; b) seu conteúdo é original e resulta do trabalho do autor; c) seu conteúdo tem origem em outro trabalho (ainda que seja do mesmo autor, não é original).

Toda afirmação enquadrada na categoria c) deve ser acompanhada de uma citação. Para afirmações da categoria b), deixe claro que se trata de ideia original do autor. Isso evita que o leitor se confunda ao pensar que possa se tratar de a) ou c).

No caso a), pode ser um tanto mais sutil determinar o que deve ser de conhecimento geral. Procure evitar o excesso de citações. Se todo um parágrafo se baseia em ideias de uma certa referência, em geral basta que ela seja citada no seu início.

\textbf{Atenção:} Não copie frases das referências usadas. Reescreva as ideias com suas próprias palavras e não deixe de citar a fonte. Se for necessário manter as palavras do original, cite a frase entre aspas e em itálico.

\section{Honestidade e Plágio}

Seja honesto ao escrever. \textbf{Não ``maqueie'' seus resultados}. Não apresente apenas as melhores amostras dos seus resultados para dar a impressão de que foi bem sucedido. Não escreva aquilo que não entende. Não escreva de forma vaga para mascarar o fato de que não entende algo.

Dê crédito a quem o merece. Inclua referências sempre que usar o trabalho de outros. Seja sempre claro para não dar a impressão de que fez algo feito por outrem. \textbf{Não assuma crédito pelo trabalho dos outros}. Isso pode ter implicações legais e acadêmicas.

\section{Cuidado com a gramática}

\begin{itemize}

\item Erros gramaticais deixam uma \textbf{impressão ruim} e podem alterar a disposição do leitor para com o texto.

\item Use a vírgula corretamente. Seu uso incorreto confunde o leitor. Nunca use a vírgula porque acha que a frase precisa de uma pausa. Não separe sujeito e verbo. Quando há inversão da ordem natural em uma frase, \emph{toda} a parte movida deve estar entre vírgulas.

\item Cuidado com a concordância da voz passiva sintética. Lembre-se de que o correto é ``Vendem-se ovos'' e não ``Vende-se ovos''.

\item Use a crase corretamente. Faça sempre o exercício de substituir o nome que sucede o ``à'' por um nome no masculino. Se o correto for usar ``ao'' com o nome masculino, então deve haver crase. Nunca use crase antes de nomes no masculino!

\item Escreva ``em que'' em vez de ``onde'' quando não houver indicação de lugar.

\item Não se escreve ``o fato \textbf{dela} ser'' ou ``a razão \textbf{do} texto ser escrito''. Escreve-se ``o fato \textbf{de ela} ser'' e ``a razão \textbf{de o} texto ser escrito''.

\item Releia o que escreve e na dúvida busque ajuda.

\end{itemize}

\section{Resumo do Capítulo}
\label{sec:metodo1b}

Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!

\clearpage

### 2022-12-07 Documentation/modelo_PFC_latex/Resultados/Resultados.tex

--- 2022-12-02 Documentation/modelo_PFC_latex/Resultados/Resultados (Alexandre Mesquita's conflicted copy 2019-02-22).tex
@@
 Ao fazer conclusões, sempre considere se o tamanho da sua amostra é grande o suficiente do ponto de vista estatístico.
+Lembre que a média empírica $\hat{\mu}_X$ de $N$ observações independentes da variável $X_i$ possui variância
+\[
+\hat{\sigma}_{\mu}^2 = \frac{1}{N(N-1)} \sum_{i=1}^N (X_i-\hat{\mu}_X)^2
+\enspace,
+\]
+onde se assume que as variáveis $X_i$ possuem uma mesma ditribuição e que essa distribuição possui segundo momento finito.
 
@@
 
-A fonte \textsf{Times}, indicada pela resolução do PFC e usada neste documento, não possui uma das aparências mais agradáveis, especialmente para os símbolos matemáticos.
-Se preferir símbolos matemáticos mais harmoniosos, remova a inclusão da fonte \textsf{newtxmath} no cabeçalho do .tex.
-
 Nesta seção você deve encontrar exemplos dos comandos mais usados em \LaTeX. Outros exemplos e manuais podem ser encontrados na internet com facilidade.
@@
 
-Ao escrever expressões matemáticas, defina todas as variáveis antes de usá-las ou imediatamente depois da expressão. Deixar de fazê-lo torna seu texto ilegível. Segue um exemplo.
+Ao escrever expressões matemáticas, defina todas as variáveis antes de usá-las ou imediatamente depois da expressão. Deixar de fazê-lo torna seu texto \textbf{ilegível}. Segue um exemplo.
 
@@
 Agora podemos citar os polos dados pela Equação (\ref{eq:polos}) (aqui adotamos a convenção de citar sempre com o número entre parênteses precedido da palavra Equação).
-Note como usamos um comando especial na Equação (\ref{eq:polos}) para garantir o ajuste automático do tamanho dos parênteses.
+Note como usamos um comando especial na Equação \ref{eq:polos} para garantir o ajuste automático do tamanho dos parênteses.
 

### 2022-12-07 Documentation/modelo_PFC_latex/Resumo/Resumo.tex

\addcontentsline{toc}{chapter}{Resumo}

\begin{center}
\huge{{\bf Resumo}}
\vspace{2cm}
\end{center}

No Resumo, em uma única página, em no máximo dois parágrafos, você explicita os seguintes itens: objetivos do projeto e descrição sucinta do local onde ele foi desenvolvido; metodologia utilizada; e resultados alcançados. Leitores experientes decidem se prosseguirão para a leitura do texto completo após lerem o resumo, a conclusão e a introdução. Por isso nestes lugares você deve colocar um esforço maior de convencimento. Além disso, a linguagem utilizada deve ser acessível a leitores com pouca familiaridade com a área, limitando-se o uso de jargões.

\begin{sloppypar}
Este novo parágrafo serve para mostrar que ao pular uma ou mais linhas no texto do arquivo .tex, o \TeX\ entende que você está iniciando outro parágrafo. O comando \textsf{sloppypar} força o texto a não ultrapassar as margens. Só deve ser usado se este problema ocorrer.
\end{sloppypar}

\clearpage
\thispagestyle{empty}
\cleardoublepage

### 2023-01-17 software/controller.py
putting it to work

@@ -74,17 +74,17 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
         get_volume(obj_pump_com)
         low_motor_noize(obj_pump_com)
 
-        flow_rate = [1.5, 2.5, 3.5]
+        flow_rate = ["1.5", "2.5", "3.5"]
 
         for fr in flow_rate:
             print("\n Starting experiment with flowrate:", fr)
-            set_flowrate(obj_pump_com, str(fr), "UM")
+            set_flowrate(obj_pump_com, fr, "UM")
             start_pumping(obj_pump_com)
             beep_command(obj_pump_com)
             while voltage < typeofmeasurement['voltage_stop']:
                 responses.append(FUG_sendcommands(obj_fug_com, ['U ' + str(voltage)]))
                 time.sleep(typeofmeasurement['step_time'])
-                controller_output = [get_voltage_from_PS(obj_fug_com), get_current_from_PS(obj_fug_com), voltage, flow_rate]
+                controller_output = [get_voltage_from_PS(obj_fug_com), get_current_from_PS(obj_fug_com), voltage, fr]
                 voltage += typeofmeasurement['step_size']
                 controller_output_queue.put(controller_output)
                 # print("[FUG THREAD] put values in controller_output_queue")

### 2023-01-17 software/data_acquisition.py

@@ -99,7 +99,7 @@ def data_acquisition(data_queue,
                                                          humidity, day_measurement, current_from_PS, target_voltage)
 
         except:
-            print("[DATA_ACQUISITION THREAD] Failed to EsctrosprayMeasurements")
+            print("[DATA_ACQUISITION THREAD] Failed to ElectrosprayMeasurements")
             sys.exit(1)
 
         try:

### 2023-01-17 software/data_processing.py

@@ -128,7 +128,7 @@ def data_processing(data_queue,
 
             # put values in the queue
             message = [electrospray_data, datapoints_filtered, time_step, electrospray_processing, txt_sjaak_str, txt_monica_str, txt_max_peaks]
-            # plotting_data_queue.put(message)
+            plotting_data_queue.put(message)
 
             sample += 1
 

### 2023-01-17 software/mainElectrospray.py

@@ -238,7 +238,7 @@ if __name__ == '__main__':
             # voltage = str(voltage) + 'V'
             if electrospray_config_setup["save_json"]:
                 # arbitrary, defined in the header
-                file_name = name_liquid + '_step_size_' + str(typeofmeasurement['step_size']) + "_step_time_" + str(typeofmeasurement['step_time']) +  ".json"
+                file_name = name_liquid + '_step_size_' + str(typeofmeasurement['step_size']) + "_step_time_" + str(typeofmeasurement['step_time']) + ".json"
                 completeName = os.path.join(save_path, file_name)
 
                 with open(completeName, 'w') as file:

### 2023-01-17 Documentation/UFMG/Relatorio_1/Introduction/Introduction.tex
documentation

\section{Introduction}

The EHDA setup used in the lab for this project can be seen in the Figure 2.
For this project we are going to focus on nozzle to plate configuration and the high voltage
will be applied to the nozzle.
We use a variety of liquids to make the experiment such as ethyleneglycol + HNO3, ethanol, water + ethanol and 2-propanol.
Those liquid properties were already been analysed and considered in the automation routine.
The experiment can be made by voltage steps or voltage ramp. Both of the dynamics are being tested.
The flowrate is still being used as a constant.

\begin{figure}[H]
    \center
    \includegraphics[width=8cm]{images/system_setup.png}
    \label{img3}
    \caption{system setup}
\end{figure}

### 2023-01-17 Documentation/WT group/article1/main.tex
documentation

\documentclass{article}
\usepackage[a4paper, portrait, margin=1.1811in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\usepackage{etoolbox}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{xcolor} 
\usepackage[colorlinks, citecolor=cyan]{hyperref}
\usepackage{caption}
\captionsetup[figure]{name=Figure}
\graphicspath{ {./images/} }
\usepackage{scrextend}
\usepackage{fancyhdr}
\usepackage{graphicx}
\newcounter{lemma}
\newtheorem{lemma}{Lemma}
\newcounter{theorem}
\newtheorem{theorem}{Theorem}

\fancypagestyle{plain}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\familydefault}{\sfdefault}

	\lhead{\color{cyan}\small \textbf{Journal of Aerosol Science}\\ \color{black}
	\textit{Vol. XX (X)  (XXXX), XX-XX, p-ISSN: 693-7554, e-ISSN:2654-3990}\\ }
	%\rhead{p-ISSN: 693-7554 \\ e-ISSN:2654-3990}
	%\rfoot{\thepage} --> Show the page number

}

%\pagestyle{plain}
\makeatletter
\patchcmd{\@maketitle}{\LARGE \@title}{\fontsize{16}{19.2}\selectfont\@title}{}{}
\makeatother

\usepackage{authblk}
\renewcommand\Authfont{\fontsize{10}{10.8}\selectfont}
\renewcommand\Affilfont{\fontsize{10}{10.8}\selectfont}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\setlength{\affilsep}{2em}  
\newsavebox\affbox
\author[1]{\textbf{João P. M. Marques}}
\author[2]{\textbf{Luewton F. L. Agostinho}}
\author[3]{\textbf{Antonio Carrasco}}
\author[4*]{\textbf{Fourth author}}
\affil[1,2]{ Study Program, Faculty, University
	Bogor, West Java, 16143, Indonesia
}
\affil[3]{ Department of Computer Science, Faculty of Mathematics and Natural Science, Pakuan University, 
	Bogor, West Java, 16143, Indonesia
}
\affil[4]{ Department of Mathematical Sciences, Faculty of Science,
	Universiti Teknologi Malaysia,
	81310 Johor Bahru,
	Johor, Malaysia
}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{12pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{12pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\titleformat{\section}{\normalfont\fontsize{10}{15}\bfseries}{\thesection.}{1em}{}
\titleformat{\subsection}{\normalfont\fontsize{10}{15}\bfseries}{\thesubsection.}{1em}{}
\titleformat{\subsubsection}{\normalfont\fontsize{10}{15}\bfseries}{\thesubsubsection.}{1em}{}

\titleformat{\author}{\normalfont\fontsize{10}{15}\bfseries}{\thesection}{1em}{}

\title{\textbf{\huge EHDA closed loop control system based on real time non-visual spray mode classification}\\
	(Center, Bold, Times New Roman 14, maximum 15 words in english)}
\date{}

\begin{document}

\pagestyle{headings}	
\newpage
\setcounter{page}{1}
\renewcommand{\thepage}{\arabic{page}}

\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Figure }}	\captionsetup[table]{labelfont={bf},labelformat={default},labelsep=period,name={Table }}
\setlength{\parskip}{0.5em}

\maketitle

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		\textbf{Electrohydrodynamic Atomization (EHDA)} also known as Electrospray (ES), is a technology that uses a strong electric field (kV/cm) to manipulate liquid breakup into droplets. This technique allows the generation of droplets smaller than the nozzle diameter with a controlled droplet size, which means it can be used to produce uniformly sized particles in the micro/nanoscale range. This liquid spraying technique can generate different modes when both the liquid flow rate and the voltage vary with a narrow size dispersion. The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.
		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. The system utilizes current data from the experiment to classify the spray mode dynamics in real-time and adjust the EHDA parameters, such as pump flowrate and power supply voltage, to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The results of the system are discussed and its potential applications in industrial settings are highlighted.
		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}. Furthermore, the determination of keywords needs to pay attention to important words contained in the title and abstract, separated by a semicolon. \textbf{The novelty} in this paper briefly explains why no one else has adequately researched the question. Then \textbf{the results} are made a list of the empirical findings and write the discussion in one or two sentences. \\ \\
		\let\thefootnote\relax\footnotetext{
			\small $^{*}$\textbf{Corresponding author.} \textit{
				\textit{E-mail address: \color{cyan}author4@email.com}}\\
			\color{black} Received: xx xxxxx 20xx,\quad
			Accepted: xx xxxxx 20xx and available online XX July 2022 \\
			\color{cyan} https://doi.org/10.1016/j.compeleceng.2021.107553

		}
		\textbf{\textit{Keywords}}: \textit{Keyword 1; keyword 2; keyword 3; keyword 4; keyword 5}
	\end{abstract}
\noindent\rule{15cm}{0.4pt}

\section{Introduction (10pt, bold)}
The introduction is about 400-600 words and provides background information, previous references related to the main topic, reason, purpose of the research, and the novelty of the research.  Content should be relatively non-technical, but clear enough for a knowledgeable reader to understand the manuscript’s contribution. Explain what the purpose of the research is and why the research was conducted the main body of the article should begin with an introduction, which provides further details on the purpose of the paper, motivation, research methods, and findings. For citations use numbering which must be used for reference titles, for example, citations for journals consisting of 1 article  \cite{Septiawan1} or two articles \cite{Septiawan2}, \cite{Lucy}, while for writing citations of more than two articles \cite{Gingold} - \cite{Morikawa}.

In writing a bibliography using the IEEE style, the conditions are numbered, as follows: \cite{Septiawan1}, in order from the first citation to the last. References with IEEE style use a numeric number placed in a square box for the reference taken and put it at the end of the sentence. The numeric numbers located in the square box are made the same as the bibliography on the final page of the scientific paper.

\section{Methods (10pt, bold)}
The methods section describes the steps followed in the execution of the study and also provides a brief justification for the research methods used. A chronological explanation of the research, including research design, research procedures (in the form of algorithms, codes, or others), how the procedures are to obtain and test data \cite{Lo} - \cite{Hang}. The description of the research has been supported by references, so that the implementation can be accepted scientifically [6]. Figure are presented in the center, as shown below and are cited in the manuscript. An example of a membership function graph can be seen in Figure \ref{table1}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{images/figur1.PNG}
	\caption{Font 10pt and center not bold for captions except for the words "Figure"}
	\label{fig1}
\end{figure}

Each image (photos, graphs, and diagrams) in the article must be accompanied by a caption/image title and sequential image numbers, written below the image in the middle position. Images must be directly relevant to the article and are always referenced in the article referred to as Figur \ref{table1}, where the capital letters are capitalized.

\subsection{Table (10pt, bold)}
Writing tables are numbered followed by the title of the table above the table, centered, 1 spaced with a short and precise title. Consider the example in Table \ref{table1}
\begin{table}[h]
	\centering
	\caption{Font 10pt and center not bold for captions except for the words "Table"}
	\label{table1}
	\begin{tabular}{@{}cccc@{}}
		\toprule
		\textbf{Characteristics}& \textbf{Description }& \textbf{Frequency }& \textbf{Percentage} \\
		\midrule
		Gender & Male & 198 & 80.2\% \\
		& Female & 49 & 19.8\% \\
		Entry & 2018 & 54 & 21.9\% \\
		& 2019 & 64 & 25.9\% \\
		& 2020 & 59 & 23.9\% \\
		& 2021 & 70 & 28.3\% \\
		MBKM & Yes & 217 & 87.9\% \\
		& No & 30 & 12.1\% \\
		& Total & 247 & 100\% \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Figure (10pt, bold)}
Image writing techniques in scientific papers must also be symmetrical in the middle. So the settings are not aligned right or left, but in the center. This helps tidy up the position of the image or photo so that it appears side by side well with the description text as in Figure \ref{fig2}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{images/figur2.PNG}
	\caption{Font 10pt and center not bold for captions except for the words "Figure"  }
	\label{fig2}
\end{figure}

\section{Result and Discussion (10pt, bold)}
The results obtained are data or facts obtained from research. Important data or facts that cannot be clearly narrated can be displayed in the form of tables or pictures or other illustrations. If the results are presented in the form of tables or figures, they do not need to be described at length. The discussion is a review of the results, explaining the meaning of the research results, conformity with the results or previous research, the role of the results in solving the problems mentioned in the introduction, and the possibility.

This section is the most important part of your article. The following are things that you must pay attention to in writing the results and the research results must be clear and concise, the data presented has been processed (not raw data), set forth in the form of narratives, tables or pictures, and given easy-to-understand explanations. It is important to highlight differences between your results or findings and those of previous publications by other researchers. It is important to be compared with related references.
\subsection{Equation (10pt, bold)}
Mathematical equations must be numbered sequentially and starting with (1) until the end of the paper including the appendix. This numbering must begin and end with an opening and closing parenthesis and right align. Add one blank space above and below the Eq. \ref{Eq1}.
\begin{eqnarray}
	\chi(L(\Gamma); \lambda)=(\lambda+2)^{m-n}\chi(\Gamma;\lambda+2-k)
	\label{Eq1}
\end{eqnarray}
For example, from Eq. \ref{Eq2} it is derived again the next mathematical equation
\begin{eqnarray}
	\chi(L(\Gamma); \lambda)=\det (\lambda I_{m}-A_{L})
		\label{Eq2}
\end{eqnarray}
Or there is the next mathematical Eq. \ref{Eq3} as below
\begin{eqnarray}
\det(D_{0}D_{0}^{t})=\sum_{|U|=n-1} \det(D_{U})\det(D_{U}^{t})
	\label{Eq3}
\end{eqnarray}
\subsection{Therema (10pt, bold)}
The schema for writing definitions, theorems, lemmas, and proofs conforms to and follows the template below.

\begin{theorem}
	 Theorem is a statement about mathematics that still requires proof and the statement can be shown to have a truth value or is also true.
\end{theorem}

\subsubsection{Lemma (10pt, bold)}
\begin{lemma}
	An entry is a word or phrase entered in the dictionary beyond the definition given in the entry
\end{lemma}

\section{Conclusion (10pt, bold)}
The author presents brief conclusions from the results of research with suggestions for advanced researchers or general readers. A conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. Conclusions must identify the results obtained in a clear and unambiguous manner, the author should provide the answer to the question: is this a problem with error, method, validity, and or otherwise?

\section{Acknowledgement (if any)}
Contains an acknowledgment of thanks to an agency if this research was funded or supported by that agency, or if there were parties who significantly assisted directly in the research or writing of this article. If the party is already listed as the author, then there is no need to mention it again in this Acknowledgment
\bibliographystyle{IEEEtran}

%\bibliography{template} %-->reference list is on the template.bib file
\begin{thebibliography}{1.7} 
	\bibitem[1]{Septiawan1} \color{cyan}R. R. Septiawan, “An ODE control system of a rigid body on an ocean wave for a surfer simulation in the SPH method,” \textit{The Science Reports of Kanazawa University}, vol. 62, pp. 51–68, 2018. [Online]. Available: http://scirep.w3.kanazawa-u.ac.jp/articles/62-004.pdf. \color{black}
	\bibitem[2]{Septiawan2} \color{cyan}R. R. Septiawan, S. Viridi, and Suprijadi, “The Effect of Particle Size Ratio on Porosity of a Particles Deposition Process,” \textit{Key Engineering Materials,} vol. 675–676, pp. 647–650, 2016. [Online]. Available: https://www.scientific.net/KEM.675-676.647. \color{black}
	\bibitem[3]{Lucy} \color{cyan}L. B. Lucy, “A numerical approach to the testing of the fission hypothesis,” \textit{The astronomical journal}, vol. 82, pp. 1013–1024, 1977. \color{black}
	\bibitem[4]{Gingold} \color{cyan}R. A. Gingold and J. J. Monaghan, “Smoothed particle hydrodynamics: theory and application to non-spherical stars,” \textit{Monthly Notices of the Royal Astronomical Society}, vol. 181, no. 3, pp. 375–389, 1977. [Online]. Available:  https://academic.oup.com/mnras/article/181/3/375/988212. \color{black}
	\bibitem[5]{Supriadi} \color{cyan}Suprijadi, F. Faizal, and R. R. Septiawan, “Computational Study on Melting Process Using Smoothed Particle Hydrodynamics,” Journal of Modern Physics, vol. 05, no. 03, pp. 112–116, 2014. [Online]. Available: https://www.scirp.org/pdf/JMP2014022411463120.pdf.\color{black}
	\bibitem[6]{Septiawan3} \color{cyan}R. R. Septiawan, H. Abdillah, Novitrian, and Suprijadi, “Preliminary Study on Liquid Natural Convection by Temperature Differences,” 2015. [Online]. Available: https://www.atlantis-press.com/proceedings/icaet-14/16166.\color{black}
	\bibitem[7]{Morikawa}\color{cyan}D. Morikawa, M. Asai, N. Idris, Y. Imoto, and M. Isshiki, “Improvements in highly viscous fluid simulation using a fully implicit SPH method,” \textit{Computational Particle Mechanics}, vol. 6, no. 4, pp. 529–544, 2019. [Online]. Available: https://link.springer.com/article/10.1007/s40571-019-00231-6.\color{black}
	\bibitem[8]{Lo} \color{cyan}E. Y.M. Lo and S. Shao, “Simulation of near-shore solitary wave mechanics by an incompressible SPH method,” \textit{Applied Ocean Research}, vol. 24, no. 5, pp. 275–286, 2002. [Online]. Available: https://www.sciencedirect.com/science/article/abs/pii/S0141118703000026.\color{black}
	\bibitem[9]{Dalrymple} \color{cyan}R. A. Dalrymple and B. D. Rogers, “Numerical modeling of water waves with the SPH method,” Coastal Engineering, vol. 53, no. 2–3, pp. 141–147, 2006. [Online]. Available: https://www.sciencedirect.com/science/article/abs/pii/S0378383905001304.\color{black}
	\bibitem[10]{Yan} \color{cyan}X. Yan, Y.-T. Jiang, C.-F. Li, R. R. Martin, and S.-M. Hu, “Multiphase SPH simulation for interactive fluids and solids,” ACM Transactions on Graphics, vol. 35, no. 4, pp. 1–11, 2016. [Online]. Available: https://dl.acm.org/doi/10.1145/2897824.2925897.\color{black}
	\bibitem[11]{Antocy} \color{cyan}C. Antoci, M. Gallati, and S. Sibilla, “Numerical simulation of fluid–structure interaction by SPH,” Computers and Structures, vol. 85, no. 11–14, pp. 879–890, 2007. [Online]. Available: https://www.sciencedirect.com/science/article/abs/pii/S0045794907000132.\color{black}
	\bibitem[12]{Monaghan1} \color{cyan}J. J. Monaghan, A. Kos, and N. Issa, “Fluid Motion Generated by Impact,” Journal of Waterway, Port, Coastal, and Ocean Engineering, vol. 129, no. 6, pp. 250–259, 2003. [Online]. Available: https://ascelibrary.org/doi/10.1061/\%28ASCE\%290733-950X\%282003\%29129\%3A6\%28250\%29.\color{black}
	\bibitem[13]{Akinci} \color{cyan}N. Akinci, M. Ihmsen, G. Akinci, B. Solenthaler, and M. Teschner, “Versatile rigid-fluid coupling for incompressible SPH,” ACM \textit{Transactions on Graphics}, vol. 31, no. 4, pp. 1–8, 2012. [Online]. Available: https://dl.acm.org/doi/10.1145/2185520.2185558. \color{black}
	\bibitem[14]{Liu} \color{cyan}G. R. Liu and M. B. Liu, \textit{Smoothed Particle Hydrodynamics}. Singapore: World Scientific Publishing Co Pte Ltd, 2003. doi: 10.1142/5340. \color{black}
	\bibitem[15]{John} \color{cyan}John F. Wendt, \textit{Computational Fluid Dynamics}. Berlin, Heidelberg: Springer Berlin Heidelberg, 2009. doi: 10.1007/978-3-540-85056-4.\color{black}
	\bibitem[16]{Lattanzio} \color{cyan}J. J. Monaghan and J. C. Lattanzio, “A refined particle method for astrophysical problems,” \textit{Astron Astrophys}, vol. 149, pp. 135–143, 1985.\color{black}
	\bibitem[17]{Batchelor}\color{cyan}G. K. Batchelor, \textit{An Introduction to Fluid Dynamics.} Cambridge: Cambridge University Press, 2000. doi: 10.1017/CBO9780511800955.\color{black}
	\bibitem[18]{Monaghan2} \color{cyan}J. J. Monaghan, “Simulating Free Surface Flows with SPH,” \textit{Journal of Computational Physics}, vol. 110, no. 2, pp. 399–406, 1994. [Online]. Available: https://www.sciencedirect.com/science/article/pii/S0021999184710345.\color{black}
	\bibitem[19]{Managhan3} \color{cyan}J. J. Monaghan, “Smoothed particle hydrodynamics,” \textit{Reports on Progress in Physics}, vol. 68, no. 8, pp. 1703–1759, 2005. [Online]. Available: https://iopscience.iop.org/article/10.1088/0034-4885/68/8/R01.\color{black}
	\bibitem[20]{Rao} \color{cyan}A. Rao, Dynamics of Particles and Rigid Bodies. Cambridge: Cambridge University Press, 2005. doi: 10.1017/CBO9780511805455.\color{black}
	\bibitem[21]{Ogata1} \color{cyan}K. Ogata, \textit{Discrete-Time Control Systems (2nd Ed.)}. USA: Prentice-Hall, Inc., 1995.\color{black}
	\bibitem[22]{Ogata2} \color{cyan}K. Ogata, \textit{Modern Control Engineering,} 5th ed. Pearson, 2009.\color{black}
	\bibitem[23]{Hang} \color{cyan}J.-X. Xu, C.-C. Hang, and C. Liu, “Parallel structure and tuning of a fuzzy PID controller,” Automatica, vol. 36, no. 5, pp. 673–684, 2000. [Online]. Available: https://www.sciencedirect.com/science/article/abs/pii/S0005109899001922.\color{black}

\end{thebibliography}
\textbf{Reference list format}\\
The reference list format is based on the IEEE and should appear at the end of the article, covering only the literature actually cited in the manuscript. Authors should use reference management tools such as Mendeley, End Note and Grammarly. Reference writing rules:
\begin{itemize}
	\item  References used within the last 10 years.
	\item Using the numbering that should be used for the reference title.
	\item Last name and year must be used for each reference citation.
	\item All references must be cited in the paper.
	\item Journal and conference names should be italicized.
	\item  The title of the book must be italicized.
\end{itemize}
.

\end{document}

### 2023-01-17 software/mainElectrospray.py

@@ -257,4 +257,4 @@ if __name__ == '__main__':
         print("[SAVING] Failed to on saving function")
         sys.exit(1)
 
-
+    print("[SAVING] END SAVING")

### 2023-01-17 Documentation/UFMG/Relatorio_2/Summary/Summary.tex

--- 2022-12-02 Documentation/Relatorio_2/Summary/Summary.tex
@@
 
+The setup used for this project can be seen in the Figure 2.
+To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera
+and also the system actuators which is represented by the high voltage power supply and the syringe pump.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+The algorithms implemented in the computer machine was developed in python by another student and it is already collecting data and classifying the spraying dynamics.
+In Figure 3 and Figure 4 shows pictures took by the high speed camera of some of the possible spraying dynamics we can reach. The videos took by the camera is not being used in the classification
+algorithm. It is used for manual validation of it.
 

### 2023-01-17 Documentation/UFMG/modelo_PFC_latex/Conclusao/Conclusao.tex

\chapter{Conclusões}

Novamente, este será um dos trechos que o leitor experiente lerá antes de decidir se vale a pena ler o texto integral. Seja convincente.

\section{Considerações Finais}

Reitere o que de mais importante foi feito, qual era o objetivo inicial e qual o resultado obtido. Se houve requisitos ou especificações de projeto, discuta se foram atingidos. Se os resultados não foram conclusivos ou contrariam o que se esperava, seja honesto e diga-o explicitamente. Busque explicar os insucessos com argumentos sólidos e plausíveis.

\section{Propostas de Continuidade}

Se houve questões ainda não respondidas ou resultados insatisfatórios, aponte direções de continuação.

\clearpage

### 2023-01-17 Documentation/UFMG/modelo_PFC_latex/Introducao/Introducao.tex

\chapter{Introdução}
\label{chap:intro} %este label será usado para referenciar este capítulo

As primeiras frases têm a missão de prender a atenção do leitor e por isso são as mais importantes do texto. Diga o quanto antes o que você fez e quais são os resultados alcançados. Ao terminar de ler a introdução o leitor tomará uma nova decisão de se vale a pena ou não continuar lendo o texto. Capte a atenção do leitor bem aqui.

A comunicação escrita é considerada umas das cinco habilidades mais importantes por profissionais de engenharia e um engenheiro passa em média mais de $25$\% do seu tempo escrevendo \cite{eggert2002response,spretnak1982survey}. Uma quantidade similar de tempo é gasta na escrita de correspondência e de relatórios técnicos \cite{cunningham2012perceptions}. Dessa forma, encare a escrita do seu projeto como um treinamento nessa importante habilidade.

Neste texto você encontrará não apenas uma estrutura para escrever seu trabalho em \LaTeX, mas também um pequeno manual de boas práticas na escrita técnica. Leia com atenção e coloque as sugestões em prática à medida que preenche o texto com o conteúdo do seu próprio projeto. Também será apresentado um número de vícios de escrita comumente encontrados nas monografias de alunos.

A seguir está a estrutura de organização sugerida pelo colegiado do curso. Note que ela não é necessariamente a melhor para contar a história do seu projeto. Você pode por exemplo preferir usar títulos mais pertinentes ao seu contexto. Contudo, o seu texto deve conter cada um dos pontos a seguir.

\section{Motivação e Justificativa}
\label{sec:motivacao}

Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes. Contextualize seu projeto dentro do local de execução ou da literatura e explique como ele é necessário ou inovador. É possível fazer uma breve revisão bibliográfica, confrontando seu trabalho com outras referências bibliográficas para mostrar a sua contribuição. No quesito contribuição, é muito importante deixar claro o tempo todo que partes do projetos foram executadas por outros e que partes foram executadas por você. Caso contrário, corre-se o risco de inadvertidademente tomar crédito pelo trabalho de outrem, o que pode ter implicações legais.

\section{Objetivos do Projeto}
\label{sec:objetivos}

Tendo em vista o exposto acima, este projeto tem por objetivos:

\begin{enumerate}[a)]
\item Item 1;
\item Item 2; 
\item Etc.     
\end{enumerate}

O conteúdo desta seção pode se sobrepor um pouco com o da seção anterior, podendo ela ser um sumário dos pontos expostos anteriormente. A escolha do título da seção talvez seja mais apropriada para a fase de proposta do projeto. Afinal, nesta fase se conhecem os objetivos e não os resultados. Por outro lado, fará pouco sentido discutir objetivos quando o projeto está finalizado, especialmente se tais objetivos não foram alcançados.

\section{Local de Realização}
\label{sec:empresa}

Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido. Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc. Descreva também o seu vínculo com a empresa.

\section{Estrutura da Monografia}
\label{sec:organizacao}

O trabalho está dividido em quatro capítulos. Este capítulo apresentou uma introdução ao projeto a ser descrito nesta monografia e a empresa onde o trabalho foi realizado. O Capítulo 2 descreve os princípios básicos de um sistema ... (sistema onde se insere o trabalho) e abrange todos os conceitos necessários para um melhor entendimento do projeto. O Capítulo 3 aborda a metodologia de desenvolvimento, seguida pela implementação dos .... No Capítulo 4 tem-se a conclusão da  monografia e algumas sugestões e dificuldades encontradas na realização do projeto.

\clearpage

### 2023-01-17 software/controller.py
putting it to work

@@ -74,7 +74,7 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
         get_volume(obj_pump_com)
         low_motor_noize(obj_pump_com)
 
-        flow_rate = ["1.5", "2.5", "3.5"]
+        flow_rate = ["0.5", "0.7", "0.9", "1.1", "1.3", "1.5", "1.7", "1.9"]
 
         for fr in flow_rate:
             print("\n Starting experiment with flowrate:", fr)

### 2023-01-17 software/mainElectrospray.py

@@ -249,6 +249,7 @@ if __name__ == '__main__':
             sys.exit(0)
 
 
+
         except:
             print("[SAVING] Failed to SAVE JSON")
             sys.exit(1)

### 2023-01-17 Documentation/UFMG/Relatorio_1/Development/Development.tex

\section{Development}

\subsection*{3.1 Peripherals integration}

The peripherals automation routine was already developed by another student. 
In order to continue the research I took some time to understand the physical concept 
behind EHDA experiments and the project knowledge.

I made upgrades in the routine to include the high speed camera with a hardware triggering routine using an
arduino microcontroler. This will be usefull to validate the further classification of the spray dynamics.

\subsection*{3.2 Experiment tests}

Initial tests were made to verify the setup assembly and the automation routine integration. 
In this step I could unterstand in practise how electrospray works.

I noticed that we need a large set of variables in the range to produce the desired dynamics of electrospray, which most of the time is cone-jet mode.
Those variables can be the liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permitivity.
And also physical variables such as flowrate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.

The instruments used in the setup are:

  - High Voltage Power Supply (FUG)

  - Oscilloscope TiePie WS6 DIFF

  - Humidity and Temperature sensor - DHT11

  - High Speed Camera - Photron fastcam mini

  - Syringe pump

  - Arduino Uno for hardware triggering camera and DHT11 interface

\subsection*{3.3 Data Analysis}

According to Sjaaks paper \emph{A Generic Electrospray Classification}\cite*{Sjaaks} we can classify the spray modes using
only the current data measured by the oscilloscope. With the relations between the statistical values of mean, standart deviation and median of the signal
we can classify if it's in dripping or cone-jet dynamics. In the figure bellow we can see the current data acquired from one experiment and also the statistical levels
above. Each sample takes a frame window of 0.5s of current data and then classifies it.

For each sample color the algorithm classifies:

  - green: dripping mode

  - blue: intermittent mode

  - red: Cone-jet mode

  - purple: corona spark mode

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{images/exp_data.png}
    \label{img2}
    \caption{Data Analysis}
\end{figure}

### 2023-01-17 Documentation/UFMG/modelo_PFC_latex/Capa/capa.tex

\begin{titlepage}
\begin{center}
{\large Universidade Federal de Minas Gerais\\
Escola de Engenharia \\
Curso de Graduação em Engenharia de Controle e Automação\\}

\vspace{6cm}
{\bf\Large Primeira Linha do Título\vspace{0.2cm}

Segunda Linha do Título, se Houver}
\vspace{4cm}

%\hspace{0.3\textwidth} \parbox{0.65\textwidth}
{\large Fulano de Tal}
\vspace{2cm}

\vspace{2cm}          
%\hspace{0.3\textwidth} 
{\large Orientador: Prof. Beltrano, Dr.}\\
{\large Supervisor: Eng. Cicrano}

\vfill
%\hspace{0.3\textwidth} 
{\large Belo Horizonte, Julho de 2014 }
\end{center}

\end{titlepage}

\newpage
\clearpage
\thispagestyle{empty}

\begin{titlepage}

\centering
\textbf{Monografia}\\
\vspace{2cm}
\centering
\textbf{Título da Monografia}\\
\vspace{5cm}

\parbox{1.0\textwidth} 
{\large 
Monografia submetida à banca examinadora
designada pelo Colegiado Didático do Curso de
Graduação em Engenharia de Controle e
Automação da Universidade Federal de Minas
Gerais, como parte dos requisitos para aprovação na
atividade Projeto Final de Curso II.}

\vspace{7cm} 
\centering
Belo Horizonte, Julho de 2014

\end{titlepage}

### 2023-01-17 Documentation/UFMG/modelo_PFC_latex/Resumo/Abstract.tex

\addcontentsline{toc}{chapter}{Abstract}

\begin{center}
\huge{{\bf Abstract}}
\vspace{2cm}
\end{center}

Write a version of your ``resumo'' in English. Beware of literal translations and double check the translation of technical terms.

\clearpage
\thispagestyle{empty}
\cleardoublepage

### 2023-01-17 data_analysis/map_analysis.py
mapping data_analysis

@@ -30,16 +30,6 @@ with open(file_path + file_name + ".json", 'r') as data_file:
 ######################################
 
 
-print("\ndata_sample\n")
-data_sample = pd.json_normalize(
-    data['measurements'], 
-    record_path = ["data [nA]"], 
-    record_prefix ='data-',
-    meta = ["name", "flow rate [m3/s]", "voltage", "current PS", "temperature", "humidity", "target voltage"]
-)
-print(data_sample.info())
-
-
 print("\data_window\n")
 measurements_data_window = pd.json_normalize(data['measurements'])
 processing_data_window = pd.json_normalize(data['processing'])
@@ -110,48 +100,26 @@ def onpick(event):
 #              PLOTTING
 ######################################
 
-#Oscilloscope data
-fig, axs = plt.subplots(2, 1)
-plt.title(file_name)
+fig, axs = plt.subplots(3, 1)
+
 axs[0].set(ylabel='ccurent nA')
-axs[0].plot(data_sample.index/sampling_frequency, data_sample['data-0'])
+axs[0].plot(data_window['data [nA]'].explode())
 axs[0].grid()
 
 axs[1].set(ylabel='voltage (V)')
-axs[1].set_yticks(np.arange(0, 7500, 10))
-axs[1].plot(data_sample.index/sampling_frequency, data_sample['voltage'])
+axs[1].set_yticks(np.arange(0, 7500, 500))
+axs[1].scatter(data_window.index, data_window['target voltage'], color=data_window['colormap'])
 axs[1].grid()
+
+axs[2].set(ylabel='mean')
+axs[2].set_ylim(0, 300)
+axs[2].scatter( data_window.index, data_window['mean'], color=data_window['colormap'])
+axs[2].grid()
+
+fig.canvas.mpl_connect('button_press_event', onpick)
+
+plt.xlabel('Legend:  blue = Intermittend ; red = Cone Jet ; green = Dripping ; purple = streamer onset ; black = Undefined ')
 plt.show()
-
-# # Other data
-# fig, axs = plt.subplots(5, 1)
-
-# axs[0].set(ylabel='ccurent nA')
-# axs[0].plot((data_sample.index/sampling_frequency)/60, data_sample['data-0'])
-# axs[0].grid()
-
-# axs[1].set(ylabel='voltage (V)')
-# axs[1].set_yticks(np.arange(0, 5000, 10))
[…]

### 2023-01-17 software/controller.py

@@ -83,8 +83,9 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
             beep_command(obj_pump_com)
             while voltage < typeofmeasurement['voltage_stop']:
                 responses.append(FUG_sendcommands(obj_fug_com, ['U ' + str(voltage)]))
-                time.sleep(typeofmeasurement['step_time'])
+                time.sleep(typeofmeasurement['step_time']/2)
                 controller_output = [get_voltage_from_PS(obj_fug_com), get_current_from_PS(obj_fug_com), voltage, fr]
+                time.sleep(typeofmeasurement['step_time']/2)
                 voltage += typeofmeasurement['step_size']
                 controller_output_queue.put(controller_output)
                 # print("[FUG THREAD] put values in controller_output_queue")

### 2023-01-17 data_analysis/map_analysis.py
data_analysis

@@ -18,7 +18,7 @@ sampling_frequency = 1e5
 
 file_path = "joaoData/mapping/"
 
-file_name = "map2"
+file_name = "map1"
 
 
 with open(file_path + file_name + ".json", 'r') as data_file:    
@@ -36,6 +36,8 @@ processing_data_window = pd.json_normalize(data['processing'])
 data_window = [measurements_data_window, processing_data_window]
 data_window = pd.concat(data_window, axis=1)
 
+colors = {'Cone Jet':'red', 'Dripping':'green', 'Intermittent':'blue', 'Multi Jet':'purple', 'Undefined':'black', 'Corona':'cyan'}
+
 colormap = []
 for electro_class in data_window['spray mode.Sjaak']:
     if electro_class == 'Intermittent':
@@ -44,6 +46,12 @@ for electro_class in data_window['spray mode.Sjaak']:
         colormap.append('red')
     elif electro_class == 'Dripping':
         colormap.append('green')
+    elif electro_class == 'Multi Jet':
+        colormap.append('purple')
+    elif electro_class == 'Corona':
+        colormap.append('cyan')
+    elif electro_class == 'Undefined':
+        colormap.append('black')
     else:
         colormap.append('black')
 
@@ -51,7 +59,7 @@ for electro_class in data_window['spray mode.Sjaak']:
 sampleIndex = 0
 for monica_class in data_window['spray mode.Monica']:
     if monica_class == 'streamer onset':
-        colormap[sampleIndex] = 'purple'
+        colormap[sampleIndex] = 'cyan'
     sampleIndex+=1
 
 
@@ -96,29 +104,41 @@ def onpick(event):
 
 
 
+# ######################################
+# #              PLOTTING
+# ######################################
+
+# fig, axs = plt.subplots(3, 1)
+
+# axs[0].set(ylabel='ccurent nA')
+# axs[0].plot(data_window['data [nA]'].explode())
+# axs[0].grid()
+
+# axs[1].set(ylabel='voltage (V)')
+# axs[1].set_yticks(np.arange(0, 7500, 500))
+# axs[1].scatter(data_window.index, data_window['target voltage'], color=data_window['colormap'])
+# axs[1].grid()
+
+# axs[2].set(ylabel='mean')
+# axs[2].set_ylim(0, 300)
[…]

### 2023-01-18 Documentation/UFMG/Relatorio_3/Development/Development.tex
Documentation

\section{Metodology and Results}

% \subsection*{3.1 Setup and Routine Algorithm Optimization}

%     About the python algorithm to turn the experiment autonomous it was made a study and modelling of the software architecture to optimize it 
%     for further control loop application to be implemented.
%     From the changes made until now it highlights:

%     - Integrate high speed camera to the experiment routine.

%     - Remodel the software to support threads in order to separate the sensoring and controlling routines.

%     - Reduce the data collected size.

%     - Synchronize the power supply step commands and voltage sensoring.

%     - Reestructure the setup file in order to make it more intuitive to use the experiment.

%     - Improvements in code organization and readability.

%     About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to make the experiment 
%     the most stable and easy to reach cone-jet mode as possible.
%     For example, while doing experiments we discovered that the frequency of the pump machine internal motors was
%     creating an interference in the flowrate. Therefore compromising the stabilization in cone jet mode.
%     A solution for that was to increase the flowrate wich smooths this pumping noise. For that was also necessary
%     to increase the nozzle diameter to balance with all other variables from the experiment.

% \subsection*{3.2 Experiment 1}

%     This first experiment was made using the setup:

%     - liquid: water60alcohol40

%     - flow rate min: 1.45 mL/hr

%     - config: nozzle to plate

%     - nozzle to plate or ring distance: 1.5 cm

%     - nozzle diameter: 0.136 mm

%     In Figure 5 we can see 5 graphs:

%     1 - current values measured by the oscilloscope. As it is a lot of data it is compressed in the figure.

%     2 - Voltage step sequence in order to evaluate the dynamics in each high voltage level.

%     3,4,5 - Statistical values measured by each window of 0.5s of data collected. This values will be used in the classification algorithm.
%     Those values are already classified by colour and the legend is showed below.

%     LEGEND:

%     - Green = Dripping

%     - Blue =  Intermittend

%     - Red = Cone Jet mode

%     - Purple = Streamer Onset (high current values)

%     - Black = Undefined

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=17cm]{images/images_folder_2/img1.png}
%         \caption{Data acquired in the experiment 1 - liquid: Water AND alcohol}
%     \end{figure}

%     In Figure 6 and 7 we can see one data window sample of dripping and one of cone jet dynamics. There are two graphs. The first one its
%     the current datapoints filtered by a ideal low pass butterworth filter. In the second graph we can see the module of the fast fourier transform real values.

%     We can see in Figure 6 that there were two droplets expelled by the nozzle. This can be seen as the two signal waves in the current value and the amount of frequencies seen in the second graph.

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=12cm]{images/images_folder_2/img2.png}
%         \caption{Dripping sample}
%     \end{figure}

%     We can see in Figure 7 that the current signal is more stable and also with an offset current arround 100nA showing that the spray is in cone jet mode. Also seen as the 0 Hz DC component value in the frequency domain graph.

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=12cm]{images/images_folder_2/img3.png}
%         \caption{Cone jet sample}
%     \end{figure}

%     Other interesting grahps exposed in Sjaaks\cite*[]{Sjaaks} paper is correlating statistical values relations to each voltage step and classification. This is also good to evaluate the separability of each classification method.
%     Those graphs can be seen in Figures 8, 9 and 10.

%     \begin{multicols}{3}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph1.png}
%             \caption{mean current X voltage}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph2.png}
%             \caption{deviation/mean}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph3.png}
%             \caption{mean/median}
%         \end{figure}

%     \end{multicols}

% \subsection*{3.3 Experiment 2}

% In this experiment the liquid was changed in order to have a bigger voltage range in the cone jet mode. Which is the most valuable mode in this project.

%     - liquid: ethanol pure

%     - flow rate min: 1.5 mL/hr

%     - camera to nozzle distance: 16.5 cm

%     - config: nozzle to plate

%     - nozzle to plate or ring distance: 1.5 cm

%     - nozzle diameter: 0.136 mm

%     - type of measurement:

%         * voltage start: 3000 V

%         * voltage stop: 10000 V

%         * step size: 100 V

%         * step time: 5 s

%     In Figure 11, the data is well classified but it also have a noise in the system that can been seen in the peak current values.
%     Those peaks can be seen in all the voltage ranges in this experiment and also have similar distances in beetween the peaks. This is probably caused by
%     external interference but it is still not certain what is it about.

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=17cm]{images/images_folder_3/data3.png}
%         \caption{Data acquired in the experiment 2 - pure ethanol}
%     \end{figure}

%     The Figure 12 shows the same current x time graph but with a zoom in y axis in order to see the signal steps in the experiment. It is also classified by the same color legend as all graphs in this overview.

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=15cm]{images/images_folder_3/data3current.png}
%         \caption{current graph with classification}
%     \end{figure}

%     The Figures 13, 14 and 15 shows graphs with statistical realations in the data.

%     \begin{multicols}{3}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph1.png}
%             \caption{current mean X voltage}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph2.png}
%             \caption{deviation/mean}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph3.png}
%             \caption{mean/median}
%         \end{figure}

%     \end{multicols}

% \subsection*{3.4 Experiment 3}

%     - liquid: ethanol pure

%     - flow rate min: 1.5 mL/hr

%     - camera to nozzle distance: 16.5 cm

%     - config: nozzle to plate

%     - nozzle to plate or ring distance: 1.5 cm

%     - nozzle diameter: 0.136 mm

%     - type of measurement:

%         * voltage start: 3000 V

%         * voltage stop: 11000 V

%         * step size: 50 V

%         * step time: 1 s

%     \begin{figure}[H]
%         \center
%         \includegraphics[width=17cm]{images/images_folder_3/data4.png}
%         \caption{Data acquired in the experiment 3 - pure ethanol}
%     \end{figure}

%     \begin{multicols}{3}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph1.png}
%             \caption{current mean X voltage}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph2.png}
%             \caption{deviation/mean}
%         \end{figure}

%         \begin{figure}[H]
%             \center
%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph3.png}
%             \caption{mean/median}
%         \end{figure}

%     \end{multicols}

### 2023-01-18 Documentation/UFMG/Relatorio_3/Summary/Summary.tex
Documentation

--- 2022-12-02 Documentation/Relatorio_2/Summary/Summary.tex
@@
 
-\begin{figure}[H]
-    \center
-    \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
-    \caption{System Architecture}
-\end{figure}
+The setup used for this project can be seen in the Figure 2.
+To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera
+and also the system actuators which is represented by the high voltage power supply and the syringe pump.
 
-\begin{multicols}{2}
+% \begin{figure}[H]
+%     \center
+%     \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
+%     \caption{System Architecture}
+% \end{figure}
 
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=5cm]{images/images_folder_3/conejetexample.png}
-        \caption{cone jet mode}
-    \end{figure}
+% The algorithms implemented in the computer machine was developed in python by another student and it is already collecting data and classifying the spraying dynamics.
+% In Figure 3 and Figure 4 shows pictures took by the high speed camera of some of the possible spraying dynamics we can reach. The videos took by the camera is not being used in the classification
+% algorithm. It is used for manual validation of it.
 
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=5cm]{images/images_folder_3/multijetexample.png}
-        \caption{multi jet mode}
-    \end{figure}
+% \begin{multicols}{2}
 
-\end{multicols}
+%     \begin{figure}[H]
+%         \center
+%         \includegraphics[width=5cm]{images/images_folder_3/conejetexample.png}
+%         \caption{cone jet mode}
+%     \end{figure}
+
+%     \begin{figure}[H]
+%         \center
+%         \includegraphics[width=5cm]{images/images_folder_3/multijetexample.png}
+%         \caption{multi jet mode}
+%     \end{figure}
+
+% \end{multicols}

### 2023-01-18 Documentation/UFMG/Relatorio_3/front_cover/front_cover.tex
Documentation

\begin{titlepage}
    \begin{center}

    {\large Universidade Federal de Minas Gerais\\
    Escola de Engenharia \\
    Curso de Graduação em Engenharia de Controle e Automação\\}
    \vfill

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.5]{images/brasao_ufmg.png}
    \end{figure}
    \vspace{2cm}

    {\bf\Large EHDA closed loop control system based on real time non-visual spray mode classification\\}
    \vspace{1cm} 
    {\Large Relatório de Atividades 3   \\  Projeto Final de Curso}
    \vspace{2cm}

    %\hspace{0.3\textwidth} 
    {\large Orientador: Vitor Angelo\\
            Supervisor: Luewton L F Agostinho}\\

    %\hspace{0.3\textwidth} \parbox{0.65\textwidth}
    {\large Aluno: João Pedro Miranda Marques \\
    Matricula: 2017050495}
    \vspace{2cm}

    \today
    \vspace{2cm}

    %\hspace{0.3\textwidth} 
    \large \date{\today}
    \end{center}

    \end{titlepage}

    \newpage
    \clearpage
    \thispagestyle{empty}

    \cleardoublepage

\title{
    EHDA closed loop control system based on real time non-visual spray mode classification \\
    \large Relatório de Atividades PFC}

### 2023-01-18 Documentation/WT group/article1/main.tex
Documentation

@@
 The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.
+
 		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency.
@@
 The results of the system are discussed and its potential applications in industrial settings are highlighted.
+
+		The beginning of EHDA researches started with Taylor. He noticed that using electric field in liquids small droplets could be created. That dynamics received his name as Taylor Cone jet.
+		After that other scientists such as Willian Gilber, Prunet published about "Electric Modes".
+In the work of Sjaaks\cite{Sjaaks} he could classify the spraying dynamics using non-visual data.
+The data was
+		being collected is the currrent data flowing throught the system.
+However, the automation of the experiment is not very well explored.
+This could bring better knowledge about the experiment since the variables are normally adjusted manually.
+		This work is structured with the goal of .....
+
 		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}.

### 2023-01-19 Documentation/UFMG/Relatorio_3/Development/Development.tex

@@
 
-% \subsection*{3.1 Setup and Routine Algorithm Optimization}
+\subsection*{3.1 Pump Integration}
+
+    The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
+    two main variables that afect the system. 
+    It will bring more complexity for the system since now we are dealing with multivariable control.
+    Fortunatelly those two variables are uncuppled (* be certain of that first *) which means that actuating in one of them will not interfere in the other one.
+    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
+
+    The pump integration was developed using also python language. As I could not find a good library for this pump I developed an quick and easy interface for sending the pump
+    commands to be integrated with the main automation routine. The communication with the pump was made using the serial interface and the commands list were found in the pump user manual.
+
+\subsection*{3.2 First mapping Experiments}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/map2Data.png}
+        \caption{Mapping Experiment data}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/map1.png}
+        \caption{First mapping trial}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/map2.png}
+        \caption{Second mapping trial}
+    \end{figure}
+
+    It was noticed that the motor of the pump in certains speed generate a noise caused by the stepping from the stepper motor.
+    This noise from the motor was being acquired by the current data and was interfering in the classification method.
+    Because of that the firsts results of the map have a lot of undefined or incorrect classifications.
+    This can be reduced inserting a bubble in the syringe to atenuate mechanical noises.
 

### 2023-01-19 Documentation/WT group/article1/main.tex

--- 2023-01-17 Documentation/WT group/article1/main.tex
@@
 	\begin{abstract}
-		\textbf{Electrohydrodynamic Atomization (EHDA)} also known as Electrospray (ES), is a technology that uses a strong electric field (kV/cm) to manipulate liquid breakup into droplets.
-This technique allows the generation of droplets smaller than the nozzle diameter with a controlled droplet size, which means it can be used to produce uniformly sized particles in the micro/nanoscale range.
-This liquid spraying technique can generate different modes when both the liquid flow rate and the voltage vary with a narrow size dispersion.
-The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.
-		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency.
-The system utilizes current data from the experiment to classify the spray mode dynamics in real-time and adjust the EHDA parameters, such as pump flowrate and power supply voltage, to reach the desired spray mode and stabilize it.
+		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency.
+EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size.
+The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it.
 The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods.
-The results of the system are discussed and its potential applications in industrial settings are highlighted.
-		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}.
-Furthermore, the determination of keywords needs to pay attention to important words contained in the title and abstract, separated by a semicolon.
-\textbf{The novelty} in this paper briefly explains why no one else has adequately researched the question.
-Then \textbf{the results} are made a list of the empirical findings and write the discussion in one or two sentences.
-\\ \\
+The potential applications of the system are discussed, including in industrial processes such as spray coating and inkjet printing.
+EHDA has been widely used in various fields such as agriculture, biomedical and energy, specifically in the production of micron- and nano-size droplets for better control and efficient in the process.
+
 		\let\thefootnote\relax\footnotetext{

### 2023-01-19 software/classification_electrospray.py
concatenate classifications

@@ -9,6 +9,7 @@ import math
 
 
 class ElectrosprayClassification:
+    
     def __init__(self, name_liquid):
         self.name_liquid = name_liquid
         self.all_data = []
@@ -19,6 +20,7 @@ class ElectrosprayClassification:
         self.sjaak_verified = []
         self.sjaak_verified_false = []
         self.sjaak_verified_true = []
+        self.previous_state = "Dripping"
 
         self.data_points_list = 0
         self.electrical_conductivity = 0
@@ -30,100 +32,162 @@ class ElectrosprayClassification:
         self.density = 0
 
 
-    def do_sjaak(self, mean, median, stddeviation, psd_values, variance):
+
+
+    def do_classification(
+            self,
+            mean,
+            median,
+            stddeviation,
+            psd_values,
+            variance,
+            max_value_of_the_data,
+            quantity_max_data,
+            percentage_max,
+            flow_rate,
+            fft_max_peaks_array,
+            cont_fft_max_peaks):
+
         self.med_value_array.append(median)
-        sjaak_classification_txt = ""
+        classification_txt = ""
 
-        if mean != 0:
-            self.sjaak_std_mean = (stddeviation / mean)
-            # print("std/mean = %f ;" % (self.sjaak_std_mean))
-        else:
-            self.sjaak_std_mean = 0
-        self.sjaak_std_mean_array.append(self.sjaak_std_mean)
 
-        if median != 0:
-            self.sjaak_mean_median = (mean / median)
-            # print('sjaak_mean_median: ', self.sjaak_mean_median)
-        else:
-            self.sjaak_mean_median = 0
-        self.sjaak_mean_median_array.append(self.sjaak_mean_median)
+        #
+        #       SJAAKS  -> Is capable of classifiying Dripping, Intermittent and Cone Jet
+        #
 
-        # classification for dripping
-        # if mean <= 5:
-        if self.sjaak_std_mean > 2.5:
-            sjaak_classification_txt = "Dripping"
-            if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
-                # logging.info("Dripping Sjaak")
-                # print("classification dripping confirmed!")
-                sjaak_classification_txt = "Dripping"
-
-        # classification for intermittent
-        # if mean > 5:
-        if (self.sjaak_std_mean) < 2.5 and self.sjaak_std_mean > 0.5:
-            # print("intermittent Sjaak!")
-            sjaak_classification_txt = "Intermittent"
[…]

### 2023-01-19 software/data_processing.py

@@ -70,21 +70,12 @@ def data_processing(data_queue,
 
         try:
 
-            classification_sjaak = electrospray_classification.do_sjaak(
+            classification_txt = electrospray_classification.do_classification(
                                                                         electrospray_processing.mean_value,
                                                                         electrospray_processing.med,
                                                                         electrospray_processing.stddev,
                                                                         electrospray_processing.psd_welch,
-                                                                        electrospray_processing.variance
-                                                                        )
-        except:
-            print("[DATA_PROCESSING THREAD] Failed to sjaak classify")
-            sys.exit(1)
-
-        try:
-
-
-            classification_monica = electrospray_classification.do_monica(
+                                                                        electrospray_processing.variance,
                                                                         float(max_data), 
                                                                         float(quantity_max_data),
                                                                         float(percentage_max),
@@ -92,23 +83,18 @@ def data_processing(data_queue,
                                                                         max_fft_peaks,
                                                                         cont_max_fft_peaks
                                                                         )
-
-
         except:
-            print("[DATA_PROCESSING THREAD] Failed to monica classify")
+            print("[DATA_PROCESSING THREAD] Failed to classify")
             sys.exit(1)
+
 
         try:
 
-            txt_sjaak_str = str(classification_sjaak)
-            txt_monica_str = str(classification_monica)
+            txt_sjaak_str = str(classification_txt)
 
-            current_shape = {
-                "Sjaak":  str(classification_sjaak),
-                "Monica": str(classification_monica),
-            }
+            current_shape = str(classification_txt),
 
-            feedback_queue.put(str(classification_sjaak))
+            feedback_queue.put(str(classification_txt))
 
             electrospray_processing.set_shape(current_shape)
 
@@ -117,7 +103,7 @@ def data_processing(data_queue,
             electrospray_processing.calculate_fft_filtered()
             electrospray_processing.calculate_fft_peaks()
 
-            if current_shape["Sjaak"] == "cone jet" and FLAG_PLOT:
+            if current_shape == "cone jet" and FLAG_PLOT:
                 electrospray_validation.set_data_from_dict_liquid(electrospray_config_liquid_setup_obj.get_json_liquid())
 
                 electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data, electrospray_processing.mean_value, electrospray_data.flow_rate)

### 2023-01-20 data_analysis/mapping/classification_electrospray.py
Data Analysis and Documentation

@@ -1,0 +1,327 @@
+import itertools
+import os
+import re
+from typing import TextIO
+import logging
+import numpy as np
+import json
+import math
+
+
+class ElectrosprayClassification:
+    
+    def __init__(self, name_liquid):
+        self.name_liquid = name_liquid
+        self.all_data = []
+        self.sjaak_std_mean_array = []
+        self.sjaak_mean_median_array = []
+        self.med_value_array = []
+        self.mean_value_array = []
+        self.sjaak_verified = []
+        self.sjaak_verified_false = []
+        self.sjaak_verified_true = []
+        self.previous_state = "Dripping"
+
+        self.data_points_list = 0
+        self.electrical_conductivity = 0
+        self.surface_tension = 0
+        self.dieletric_const = 0
+        self.electrical_conductivity = 0
+        self.permitivity = 0
+        self.rho = 0
+        self.density = 0
+
+
+
+
+    def do_classification(
+            self,
+            mean,
+            median,
+            stddeviation,
+            psd_values,
+            variance,
+            max_value_of_the_data,
+            quantity_max_data,
+            percentage_max,
+            flow_rate,
+            fft_max_peaks_array,
+            cont_fft_max_peaks):
+
+        self.med_value_array.append(median)
+        classification_txt = "Undefined"
+
+
+        #
+        #       SJAAKS  -> Is capable of classifiying Dripping, Intermittent and Cone Jet
+        #
+
+        try:
+                
+            if mean != 0:
+                self.sjaak_std_mean = (stddeviation / mean)
+                # print("std/mean = %f ;" % (self.sjaak_std_mean))
+            else:
+                self.sjaak_std_mean = 0
+            self.sjaak_std_mean_array.append(self.sjaak_std_mean)
+
+            if median != 0:
+                self.sjaak_mean_median = (mean / median)
+                # print('sjaak_mean_median: ', self.sjaak_mean_median)
+            else:
+                self.sjaak_mean_median = 0
+            self.sjaak_mean_median_array.append(self.sjaak_mean_median)
+
+            # classification for dripping
+            # if mean <= 5:
+            if self.sjaak_std_mean > 2.5:
+                classification_txt = "Dripping"
+                if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
[…]

### 2023-01-20 data_analysis/mapping/map_analysis.py

@@ -1,7 +1,7 @@
 '''
-	JSON Data analysis from the experiments
+	Analysis of mapping V x FR experiments
 	AUTHOR: 乔昂 - jueta
-	DATE: 24/11/2022
+	DATE: 19/01/2023
 '''
 
 import pandas as pd
@@ -16,9 +16,9 @@ from scipy.signal import butter, lfilter
 # warnings.filterwarnings('ignore')
 sampling_frequency = 1e5
 
-file_path = "joaoData/mapping/"
+file_path = "../Data/mapping/"
 
-file_name = "map1"
+file_name = "map3"
 
 
 with open(file_path + file_name + ".json", 'r') as data_file:    
@@ -36,10 +36,13 @@ processing_data_window = pd.json_normalize(data['processing'])
 data_window = [measurements_data_window, processing_data_window]
 data_window = pd.concat(data_window, axis=1)
 
+
+print(data_window.head())
+
 colors = {'Cone Jet':'red', 'Dripping':'green', 'Intermittent':'blue', 'Multi Jet':'purple', 'Undefined':'black', 'Corona':'cyan'}
 
 colormap = []
-for electro_class in data_window['spray mode.Sjaak']:
+for electro_class in data_window['spray mode']:
     if electro_class == 'Intermittent':
         colormap.append('blue')
     elif electro_class == 'Cone Jet':
@@ -52,21 +55,22 @@ for electro_class in data_window['spray mode.Sjaak']:
         colormap.append('cyan')
     elif electro_class == 'Undefined':
         colormap.append('black')
-    else:
-        colormap.append('black')
+    # else:
+    #     colormap.append('black')
 
-# Monica spark classification
-sampleIndex = 0
-for monica_class in data_window['spray mode.Monica']:
-    if monica_class == 'streamer onset':
-        colormap[sampleIndex] = 'cyan'
-    sampleIndex+=1
+# # Monica spark classification
+# sampleIndex = 0
+# for monica_class in data_window['spray mode.Monica']:
+#     if monica_class == 'streamer onset':
+#         colormap[sampleIndex] = 'cyan'
+#     sampleIndex+=1
 
 
 
 data_window.insert(1, 'colormap', colormap)
 
 print(data_window.info())
+print(data_window.head())
 
 
 

### 2023-01-20 data_analysis/mapping/map_analysis2.py

@@ -1,0 +1,55 @@
+'''
+	Analysis of mapping V x FR experiments
+	AUTHOR: 乔昂 - jueta
+	DATE: 19/01/2023
+'''
+
+import pandas as pd
+from pandas.io.json import json_normalize
+import json
+import matplotlib.pyplot as plt
+from sklearn.utils import column_or_1d
+import numpy as np
+from scipy.signal import butter, lfilter
+
+
+# warnings.filterwarnings('ignore')
+sampling_frequency = 1e5
+
+file_path = "../Data/mapping/"
+
+file_name = "map3"
+
+
+data = pd.read_feather("map3.feather")
+
+colormap = []
+for electro_class in data['spray mode']:
+    if electro_class == 'Intermittent':
+        colormap.append('blue')
+    elif electro_class == 'Cone Jet':
+        colormap.append('red')
+    elif electro_class == 'Dripping':
+        colormap.append('green')
+    elif electro_class == 'Multi Jet':
+        colormap.append('purple')
+    elif electro_class == 'Corona':
+        colormap.append('cyan')
+    elif electro_class == 'Undefined':
+        colormap.append('black')
+    else:
+        colormap.append('black')
+
+
+data.insert(1, 'colormap', colormap)
+
+print(data.info())
+print(data.head())
+
+
+data['flow rate [m3/s]'] = data['flow rate [m3/s]'].astype(float)
+plt.scatter(data['flow rate [m3/s]'], data['target voltage'], color=data['colormap'])
+plt.ylabel('Voltage [V]')
+plt.xlabel('Flow Rate [uL/min]')
+plt.title("colors = {'Cone Jet':'red', 'Dripping':'green', 'Intermittent':'blue', 'Multi Jet':'purple', 'Undefined':'black', 'Corona':'cyan'}")
+plt.show()

### 2023-01-20 data_analysis/mapping/processing.py

@@ -1,0 +1,177 @@
+'''
+	Non Real Time Processing the data
+	AUTHOR: 乔昂 - jueta
+	DATE: 19/01/2023
+'''
+
+import pandas as pd
+from pandas.io.json import json_normalize
+import json
+import matplotlib.pyplot as plt
+from sklearn.utils import column_or_1d
+import numpy as np
+from scipy.signal import butter, lfilter
+from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig
+from classification_electrospray import ElectrosprayClassification
+
+# tiepie params
+sampling_frequency = 1e5  # 100 KHz
+multiplier_for_nA = 500
+
+append_array_data = True
+append_array_processing = True
+FLAG_PLOT = True
+
+
+
+# warnings.filterwarnings('ignore')
+sampling_frequency = 1e5
+
+file_path = "../Data/mapping/"
+
+file_name = "map3"
+
+electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
+electrospray_classification = ElectrosprayClassification("name_liquid")
+
+array_electrospray_processing = []
+array_values = []
+
+
+data = pd.read_feather("map3.feather")
+
+
+
+#
+#
+#
+#
+#
+
+# time_step = 1 / sampling_frequency
+
+# # THREAD LOOP
+# for data_queue in data['data [nA]']:
+
+
+#     electrospray_data  = data_queue 
+
+#     try:
+
+#         # low pass filter to flatten out noise
+#         cutoff_freq_normalized = 3000 / (0.5 * sampling_frequency)  # in Hz
+#         b, a = butter(6, Wn=cutoff_freq_normalized, btype='low', analog=False)  # first argument is the order of the filter
+#         datapoints_filtered = lfilter(b, a, electrospray_data)
+
+#     except:
+#         print("[DATA_PROCESSING THREAD] Failed to filter points!")
+
+#     try:
+
+#         electrospray_processing.calculate_filter(a, b, electrospray_data)
+        
+#         electrospray_processing.calculate_fft_raw(electrospray_data)
+
+#         electrospray_processing.calculate_statistics( electrospray_data)
+        
+#         electrospray_processing_freq, electrospray_processing_psd = electrospray_processing.calculate_power_spectral_density(electrospray_data)
+
+#         max_data, quantity_max_data, percentage_max = electrospray_processing.calculate_peaks_signal(electrospray_data)
+
[…]

### 2023-01-20 Documentation/WT group/article1/main.tex
documentation

@@
 	\begin{abstract}
-		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency.
+		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industries applications.
 		EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size.
 		The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it.
-The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods.
-The potential applications of the system are discussed, including in industrial processes such as spray coating and inkjet printing.
-EHDA has been widely used in various fields such as agriculture, biomedical and energy, specifically in the production of micron- and nano-size droplets for better control and efficient in the process.
+		The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous manual methods.
+		The potential applications of the system are discussed, including in industrial processes such as spray coating and gas odorizing.
 
@@
 		}
-		\textbf{\textit{Keywords}}: \textit{Keyword 1; keyword 2; keyword 3; keyword 4; keyword 5}
+		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; keyword 4; keyword 5}
 	\end{abstract}
@@
 
-\section{Introduction (10pt, bold)}
+\section{Introduction (10pt, bold)  --> Do Luewtons Timeline}
 The introduction is about 400-600 words and provides background information, previous references related to the main topic, reason, purpose of the research, and the novelty of the research.

### 2023-01-26 software/data_acquisition.py
exp-26-01

@@ -32,6 +32,7 @@ def data_acquisition(data_queue,
         baudrate=9600,
         timeout=0.1
     )
+    arduino_port.write(bytes('1', 'utf-8'))
 
     #           OSCILLOSCOPE
     # print_library_info()

### 2023-01-26 software/mainElectrospray.py

@@ -82,10 +82,10 @@ if __name__ == '__main__':
 # # # **************************************
 
     threads = list()
-    controller_output_queue = queue.Queue(maxsize=3000)
-    feedback_queue = queue.Queue(maxsize=3000)
-    data_queue = queue.Queue(maxsize=3000)
-    plotting_data_queue = queue.Queue(maxsize=3000)
+    controller_output_queue = queue.Queue(maxsize=100000)
+    feedback_queue = queue.Queue(maxsize=100000)
+    data_queue = queue.Queue(maxsize=100000)
+    plotting_data_queue = queue.Queue(maxsize=100000)
 
 
     # 

### 2023-01-26 Documentation/UFMG/Relatorio_3/Development/Development.tex
Documentation

@@
 
-%     About the python algorithm to turn the experiment autonomous it was made a study and modelling of the software architecture to optimize it 
-%     for further control loop application to be implemented.
-%     From the changes made until now it highlights:
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/map3.png}
+        \caption{map3}
+    \end{figure}
 
-%     - Integrate high speed camera to the experiment routine.
+\subsection*{3.3 Capacitance of the system in step response}
 
-%     - Remodel the software to support threads in order to separate the sensoring and controlling routines.
+    We were discussing if the voltage step implies in a transient state in the current acquired.
+    If yes, the data acquired in this transient should not be used in the classification step. Since we want to analise
+    the spraying in a constant dynamics.
 
-%     - Reduce the data collected size.
+    \begin{multicols}{2}
 
-%     - Synchronize the power supply step commands and voltage sensoring.
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=8cm]{images/idea.png}
+            \caption{ map3 reproccessed data head }
+        \end{figure}
 
-%     - Reestructure the setup file in order to make it more intuitive to use the experiment.
+        For that I reproccessed all raw data acquired cutting the head of the data window. The new classification map is showed in the figure 10.
 
-%     - Improvements in code organization and readability.
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=8cm]{images/map3_reproccessed_data_head.png}
+            \caption{ map3 reproccessed data head }
+        \end{figure}
 
-%     About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to make the experiment 
-%     the most stable and easy to reach cone-jet mode as possible.
-%     For example, while doing experiments we discovered that the frequency of the pump machine internal motors was
-%     creating an interference in the flowrate. Therefore compromising the stabilization in cone jet mode.
-%     A solution for that was to increase the flowrate wich smooths this pumping noise. For that was also necessary
-%     to increase the nozzle diameter to balance with all other variables from the experiment.
+        Also tested cutting the tail of the data window to see if have improvements in the classification.
 
-% \subsection*{3.2 Experiment 1}
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=8cm]{images/map3_reproccessed_data_tail.png}
+            \caption{ map reproccessed data tail }
+        \end{figure}
 
-%     This first experiment was made using the setup:
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=8cm]{images/data_samples.png}
+            \caption{ USE ANOTHER IMAGE WITH STABLE SAMPLES OR DELETE THIS ONE }
+        \end{figure}
 
-%     - liquid: water60alcohol40
+    \end{multicols}
 
-%     - flow rate min: 1.45 mL/hr
+    {TRY TO PUT STEP RESPONSE OF THE POWER SUPPLY HERE}
 
-%     - config: nozzle to plate
+    CONCLUSION: Does not made much difference. For steps under 250V the system does not show a transition dynamic. 
+    With steps above 250V the capacitance of the system reacts with a capacitance curve.
 
-%     - nozzle to plate or ring distance: 1.5 cm
+\subsection*{3.4 Manual x Automatic Cone Jet stability island maps}
 
-%     - nozzle diameter: 0.136 mm
+    Metodology
 
-%     In Figure 5 we can see 5 graphs:
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=14cm]{joao_26-01-22/screenshots/stableConeExp.png}
+        \caption{exp 24}
+    \end{figure}
 
-%     1 - current values measured by the oscilloscope. As it is a lot of data it is compressed in the figure.
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=8cm]{joao_26-01-22/epx_24-01.png}
+        \caption{exp 24}
+    \end{figure}
 
-%     2 - Voltage step sequence in order to evaluate the dynamics in each high voltage level.
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=8cm]{joao_26-01-22/exp25-01-1.png}
+        \caption{ exp25-01-1 }
+    \end{figure}
 
-%     3,4,5 - Statistical values measured by each window of 0.5s of data collected. This values will be used in the classification algorithm.
-%     Those values are already classified by colour and the legend is showed below.
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=8cm]{joao_26-01-22/exp-26-01-1.png}
+        \caption{ exp-26-01-1 }
+    \end{figure}
 
-%     LEGEND:
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=8cm]{joao_26-01-22/exp26-01-2.png}
+        \caption{ exp-26-01-2 }
+    \end{figure}
 
-%     - Green = Dripping
+\subsection*{3.5 Temperature and Humidity influences}
 
-%     - Blue =  Intermittend
-
-%     - Red = Cone Jet mode
-
-%     - Purple = Streamer Onset (high current values)
-
-%     - Black = Undefined
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=17cm]{images/images_folder_2/img1.png}
-%         \caption{Data acquired in the experiment 1 - liquid: Water AND alcohol}
-%     \end{figure}
-
-%     In Figure 6 and 7 we can see one data window sample of dripping and one of cone jet dynamics. There are two graphs. The first one its
-%     the current datapoints filtered by a ideal low pass butterworth filter. In the second graph we can see the module of the fast fourier transform real values.
-
-%     We can see in Figure 6 that there were two droplets expelled by the nozzle. This can be seen as the two signal waves in the current value and the amount of frequencies seen in the second graph.
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=12cm]{images/images_folder_2/img2.png}
-%         \caption{Dripping sample}
-%     \end{figure}
-
-%     We can see in Figure 7 that the current signal is more stable and also with an offset current arround 100nA showing that the spray is in cone jet mode.
-Also seen as the 0 Hz DC component value in the frequency domain graph.
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=12cm]{images/images_folder_2/img3.png}
-%         \caption{Cone jet sample}
-%     \end{figure}
-
-%     Other interesting grahps exposed in Sjaaks\cite*[]{Sjaaks} paper is correlating statistical values relations to each voltage step and classification.
-This is also good to evaluate the separability of each classification method.
-%     Those graphs can be seen in Figures 8, 9 and 10.
-
-%     \begin{multicols}{3}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph1.png}
-%             \caption{mean current X voltage}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph2.png}
-%             \caption{deviation/mean}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data2_sjaaksgraph3.png}
-%             \caption{mean/median}
-%         \end{figure}
-
-%     \end{multicols}
-
-% \subsection*{3.3 Experiment 2}
-
-% In this experiment the liquid was changed in order to have a bigger voltage range in the cone jet mode. Which is the most valuable mode in this project.
-
-%     - liquid: ethanol pure
-
-%     - flow rate min: 1.5 mL/hr
-
-%     - camera to nozzle distance: 16.5 cm
-
-%     - config: nozzle to plate
-
-%     - nozzle to plate or ring distance: 1.5 cm
-
-%     - nozzle diameter: 0.136 mm
-
-%     - type of measurement:
-
-%         * voltage start: 3000 V
-
-%         * voltage stop: 10000 V
-
-%         * step size: 100 V
-
-%         * step time: 5 s
-
-%     In Figure 11, the data is well classified but it also have a noise in the system that can been seen in the peak current values.
-%     Those peaks can be seen in all the voltage ranges in this experiment and also have similar distances in beetween the peaks. This is probably caused by
-%     external interference but it is still not certain what is it about.
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=17cm]{images/images_folder_3/data3.png}
-%         \caption{Data acquired in the experiment 2 - pure ethanol}
-%     \end{figure}
-
-%     The Figure 12 shows the same current x time graph but with a zoom in y axis in order to see the signal steps in the experiment.
-It is also classified by the same color legend as all graphs in this overview.
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=15cm]{images/images_folder_3/data3current.png}
-%         \caption{current graph with classification}
-%     \end{figure}
-
-%     The Figures 13, 14 and 15 shows graphs with statistical realations in the data.
-
-%     \begin{multicols}{3}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph1.png}
-%             \caption{current mean X voltage}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph2.png}
-%             \caption{deviation/mean}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data3_sjaaksgraph3.png}
-%             \caption{mean/median}
-%         \end{figure}
-
-%     \end{multicols}
-
-% \subsection*{3.4 Experiment 3}
-
-%     - liquid: ethanol pure
-
-%     - flow rate min: 1.5 mL/hr
-
-%     - camera to nozzle distance: 16.5 cm
-
-%     - config: nozzle to plate
-
-%     - nozzle to plate or ring distance: 1.5 cm
-
-%     - nozzle diameter: 0.136 mm
-
-%     - type of measurement:
-
-%         * voltage start: 3000 V
-
-%         * voltage stop: 11000 V
-
-%         * step size: 50 V
-
-%         * step time: 1 s
-
-%     \begin{figure}[H]
-%         \center
-%         \includegraphics[width=17cm]{images/images_folder_3/data4.png}
-%         \caption{Data acquired in the experiment 3 - pure ethanol}
-%     \end{figure}
-
-%     \begin{multicols}{3}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph1.png}
-%             \caption{current mean X voltage}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph2.png}
-%             \caption{deviation/mean}
-%         \end{figure}
-
-%         \begin{figure}[H]
-%             \center
-%             \includegraphics[width=5cm]{images/images_folder_3/data4_sjaakgraph3.png}
-%             \caption{mean/median}
-%         \end{figure}
-
-%     \end{multicols}
+    - Started collecting temperature and humidity values for each sample using arduino and DHT11 sensor from adafruit.
+    - Closed the system and sprayed pure oxygen O2 to decrease the humidity of the system.

### 2023-01-30 Documentation/UFMG/Relatorio_3/Development/Development.tex
Documentation

@@
 
-\subsection*{3.1 Pump Integration}
+    The following subsections are about the work done in this 3rd part of the project.
+
+\subsection*{2.1 Pump Integration}
 
@@
     It will bring more complexity for the system since now we are dealing with multivariable control.
-    Fortunatelly those two variables are uncuppled (* be certain of that first *) which means that actuating in one of them will not interfere in the other one.
     Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
+    Our control model is now a MISO\footcite{MISO: Multiple Inputs Single Output} system. The crossover (couple) between the controlled variables will be evaluated in further reports.
 
-    The pump integration was developed using also python language. As I could not find a good library for this pump I developed an quick and easy interface for sending the pump
-    commands to be integrated with the main automation routine. The communication with the pump was made using the serial interface and the commands list were found in the pump user manual.
+    About the pump interface. As I could not find a good ready-to-use library for this pump I developed an simple and intuitive interface to be our software routine.
+    The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
 
-\subsection*{3.2 First mapping Experiments}
+\subsection*{2.2 Exploring Flowrate}
+
+    As a first test with the new controlled variable, Flowrate a new procedure was developed.
+With the goal to scan the stability region of the cone jet mode through the voltage and flowrate variables.
+    This procedure was implemented in the controller thread routine as a new sequence that can be configured in the setup file before an experiment.
+    The algorithm of this sequence in the controller thread is shown bellow.
+
+    \begin{algorithm}
+        \caption{MAP sequence in controller thread}\label{alg:cap}
+        \begin{algorithmic}
+        \Procedure{MAP}{$flowrate\textunderscore values$} 
+            \ForAll{flowrate\textunderscore values}  \Comment{scanning in the flowrate range}
+                \State \Call{send\textunderscore flowrate\textunderscore command}{flowrate}
+                \State $voltage \gets voltage\textunderscore start$
+                \While{$voltage \leq voltage\textunderscore stop$} \Comment{scanning in the voltage range}
+                    \State \Call{send\textunderscore voltage\textunderscore command}{voltage}
+                    \State \Call{sleep}{step \textunderscore time}
+                    \State $voltage \gets voltage + step\textunderscore size$
+                \EndWhile
+            \EndFor
+        \EndProcedure
+
+        \end{algorithmic}
+    \end{algorithm}
+
+    In the figures 5 and 6 we can see the results of this mapping experiments. The liquid used is pure ethanol. 
+    Each figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
+    The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
+    The third graph shows the current mean value of each data sample.
+    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.
 
@@
         \includegraphics[width=15cm]{images/map2Data.png}
-        \caption{Mapping Experiment data}
+        \caption{Mapping Experiment example 1 }
     \end{figure}
@@
         \center
-        \includegraphics[width=15cm]{images/map1.png}
+        \includegraphics[width=15cm]{joao_26-01-22/graphs-exp-26-01.png}
+        \caption{Mapping Experiment example 2}
+    \end{figure}
+
+\subsection*{2.3 Manual experiments}
+
+    For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
+    Also in order to find the stability region of cone jet mode for the liquid and setup used.
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=12cm]{joao_26-01-22/exp25-01-1.png}
+            \caption{ exp25-01-1 (V x Q)}
+        \end{figure}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=12cm]{joao_26-01-22/exp-26-01-1.png}
+            \caption{ exp-26-01-1 (V x Q)}
+        \end{figure}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=12cm]{joao_26-01-22/exp26-01-2.png}
+            \caption{ exp-26-01-2 (V x Q)}
+        \end{figure}
+
+\subsection*{2.4 Automatic experiments}
+
+    With the desired voltage and flowrate range defined for the automatic experiment the next part is to define how many datapoints will be collected in both
+    x and y axis. Since we are introducing a new dimension for our experiment it is also increasing fast the amount of data collected.
+    The goal of this part is to find the ideal combination of voltage step size, voltage step time and flowrate step size in order to get the most accurate results without exceding the separate memory for each experiment.
+
+    In the further improvements of the routine it's ideal to apply a real time file writing with all experiment data.
+    This will prevent that any crashes in the program lose all data and not overflow the memory allocated for the program.
+
+    \begin{multicols}{3}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=5cm]{images/map1.png}
             \caption{First mapping trial}
@@
             \center
-        \includegraphics[width=15cm]{images/map2.png}
+            \includegraphics[width=5cm]{images/map2.png}
             \caption{Second mapping trial}
@@
 
-    It was noticed that the motor of the pump in certains speed generate a noise caused by the stepping from the stepper motor.
-    This noise from the motor was being acquired by the current data and was interfering in the classification method.
-    Because of that the firsts results of the map have a lot of undefined or incorrect classifications.
-    This can be reduced inserting a bubble in the syringe to atenuate mechanical noises.
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=6cm]{images/map3.png}
+            \caption{third map - better result}
+        \end{figure}
+
+    \end{multicols}
+
+\subsection*{2.5 Manual x Automatic Cone Jet stability island maps}
+
+    For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.
+
+    The Figure 13 shows a printscreen of how the experiment looks like in real time.
+    We can see the image generated by the camera in the back.
+    The routine code running in pycharm software on the right.
+    And also real time signal plottings of the current data on the left.
 
@@
         \center
-        \includegraphics[width=15cm]{images/map3.png}
-        \caption{map3}
+        \includegraphics[width=17cm]{joao_26-01-22/screenshots/stableConeExp.png}
+        \caption{running experiment print screen}
     \end{figure}
 
-\subsection*{3.3 Capacitance of the system in step response}
+    In Figure 14 we can see a result of the map generated by the automatic classification in this experiment.
 
-    We were discussing if the voltage step implies in a transient state in the current acquired.
-    If yes, the data acquired in this transient should not be used in the classification step. Since we want to analise
-    the spraying in a constant dynamics.
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=10cm]{joao_26-01-22/map-exp-26-01.png}
+        \caption{ exp-26-01-23 }
+    \end{figure}
+
+    \pagebreak
+
+    Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
 
@@
             \center
-            \includegraphics[width=8cm]{images/idea.png}
-            \caption{ map3 reproccessed data head }
-        \end{figure}
-
-        For that I reproccessed all raw data acquired cutting the head of the data window. The new classification map is showed in the figure 10.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/map3_reproccessed_data_head.png}
-            \caption{ map3 reproccessed data head }
-        \end{figure}
-
-        Also tested cutting the tail of the data window to see if have improvements in the classification.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/map3_reproccessed_data_tail.png}
-            \caption{ map reproccessed data tail }
+            \includegraphics[width=9cm]{joao_26-01-22/manual-mapping.png}
+            \caption{ exp-26-01 manual classification}
         \end{figure}
@@
             \center
-            \includegraphics[width=8cm]{images/data_samples.png}
-            \caption{ USE ANOTHER IMAGE WITH STABLE SAMPLES OR DELETE THIS ONE }
+            \includegraphics[width=9cm]{joao_26-01-22/map4-stabilityIsland.png}
+            \caption{ exp-26-01 automatic classification}
         \end{figure}
@@
 
-    {TRY TO PUT STEP RESPONSE OF THE POWER SUPPLY HERE}
+\subsection*{2.6 Pump machine and stepper motor noise}
 
-    CONCLUSION: Does not made much difference. For steps under 250V the system does not show a transition dynamic. 
-    With steps above 250V the capacitance of the system reacts with a capacitance curve.
+    It was noticed that the motor of the pump in certains speed generate a noise caused by the stepping from the stepper motor.
+    This noise from the motor was being acquired by the current data and was interfering in the classification method.
+    Because of that the firsts results of the map have a lot of undefined or incorrect classifications.
+    This can be reduced inserting a air bubble in the syringe to atenuate mechanical noises applied.
+    Also was found a command that can be send to the pump machine to activate microstepping in the stepper motor.
+    Both of this changes were made in order to add the pump machine to the system.
 
-\subsection*{3.4 Manual x Automatic Cone Jet stability island maps}
+\subsection*{2.7 Capacitance of the system in step response}
 
-    Metodology
+    We had discussions if the voltage step implies in a transient state in the current acquired.
+    If yes, the data acquired in this transient should not be used in the classification step. Since we want to analise
+    the spraying in a constant dynamics.
 
+    For that I reproccessed all raw data acquired cutting the head of the data window. The new classification map is showed in the figure 10.
+    Also tested cutting the tail of the data window to see if have improvements in the classification.
+
+    \begin{multicols}{2}
         \begin{figure}[H]
             \center
-        \includegraphics[width=14cm]{joao_26-01-22/screenshots/stableConeExp.png}
-        \caption{exp 24}
+            \includegraphics[width=7cm]{images/map3_reproccessed_data_head.png}
+            \caption{ map3 reproccessed data head }
         \end{figure}
@@
             \center
-        \includegraphics[width=8cm]{joao_26-01-22/epx_24-01.png}
-        \caption{exp 24}
+            \includegraphics[width=7cm]{images/map3_reproccessed_data_tail.png}
+            \caption{ map reproccessed data tail }
         \end{figure}
+
+    \end{multicols}
+
+    After noticing that cutting out the data collected in the transient of the step voltage did not bring any improvements to the classification.
+    In the Figure 20 we see 3 random samples of current data in the experiment and there's no transient shown in the current data.
 
@@
         \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp25-01-1.png}
-        \caption{ exp25-01-1 }
+        \includegraphics[width=8cm]{images/random_samples.png}
+        \caption{ 3 samples of current data }
     \end{figure}
 
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp-26-01-1.png}
-        \caption{ exp-26-01-1 }
-    \end{figure}
+    As a conclusion of this discussion we got that with voltage steps under 250V the system does not show a transition dynamic. 
+    For steps above this value we can see a capacitance curve in the current data. This is explained by the system capacitance which resists to fast changes in eletric potential.
+    This treshold value of 250V will vary depending on the resultant capacitance of setup used.
 
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp26-01-2.png}
-        \caption{ exp-26-01-2 }
-    \end{figure}
+\subsection*{2.8 Temperature and Humidity influences}
 
-\subsection*{3.5 Temperature and Humidity influences}
-
-    - Started collecting temperature and humidity values for each sample using arduino and DHT11 sensor from adafruit.
-    - Closed the system and sprayed pure oxygen O2 to decrease the humidity of the system.
+    During this time it was noticed that breaks in beetween the experiments was getting different results for the same setup. This can be caused by the temperature and humidity effects on the system.
+    For that I included the sensor DHT11 in the system setup and software routine to collect data of this two variables.
+Also closed the system chamber and sprayed pure oxygen O2 to decrease the humidity inside.

### 2023-01-30 data_analysis/mapping/map_analysis2.py

@@ -18,33 +18,32 @@ sampling_frequency = 1e5
 
 file_path = "../Data/mapping/"
 
-file_name = "map3"
+
+data = pd.read_feather("map4.feather")
+
+# colormap = []
+# for electro_class in data['spray mode']:
+#     if electro_class == 'Intermittent':
+#         colormap.append('blue')
+#     elif electro_class == 'Cone Jet':
+#         colormap.append('red')
+#     elif electro_class == 'Dripping':
+#         colormap.append('green')
+#     elif electro_class == 'Multi Jet':
+#         colormap.append('purple')
+#     elif electro_class == 'Corona':
+#         colormap.append('cyan')
+#     elif electro_class == 'Undefined':
+#         colormap.append('black')
+#     else:
+#         colormap.append('black')
 
 
-data = pd.read_feather("map3.feather")
-
-colormap = []
-for electro_class in data['spray mode']:
-    if electro_class == 'Intermittent':
-        colormap.append('blue')
-    elif electro_class == 'Cone Jet':
-        colormap.append('red')
-    elif electro_class == 'Dripping':
-        colormap.append('green')
-    elif electro_class == 'Multi Jet':
-        colormap.append('purple')
-    elif electro_class == 'Corona':
-        colormap.append('cyan')
-    elif electro_class == 'Undefined':
-        colormap.append('black')
-    else:
-        colormap.append('black')
-
-
-data.insert(1, 'colormap', colormap)
+# data.insert(1, 'colormap', colormap)
 
 print(data.info())
 print(data.head())
+
 
 
 data['flow rate [m3/s]'] = data['flow rate [m3/s]'].astype(float)

### 2023-01-31 Documentation/UFMG/Relatorio_3/Summary/Summary.tex
report 3

@@
 Industrial applications demand automated stabilization of a spray mode.
-This can be achieved by a closed-loop control system.
+This can be achieved by a closed-loop control system. Figure 2 shows the control model implemented in this project.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=14cm]{images/software-design.png}
+    \caption{Control model implemented in software}
+\end{figure}
+
+The setup used for this project can be seen in the Figure 3 and 4.
+To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera
+and also the system actuators which is represented by the high voltage power supply and the syringe pump.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=10cm]{images/system_setup.png}
+    \caption{System Diagram}
+\end{figure}
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=14cm]{images/system-design.png}
+    \caption{System Automation Diagram}
+\end{figure}
+
 Automated classification of the spray mode is a crucial part of a control system same as the development of an appropriate control algorithm. 
@@
 Further research is necessary to improve the classification accuracy and research and implementation of a suitable classification algorithm. 
-Because of that, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to match analysis possibilities with knowledge and infrastructure availability.
-
-The setup used for this project can be seen in the Figure 2.
-To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera
-and also the system actuators which is represented by the high voltage power supply and the syringe pump.
-
-% \begin{figure}[H]
-%     \center
-%     \includegraphics[width=12cm]{images/images_folder_1/system_design.png}
-%     \caption{System Architecture}
-% \end{figure}
+Because of that, this work is being done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to match analysis possibilities with knowledge and infrastructure availability.
 

### 2023-02-02 Documentation/WT group/article1/main.tex
new abstract

@@
 	\begin{abstract}
-		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industries applications.
-		EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size.
-		The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it.
+
+			We present a closed-loop control system for Electrohydrodynamic Atomization (EHDA) systems that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industrial applications.
+		EHDA is a liquid atomization technique which, by using a high electric field, tiny charged droplets, much smaller than the nozzle diameter, can be generated with a controlled droplet size. 
+		The system uses real-time acquired data to classify the spray mode dynamics and adjusts EHDA operation parameters such as liquid flowrate and applied voltage to reach the desired spray mode maintain it stable.
 		The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous manual methods. 
-		The potential applications of the system are discussed, including in industrial processes such as spray coating and gas odorizing.
+		The potential applications of the system are discussed, including industrial processes such as spray coating and gas odorization.
 
@@
 		}
-		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; keyword 4; keyword 5}
+		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; Electrospray mode classification}
 	\end{abstract}

### 2023-02-02 software/data_processing.py
saving in real time thread

@@ -18,7 +18,8 @@ def data_processing(data_queue,
                     array_electrospray_processing,
                     electrospray_classification,
                     electrospray_validation,
-                    feedback_queue
+                    feedback_queue,
+                    save_data_queue
                     ):
 
 
@@ -110,7 +111,12 @@ def data_processing(data_queue,
                 d_electrospray_processing = electrospray_processing.get_statistics_dictionary()
                 array_electrospray_processing.append(d_electrospray_processing)
 
-            # put values in the queue
+
+            # put values in the saving queue
+            save_message = [electrospray_data.get_measurements_dictionary(), electrospray_processing.get_statistics_dictionary()]
+            save_data_queue.put(save_message)
+
+            # put values in the plotting queue
             message = [electrospray_data, datapoints_filtered, time_step, electrospray_processing, classification_txt, txt_max_peaks]
             plotting_data_queue.put(message)
 

### 2023-02-02 software/mainElectrospray.py

@@ -13,8 +13,7 @@ import cameraTrigger
 import data_acquisition
 import plotting 
 import data_processing
-import os
-import json
+import save_data
 import logging
 
 
@@ -77,15 +76,25 @@ if __name__ == '__main__':
     fug_COM_port = 5
     pump_COM_port = 0
 
+
 # # # **************************************
-# # #                THREADS
+# # #                QUEUES
 # # # **************************************
+
 
     threads = list()
     controller_output_queue = queue.Queue(maxsize=100000)
     feedback_queue = queue.Queue(maxsize=100000)
     data_queue = queue.Queue(maxsize=100000)
+    save_data_queue = queue.Queue(maxsize=100000)
     plotting_data_queue = queue.Queue(maxsize=100000)
+
+
+
+
+# # # **************************************
+# # #                THREADS
+# # # **************************************
 
 
     # 
@@ -104,6 +113,7 @@ if __name__ == '__main__':
     controller_thread.start()
 
 
+
     #
     #           VIDEO   ->   Camera trigger thread using arduino microcontroller
     #
@@ -113,6 +123,7 @@ if __name__ == '__main__':
     # makeVideo_thread.start()
 
     
+
     # 
     #          SENSOR  ->   Data acquisition
     #   
@@ -134,6 +145,7 @@ if __name__ == '__main__':
     data_acquisition_thread.start()
 
     
+
     # 
     #          DATA PROCESSING  ->  data proccessing
     #   
@@ -150,11 +162,34 @@ if __name__ == '__main__':
             array_electrospray_processing,
             electrospray_classification,
             electrospray_validation,
-            feedback_queue
+            feedback_queue,
+            save_data_queue
         )
     )
     threads.append(data_processing_thread)
     data_processing_thread.start()
+
+
+
+    # 
+    #          SAVE DATA  ->  save data thread
+    #   
+
+
+    save_data_thread = threading.Thread(
+        target=save_data.save_data,
+        name='Saving Data thread',
+        args=(save_data_queue,
+            typeofmeasurement,
+            name_liquid,
+            save_path,
+            finish_event,
+            electrospray_config_liquid_setup_obj
+        )
+    )
+    threads.append(save_data_thread)
+    save_data_thread.start()
+
 
 
     # 
@@ -179,84 +214,16 @@ if __name__ == '__main__':
     # makeVideo_thread.join()
     # print('[MAKE VIDEO THREAD] thread CLOSED!')
 
+    data_acquisition_thread.join()
[…]

### 2023-02-02 software/save_data.py

@@ -1,0 +1,108 @@
+import os
+import json
+import time
+import sys
+
+def save_data(
+            save_data_queue,
+            typeofmeasurement,
+            name_liquid,
+            save_path,
+            finish_event,
+            electrospray_config_liquid_setup_obj
+            ):
+
+    try:
+
+        # voltage = str(voltage) + 'V'
+        if electrospray_config_setup["save_json"]:
+            # arbitrary, defined in the header
+            file_name = name_liquid + '_step_size_' + \
+                str(typeofmeasurement['step_size']) + "_step_time_" + \
+                str(typeofmeasurement['step_time']) + ".json"
+            completeName = os.path.join(save_path, file_name)
+
+
+        file = open(completeName, 'w')
+            # with open(completeName, 'w') as file:
+            #     json.dump((full_dict), file, indent=4)
+            # electrospray_validation.open_load_json_data(filename=completeName)
+
+        print("[SAVING] File Opened")
+
+    except:
+        print("[SAVING] Failed to open file")
+
+
+    try:
+
+        # electrospray_config_liquid_setup_obj.set_comment_current(current_shape_comment)
+
+        electrospray_config_liquid_setup_obj.set_type_of_measurement(typeofmeasurement)
+        aux_obj = electrospray_config_liquid_setup_obj.get_dict_config()
+
+        # if FLAG_PLOT:
+        #     electrospray_classification.plot_sjaak_cone_jet()
+        #     electrospray_classification.plot_sjaak_classification()
+
+        config_dict = {}
+        config_dict['config'] = {}
+
+    except:
+        print("[SAVING] failed creating saving files")
+        sys.exit(1)
+
+    try:
+
+        if electrospray_config_setup["save_config"]:
+            electrospray_config_liquid = electrospray_config_liquid_setup_obj.get_json_liquid()
+            electrospray_config_setup = electrospray_config_liquid_setup_obj.get_json_setup()
+            config_dict['config']['liquid'] = electrospray_config_liquid
+            config_dict['config']['liquid']['flow rate min'] = electrospray_config_liquid_setup_obj.get_flow_rate_min_ian()
+            config_dict['config']['setup'] = electrospray_config_setup
+
+            json.dump(config_dict, file, indent=4)
+
+
+    except:
+        print("[SAVING] failed saving configuration values")
+        sys.exit(1)
+
+
+
+    #
+    #     THREAD LOOP
+    #
+    
+    sample = 0
+    print("[SAVE DATA THREAD] starting loop")
[…]

### 2023-02-06 Documentation/UFMG/Relatorio_4/Conclusion/Conclusion.tex
starting report 4

\section{Conclusion}

The integration with the pump machine in the automatic system brings a new dimension of possibilities in this project.
The goal at the moment is to improve the algorithm in order to be capable of scanning the stable region of cone jet mode in the Voltage X Flowrate map.
After that define the middle point in the stability island to set as a setpoint to our control system.
The control system will be capable of rejecting noises and disturbance in the system in order to keep always in the stable cone jet spraying mode.

For further goals we have:

 - Save the experiment data in a file while running the experiment. This will prevent lost of data if the program crashes and also not overflowing the program memory.

 - Install and run the experiments in a raspberry pi portable computer running Linux.

 - Study about the fourier transform peaks and how it can be used in the classification and in the mapping.

 - Improve the classification and routine performance.

 - Optimize the controller.

Until the moment the project has been shown good results.
The map routine, the control routine and the classification are already implemented and working.
Now its more about improvements to get better accuracy in results.

### 2023-02-06 Documentation/UFMG/Relatorio_4/Development/Development.tex
starting report 4

--- 2023-01-26 Documentation/UFMG/Relatorio_3/Development/Development.tex
@@
 
-\subsection*{3.1 Pump Integration}
+    The following subsections are about the work done in this 3rd part of the project.
 
-    The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
-    two main variables that afect the system. 
-    It will bring more complexity for the system since now we are dealing with multivariable control.
-    Fortunatelly those two variables are uncuppled (* be certain of that first *) which means that actuating in one of them will not interfere in the other one.
-    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
+\subsection*{2.1 Save experiment in real time}
 
-    The pump integration was developed using also python language. As I could not find a good library for this pump I developed an quick and easy interface for sending the pump
-    commands to be integrated with the main automation routine. The communication with the pump was made using the serial interface and the commands list were found in the pump user manual.
+\subsection*{2.1 Raspberry pi}
 
-\subsection*{3.2 First mapping Experiments}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=15cm]{images/map2Data.png}
-        \caption{Mapping Experiment data}
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=15cm]{images/map1.png}
-        \caption{First mapping trial}
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=15cm]{images/map2.png}
-        \caption{Second mapping trial}
-    \end{figure}
-
-    It was noticed that the motor of the pump in certains speed generate a noise caused by the stepping from the stepper motor.
-    This noise from the motor was being acquired by the current data and was interfering in the classification method.
-    Because of that the firsts results of the map have a lot of undefined or incorrect classifications.
-    This can be reduced inserting a bubble in the syringe to atenuate mechanical noises.
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=15cm]{images/map3.png}
-        \caption{map3}
-    \end{figure}
-
-\subsection*{3.3 Capacitance of the system in step response}
-
-    We were discussing if the voltage step implies in a transient state in the current acquired.
-    If yes, the data acquired in this transient should not be used in the classification step. Since we want to analise
-    the spraying in a constant dynamics.
-
-    \begin{multicols}{2}
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/idea.png}
-            \caption{ map3 reproccessed data head }
-        \end{figure}
-
-        For that I reproccessed all raw data acquired cutting the head of the data window. The new classification map is showed in the figure 10.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/map3_reproccessed_data_head.png}
-            \caption{ map3 reproccessed data head }
-        \end{figure}
-
-        Also tested cutting the tail of the data window to see if have improvements in the classification.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/map3_reproccessed_data_tail.png}
-            \caption{ map reproccessed data tail }
-        \end{figure}
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{images/data_samples.png}
-            \caption{ USE ANOTHER IMAGE WITH STABLE SAMPLES OR DELETE THIS ONE }
-        \end{figure}
-
-    \end{multicols}
-
-    {TRY TO PUT STEP RESPONSE OF THE POWER SUPPLY HERE}
-
-    CONCLUSION: Does not made much difference. For steps under 250V the system does not show a transition dynamic. 
-    With steps above 250V the capacitance of the system reacts with a capacitance curve.
-
-\subsection*{3.4 Manual x Automatic Cone Jet stability island maps}
-
-    Metodology
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=14cm]{joao_26-01-22/screenshots/stableConeExp.png}
-        \caption{exp 24}
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/epx_24-01.png}
-        \caption{exp 24}
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp25-01-1.png}
-        \caption{ exp25-01-1 }
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp-26-01-1.png}
-        \caption{ exp-26-01-1 }
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=8cm]{joao_26-01-22/exp26-01-2.png}
-        \caption{ exp-26-01-2 }
-    \end{figure}
-
-\subsection*{3.5 Temperature and Humidity influences}
-
-    - Started collecting temperature and humidity values for each sample using arduino and DHT11 sensor from adafruit.
-    - Closed the system and sprayed pure oxygen O2 to decrease the humidity of the system.
+\subsection*{2.1 Correctly Join threads and qeues}

### 2023-02-14 Documentation/UFMG/Relatorio_4/Development/Development.tex

@@
 
-    The following subsections are about the work done in this 3rd part of the project.
+    The following subsections are about the work done in this 4rd part of the project.
 
 \subsection*{2.1 Save experiment in real time}
+
+    With the mapping routine the experiments time and data size started to make difference.
+    One experiment generates in average 6GB of data and takes arround 1,5 hours to complete.
+    The saving section was working with the python json library and with the function json\textunderscore{}dump().
+    One thing about using json objects is that the structure should be closed.
+    The function json\textunderscore{}dump() need the complete json file in order to save it.
+    For that the routine was saving all the data in python dictionaries. And after that creating and saving the json file.
+    Two new problems were happening. If the experiment crashes in the middle all the experiment data get lost. 
+    And it is not clear if the operational system or python kernel will support all the experiment data in program memory.
+
+    To solve that a new thread was created \emph{save\textunderscore{}data\textunderscore{}thread()} in order to save each sample in a selected file in the non-volatile memory.
+    Also was needed to use another python json library developed for streamming data in json structure in a file. It is called \emph{jsonstreams}.
+
+    With those new improvements we are abble to:
+
+        - Save data for big experiments. Depending just on the non-volatile memory storage.
+
+        - Use a raspberry pi for processing and saving big experiments.
+
+        - Interrupt and exit an experiment in real time and get the data saved.
+
+        - Less waiting time after the experiment to save all the data.
+
+    The new software design can ben represented in the model showed in Figure 2.
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=18cm]{images/image_folder_report_4/new_system_design.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+\subsection*{2.2 Saved Data Structure}
+
+    With the new streamming model of saving a new structure of the collected data were created.
+    Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
+    The structure of the
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=5cm]{images/image_folder_report_4/json_structure.png}
+        \caption{Output data json structure}
+    \end{figure}
+
+    To work with this data I'm using pandas Dataframe.
+    With the command:
+
+    pandas.read\textunderscore{}json("PATH", orient='index').
+
+    The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
+    type of file called feather is much faster to work with the data.
 

### 2023-02-14 Documentation/UFMG/Relatorio_4/Development/Development.tex
documentation

@@
 
+\subsection*{2.1 Mapping experiments}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap1.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap2.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap3.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/image_folder_report_4/mapXman-1.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/image_folder_report_4/mapXman-2.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
 \subsection*{2.1 Correctly Join threads and qeues}

### 2023-02-21 software/save_data.py
rebase software changes

@@ -69,12 +69,12 @@ def save_data(
 
             while not finish_event.is_set():
                 # wait for first value
-                # while save_data_queue.empty():
-                #     time.sleep(0.1)
+                while save_data_queue.empty():
+                    time.sleep(0.1)
 
-                print("[SAVING] before get, queue size:", save_data_queue.qsize())
-                data_measurement, data_processing = save_data_queue.get(block=True, timeout=None)  # expecting a list with two dictionary objects
-                print("[SAVING] after get, queue size:", save_data_queue.qsize())
+                # print("[SAVING] before get, queue size:", save_data_queue.qsize())
+                data_measurement, data_processing = save_data_queue.get() # block=True, timeout=None)  # expecting a list with two dictionary objects
+                # print("[SAVING] after get, queue size:", save_data_queue.qsize())
 
                 try:
                     if electrospray_config_setup["save_data"]:

### 2023-02-21 software/FUG_functions.py
sotfware small changes

@@ -43,7 +43,6 @@ def FUG_initialize(com_port_idx):
         except Exception as e:
             print('[FUG] Error FUG_initialize()')
             print('[FUG] Exception: ' + e.message)
-            return e.message
             sys.exit(1)
 
     else:

### 2023-02-21 software/controller.py

@@ -8,13 +8,17 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
 
     #              FUG INIT
     obj_fug_com = FUG_initialize(fug_COM_port)  # parameter: COM port idx
-    print("[FUG] obj_fug_com: ", obj_fug_com)
-    get_voltage_from_PS(obj_fug_com)
+    try:
+        get_voltage_from_PS(obj_fug_com)
+    except Exception as e:
+        print("ERROR: ", str(e))
+        print("[CONTROLLER THREAD] FAILED TO COMMUNICATE WITH POWER SUPPLY!")
+        sys.exit(1)
+
     voltage = typeofmeasurement['voltage_start']
 
-    #              FUG INIT
+    #              PUMP INIT
     obj_pump_com = PUMP_initialize(pump_COM_port)  # parameter: COM port idx
-    print("[PUMP] obj_pump_com: ", obj_pump_com)
     flow_rate = typeofmeasurement['flow_rate']
 
 

### 2023-02-21 software/mainElectrospray.py

@@ -37,13 +37,12 @@ if __name__ == '__main__':
     array_electrospray_measurements = []
     array_electrospray_processing = []
 
-    name_setup = "setup3"
+    name_setup = "mapsetup"
     setup = "setup/nozzle/" + name_setup
     name_liquid = "ethanol" # ["ethyleneglycolHNO3", "ethanol", water60alcohol40, 2propanol]
     liquid = "setup/liquid/" + name_liquid
     current_shape_comment = "difficult cone jet stabilization"
    
-    FLAG_PLOT = True
     plt.style.use('seaborn-colorblind')
     plt.ion()
 
@@ -57,14 +56,15 @@ if __name__ == '__main__':
     impedance = electrospray_config_setup["osc_impedance"]
     typeofmeasurement = electrospray_config_setup["typeofmeasurement"]
     save_path = electrospray_config_setup["save_path"]
+    plot_real_time = electrospray_config_setup["plot_real_time"]
     syringe_diameter = electrospray_config_setup["diameter syringe"]
     number_camera_partitions = electrospray_config_setup["number_camera_partitions"]
 
 
     #        PORTS
-    arduino_COM_port = 1
-    fug_COM_port = 5
-    pump_COM_port = 0
+    arduino_COM_port = 2
+    fug_COM_port = 0
+    pump_COM_port = 1
 
 
 # # # **************************************
@@ -188,10 +188,12 @@ if __name__ == '__main__':
     #          PLOTTING LOOP  ->    (注意) It's not a Thread 
     #  
 
-     # plotting is not a thread. It is a function running in a loop in the main.
-    fig, ax, ln0, ln1, ln2, bg = plotting.start_plot(plotting_data_queue)
+    # plotting is not a thread. It is a function running in a loop in the main.
+    if(plot_real_time):
+        fig, ax, ln0, ln1, ln2, bg = plotting.start_plot(plotting_data_queue)
     while not finish_event.is_set():
-        plotting.real_time_plot(plotting_data_queue, finish_event, fig, ax, ln0, ln1, ln2, bg)
+        if(plot_real_time):
+            plotting.real_time_plot(plotting_data_queue, finish_event, fig, ax, ln0, ln1, ln2, bg)
 
 
         

### 2023-02-21 software/save_data.py

@@ -43,7 +43,7 @@ def save_data(
                 config_dict['setup'] = electrospray_config_setup
 
             # Writing
-            os.mkdir(save_path)
+            os.makedirs(save_path, exist_ok=True)
             out_file = open(save_path + "/config.json", "w")
             json.dump(config_dict, out_file, indent = 6)
             out_file.close()

### 2023-02-21 software/data_acquisition.py
stop creating huge list

@@ -16,8 +16,7 @@ def data_acquisition(data_queue,
                      finish_event,
                      typeofmeasurement,
                      liquid,
-                     arduino_COM_port,
-                     array_electrospray_measurements
+                     arduino_COM_port
                      ):
 
     temperature = 0
@@ -134,16 +133,6 @@ def data_acquisition(data_queue,
         except Exception as e:
             print("ERROR: ", str(e))
             print("[DATA_ACQUISITION THREAD] Failed to ElectrosprayMeasurements")
-            sys.exit(1)
-
-        try:
-
-            d_electrospray_measurements = electrospray_data.get_measurements_dictionary()
-            array_electrospray_measurements.append(d_electrospray_measurements)
-
-        except Exception as e:
-            print("ERROR: ", str(e))
-            print("[DATA_ACQUISITION THREAD] Failed to append array")
             sys.exit(1)
 
         try:

### 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Capa/capa.tex
PFC

@@
 
-\vspace{6cm}
-{\bf\Large Primeira Linha do Título\vspace{0.2cm}
+\vspace{2cm}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{Capa/Figuras/brasao_ufmg.png}
+\end{figure}
 
-Segunda Linha do Título, se Houver}
+\vspace{2cm}
+{\bf\Large Controle e Classificação Automática da Dinâmica de Atomização por Electrospray (EHDA)}
 \vspace{4cm}
@@
 %\hspace{0.3\textwidth} \parbox{0.65\textwidth}
-{\large Fulano de Tal}
+{\large João Pedro Miranda Marques}
 \vspace{2cm}
@@
 %\hspace{0.3\textwidth} 
-{\large Orientador: Prof. Beltrano, Dr.}\\
-{\large Supervisor: Eng. Cicrano}
+{\large Orientador: Vitor Angelo}\\
+{\large Supervisor: Luewton L. Agostinho}
 
@@
 \centering
-\textbf{Título da Monografia}\\
+\textbf{Controle e Classificação Automática da Dinâmica de Atomização por Electrospray (EHDA)}\\
 \vspace{5cm}

### 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Introducao/Introducao.tex
PFC

@@
 
-As primeiras frases têm a missão de prender a atenção do leitor e por isso são as mais importantes do texto.
+A atomização eletrohidrodinâmica (EHDA), também conhecida como eletrospray (ES), é uma maneira de desintegrar um líquido
+em gotículas, expondo-o a um forte campo elétrico.
+
+% As primeiras frases têm a missão de prender a atenção do leitor e por isso são as mais importantes do texto.
 Diga o quanto antes o que você fez e quais são os resultados alcançados.
@@
 
-A comunicação escrita é considerada umas das cinco habilidades mais importantes por profissionais de engenharia e um engenheiro passa em média mais de $25$\% do seu tempo escrevendo \cite{eggert2002response,spretnak1982survey}.
+% A comunicação escrita é considerada umas das cinco habilidades mais importantes por profissionais de engenharia e um engenheiro passa em média mais de $25$\% do seu tempo escrevendo \cite{eggert2002response,spretnak1982survey}.
 Uma quantidade similar de tempo é gasta na escrita de correspondência e de relatórios técnicos \cite{cunningham2012perceptions}.
@@
 
-Neste texto você encontrará não apenas uma estrutura para escrever seu trabalho em \LaTeX, mas também um pequeno manual de boas práticas na escrita técnica.
+% Neste texto você encontrará não apenas uma estrutura para escrever seu trabalho em \LaTeX, mas também um pequeno manual de boas práticas na escrita técnica.
 Leia com atenção e coloque as sugestões em prática à medida que preenche o texto com o conteúdo do seu próprio projeto.
@@
 
-A seguir está a estrutura de organização sugerida pelo colegiado do curso.
+% A seguir está a estrutura de organização sugerida pelo colegiado do curso.
 Note que ela não é necessariamente a melhor para contar a história do seu projeto.
@@
 \label{sec:motivacao}
-
-Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes.
+% Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes.
 Contextualize seu projeto dentro do local de execução ou da literatura e explique como ele é necessário ou inovador.
@@
 Caso contrário, corre-se o risco de inadvertidademente tomar crédito pelo trabalho de outrem, o que pode ter implicações legais.
+
+As pesquisas de EHDA têm contribuído como uma importante ferramenta para
+o desenvolvimento da tecnologia da água (dessalinização térmica e recuperação de metais), ciências dos materiais (nanofibras e
+fabricação de nanoesferas, recuperação de metal, membranas seletivas e baterias) e aplicação biomédica
+(encapsulamento). Além disso, o projeto está integrado à estratégia de Transição Energética e à Agenda de Inovação
+Agricultura, água e alimentos, tecnologias facilitadoras essenciais (KETs). Embora existam aplicações de EHDA em
+indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.
+A corrente elétrica que flui transportada pelo spray revela formas características para diferentes modos de atomização.
+Essas formas não podem ser simplesmente resumidas por seu valor médio. Na figura um podemos ver um exemplo de cone-jet
+modo eletrospray.
+
+Figura 1: exemplo de EHDA
+
+As técnicas de processamento de sinal podem permitir uma classificação não visual do modo de pulverização com base no elétrico
+forma atual. O processo de pulverização impõe ruídos e sequências aleatórias no sinal medido tornando-o
+classificação não é uma tarefa trivial.
+Aplicações industriais exigem estabilização automatizada de um modo de pulverização. Isso pode ser obtido por um sistema fechado
+sistema de controle de circuito. A classificação automatizada do modo de pulverização é uma parte crucial de um sistema de controle, assim como
+o desenvolvimento de um algoritmo de controle apropriado.
 
@@
 
-Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido.
+% Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido.
 Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc.
 Descreva também o seu vínculo com a empresa.
+Implementações de processamento de sinal de projetos anteriores
+do grupo NHL Stenden Water Technology estão mostrando bons resultados de classificação. Mais pesquisas são
+necessário para melhorar a precisão da classificação e pesquisa e implementação de uma classificação adequada
+algoritmo. Por causa disso, o trabalho será feito pelo Water Technology Group da NHL Stenden University
+de Ciências Aplicadas e em combinação com empresas holandesas para combinar possibilidades de análise com conhecimento
+e disponibilidade de infraestrutura.
 

### 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Resumo/Abstract.tex
PFC

@@
 
-Write a version of your ``resumo'' in English. Beware of literal translations and double check the translation of technical terms.
+    Electrohydrodynamic Atomization (EHDA), also called electrospray, is a liquid atomization technique that
+    produces micro- and nanometric charged droplets within a narrow size distribution by using high electric fields (kV/cm).
+    According to Cloupeau and Prunet-Foch\cite{prunet} (1994), electrosprays can generate droplets in different ways, which the authors
+    named "electrospray modes". These modes may be adjusted by varying the strength of the electric field and flow rate,
+    but also depend on liquid properties and system geometry. In their work, the authors proposed four possible EHDA
+    modes: dripping, intermittent, cone-jet and multi-jet, which are generally distinguished visually. Verdoold et al.\cite{Sjaaks} (2014)
+    recently suggested a classification approach based on the behavior of the electric current of the electrospray process.
+
+    This project develops a closed-loop control method for EHDA devices that uses real-time, electric current-based (hence
+    non-visual) spray mode classification.
+    The proposed electrospray system is entirely automatic, where all the peripherals, such as HV power supply and syringe
+    pump, are controlled by a computer which executes their routines.
+    The system classifies spray mode dynamics using real-time current data and changes EHDA operating parameters such
+    as liquid flowrate and applied voltage to achieve and maintain the chosen spray mode. The electrospray modes are
+    validated in real time by using a high-speed camera.
+    As compared to conventional manual approaches, the implemented control algorithm achieves higher
+    accuracy and lower transient time. Therefore, a completely autonomous EHDA system opens the door to potential
+    industrial applications. In addition, the use of the electric current signal will be useful to further study electrospray
+    processes, leading to better control on droplet generation (frequency, size and charge). The incorporation of Machine
+    Learning to improve mode categorization will be a future development.
 

### 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Resumo/Resumo.tex
PFC

\addcontentsline{toc}{chapter}{Resumo}

\begin{center}
\huge{{\bf Resumo}}
\vspace{2cm}
\end{center}

A Atomização Eletro-hidrodinâmica (EHDA), também chamada de electrospray, é uma técnica de atomização de líquidos que produz gotículas de dimensão micro e nanométricas, utilizando campos elétricos elevados (kV/cm).
De acordo com Cloupeau e Prunet-Foch\cite{prunet} (1994) , os electrosprays podem gerar gotículas em diferentes dinâmicas, que os autores denominaram "modos de electrospray". 
 Esses modos podem ser ajustados variando a força do campo elétrico e a vazão de líquido, mas também dependem da geometria e das propriedades físico químicas sistema. 
 Em seu trabalho, os autores propuseram quatro possíveis modos EHDA: gotejamento, intermitente, jato cone e jato multi, que são geralmente distinguíveis visualmente.
 Verdoold et al.\cite{Sjaaks} (2014) sugeriram recentemente uma abordagem de classificação com base no comportamento da corrente elétrica do processo de electrospray.

Este projeto desenvolve um método de controle em malha fechada para dispositivos EHDA que utiliza classificação de modo de spray em tempo real com base em corrente elétrica (portanto, não visual). 
O projeto de sistema de electrospray é totalmente automático, onde todos os periféricos, como fonte de alimentação HV e bomba de seringa, são controlados por um computador que executa suas rotinas. 
O sistema classifica a dinâmica do modo de spray usando dados de corrente em tempo real e altera os parâmetros operacionais do EHDA, como vazão do líquido e tensão aplicada, para alcançar e manter o modo de spray escolhido. 
Os modos de electrospray são validados em tempo real usando uma câmera de alta velocidade.
Em comparação com as abordagens manuais convencionais, o algoritmo de controle implementado alcança maior precisão e menor tempo de transição. 
Portanto, um sistema EHDA completamente autônomo abre portas para potenciais aplicações industriais. 
Além disso, o uso do sinal de corrente elétrica será útil para estudar mais a fundo os processos de electrospray, levando a um melhor controle na geração de gotículas (frequência, tamanho e carga). 
A incorporação de Aprendizado de Máquina para melhorar a categorização de modos será um desenvolvimento futuro.

\clearpage
\thispagestyle{empty}
\cleardoublepage

% No Resumo, em uma única página, em no máximo dois parágrafos, você explicita os seguintes itens: objetivos do projeto e descrição sucinta do local onde ele foi desenvolvido; metodologia utilizada; e resultados alcançados. Leitores experientes decidem se prosseguirão para a leitura do texto completo após lerem o resumo, a conclusão e a introdução. Por isso nestes lugares você deve colocar um esforço maior de convencimento. Além disso, a linguagem utilizada deve ser acessível a leitores com pouca familiaridade com a área, limitando-se o uso de jargões.

% \begin{sloppypar}
% Este novo parágrafo serve para mostrar que ao pular uma ou mais linhas no texto do arquivo .tex, o \TeX\ entende que você está iniciando outro parágrafo. O comando \textsf{sloppypar} força o texto a não ultrapassar as margens. Só deve ser usado se este problema ocorrer.
% \end{sloppypar}

### 2023-03-03 Documentation/WT group/NHL/Capa/capa.tex
documentação

--- 2023-01-18 Documentation/UFMG/Relatorio_3/front_cover/front_cover.tex
@@
 
-    {\large Universidade Federal de Minas Gerais\\
-    Escola de Engenharia \\
-    Curso de Graduação em Engenharia de Controle e Automação\\}
-    \vfill
-
-    \begin{figure}[h]
+    \begin{figure}
             \centering
-        \includegraphics[scale=0.5]{images/brasao_ufmg.png}
+            % \subfigure{\includegraphics[width=5cm]{Capa/Figuras/wac.png}}
+            \hspace{0.1\textwidth}
+            \subfigure{\includegraphics[width=6cm]{Capa/Figuras/nhl-stenden.png}}
+            \vspace{3cm} 
         \end{figure}
-    \vspace{2cm}
 
@@
     \vspace{1cm} 
-    {\Large Relatório de Atividades 3   \\  Projeto Final de Curso}
+    {\Large Report}
     \vspace{2cm}
@@
     %\hspace{0.3\textwidth} 
-    {\large Orientador: Vitor Angelo\\
-            Supervisor: Luewton L F Agostinho}\\
-
-    %\hspace{0.3\textwidth} \parbox{0.65\textwidth}
-    {\large Aluno: João Pedro Miranda Marques \\
-    Matricula: 2017050495}
+    {\bf\large Student: João Pedro Miranda Marques}\\
+    \vspace{2cm}
+    {\large Supervisor: Luewton L F Agostinho}
     \vspace{2cm}
@@
 
-    \newpage
-    \clearpage
-    \thispagestyle{empty}
-
-    \cleardoublepage
-
 \title{
     EHDA closed loop control system based on real time non-visual spray mode classification \\
-    \large Relatório de Atividades PFC}
+    \large Relatório de Atividades}

### 2023-03-03 Documentation/WT group/NHL/Introducao/Introducao.tex
documentação

--- 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Introducao/Introducao.tex
@@
-\chapter{Introdução}
+\chapter{Introduction}
 \label{chap:intro} %este label será usado para referenciar este capítulo
@@
 
-\section{Motivação e Justificativa}
+\section{Motivation and Justify}
 \label{sec:motivacao}
@@
 
-\section{Objetivos do Projeto}
+\section{Project objectives}
 \label{sec:objetivos}
@@
 
-\section{Local de Realização}
+\section{People envolved}
 \label{sec:empresa}
@@
 
-\section{Estrutura da Monografia}
-\label{sec:organizacao}
-
-O trabalho está dividido em quatro capítulos.
-Este capítulo apresentou uma introdução ao projeto a ser descrito nesta monografia e a empresa onde o trabalho foi realizado.
-O Capítulo 2 descreve os princípios básicos de um sistema ...
-(sistema onde se insere o trabalho) e abrange todos os conceitos necessários para um melhor entendimento do projeto.
-O Capítulo 3 aborda a metodologia de desenvolvimento, seguida pela implementação dos ....
-No Capítulo 4 tem-se a conclusão da  monografia e algumas sugestões e dificuldades encontradas na realização do projeto.
-
 \clearpage

### 2023-03-03 Documentation/UFMG/Relatorio_4/Development/Development.tex
documentation

@@
         \center
-        \includegraphics[width=18cm]{images/image_folder_report_4/new_system_design.png}
+        \includegraphics[width=18cm]{images/image_folder_report_4/control_loop.png}
         \caption{Control model implemented in software}
@@
 
-\subsection*{2.1 Raspberry pi}
-
-\subsection*{2.1 Mapping experiments}
+\subsection*{2.3 Mapping experiments}
 
@@
 
+\subsection*{2.4 Manual x Automatic Mapping}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/image_folder_report_4/experiment_print1.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/image_folder_report_4/multi_jet_print.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
     \begin{figure}[H]
@@
 
-\subsection*{2.1 Correctly Join threads and qeues}
+\subsection*{2.5 Multi Jet classification by mean value}
+
+    There is not many articles about the multi jet dynamics and classification. This makes sometimes hard to define when
+    is in multi jet mode, if its defined by the meniscus, quantity of jets or stability.
+
+    We therefore know that the multijet current mean value is above of the cone jet mean value.\cite{Ryan}. This current mean value
+    increases for each new jet created. This could also be noticed experimentally in our setup.
+
+    For that, in our automatic classification algorithm, as the current acquired in cone jet and multi jet has the shape (constant) but different DC values. We decided
+    to save the cone jet mean value and multi jet mean values and analyse what is this step.
+
+    Making a statistical analysis in all data collected using the same liquid (ethanol) and setup we found that the Multi jet can be classified when the current is 1.14 the value of the Cone Jet mean.
+    I implemented this logic in the automatic classification and got the following results.
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{images/image_folder_report_4/map7-automatic.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+    Comparing this results with the manual results of the same experiment we can see that the algorithm could classify the Multi Jet with a good accuracy.
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=18cm]{images/image_folder_report_4/map7-comparison.png}
+        \caption{Control model implemented in software}
+    \end{figure}
+
+\subsection*{2.1 Raspberry pi}

### 2023-03-03 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

--- 2023-03-03 Documentation/WT group/NHL/Introducao/Introducao.tex
@@
 
-A atomização eletrohidrodinâmica (EHDA), também conhecida como eletrospray (ES), é uma maneira de desintegrar um líquido
-em gotículas, expondo-o a um forte campo elétrico.
-
-% As primeiras frases têm a missão de prender a atenção do leitor e por isso são as mais importantes do texto.
-Diga o quanto antes o que você fez e quais são os resultados alcançados.
-Ao terminar de ler a introdução o leitor tomará uma nova decisão de se vale a pena ou não continuar lendo o texto.
-Capte a atenção do leitor bem aqui.
-
-% A comunicação escrita é considerada umas das cinco habilidades mais importantes por profissionais de engenharia e um engenheiro passa em média mais de $25$\% do seu tempo escrevendo \cite{eggert2002response,spretnak1982survey}.
-Uma quantidade similar de tempo é gasta na escrita de correspondência e de relatórios técnicos \cite{cunningham2012perceptions}.
-Dessa forma, encare a escrita do seu projeto como um treinamento nessa importante habilidade.
-
-% Neste texto você encontrará não apenas uma estrutura para escrever seu trabalho em \LaTeX, mas também um pequeno manual de boas práticas na escrita técnica.
-Leia com atenção e coloque as sugestões em prática à medida que preenche o texto com o conteúdo do seu próprio projeto.
-Também será apresentado um número de vícios de escrita comumente encontrados nas monografias de alunos.
-
-% A seguir está a estrutura de organização sugerida pelo colegiado do curso.
-Note que ela não é necessariamente a melhor para contar a história do seu projeto.
-Você pode por exemplo preferir usar títulos mais pertinentes ao seu contexto.
-Contudo, o seu texto deve conter cada um dos pontos a seguir.
+Electrohydrodynamic Atomization (EHDA), also known as Electrospray (ES), is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.
+The electric current flowing transported by the spray reveals characteristic shapes for different spray modes.
+Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
+The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
+Industrial applications demand automated stabilization of a spray mode. 
+This can be achieved by a closed-loop control system. 
+This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode. 
+In the figure we can see how EHDA experiment works.
 

### 2023-03-03 Documentation/WT group/NHL/systemDescription/systemDescription.tex
documentation

--- 2022-12-07 Documentation/modelo_PFC_latex/DescricaoProcesso/DescricaoProcesso.tex
@@
-\chapter[Descrição do Processo]{Descrição do Problema/Processo ou O Processo de Fazer Alguma Coisa}
+\chapter[System Description]{System Description}
 \label{chap:descricaoproblema}
-%Note que, como nome do capítulo é muito longo, fornecemos um nome abreviado uso no cabeçalho
-
-Se desejar, uma visão geral do capítulo pode ser colocada antes da primeira seção.
-Este é o capítulo de descrição do processo e formulação do problema.
-Tendo em vista que se trata de uma monografia de engenharia de controle e automação, em muitos casos será fundamental a apresentação dos sensores e atuadores do processo.
 
@@
 
-Como uma imagem vale mais que mil palavras, e como usar mil palavras prejudicaria a clareza do texto, ilustramos o processo com a Figura \ref{fig:processo}.
-Lembrar que toda figura deve ser comentada no texto, você nunca deve colocar figuras que fiquem ``soltas'' no texto.
+ilustramos o processo com a Figura \ref{fig:setup}.
 
@@
   \centering
-  \resizebox{120mm}{!}{\includegraphics{DescricaoProcesso/Figuras/FiguraProcesso.pdf}}
-  \caption{Aqui escrevemos \textbf{toda} informação pertinente à figura.
-Ou seja, este texto deve ser uma descrição auto-contida da figura, não sendo necessário recorrer ao corpo de texto para saber detalhes sobre a mesma.
-\emph{Fonte:} Citar fonte se figura 	não for elaborada pelo autor e \textbf{pedir permissão para usar!}}
-  \label{fig:processo}
+  \resizebox{150mm}{!}{\includegraphics{systemDescription/Figuras/new_system_setup.png}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup}
 \end{figure}
 
-\section{Situação Atual/Estado da Arte/Revisão da Literatura}
+\section{section title}
 \label{sec:revisão}
 
-Este é o espaço para uma revisão detalhada do enquadramento do problema.
-Isso inclui descrever a situação atual do processo, aquilo que foi feito até então dentro da empresa/laboratório, e aquilo que se pode chamar de ``Estado da Arte'', ou seja, uma apresentação do conhecimento preexistente
-sobre o tema do projeto.
-
-A elaboração desta seção tipicamente demanda uma boa revisão da literatura. Deve haver, quando aplicável uma análise das soluções potencialmente concorrentes, elencando vantagens e desvantagens.
-
-\subsection{Como Elaborar uma Revisão da Literatura}
-
-Ao selecionar referências, devem-se preferir referências de veículos confiáveis, que tenham por exemplo processo de revisão por pares.
-Portanto, dá-se preferência a artigos em periódicos e livros, em seguida teses e dissertações, artigos em anais de congresso e por fim relatórios.
-Evitar citar páginas da internet por oferecem menor garantia da informação nelas contida.
-
-Pesquise sua bibliografia em bases confiáveis como o \textsf{Web of Science}, \textsf{Scopus}, ou o \textsf{Google Scholar}.
-\textbf{Não use uma ferramenta de busca comum!} (elas não foram feitas pensando no \emph{ranking} de textos científicos) Use o número de citações de uma dada referência como um indicador de sua qualidade.
-Explore os artigos que citam a referência estudada bem como os artigos que ela cita.
-
-Prefira as referências mais recentes quando se tratar de um assunto na fronteira do conhecimento ou de tecnologia de ponta.
-Quando se tratar de um assunto já consolidado, prefira citar livros ou artigos com muitas citações.
-
-Evite citar informações de segunda-mão e procure na medida do possível rastrear a fonte original.
-Contudo, em situações em que a fonte original é de acesso mais difícil, seja por ter tido publicação limitada como no caso de relatórios ou por não ser em língua inglesa ou portuguesa, é preferível a citação de segunda-mão em um veículo mais acessível.
-
-Para gerenciar suas referências, use uma ferramenta de software como o \textsf{Mendeley}, que permite gerar arquivos .bib para uso em {\LaTeX} ou simplesmente gerar a lista de referências para uso direto em editores de texto.
-Em \LaTeX, mais especificamente Bib\TeX, a lista de referências é criada a partir de um arquivo .bib, que é uma espécie de banco de informações bibliográficas em que cada entrada é uma referência associada a uma chave para citação.
-A lista criada incluirá apenas as referências citadas ao longo do texto, mesmo que haja mais referências no arquivo .bib.
-As informações bibliográficas no formato Bib\TeX também podem ser obtidas para cada referência em ferramentas como o \textsf{Google Scholar} e então coladas no arquivo .bib.
-
-Na Seção \ref{sec:comocitar} discutiremos como e quando as citações devem ser usadas.
-
-\section{Resumo do Capítulo}
-
-Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!
-
 \clearpage

### 2023-03-06 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation
Documentation

--- 2022-12-07 Documentation/modelo_PFC_latex/Metodologia/Metodologia.tex
@@
-\chapter{Metodologia}
-\label{chap:metodologia}
+\chapter{Metodology}
+\label{chap:Metodology}
 
-Este capítulo deve descrever os métodos utilizados no projeto.
-As teorias e ferramentas utilizadas, assim como as ações executadas, devem ser escritas de forma clara e precisa, sem deixar espaço para ambiguidades.
-Tenha em mente que \textbf{o objetivo aqui é dar credibilidade ao seu trabalho e permitir que ele possa ser reproduzido por quem tenha interesse (algumas vezes por você mesmo!)}.
+\section{System Model}
+\label{sec:control_model}
 
-É natural que este capítulo contenha uma revisão bibliográfica mais detalhada das técnicas utilizadas.
-O ideal é que o capítulo seja auto-contido, de modo que o leitor não necessite recorrer às referências para entender seu trabalho ou reproduzi-lo.
+ilustramos o processo com a Figura \ref{fig:control_model_fig}.
 
-Ao apresentar os métodos, será importante justificar devidamente as opções tomadas e discutir as alternativas disponíveis e os critérios que o levaram à escolha do método.
+\begin{figure}[thpb]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Metodology/Figuras/control_loop.png}}
+  \caption{EHDA automation system setup}
+  \label{fig:control_model_fig}
+\end{figure}
 
-No restante do capítulo, apresentamos um pequeno manual de escrita técnica.
+\section{Threading and Queues}
+\label{sec:concurrency}
 
-\section{Técnica 1 - Organização do texto}
-\label{sec:metodo1}
+\section{Routine Sequences}
+\label{sec:routine_sequences}
 
-Procure \textbf{definir a estrutura} de seu texto \textbf{antes de começar a escrever}.
-Isso evitará que as ideias apareçam foram de ordem.
-A falta de organização é uma das características mais comuns de textos difíceis de ler.
+\subsection{Ramp}
 
-Nunca invoque conceitos ou objetos antes de defini-los. Procure fornecer o máximo de informação \emph{a priori} possível. Evite referências para frente no texto.
+\subsection{Step}
 
-Para evitar que o leitor se perca, antes de iniciar um trecho longo de texto que contenha ideias diversas, \textbf{adiante para o leitor o que será feito}, aonde se quer chegar.
-Ao fim do trecho, declare explicitamente que chegou à conclusão que desejava.
-Esta técnica vale especialmente para seções e capítulos do texto.
+\subsection{Map}
 
-\section{Técnica 2 - Estilo}
-\label{sec:estilo}
+\subsection{Control}
 
-O texto técnico deve ser preciso, claro, sem ambiguidades, objetivo e conciso.
-Mesmo com esse rigor, não deixe de prender a atenção do leitor.
-Lembre-se de que o início e o fim de cada parágrafo, de cada frase, são as partes mais importantes e onde você deve colocar maior ênfase.
+\section{Optimizations}
+\label{sec:routine_optimization}
 
-\subsection{Precisão}
+About the python algorithm to turn the experiment autonomous it was made a study and modelling of the software architecture to optimize it for further control loop application to be implemented.
+From the changes made until now it highlights:
 
-Use as palavras corretas!
-Não escreva redondo se é esférico.
-Não escreva igual se é aproximado.
-Não escreva sistema se é função de transferência.
-Não escreva grande, pequeno, máximo, mínimo, ótimo, se não há uma escala que defina tais conceitos.
+- Integrate high speed camera to the experiment routine.
 
-Prefira usar números que deem uma noção de escala a usar adjetivos difíceis de precisar.
+- Remodel the software to support threads in order to separate the sensoring and controlling routines.
 
-Seja específico e evite generalidades.
-Por exemplo, em vez de dizer ``O processo 1 é um processo de alto custo'', devemos ser mais precisos com relação à natureza do custo e dizer ``O processo 1 possui custo operacional elevado com relação a processos tradicionais tais como o processo 2''.
+- Reduce the data collected size.
 
-\subsection{Clareza}
+- Synchronize the power supply step commands and voltage sensoring.
 
-Não deixe margem para dúvidas!
-Para reduzir a possibilidade de confusão na leitura do seu texto, \textbf{evite frases longas}.
-Nunca escreva frases com mais de $20$ palavras.
-Procure escrever na média $12$ palavras por frase.
-Evite palavras compridas ou que possam ser consideradas difíceis.
+- Reestructure the setup file in order to make it more intuitive to use the experiment.
 
-Não deixe ideias subentendidas!
-Não assuma que seu leitor pensa como você e vai saber do que você está falando.
-Explicite todos os passos de seu raciocínio lógico.
-Pular passos de raciocínio é uma das causas mais comuns de confusão na leitura.
-Não seja preguiçoso neste quesito.
+- Improvements in code organization and readability.
 
-Novamente, defina todos os conceitos antes de fazer uso deles.
-
-Não deixe o sujeito verbal subentendido.
-Para evitar ambiguidades, tome cuidado ao usar pronomes como ``esse, este, isso, ele''.
-É preferível repetir um nome a deixar margem para dúvidas.
-Por exemplo, após a primeira frase deste parágrafo poderíamos dizer de forma não tão clara: ``Esta é uma causa de confusão na escrita.''; ou poderíamos dizer de forma mais clara: ``Essa falta de informação é uma causa de confusão na escrita.''
-
-Não há problemas em haver repetições em textos técnicos.
-O mais importante é a clareza, a inexistência de ambiguidades, não a beleza.
-Se acha que uma determinada frase pode ser confusa ou se alguma ideia parece difícil de explicar, repita a mesma ideia em outras palavras ou, melhor ainda, dê um exemplo.
-
-Por fim, domine o significado das palavras utilizadas para evitar ambiguidades.
-Se uma palavra pode ter mais de um significado em determinada frase, tente trocá-la por outra que não deixe dúvidas.
-Mais importante ainda, não use palavras sobre cuja definição você não tem certeza.
-
-\subsection{Ojetividade}
-
-O texto técnico deve ser direto ao ponto, sem rodeios, e livre de opiniões. Evite apartes, evite divagações e discussões irrelevantes com relação ao tema principal.
-
-\textbf{Nunca use hipérboles}.
-Cuidado com termos como ``otimizar, muito grande, enorme, muito bom''.
-Usar números sempre que possível para quantificar conceitos, sejam eles precisos ou apenas uma estimativa.
-Em especial deve-se tomar cuidado com as palavras ``muito'' e ``muitos''.
-
-O tom deve ser impessoal, apresentando apenas fatos e não opiniões.
-Em português, a voz passiva é um instrumento comum para se obter um tom impessoal.
-Contudo, sempre que possível, tente usar a voz ativa ou a voz passiva sintética para deixar o texto mais fluido e claro.
-
-Palavras abstratas deixam a escrita vaga.
-Prefira palavras concretas, fortes, isto é, palavras que tenham um único significado.
-Sempre que possível substitua múltiplas palavras por uma única.
-Por exemplo, na frase ``A máquina processou as amostras'' temos duas palavras genéricas: máquina e processar.
-A mesma ideia seria mais objetiva se expressa como ``A centrífuga girou as amostras''.
-
-Controle seu tom. \textbf{Não use linguagem coloquial. Não use clichês}. Não use de arrogância: ``obviamente, como é sabido, é claro que''.
-
-\subsection{Concisão}
-
-O texto técnico deve ser tão curto quanto possível, sem prejuízo de sua clareza e precisão.
-Não use palavras a mais, não inclua expressões irrelevantes ou supérfluas.
-Não escreva simplesmente para encher as páginas.
-Se um assunto não é relevante para a compreensão do seu trabalho, corte-o, mova-o para um apêndice ou aponte uma referência.
-
-Evite redundâncias como ``opinião pessoal'' e ``garantia absoluta''.
-
-\section{Vícios comuns}
-
-\begin{itemize}
-\item Estrangeirismos: ``\emph{performance}'', ``\emph{mutatis mutandis}''. Se necessário, coloque o termo estrangeiro em itálico e dê uma tradução entre parênteses.
-
-\item Usar linguagem rebuscada. Lembre-se de que a linguagem técnica deve ser clara, precisa e objetiva.
-
-\item Alternar o tempo verbal entre passado e presente. Seja consistente e escreva apenas no passado ou no presente.
-
-\item Iniciar uma frase com verbo porque o sujeito está implícito na frase anterior. Deixe sempre o sujeito explícito.
-
-\item Inserir referências no meio de uma frase. Isso quebra o fluxo da leitura. Coloque a citação no fim da frase.
-
-\item \textbf{Usar siglas sem antes defini-las}. Sempre escreva a sigla por extenso \emph{na primeira vez} que ela aparece no texto. Por exemplo, ``este é um texto de Projeto Final de Curso (PFC)''.
-
-\item Escrever ``como sabemos'', ``como é sabido'', ``por razões óbvias'', ``é evidente que'', ``talvez seja verdade que''.
-Estes termos significam apenas que você não sabe explicar o que está afirmando.
-
-\item Usar definições \emph{por exemplo}, isto é, apresentar a definição de um conceito ou termo por meio de um exemplo. Primeiro defina o conceito, depois exemplifique.
-
-\end{itemize}
-
-\section{Boas práticas}
-
-\begin{itemize}
-\item Sempre que introduzir novos termos e conceitos, destaque-os em itálico para que o leitor saiba que se trata de uma definição e para que ele ache a definição com facilidade quando for necessário rastreá-la no texto.
-\item Releia o que escreve a cada parágrafo. Releia rapidamente cada seção para verificar o encadeamento de ideias.
-\item Corte palavras sempre que possível.
-\item Nunca assuma que o leitor entenderá o que você escrever. Esforce-se para fazê-lo entender.
-\item Use um corretor ortográfico.
-\item Peça que alguém leia seu texto.
-\end{itemize}
-
-\section{Uso de referências}
-\label{sec:comocitar}
-
-Uma afirmação incluída num texto técnico se enquadra em um de três casos: a) seu conteúdo é de conhecimento geral dentro da área do texto; b) seu conteúdo é original e resulta do trabalho do autor; c) seu conteúdo tem origem em outro trabalho (ainda que seja do mesmo autor, não é original).
-
-Toda afirmação enquadrada na categoria c) deve ser acompanhada de uma citação.
-Para afirmações da categoria b), deixe claro que se trata de ideia original do autor.
-Isso evita que o leitor se confunda ao pensar que possa se tratar de a) ou c).
-
-No caso a), pode ser um tanto mais sutil determinar o que deve ser de conhecimento geral.
-Procure evitar o excesso de citações.
-Se todo um parágrafo se baseia em ideias de uma certa referência, em geral basta que ela seja citada no seu início.
-
-\textbf{Atenção:} Não copie frases das referências usadas.
-Reescreva as ideias com suas próprias palavras e não deixe de citar a fonte.
-Se for necessário manter as palavras do original, cite a frase entre aspas e em itálico.
-
-\section{Honestidade e Plágio}
-
-Seja honesto ao escrever.
-\textbf{Não ``maqueie'' seus resultados}.
-Não apresente apenas as melhores amostras dos seus resultados para dar a impressão de que foi bem sucedido.
-Não escreva aquilo que não entende.
-Não escreva de forma vaga para mascarar o fato de que não entende algo.
-
-Dê crédito a quem o merece.
-Inclua referências sempre que usar o trabalho de outros.
-Seja sempre claro para não dar a impressão de que fez algo feito por outrem.
-\textbf{Não assuma crédito pelo trabalho dos outros}.
-Isso pode ter implicações legais e acadêmicas.
-
-\section{Cuidado com a gramática}
-
-\begin{itemize}
-
-\item Erros gramaticais deixam uma \textbf{impressão ruim} e podem alterar a disposição do leitor para com o texto.
-
-\item Use a vírgula corretamente.
-Seu uso incorreto confunde o leitor.
-Nunca use a vírgula porque acha que a frase precisa de uma pausa.
-Não separe sujeito e verbo.
-Quando há inversão da ordem natural em uma frase, \emph{toda} a parte movida deve estar entre vírgulas.
-
-\item Cuidado com a concordância da voz passiva sintética. Lembre-se de que o correto é ``Vendem-se ovos'' e não ``Vende-se ovos''.
-
-\item Use a crase corretamente.
-Faça sempre o exercício de substituir o nome que sucede o ``à'' por um nome no masculino.
-Se o correto for usar ``ao'' com o nome masculino, então deve haver crase.
-Nunca use crase antes de nomes no masculino!
-
-\item Escreva ``em que'' em vez de ``onde'' quando não houver indicação de lugar.
-
-\item Não se escreve ``o fato \textbf{dela} ser'' ou ``a razão \textbf{do} texto ser escrito''. Escreve-se ``o fato \textbf{de ela} ser'' e ``a razão \textbf{de o} texto ser escrito''.
-
-\item Releia o que escreve e na dúvida busque ajuda.
-
-\end{itemize}
-
-\section{Resumo do Capítulo}
-\label{sec:metodo1b}
-
-Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!
+About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to
+make the experiment the most stable and easy to reach cone-jet mode as possible.
+For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
+Therefore compromising the stabilization in cone jet mode.
+A solution for that was to increasethe flowrate wich smooths this pumping noise.
+For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
 

### 2023-03-06 Documentation/WT group/NHL/Results/Results.tex
documentation
Documentation

--- 2022-12-02 Documentation/modelo_PFC_latex/Resultados/Resultados (Alexandre Mesquita's conflicted copy 2019-02-22).tex
@@
-\chapter{Resultados}
+\chapter{Results}
 
@@
 
-\section{Desenvolvimeto e Implementação}
-
-A Tabela \ref{tab:tabela} apresenta as atividades executadas.
-
-\begin{table}
-\centering
-%Note os alinhamentos diferentes em cada coluna
-\begin{tabular}{|c|r|l|}\hline
-		Atividade 1 & aa  & ab  \\ 
-					 & a & b \\ \hline
-		Ativ. 2  & aa & ab \\			
-					 &  a & b \\ \hline
-		\end{tabular}
-	\caption{Exemplo de tabela - Coloque toda informação sobre a tabela aqui}
-	\label{tab:tabela}
-\end{table}
-
-\section{Testes}
-
-\section{Análise dos Resultados}
-
-Apresente os resultados sem adulterações e faça análises objetivas.
-Pense na melhor maneira de apresentar os resultados graficamente.
-Se os gráficos são difíceis de interpretar, talvez tabelas sejam uma forma melhor de apresentar resultados.
-Não apresente dados (gráficos e tabelas) se não há uma conclusão interessante a ser tirada.
-Lembre-se de ser conciso.
-
-\emph{Não se esqueça das unidades!} Pense que \emph{a priori} todo número deve ter uma unidade.
-Não escreva as unidades em itálico (no ambiente matemático) e tome cuidado para diferenciar maiúsculas e minúsculas.
-Um exemplo é escrever $22$ [kN] e não $22 KN$ (Kelvin vezes Newton!).
-
-Ao apresentar resultados experimentais, tome o cuidado para também apresentar o cálculo das incertezas sempre que forem significativas.
-Ao fazer conclusões, sempre considere se o tamanho da sua amostra é grande o suficiente do ponto de vista estatístico.
-
-\section{Resumo do Capítulo}
-\label{sec:resumoo4}
-Tente não terminar de forma abrupta. Se for escrever algo aqui, não seja genérico!
-
-\section{Formato, expressões matemáticas e o \LaTeX}
-
-\subsection{O \LaTeX}
-
-O {\LaTeX}  é o método preferencial de preparação de documentos para textos técnicos nas ciências exatas.
-O {\LaTeX} permite não só lidar com equações de uma forma mais prática que em editores de texto, mas também facilita a formatação de documentos e tem um desempenho marcadamente superior a editores de texto na preparação de documentos longos como monografias.
-
-Documentos em {\LaTeX} são escritos em um ou mais arquivos de texto com extensão .tex.
-Após a escrita, o .tex é \emph{compilado} para gerar arquivos nos formatos .pdf, .dvi ou .ps.
-Hoje há duas distribuições padrão para o \LaTeX.
-Sistemas Windows usam o {Mik\TeX} e sistemas Unix usam o \TeX Live.
-Além das distribuições, muitos usuários utilizam \emph{front-ends} que facilitam a edição do texto, a compilação e a instalação de pacotes.
-
-Os pacotes necessários para compilar o presente documento devem ser encontrados numa instalação completa dessas distribuições.
-Se tiver dificuldades com os pacotes, você pode instalá-los manualmente ou tentar alterar o código para usar versões antigas dos mesmos.
-
-A compilação pode ser feita pelos comandos \textsf{latex} ou \textsf{pdflatex}, invocados pela linha de comando ou pelo \emph{front-end}.
-Note que será necessário empregar o comando \textbf{mais de uma vez} para que as referências cruzadas saiam corretas.
-
-Como discutido na Seção \ref{sec:revisão}, uma ferramenta útil para gerenciar as citações em {\LaTeX} é o Bib\TeX.
-Para gerar uma lista bibliográfica a partir do arquivo .bib, este arquivo deve ser indicado no arquivo .tex.
-Em seguida devem-se executar os comandos \textsf{pdflatex}, \textsf{bibtex} e \textsf{pdflatex} novamente sempre usando o .tex como argumento.
-Note que os comandos são executados nesta ordem e de forma repetida para que as referências cruzadas sejam geradas corretamente.
-
-A fonte \textsf{Times}, indicada pela resolução do PFC e usada neste documento, não possui uma das aparências mais agradáveis, especialmente para os símbolos matemáticos.
-Se preferir símbolos matemáticos mais harmoniosos, remova a inclusão da fonte \textsf{newtxmath} no cabeçalho do .tex.
-
-Nesta seção você deve encontrar exemplos dos comandos mais usados em \LaTeX. Outros exemplos e manuais podem ser encontrados na internet com facilidade.
-
-\subsection{Expressões Matemáticas}
-
-Ao escrever expressões matemáticas, defina todas as variáveis antes de usá-las ou imediatamente depois da expressão. Deixar de fazê-lo torna seu texto ilegível. Segue um exemplo.
-
-Seja o par $(a_1,a_2)\in \mathbb{R}^2$. Para $s\in\mathbb{C}$, definimos a função $f(s)$ como
-\[%cria equações sem numeração
-f(s)\triangleq \frac{a_1 s+a_2}{s^2+2\zeta\omega_n s+\omega_n^2}
-\enspace,
-\]
-onde os escalares $\zeta,\omega_n>0$ são constantes.
-
-Note que não foi necessário atribuir valores às variáveis neste momento.
-Repare também como devemos \textbf{usar pontuação} (vírgula) nas equações, tratando-as como parte da frase.
-Usamos o símbolo $\triangleq$ ou $:=$ para deixar explícito que se trata de uma definição.
-Ser claro nesse aspecto facilita o entendimento do leitor.
-
-A equação acima não foi numerada porque não será citada no texto. Vejamos um exemplo com numeração.
-
-A função $f(\cdot)$ possui um zero em $-a_2/a_1$ (ou $-\frac{a_2}{a_1}$) e, para $\zeta<1$, possui polos complexos $p_{1,2}$ dados por
-\begin{equation}
-\label{eq:polos}
-p_{1,2}=\omega_n \left(-\zeta\pm j\sqrt{1-\zeta^2}\right)
-\enspace.
-\end{equation}
-Agora podemos citar os polos dados pela Equação (\ref{eq:polos}) (aqui adotamos a convenção de citar sempre com o número entre parênteses precedido da palavra Equação).
-Note como usamos um comando especial na Equação (\ref{eq:polos}) para garantir o ajuste automático do tamanho dos parênteses.
-
-Vejamos agora como criar equações alinhadas. Considere o sistema dinâmico dado pelas equações diferenciais:
-
-\begin{align}
-\dot{x}_1 & = \cos(x_2)\cdot\ln(1/x_1)+\tan(u) \label{eq:x1dot} \\
-\dot{x}_2 & = e^{-x_1-x_2} \nonumber \\
-& y  = \min\{x_1,x_2\}  \label{eq:saida}
-\enspace,
-\end{align}
-onde $x(t)=[x_1(t) ~ x_2(t)]'$, $t>0$, é a variável de estado do sistema, $u(t)$ é o sinal de entrada e $y(t)$ é o sinal de saída do sistema.
-Note no .tex que o caracter de tabulação \textsf{\&} foi usado para indicar o ponto de alinhamento horizontal das equações.
-Além disso, para ilustrar o uso do \LaTeX, retiramos a numeração da segunda equação e citamos as equações separadamente.
-
-Nas Equações (\ref{eq:x1dot}) e (\ref{eq:saida}), aparecem operadores como $\min$, $\ln$, $\cos$ e $\tan$.
-A convenção aqui é que \textbf{variáveis devem ser escritas em itálico e operadores não}.
-Por essa razão todas as expressões matemáticas devem ser escritas no ambiente matemático (entre cifrão) mesmo quando for possível usar texto comum.
-Isso garante a consistência das fontes utilizadas (nem sempre a fonte do ambiente matemático é a mesma fonte do texto).
-
-Para escrever matrizes, podemos fazer por exemplo:
-\[
-\sum_{n=0}^{\infty}z^{-n}\left[\begin{array}{cc}
-\lambda & 1 \\
-0 & \lambda
-\end{array}\right]^n=
-\left[\begin{array}{cc}
-\frac{z}{z-\lambda} & \frac{z}{(z-\lambda)^2} \\
-0 & \frac{z}{z-\lambda}
-\end{array}\right]
-,~\forall \lambda<|z|
-\enspace.
-\]
-
-Para escrever uma expressão com múltiplos casos, podemos fazer, para um inteiro $N$ positivo,
-\[
-g[n]=
-\left\{
-\begin{array}{ll}
-0,& \mbox{se }~ n\leq 0 \\
-n,& \mbox{se }~ n=1,2,\ldots,N-1 \\
-N,& \mbox{se }~ n\mod N = 0 \\
-0,& \mbox{caso contrário}\enspace.
-\end{array}
-\right.
-\]
-
-\textbf{Nunca reaproveite símbolos} matemáticos, isto é, nunca use o mesmo símbolo para designar variáveis diferentes.
-
-Para um exemplo com múltiplas linhas de expressão matemática: tem-se que, para $a\neq 0$,
-
-\begin{equation}
-\begin{split}
-ax^2+bx+c &= 0 \\
-& \Rightarrow a(x^2+bx/a+c/a) =0 \Rightarrow a((x+b/(2a))^2+c/a-b^2/(4a^2))=0  \\
-& \Rightarrow (x+b/(2a))^2=(b^2-4ac)/(4a^2) \\
-& \Rightarrow (x+b/(2a))=\pm\sqrt{b^2-4ac}/(2a) \\
-& \Rightarrow x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}
-\enspace.
-\end{split}
-\end{equation}
-
-Note a argumentação lógica aqui.
-Não estamos dizendo que o valor de $x$ é dado pela última linha.
-Estamos dizendo que a hipótese da primeira linha juntamente com a hipótese $a\neq 0$ implicam os referidos valores de $x$.
-\textbf{Um erro comum dos alunos ao escrever é não distinguir a veracidade das implicações com a veracidade das hipóteses}.
-
 \clearpage

### 2023-03-06 Documentation/WT group/NHL/systemDescription/systemDescription.tex
Documentation

@@
 
-\section{Processo de Fazer Alguma Coisa}
-\label{sec:hist}
+\section{EHDA}
+\label{sec:ehda_resume}
 
-Cada seção inicia pela descrição do seu conteúdo e pode terminar com um parágrafo de conexão com a seção seguinte.
+\begin{multicols}{3}
 
-Antes de formular o problema, \textbf{não se esqueça de fazer todas as definições necessárias}.
-Também devem-se detalhar os aspectos complementares da abordagem: se estamos estudando um aspeto particular do problema, se a resposta encontrada é universal ou dependente de simplificações e hipóteses prévias.
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{systemDescription/Figuras/drippingexample.png}
+      \caption{Dripping}
+  \end{figure}
 
-\section{Instrumentação do Processo}
-\label{sec:instrumentação}
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{systemDescription/Figuras/conejetexample.png}
+      \caption{Cone Jet}
+  \end{figure}
 
-Descreva a aparelhagem e o equipamento utilizados bem como a ligação entre os diversos componentes.
-Nesta seção e, ao longo de todo o texto, você deve dar detalhes suficientes para que qualquer pessoa consiga reproduzir seus experimentos.
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{systemDescription/Figuras/multijetexample.png}
+      \caption{Multi Jet}
+  \end{figure}
 
-Contudo, \textbf{não disperse o leitor com detalhes irrelevantes} ou aspectos
-demasiado técnicos ou formais. Reserve tais detalhes para um
-apêndice.
+\end{multicols}
 
-ilustramos o processo com a Figura \ref{fig:setup}.
+\section{Instrumentation}
+\label{sec:instrumentation}
 
-\begin{figure}[thpb]
+The peripherals automation routine was already developed by another student.
+In order to continue the research I took some time to understand the physical concept behind EHDA experiments and the project knowledge.
+I made upgrades in the routine to include the high speed camera with a hardware triggering routine using an arduino microcontroler.
+This will be usefull to validate the further classification of the spray dynamics.
+
+% ilustramos o processo com a Figura \ref{fig:setup}.
+
+\begin{figure}[H]
   \centering
@@
 
-\section{section title}
-\label{sec:revisão}
+\section{First Experiments}
+\label{sec:first_experiments}
+
+Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could unterstand in practise how electrospray works.
+I noticed that we need a large set of variables in the range to produce the desired dynamics of electrospray, which most of the time is cone-jet mode.
+Those variables can be the liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permitivity.
+And also physical variables such as flowrate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
+The instruments used in the setup are:
+
+\begin{enumerate}[a]
+  \item High Voltage Power Supply (FUG)
+  \item Oscilloscope TiePie WS6 DIFF 
+  \item Humidity and Temperature sensor (DHT11 + Arduino Uno)
+  \item High Speed Camera - Photron fastcam mini
+  \item Syringe pump
+  \end{enumerate}
 

### 2023-03-09 Documentation/WT group/NHL/Metodology/Metodology.tex
Documentation

@@
 
+\section{Classification}
+\label{sec:section_classification}
+
+\subsection{Statistical Analisys}
+
+ According to \cite{Sjaaks} evaluating the current data flowing through the nozzle to the plate we can analyze the signa that represents the spraying dynamics.
+ through statistical analysis in this signal such as mean value and standart deviation we can analyze if the signal is stable or not.
+
+ Our classification by statistical analysis was implemented in the automation library made by the previous student \cite{Monica}.
+
+ Each current sample is 0.5s of current data in 10kHz sampling frequency.
+ By the processing thread we take this sample and evaluate the followings statistical values.
+
+        - Sjaak Classification -> Classifies Dripping, Intermittent and Cone Jet
+
+        - Monica Classification -> Classifies Corona Sparks
+
+        - João Classification -> Classifies Multi Jet
+
+	The algorithm implemented works in the following way:
+	\begin{algorithm}
+        \caption{Statistical Classification}\label{alg:statistical_class}
+        \begin{algorithmic}
+        \Function{statistical\_classification}{$sample$}
+
+            \State $spray\_mode \gets "Undefined"$;
+            \State $mean \gets sample.mean$; 
+            \State $std\_deviation \gets sample.std\_deviation$;
+            \State $median \gets sample.median$;
+
+            \If{ $mean / std\_deviation$ > 2.5}
+                \Comment{Sjaak classification \cite{Sjaaks}} 
+                \State $spray\_mode \gets "Dripping"$;
+            \ElsIf{$ 2.5 < mean / std\_deviation < 2.5 \And mean / std\_deviation > 0.3 $}
+                \State $spray\_ mode \gets "Intermittent"$;
+            \ElsIf{ $mean / std\_deviation$ < 0.3}
+                \State $spray\_ mode \gets "Cone Jet"$;
+                \State $cone\_jet\_mean \gets mean$;
+            \EndIf
+
+            \If{ $mean / std\_deviation$ > 2.5}
+                \Comment{Monica classification \cite{Monica}} 
+            \EndIf
+
+            \If{ $spray\_mode == "Cone Jet"$}
+                \Comment{João classification} 
+                \If{ $cone\_jet\_mean > 1.14 \times mean$}
+                    \State $spray\_ mode \gets "Multi Jet"$;
+                \EndIf
+            \EndIf
+
+            \Return $spray\_ mode$;
+        \EndFunction
+        \end{algorithmic}
+    \end{algorithm}
+
+\subsection{Machine Learning}
+
 \section{Routine Sequences}
@@
 \subsection{Map}
+
+    \begin{algorithm}
+        \caption{MAP sequence in controller thread}\label{alg:mapping_algorithm}
+        \begin{algorithmic}
+        \Procedure{MAP}{$flowrate\_values$} 
+            \ForAll{flowrate\_values}  \Comment{scanning in the flowrate range}
+                \State \Call{send\_flowrate\_command}{flowrate}
+                \State $voltage \gets voltage\_start$
+                \While{$voltage \leq voltage\_stop$} \Comment{scanning in the voltage range}
+                    \State \Call{send\_voltage\_command}{voltage}
+                    \State \Call{sleep}{step \_time}
+                    \State $voltage \gets voltage + step\_size$
+                \EndWhile
+            \EndFor
+        \EndProcedure
+
+        \end{algorithmic}
+    \end{algorithm}
+
+    In the figures 5 and 6 we can see the results of this mapping experiments. The liquid used is pure ethanol. 
+    Each figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
+    The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
+    The third graph shows the current mean value of each data sample.
+    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{Metodology/Figuras/report2/map2Data.png}
+        \caption{Mapping Experiment example 1 }
+        \label{fig:map2Data_fig}
+    \end{figure}
 
@@
 
+\subsection{Pump Integration}
+
+    The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
+    two main variables that afect the system. 
+    It will bring more complexity for the system since now we are dealing with multivariable control.
+    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
+    % Our control model is now a MISO \footcite{MISO: Multiple Inputs Single Output} system. The crossover (couple) between the controlled variables will be evaluated in further reports.
+
+    About the pump interface. As I could not find a good ready-to-use library for this pump I developed an simple and intuitive interface to be our software routine.
+    The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
+
 \clearpage

### 2023-03-13 data_analysis/plot_raw_data.py
documentation

@@ -1,35 +1,34 @@
 
 import pandas as pd
-import json
 import matplotlib.pyplot as plt
 import numpy as np
 
+df = pd.read_feather('Data/map_23-03-02.feather')
 
 
-data = pd.read_feather('../classified_data/data1.feather')
+df = df.loc[df['flow_rate'] == 0.7]
 
-
-
-colors = {'Cone Jet':'red', 'Dripping':'green', 'Intermittent':'blue', 'Multi Jet':'purple', 'Undefined':'black', 'Corona':'cyan'}
-data.info()
-
+df.reset_index(drop=True).head()
 
 size = 50000
 last_value = 0
 
-for sample in data.index:
-    if data['class'][sample] == 'Dripping':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='green', label='Dripping')
-    elif data['class'][sample] == 'Intermittent':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='blue', label='Intermittent')
-    elif data['class'][sample] == 'Cone Jet':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='red', label='Cone Jet')
-    elif data['class'][sample] == 'Multi Jet':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='purple', label='Multi Jet')
-    elif data['class'][sample] == 'Undefined':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='black', label='Undefined')
-    elif data['class'][sample] == 'Corona':
-        plt.plot(np.arange(last_value, last_value + size), data['data'][sample], c='cyan', label='Corona')
+for sample in df.index:
+    if df['spray_mode'][sample] == 'Dripping':
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='green', label='Dripping')
+    elif df['spray_mode'][sample] == 'Intermittent':
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue', label='Intermittent')
+    elif df['spray_mode'][sample] == 'Cone Jet':
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='red', label='Cone Jet')
+    elif df['spray_mode'][sample] == 'Multi Jet':
[…]

### 2023-03-13 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@
   \centering
-  \resizebox{150mm}{!}{\includegraphics{Metodology/Figuras/control_loop.png}}
+  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
   \caption{EHDA automation system setup}
@@
 \label{sec:concurrency}
+
+    In order to implement this system model to the software and explore parallel processing each system in the
+    model was developed as a separate Thread. For cuncurrency purpose and the flux of data in the control cicle was used queues structures.
+
+    \begin{enumerate}[a)]
+        \item Item 1;
+        \item Item 2; 
+        \item Etc.     
+    \end{enumerate}
 
@@
 
+    The software was previously developed as a electrospray multipurpose library\cite{Monica}. 
+    Continuing this methodology, in the setup json file there is a "sequence" atribute which can chosen beetween "ramp", "step", "map" or "control".
+    The controller thread will manage what the algorithm must do for each sequence.
+
 \subsection{Ramp}
@@
 
+\begin{algorithm}
+    \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
+    \begin{algorithmic}
+    \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
+        \State $voltage \gets voltage\_start$
+        \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
+            \State \Call{send\_voltage\_command}{voltage}
+            \State \Call{sleep}{step \_time}
+            \State $voltage \gets voltage + step\_size$
+        \EndWhile
+    \EndProcedure
+
+    \end{algorithmic}
+\end{algorithm}
+
 \subsection{Map}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
+        \caption{Domains of existence (stability) of Taylor cone-jets. \cite{gananCalvo} }
+        \label{fig:ganan_calvo_fig}
+    \end{figure}
 
@@
         \center
-        \includegraphics[width=15cm]{Metodology/Figuras/report2/map2Data.png}
-        \caption{Mapping Experiment example 1 }
+        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
+        \caption{Mapping Experiment example 1}
         \label{fig:map2Data_fig}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
+        \caption{Mapping Experiment example 1}
+        \label{fig:map3Data_fig}
     \end{figure}

### 2023-03-13 Documentation/WT group/NHL/Results/Results.tex
documentation

@@
 
-Para a execução do projeto, algumas etapas de desenvolvimento tiveram de ser seguidas: familiarização com o sistema, estudo dos módulos envolvidos, leitura dos requisitos, elaboração de documento descrevendo todo o processo de implementação e relacionamento com os diversos módulos, implementação e testes.
+\subsection*{2.3 Manual experiments}
+
+For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
+Also in order to find the stability region of cone jet mode for the liquid and setup used.
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=12cm]{Figuras/report3/exp25-01-1.png}
+        \caption{ exp25-01-1 (V x Q)}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=12cm]{Figuras/report3/exp-26-01-1.png}
+        \caption{ exp-26-01-1 (V x Q)}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=12cm]{Figuras/report3/exp26-01-2.png}
+        \caption{ exp-26-01-2 (V x Q)}
+    \end{figure}
+
+\subsection*{2.4 Automatic experiments}
+
+With the desired voltage and flowrate range defined for the automatic experiment the next part is to define how many datapoints will be collected in both
+x and y axis. Since we are introducing a new dimension for our experiment it is also increasing fast the amount of data collected.
+The goal of this part is to find the ideal combination of voltage step size, voltage step time and flowrate step size in order to get the most accurate results without exceding the separate memory for each experiment.
+
+In the further improvements of the routine it's ideal to apply a real time file writing with all experiment data.
+This will prevent that any crashes in the program lose all data and not overflow the memory allocated for the program.
+
+\begin{multicols}{3}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=5cm]{Figuras/report3/map1.png}
+        \caption{First mapping trial}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=5cm]{Figuras/report3/map2.png}
+        \caption{Second mapping trial}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=6cm]{Figuras/report3/map3.png}
+        \caption{third map - better result}
+    \end{figure}
+
+\end{multicols}
+
+\subsection*{2.5 Manual x Automatic Cone Jet stability island maps}
+
+For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.
+
+The Figure 13 shows a printscreen of how the experiment looks like in real time.
+We can see the image generated by the camera in the back.
+The routine code running in pycharm software on the right.
+And also real time signal plottings of the current data on the left.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=17cm]{Figuras/report3/screenshots/stableConeExp.png}
+    \caption{running experiment print screen}
+\end{figure}
+
+In Figure 14 we can see a result of the map generated by the automatic classification in this experiment.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=10cm]{Figuras/report3/map-exp-26-01.png}
+    \caption{ exp-26-01-23 }
+\end{figure}
+
+\pagebreak
+
+Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
+
+\begin{multicols}{2}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=9cm]{Figuras/report3/manual-mapping.png}
+        \caption{ exp-26-01 manual classification}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=9cm]{Figuras/report3/map4-stabilityIsland.png}
+        \caption{ exp-26-01 automatic classification}
+    \end{figure}
+
+\end{multicols}
 

### 2023-03-13 Documentation/WT group/NHL/systemDescription/systemDescription.tex
documentation

@@
       \center
-      \includegraphics[width=3cm]{systemDescription/Figuras/drippingexample.png}
+      \includegraphics[width=3cm]{Figuras/drippingexample.png}
       \caption{Dripping}
@@
       \center
-      \includegraphics[width=3cm]{systemDescription/Figuras/conejetexample.png}
+      \includegraphics[width=3cm]{Figuras/conejetexample.png}
       \caption{Cone Jet}
@@
       \center
-      \includegraphics[width=3cm]{systemDescription/Figuras/multijetexample.png}
+      \includegraphics[width=3cm]{Figuras/multijetexample.png}
       \caption{Multi Jet}
@@
   \centering
-  \resizebox{150mm}{!}{\includegraphics{systemDescription/Figuras/new_system_setup.png}}
+  \resizebox{150mm}{!}{\includegraphics{Figuras/new_system_setup.png}}
   \caption{EHDA automation system setup}

### 2023-03-14 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@
     In order to implement this system model to the software and explore parallel processing each system in the
-    model was developed as a separate Thread. For cuncurrency purpose and the flux of data in the control cicle was used queues structures.
+    model was developed as a separate Thread.
+    For cuncurrency on flux of data beetween threads was used queues structures.
+    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.
 
-    \begin{enumerate}[a)]
-        \item Item 1;
-        \item Item 2; 
-        \item Etc.     
-    \end{enumerate}
+    \subsection{Controller Thread}
+
+        It is responsible of sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
+        Also responsible of sending the finish event command that end the routine and trigger the threads to close their routines.
+        As input we have the setup config file and the \emph{feedback\_queue}. As output we have the values in the emph{controller\_output\_queue()}.
+
+    \subsection{Data Acquisition Thread}
+
+        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the powersupply, flowrate from the pump and concatenate into one sample data.
+        As output we have the values in the emph{data\_queue()}.
+
+    \subsection{Data Processing Thread}
+
+        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
+        As output we have the values in the emph{save\_data\_queue()}, emph{plotting\_queue()} and emph{feedback\_queue()}.
+
+        \subsection{Save Data Thread}
+
+        After the processing the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
+
+        With the new streamming model of saving a new structure of the collected data were created.
+        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
+        The structure of the
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=5cm]{Figuras/report4/json_structure.png}
+            \caption{Output data json structure}
+        \end{figure}
+
+        To work with this data I'm using pandas Dataframe.
+        With the command:
+
+        pandas.read\_json('PATH', orient='index').
+
+        The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
+        type of file called feather is much faster to work with the data.
+
+    \subsection{Video Thread}
+
+        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.
+
+    \subsection{Plot}
+
+        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilites of running outside of the main function. 
+        It is responsible of plotting in real time the current sample acquired and it respective fast fourier transform to evaluate the sample frequency spectrum.
+
+    - plotting data queue
 
@@
 
+    The control sequence is the only from our list of sequences that actually uses the feedback value. 
+    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
+
 \section{Optimizations}

### 2023-03-17 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

@@
 
-Electrohydrodynamic Atomization (EHDA), also known as Electrospray (ES), is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.
-The electric current flowing transported by the spray reveals characteristic shapes for different spray modes.
+Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
+The balance beetween capilary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
+The electric current transported by the spray reveals characteristic shapes for different spray modes.
 Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
@@
 This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.
-In the figure we can see how EHDA experiment works.
 
@@
 As pesquisas de EHDA têm contribuído como uma importante ferramenta para
-o desenvolvimento da tecnologia da água (dessalinização térmica e recuperação de metais), ciências dos materiais (nanofibras e
-fabricação de nanoesferas, recuperação de metal, membranas seletivas e baterias) e aplicação biomédica
-(encapsulamento). Além disso, o projeto está integrado à estratégia de Transição Energética e à Agenda de Inovação
-Agricultura, água e alimentos, tecnologias facilitadoras essenciais (KETs). Embora existam aplicações de EHDA em
+o desenvolvimento da tecnologia . Embora existam aplicações de EHDA em
 indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.

### 2023-03-17 Documentation/WT group/NHL/systemDescription/systemDescription.tex
documentation

@@
 
+The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA).
+The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
+That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}
+
+The stable balance between the capilary and field forces on the liquid suggest a \emph{quasi static} dynamics.
+For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
+
+\begin{figure}[H]
+  \centering
+  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
+  \caption{EHDA physical concept \cite{Gabriel}}
+  \label{fig:ehda_setup_ex2}
+\end{figure}
+
+\section{Spraying modes}
+\label{sec:spraying_modes_subsec}
+
+Since 1915 with his pioneering work in EHDA, Zeleny observed several functioning modes with very different characteristics.
+Years later the same phenomena was noticed by other scientists but the classification of these modes were still not well defined by the community.
+For that Cloupeau and Prunet-Foch proposed spray mode classifications based in what they have seen experimentally and it's still being used as basis for EHDA researchs.\cite{prunet}
+
+The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.
+
 \begin{multicols}{3}
@@
       \includegraphics[width=3cm]{Figuras/drippingexample.png}
+      \label{fig:dripping_camera_example}
       \caption{Dripping}
@@
       \includegraphics[width=3cm]{Figuras/conejetexample.png}
+      \label{fig:cone_camera_jet_example}
       \caption{Cone Jet}
@@
       \includegraphics[width=3cm]{Figuras/multijetexample.png}
+      \label{fig:multi_camera_jet_example}
       \caption{Multi Jet}
@@
 
+Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:
+
+\subsection{Dripping}
+\label{subsec:dripping}
+
+In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
+In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.
+
+\subsection{Intermittent}
+\label{subsec:Intermittent}
+
+Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
+In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
+
+\subsection{Cone Jet}
+\label{subsec:Cone Jet}
+
+\subsection{Multi Jet}
+\label{subsec:Multi Jet}
+
+\subsection{Corona sparks}
+\label{subsec:Corona sparks}
+
 \section{Instrumentation}
 \label{sec:instrumentation}
+
+\subsection{Setup Organization}
+\label{subsec:setup_organization}
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
+  \caption{EHDA experiment setup \cite{Luewton}}
+  \label{fig:ehda_setup}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup_pic}
+\end{figure}
+
+\subsection{Instruments Used}
+\label{subsec:instruments}
 
@@
 
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
+  \caption{EHDA automation system setup}
+  \label{fig:microdripping_current_pic}
+\end{figure}
+
 \clearpage

### 2023-03-21 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

@@
 This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.
+
+\section{EHDA}
+\label{sec:ehda_resume}
+
+The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA).
+The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
+That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}
+
+The stable balance between the capilary and field forces on the liquid suggest a \emph{quasi static} dynamics.
+For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
+
+\begin{figure}[H]
+  \centering
+  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
+  \caption{EHDA physical concept \cite{Gabriel}}
+  \label{fig:ehda_setup_ex2}
+\end{figure}
+
+\section{Spraying modes}
+\label{sec:spraying_modes_subsec}
+
+Since 1915 with his pioneering work in EHDA, Zeleny observed several functioning modes with very different characteristics.
+Years later the same phenomena was noticed by other scientists but the classification of these modes were still not well defined by the community.
+For that Cloupeau and Prunet-Foch proposed spray mode classifications based in what they have seen experimentally and it's still being used as basis for EHDA researchs.\cite{prunet}
+
+The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.
+
+\begin{multicols}{3}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{Figuras/drippingexample.png}
+      \label{fig:dripping_camera_example}
+      \caption{Dripping}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{Figuras/conejetexample.png}
+      \label{fig:cone_camera_jet_example}
+      \caption{Cone Jet}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{Figuras/multijetexample.png}
+      \label{fig:multi_camera_jet_example}
+      \caption{Multi Jet}
+  \end{figure}
+
+\end{multicols}
+
+Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:
+
+\subsection{Dripping}
+\label{subsec:dripping}
+
+In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
+In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.
+
+\subsection{Intermittent}
+\label{subsec:Intermittent}
+
+Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
+In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
+
+\subsection{Cone Jet}
+\label{subsec:Cone Jet}
+
+\subsection{Multi Jet}
+\label{subsec:Multi Jet}
+
+\subsection{Corona sparks}
+\label{subsec:Corona sparks}
+
+\section{Non-visual classification}
+\label{sec:non-visual-classification}
+
+\begin{figure}[H]
+    \centering
+    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
+    \caption{EHDA automation system setup}
+    \label{fig:microdripping_current_pic}
+  \end{figure}
 

### 2023-03-21 data_analysis/plot_raw_data.py

@@ -13,22 +13,34 @@ df.reset_index(drop=True).head()
 size = 50000
 last_value = 0
 
+# Plot raw data
+plt.figure(1)
 for sample in df.index:
     if df['spray_mode'][sample] == 'Dripping':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='green', label='Dripping')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #green', label='Dripping')
     elif df['spray_mode'][sample] == 'Intermittent':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue', label='Intermittent')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #blue', label='Intermittent')
     elif df['spray_mode'][sample] == 'Cone Jet':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='red', label='Cone Jet')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #red', label='Cone Jet')
     elif df['spray_mode'][sample] == 'Multi Jet':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='purple', label='Multi Jet')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #purple', label='Multi Jet')
     elif df['spray_mode'][sample] == 'Undefined':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='black', label='Undefined')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #black', label='Undefined')
     elif df['spray_mode'][sample] == 'Corona':
-        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='cyan', label='Corona')
+        plt.plot(np.arange(last_value, last_value + size)/1e5, df['current'][sample], c='blue')  #cyan', label='Corona')
     last_value += size
 
 plt.ylim(-50, 250)
+plt.ylabel('current [nA]')
+plt.xlabel('time [s]')
 plt.xlim(right=113)
 
+
+# Plot voltage
+
+plt.figure(2)
+plt.xlim(right=113)
[…]

### 2023-03-23 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

@@
 This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.
+
+\section{Droplet Formation}
+\label{sec:drop_formation}
+
+In the Aerosol reasearch community there is a branch of studies about droplets formation.
+In the droplet field a very functional for applications is the atomization, which refers to breaking the liquid in small droplets.
+There is many ways of atomizing a liquid.
+Some using mechanical energy such as ultrassound, rotating disk\cite{Disk_atomization}, pressure or blowing air on the meniscus.
+But also, some of them using electric forces such as electrospray atomization.
+
+For
 
@@
 
+Since the beginning of EHDA until today the researchs are being conducted manually with visual classification of the spraying mode using a camera or even by naked eyes.
+It is recommended to use a high speed (HS) camera because some dripping or intermittent states can be in a high frequency and be wrongly noticed as a stable condition.
+The setup in \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
+  \caption{EHDA experiment setup \cite{Luewton}}
+  \label{fig:ehda_setup}
+\end{figure}
+
+Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}.
+That current signal holds a lot o information
+about the dynamics that is happening with the liquid. In \ref{fig:microdripping_current_pic} we can see an example of that. It's clear the two droplets generated in this time frame.
+
 \begin{figure}[H]
@@
     \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
-    \caption{EHDA automation system setup}
+    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
     \label{fig:microdripping_current_pic}

### 2023-03-23 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@
 
+\begin{figure}[H]
+    \centering
+    \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
+    \caption{EHDA automation system setup}
+    \label{fig:metodology_example1}
+\end{figure}
+
+%   \begin{figure}[H]
+%     \centering
+%     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/multi_jet_print.png}}
+%     \caption{EHDA automation system setup}
+%     \label{fig:metodology_example2}
+% \end{figure}
+
 ilustramos o processo com a Figura \ref{fig:control_model_fig}.
 
-\begin{figure}[thpb]
+\begin{figure}[H]
   \centering
@@
             \center
-            \includegraphics[width=5cm]{Figuras/report4/json_structure.png}
+            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
             \caption{Output data json structure}
@@
 
- According to \cite{Sjaaks} evaluating the current data flowing through the nozzle to the plate we can analyze the signa that represents the spraying dynamics.
- through statistical analysis in this signal such as mean value and standart deviation we can analyze if the signal is stable or not.
+ According to Sjaaks\cite{Sjaaks}, evaluating the current data flowing through the nozzle to the plate can give us valuable information about the spraying behaviour.
+ Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
+ It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
+In this work, the author also exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.
 
+From those analysis we are appliying in our automatic classification system the relative standard deviation. Which is refered as the sample standart deviation divided by the sample mean values.
+
+ through statistical analysis in the signal such as mean value and standart deviation.
  Our classification by statistical analysis was implemented in the automation library made by the previous student \cite{Monica}.

### 2023-03-23 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@
 
+The classification is a key step in our routine.
+For being able to be used in multipurpose applications our classification routine must be able to run in real-time.
+Which means it must be fast and automatic classification.
+Our goal is to improve and apply in our routine different approachs of non-visual spraying classification using the current data collected from the system.
+
 \subsection{Statistical Analisys}
@@
 From those analysis we are appliying in our automatic classification system the relative standard deviation. Which is refered as the sample standart deviation divided by the sample mean values.
+
+\begin{figure}[H]
+    \centering
+    \resizebox{50mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
+    \caption{EHDA automation system setup}
+    \label{fig:sjaaks_statistical_class}
+\end{figure}
 

### 2023-03-23 Documentation/WT group/NHL/Results/Results.tex
documentation

@@
 \chapter{Results}
+\label{chap:Results}
 
-\subsection*{2.3 Manual experiments}
-
-For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
-Also in order to find the stability region of cone jet mode for the liquid and setup used.
+\section{Classification}
+\label{sec:classification_results}
 
@@
     \center
-        \includegraphics[width=12cm]{Figuras/report3/exp25-01-1.png}
-        \caption{ exp25-01-1 (V x Q)}
+    \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
+    \caption{ exp-26-01-2 (V x Q)}
 \end{figure}
@@
     \center
-        \includegraphics[width=12cm]{Figuras/report3/exp-26-01-1.png}
-        \caption{ exp-26-01-1 (V x Q)}
+    \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
+    \caption{ exp-26-01-2 (V x Q)}
 \end{figure}
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
+    \caption{ exp-26-01-2 (V x Q)}
+\end{figure}
+
+\section{Map Sequence}
+\label{sec:map_results}
+
+\subsection{Manual experiments}
+
+For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
+Also in order to find the stability region of cone jet mode for the liquid and setup used.
 
@@
 
-\subsection*{2.4 Automatic experiments}
+\begin{figure}[H]
+    \center
+    \includegraphics[width=12cm]{Figuras/regions.png}
+    \caption{ exp-26-01-2 (V x Q)}
+\end{figure}
+
+\subsection{Automatic experiments}
 
@@
 
-\subsection*{2.5 Manual x Automatic Cone Jet stability island maps}
+\subsection{Manual x Automatic Cone Jet stability island maps}
 
@@
 
-\pagebreak
-
 Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
@@
 
+Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
+
+Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
+
+\begin{multicols}{2}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=7cm]{Figuras/report4/map7-manual.png}
+        \caption{ exp-26-01 manual classification}
+    \end{figure}
+
+    \begin{figure}[H]
+        \center
+        \includegraphics[width=9cm]{Figuras/report4/map7-automatic-line.png}
+        \caption{ exp-26-01 automatic classification}
+    \end{figure}
+
+\end{multicols}
+
+\subsection{Non-dimensional axis}
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=12cm]{Figuras/19:03/non-dimensional-1.png}
+    \caption{ exp-26-01-2 (V x Q)}
+\end{figure}
+
+\section{Controller}
+\label{sec:controller_results}
+
+\subsection{Simple Controller}
+
+Flowrate perturbation robustness test
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=18cm]{Figuras/19:03/control_first_results.png}
+    \caption{ exp-26-01-2 (V x Q)}
+\end{figure}
+
 \section{Atividades do Projeto}

### 2023-03-29 software/controller.py
trying a more robust controller

@@ -62,6 +62,7 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
 
         finish_event.set()
 
+
     #            MAP SEQUENCE
     elif typeofmeasurement['sequence'] == "map":
         """responses = FUG_sendcommands(obj_fug_com, ['F0', '>S1B 0', 'I 600e-6', '>S0B 2', '>S0R ' + str(step_slope),
@@ -118,7 +119,7 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
         # print("[FUG THREAD] Responses from MAP sequence: ", str(responses))
 
 
-    #             CONTROL SEQUENCE
+    #            SIMPLE CONTROL SEQUENCE
     elif typeofmeasurement['sequence'] == "control":
 
 
@@ -143,7 +144,7 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
                         responses.append(FUG_sendcommands(obj_fug_com, ['U ' + str(voltage)]))
                         print("[FUG THREAD] Increasing Voltage")
 
-                    elif current_state == "Multi Jet" or current_state == "Corona Sparks":
+                    elif current_state == "Multi Jet" or current_state == "Corona":
                         voltage -= 100
                         responses.append(FUG_sendcommands(obj_fug_com, ['U ' + str(voltage)]))
                         print("[FUG THREAD] Decreasing voltage")
@@ -153,8 +154,6 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
 
                     else:
                         print("[FUG THREAD] current state not known")
-
-                    previous_state = current_state
 
                     # SAFETY VOLTAGE LIMITS
                     if voltage > typeofmeasurement['voltage_stop']:
@@ -176,6 +175,110 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
                 print("ERROR: ", str(e))
                 print("[CONTROLLER THREAD] ERROR!")
                 sys.exit(1)
+
+
+    #            ROBUST CONTROL SEQUENCE
+    elif typeofmeasurement['sequence'] == "robust_control":
+
+
+        responses = FUG_sendcommands(obj_fug_com, ['>S1B 0', 'I 600e-6', '>S0B 0', '>S0R ' + str(typeofmeasurement['slope']), 'U ' + str(typeofmeasurement['voltage_start']), 'F1'])
+        current_state = "Dripping"
+
[…]

### 2023-03-29 Documentation/WT group/NHL/LiteratureReview/LiteratureReview.tex
documentation

\chapter{Literature Review}
\label{chap:lit_review}

\section{EHDA}
\label{sec:ehda_resume}

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}

The stable balance between the capilary and field forces on the liquid suggest a \emph{quasi static} dynamics.
For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.

\begin{figure}[H]
  \centering
  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
  \caption{EHDA physical concept \cite{Gabriel}}
  \label{fig:ehda_setup_ex2}
\end{figure}

\section{Droplet Formation}
\label{sec:drop_formation}

In the Aerosol reasearch community there is a branch of studies about droplets formation. In the droplet field a very functional for applications is the atomization, which refers to breaking the liquid in small droplets.
There is many ways of atomizing a liquid. Some using mechanical energy such as ultrassound, rotating disk\cite{Disk_atomization}, pressure or blowing air on the meniscus. But also, some of them using electric forces such as electrospray atomization.

For

\section{Spraying modes}
\label{sec:spraying_modes_subsec}

Since 1915 with his pioneering work in EHDA, Zeleny observed several functioning modes with very different characteristics.
Years later the same phenomena was noticed by other scientists but the classification of these modes were still not well defined by the community.
For that Cloupeau and Prunet-Foch proposed spray mode classifications based in what they have seen experimentally and it's still being used as basis for EHDA researchs.\cite{prunet}

The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.

\begin{multicols}{3}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/drippingexample.png}
      \label{fig:dripping_camera_example}
      \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/conejetexample.png}
      \label{fig:cone_camera_jet_example}
      \caption{Cone Jet}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/multijetexample.png}
      \label{fig:multi_camera_jet_example}
      \caption{Multi Jet}
  \end{figure}

\end{multicols}

Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:

\subsection{Dripping}
\label{subsec:dripping}

In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.

\subsection{Intermittent}
\label{subsec:Intermittent}

Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.

\subsection{Cone Jet}
\label{subsec:Cone Jet}

\subsection{Multi Jet}
\label{subsec:Multi Jet}

\subsection{Corona sparks}
\label{subsec:Corona sparks}

\section{Non-visual classification}
\label{sec:non-visual-classification}

Since the beginning of EHDA until today the researchs are being conducted manually with visual classification of the spraying mode using a camera or even by naked eyes.
It is recommended to use a high speed (HS) camera because some dripping or intermittent states can be in a high frequency and be wrongly noticed as a stable condition.
The setup in \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
  \caption{EHDA experiment setup \cite{Luewton}}
  \label{fig:ehda_setup}
\end{figure}

Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. That current signal holds a lot o information 
about the dynamics that is happening with the liquid. In \ref{fig:microdripping_current_pic} we can see an example of that. It's clear the two droplets generated in this time frame.

\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
    \label{fig:microdripping_current_pic}
  \end{figure}

\clearpage

### 2023-03-29 Documentation/WT group/NHL/Results/Results.tex
documentation

@@
 \label{chap:Results}
+
+\begin{figure}[H]
+    \centering
+    \resizebox{170mm}{!}{\includegraphics{Figuras/19:03/axs2.png}}
+    \caption{Cone Jet Classification}
+    \label{fig:multi_class_exp}
+\end{figure}
 
@@
             \center
-    \includegraphics[width=17cm]{Figuras/report3/screenshots/stableConeExp.png}
+            \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
             \caption{running experiment print screen}
@@
 
+        \begin{algorithm}
+            \caption{simple controller}\label{alg:simple_controller}
+            \begin{algorithmic}
+            \Function{controller}{$spray\_mode$}
+
+                \If{$spray\_mode$ = $'Intermittent'$ or $spray\_mode$ = $'Dripping'$}
+                    \State \Call{send\_voltage\_command}{$voltage$ + 100}
+                \ElsIf{$spray\_mode$ = $'Multi Jet'$ or $spray\_mode$ = $'Corona'$}
+                    \State \Call{send\_voltage\_command}{$voltage$ - 100}
+                \ElsIf{ $spray\_mode$ = $"Cone Jet"$}
+                    \Comment{Keep Stable}
+                \EndIf
+
+            \EndFunction
+            \end{algorithmic}
+        \end{algorithm}
+
         Flowrate perturbation robustness test
@@
             \center
-    \includegraphics[width=18cm]{Figuras/19:03/control_first_results.png}
+            \includegraphics[width=15cm]{Figuras/19:03/control_first_results.png}
             \caption{ exp-26-01-2 (V x Q)}
@@
 
+    \subsection{Robust Controller}
+
+    \subsection{Fuzzy Controller}
+
+        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
+        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzified.
+        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.
+
+        For that, I tried to fuzzyfi the controller input by the data acquired in the step routine.
+With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.
+
+        \begin{multicols}{2}
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
+                \caption{Fuzzyfication}
+                \label{fig:fuzzy_input}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
+                \caption{Defuzzyfication}
+                \label{fig:fuzzy_output}
+            \end{figure}
+        \end{multicols}
+
+        \begin{figure}[H]
+            \centering
+            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
+            \caption{Fuzzy Rules}
+            \label{fig:fuzzy_rules}
+        \end{figure}
+
+        \begin{multicols}{2}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
+                \caption{Test 1: fuzzy controller}
+                \label{fig:fuzzy_test1}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
+                \caption{Test 2: fuzzy controller}
+                \label{fig:fuzzy_test2}
+            \end{figure}
+
+        \end{multicols}
+
 \section{Atividades do Projeto}
-\label{metodo3}
+\label{sec:metodo3}
 
 \section {Requisitos do Sistema}
-\label{req}
+\label{sec:req}
 

### 2023-03-30 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

--- 2023-03-17 Documentation/WT group/NHL/Introduction/Introduction.tex
@@
 
+The biggest motivation to use EHDA is to have a more precise and uniform size and shape of droplets creation.
+
 As pesquisas de EHDA têm contribuído como uma importante ferramenta para
@@
 
-\section{Project objectives}
+\section{Project Goals}
 \label{sec:objetivos}
@@
 
+multipurpose applications
+both scientific and industrial application
+
 \begin{enumerate}[a)]
-\item Item 1;
-\item Item 2; 
-\item Etc.     
+\item Fully automated and intuitive system for EHDA research and industrial application.
+\item Real Time non-visual classification.    
+\item Control and stabilization of desired spraying modes.   
+\item System Portability.
 \end{enumerate}
@@
 e disponibilidade de infraestrutura.
-
-\clearpage

### 2023-04-01 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@
 
-\section{System Model}
-\label{sec:control_model}
+This chapter is about describing the metodology and developments to achieve the project goals. 
+The python routine which this project is about was developed by the previous student working on it.\cite{Monica}
+The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to industries application or research.
+
+From the optimizations made, it highlights the following:
+
+- Integrate high speed camera to the experiment routine.
+
+- Remodel the software to support threads in order to separate the sensoring and controlling routines.
+
+- Reduce the data collected size.
+
+- Synchronize the power supply step commands and voltage sensoring.
+
+- Reestructure the setup file in order to make it more intuitive to use the experiment.
+
+- Improvements in code organization and readability.
 
@@
 
-%   \begin{figure}[H]
-%     \centering
-%     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/multi_jet_print.png}}
-%     \caption{EHDA automation system setup}
-%     \label{fig:metodology_example2}
-% \end{figure}
+\section{System Model}
+\label{sec:control_model}
 
@@
 
-\section{Threading and Queues}
-\label{sec:concurrency}
+\subsection{Threading and Queues}
+\label{subsec:concurrency}
 
@@
 
-\section{Optimizations}
-\label{sec:routine_optimization}
+\section{System Portability}
+\label{sec:portability}
 
-About the python algorithm to turn the experiment autonomous it was made a study and modelling of the software architecture to optimize it for further control loop application to be implemented.
-From the changes made until now it highlights:
-
-- Integrate high speed camera to the experiment routine.
-
-- Remodel the software to support threads in order to separate the sensoring and controlling routines.
-
-- Reduce the data collected size.
-
-- Synchronize the power supply step commands and voltage sensoring.
-
-- Reestructure the setup file in order to make it more intuitive to use the experiment.
-
-- Improvements in code organization and readability.
-
-About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to
-make the experiment the most stable and easy to reach cone-jet mode as possible.
-For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
-Therefore compromising the stabilization in cone jet mode.
-A solution for that was to increasethe flowrate wich smooths this pumping noise.
-For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
-
-\subsection{Pump Integration}
-
-    The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
-    two main variables that afect the system. 
-    It will bring more complexity for the system since now we are dealing with multivariable control.
-    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
-    % Our control model is now a MISO \footcite{MISO: Multiple Inputs Single Output} system. The crossover (couple) between the controlled variables will be evaluated in further reports.
-
-    About the pump interface. As I could not find a good ready-to-use library for this pump I developed an simple and intuitive interface to be our software routine.
-    The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
+    Raspberry Pi
 

### 2023-04-01 Documentation/WT group/NHL/Results/Results.tex
documentation

@@
     \end{figure}
-
-    \subsection{Automatic experiments}
-
-        With the desired voltage and flowrate range defined for the automatic experiment the next part is to define how many datapoints will be collected in both
-        x and y axis. Since we are introducing a new dimension for our experiment it is also increasing fast the amount of data collected.
-        The goal of this part is to find the ideal combination of voltage step size, voltage step time and flowrate step size in order to get the most accurate results without exceding the separate memory for each experiment.
-
-        In the further improvements of the routine it's ideal to apply a real time file writing with all experiment data.
-        This will prevent that any crashes in the program lose all data and not overflow the memory allocated for the program.
-
-        \begin{multicols}{3}
-
-            \begin{figure}[H]
-                \center
-                \includegraphics[width=5cm]{Figuras/report3/map1.png}
-                \caption{First mapping trial}
-            \end{figure}
-
-            \begin{figure}[H]
-                \center
-                \includegraphics[width=5cm]{Figuras/report3/map2.png}
-                \caption{Second mapping trial}
-            \end{figure}
-
-            \begin{figure}[H]
-                \center
-                \includegraphics[width=6cm]{Figuras/report3/map3.png}
-                \caption{third map - better result}
-            \end{figure}
-
-        \end{multicols}
 

### 2023-04-01 Documentation/WT group/NHL/systemDescription/systemDescription.tex
documentation

--- 2023-03-13 Documentation/WT group/NHL/systemDescription/systemDescription.tex
@@
 \chapter[System Description]{System Description}
-\label{chap:descricaoproblema}
-
-\section{EHDA}
-\label{sec:ehda_resume}
-
-\begin{multicols}{3}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/drippingexample.png}
-      \caption{Dripping}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/conejetexample.png}
-      \caption{Cone Jet}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/multijetexample.png}
-      \caption{Multi Jet}
-  \end{figure}
-
-\end{multicols}
+\label{chap:system_description}
 
@@
 \label{sec:instrumentation}
+
+The main instruments used for this project are listed above:
+
+\begin{enumerate}[a)]
+
+  \item High Voltage Power Supply (HVPS)
+
+     - brand: FUG
+
+     - model: HCP35-20kV
+
+    HVPS provides the electrical potential to the liquid, which can be applied by connecting the HVPS directly to the liquid feeding capillary or needle to a grounded electrode (usually a plate or a ring) located downstream.\cite{Monica}
+    The setup has the USB serial interface for controlling and polling measurements.
+
+    The software has an interface to integrate the HVPS to our routine.
+This interface can be found in \emph{FUG\_function.py} file where is located the functions used to control and collect data from this instrument.
+    In case of future change of equipment brand a new interface must be created within this file to match another manufacturer specifications.
+
+  \item Wireless Oscilloscope
+
+     - Brand: \emph{TiePie engineering}
+
+     - model: TiePie WifiScope WS6 DIFF
+
+    The signal analysis with an oscilloscope using WiFi technology allows an in-depth case study of the electric current signal.
+    The current is measured via a TiePie WifiScope WS6 from TiePie engineering that is a battery powered oscilloscope capable of transmitting data via a WiFi connection allowing it to be placed in the high voltage or ground path.
+
+    Wireless communication allows us to make measurements disconnected to an external power supply, which gives us more safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
+    The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 M%Ω).
+    TiePie WifiScope WS6 has a resolution of up to 16 bit at a minimal input range of 200 mV, sufficient to measure currents down to 1 nA.
+
+    The iterface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
+Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.
+
+  \item Humidity and Temperature sensor
+
+  The stability of the system is aftected by many physical effects. Evidently having the more parameters analysed favours the system control.
+  The surface tension force is dependant of the liquid-gas interface on the meniscus. Hence, the gas around it must be constantly the same and so its humidity.
+  Also, temperature is a variable that interfere in many phenomenas in the system. Specially the liquid properties such as viscosity.
+
+  For that, a standart microcontroler development board (\emph{Arduino Uno}) with a temperature and humidity sensor (DHT11) was configured to add that data in real time in the routine.
+  The Arduino code can be found in the \emph{/peripherals} folder.
+
+  \item High Speed Camera
+
+  - Brand: \emph{Photron}
+
+  - model: Photron fastcam mini
+
+  \item Syringe pump
+
+  - Brand: \emph{Master dual}
+
+  - model: WPI AL-1000
+
+  The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
+    two main variables that afect the system. 
+    It will bring more complexity for the system since now we are dealing with multivariable control.
+    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
+    % Our control model is now a MISO \footcite{MISO: Multiple Inputs Single Output} system. The crossover (couple) between the controlled variables will be evaluated in further reports.
+
+    About the pump interface. As I could not find a good ready-to-use library for this pump I developed an simple and intuitive interface to be our software routine.
+    The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
+
+  Also, the supply of constant pressure can also 
+    \cite{prunet}
+  The supply at constant pressure sometimes favours the stability of the spray.
+However, the flow rate depends on the applied pressure and pressure losses between the tank and the end of the capillary, which themselves are dependent on the liquid chosen and on its temperature.
+This volume flow rate may also depend on the applied voltage, since the electrostatic pressure on the meniscus produces a suction effect.
+
+  \end{enumerate}
+
+\subsection{Setup Organization}
+\label{subsec:setup_organization}
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup_pic}
+\end{figure}
 
@@
 
-\section{First Experiments}
-\label{sec:first_experiments}
+\section{Setup Validation}
+\label{sec:setup_validation}
 
@@
  And also physical variables such as flowrate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
-The instruments used in the setup are:
 
-\begin{enumerate}[a]
-  \item High Voltage Power Supply (FUG)
-  \item Oscilloscope TiePie WS6 DIFF 
-  \item Humidity and Temperature sensor (DHT11 + Arduino Uno)
-  \item High Speed Camera - Photron fastcam mini
-  \item Syringe pump
-  \end{enumerate}
+ About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to
+make the experiment the most stable and easy to reach cone-jet mode as possible.
+For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
+Therefore compromising the stabilization in cone jet mode.
+A solution for that was to increasethe flowrate wich smooths this pumping noise.
+For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
 

### 2023-04-05 software/electrospray.py
file startup

@@ -8,9 +8,8 @@ from scipy.signal import butter, lfilter
 
 
 class ElectrosprayConfig:
-    def __init__(self, file_setup, file_liquid):
+    def __init__(self, file_setup):
         self.file_setup = file_setup
-        self.file_liquid = file_liquid
         self.ki = 6.46  # no units
 
     def __repr__(self):
@@ -39,15 +38,14 @@ class ElectrosprayConfig:
         """with open(self.file_setup) as json_file:
             self.json_setup_obj = json.load(json_file)"""
 
-    def load_json_config_liquid(self):
+    def load_json_config_liquid(self, file_liquid):
 
         print("load_json_config_liquid")
-        # print(self.file_liquid)
 
-        with open(self.file_liquid, 'r') as file:
+        with open(file_liquid, 'r') as file:
             # First we load existing data into a dict.
             self.json_liquid_obj = json.load(file)
-            # print(type(self.json_liquid_obj))
+            print(self.json_liquid_obj)
 
         """with open(self.file_liquid) as json_file:
             self.json_liquid_obj = json.load(json_file) # dictionary"""

### 2023-04-05 software/mainElectrospray.py

@@ -20,7 +20,6 @@ import save_data
 # # # **************************************
 if __name__ == '__main__':
 
-
 # # # **************************************
 # # #         INITIAL CONFIGURATION
 # # # **************************************
@@ -32,33 +31,32 @@ if __name__ == '__main__':
 
     name_setup = "mapsetup"
     setup = "setup/nozzle/" + name_setup
-    name_liquid = "ethanol" # ["ethyleneglycolHNO3", "ethanol", water60alcohol40, 2propanol]
-    liquid = "setup/liquid/" + name_liquid
-    current_shape_comment = "difficult cone jet stabilization"
    
     plt.style.use('seaborn-colorblind')
     plt.ion()
 
-    electrospray_config_liquid_setup_obj = ElectrosprayConfig(setup + ".json", liquid + ".json")
-    electrospray_config_liquid_setup_obj.load_json_config_liquid()
+    # Starting Class Objects
+    electrospray_config_liquid_setup_obj = ElectrosprayConfig(setup + ".json")
     electrospray_config_liquid_setup_obj.load_json_config_setup()
-    electrospray_validation = ElectrosprayValidation(name_liquid)
-    electrospray_classification = classification_electrospray.ElectrosprayClassification(name_liquid)
-    electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
     electrospray_config_setup = electrospray_config_liquid_setup_obj.get_json_setup()
+    electrospray_config_liquid_setup_obj.load_json_config_liquid(electrospray_config_setup["name_liquid"] + ".json")
+    electrospray_validation = ElectrosprayValidation(electrospray_config_setup["name_liquid"])
+    electrospray_classification = classification_electrospray.ElectrosprayClassification(electrospray_config_setup["name_liquid"])
+    electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
+
+    # Program variables
     impedance = electrospray_config_setup["osc_impedance"]
     typeofmeasurement = electrospray_config_setup["typeofmeasurement"]
     save_path = electrospray_config_setup["save_path"]
     plot_real_time = electrospray_config_setup["plot_real_time"]
     syringe_diameter = electrospray_config_setup["diameter syringe"]
     number_camera_partitions = electrospray_config_setup["number_camera_partitions"]
-
-
+    liquid = "setup/liquid/" + electrospray_config_setup["name_liquid"]
 
     #        PORTS
-    arduino_COM_port = 1
-    fug_COM_port = 2
[…]

### 2023-04-05 software/save_data.py

@@ -7,9 +7,9 @@ import json
 def save_data(
             save_data_queue,
             typeofmeasurement,
-            name_liquid,
             save_path,
             finish_event,
+            electrospray_validation,
             electrospray_config_liquid_setup_obj,
             electrospray_config_setup
             ):
@@ -84,6 +84,8 @@ def save_data(
                             s.write('sample '+str(sample), data_measurement)
 
                         print("[SAVING] saved electrospray sample:", sample)
+
+                        print(electrospray_validation.get_validation_dictionary())
                         
 
 

### 2023-04-05 software/validation_electrospray.py
scaling laws

@@ -8,15 +8,14 @@ class ElectrosprayValidation:
     def __init__(self, name_liquid):
         self.name_liquid = name_liquid
 
-        self.all_data = []
-        self.flow_rate_chen_pui = []
-        self.alpha_chen_pui = []
-        self.I_emitted_chen_pui = []
-        self.I_hartman = []
+        self.flow_rate_chen_pui
+        self.alpha_chen_pui
+        self.I_emitted_chen_pui
+        self.I_hartman
         self.sjaak_std_mean_array = []
         self.sjaak_mean_median_array = []
         self.med_value_array = []
-        self.mean_value_array = []
+        self.mean_value_array
         self.sjaak_verified = []
         self.sjaak_verified_false = []
         self.sjaak_verified_true = []
@@ -34,12 +33,11 @@ class ElectrosprayValidation:
 
     def get_validation_dictionary(self):
         dictionary = {
-            "all data": self.all_data.tolist(),
-            "mean_value_array": self.mean_value_array.tolist(),
-            "flow_rate chen pui": self.flow_rate_chen_pui.tolist(),
-            "alpha_chen_pui": self.alpha_chen_pui.tolist(),
-            "I_emitted_chen_pui": self.I_emitted_chen_pui.tolist(),
-            "I_hartman": self.I_hartman.tolist()
+            "mean_value_array": self.mean_value_array,
+            "flow_rate chen pui": self.flow_rate_chen_pui,
+            "alpha_chen_pui": self.alpha_chen_pui,
+            "I_emitted_chen_pui": self.I_emitted_chen_pui,
+            "I_hartman": self.I_hartman
         }
         return dictionary
 
@@ -73,31 +71,21 @@ class ElectrosprayValidation:
         ki = 6.46
 
         print("\nprocessing_mean:", mean)
-        data_points_np = np.array(data)
         self.data_points_list = data.tolist()
         print("\nmeasurements list:", self.data_points_list)
-        self.mean_value_array.append(mean)
+        self.mean_value_array = mean
 
+        self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui[i] / self.dieletric_const) ** (.5)
 
-        for i in range(len(self.data_points_list)):
-            self.flow_rate_chen_pui.append(flow_rate)
-            flow_rate_aux = self.flow_rate_chen_pui[i]
-            if flow_rate_aux == 0.0:
[…]

### 2023-04-05 software/data_processing.py
scaling laws test

@@ -27,6 +27,8 @@ def data_processing(data_queue,
     sample = 0
     previous_flowrate = 0
 
+    electrospray_validation.set_data_from_dict_liquid(electrospray_config_liquid_setup_obj.get_json_liquid())
+
     # THREAD LOOP
     print("[DATA_PROCESSING THREAD] starting loop")
     while not finish_event.is_set():
@@ -125,13 +127,10 @@ def data_processing(data_queue,
             print("ERROR: ", str(e)) 
             print("[DATA_PROCESSING THREAD] Failed to put value in save_data_queue")
 
-        try:    
+        try:
 
-            if current_shape == "Cone Jet":
-                electrospray_validation.set_data_from_dict_liquid(electrospray_config_liquid_setup_obj.get_json_liquid())
-
-                # Validation through the Chen_Pui Article
-                electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data, electrospray_processing.mean_value, electrospray_data.flow_rate)
+            # Validation through the Chen_Pui Article
+            electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data, electrospray_processing.mean_value, electrospray_data.flow_rate)
 
         except Exception as e:
             print("ERROR: ", str(e)) 

### 2023-04-05 software/mainElectrospray.py

@@ -39,7 +39,8 @@ if __name__ == '__main__':
     electrospray_config_liquid_setup_obj = ElectrosprayConfig(setup + ".json")
     electrospray_config_liquid_setup_obj.load_json_config_setup()
     electrospray_config_setup = electrospray_config_liquid_setup_obj.get_json_setup()
-    electrospray_config_liquid_setup_obj.load_json_config_liquid(electrospray_config_setup["name_liquid"] + ".json")
+    liquid = "setup/liquid/" + electrospray_config_setup["name_liquid"]
+    electrospray_config_liquid_setup_obj.load_json_config_liquid(liquid + ".json")
     electrospray_validation = ElectrosprayValidation(electrospray_config_setup["name_liquid"])
     electrospray_classification = classification_electrospray.ElectrosprayClassification(electrospray_config_setup["name_liquid"])
     electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
@@ -51,7 +52,7 @@ if __name__ == '__main__':
     plot_real_time = electrospray_config_setup["plot_real_time"]
     syringe_diameter = electrospray_config_setup["diameter syringe"]
     number_camera_partitions = electrospray_config_setup["number_camera_partitions"]
-    liquid = "setup/liquid/" + electrospray_config_setup["name_liquid"]
+
 
     #        PORTS
     arduino_COM_port = electrospray_config_setup["arduino_com_port"]

### 2023-04-05 software/validation_electrospray.py

@@ -8,14 +8,6 @@ class ElectrosprayValidation:
     def __init__(self, name_liquid):
         self.name_liquid = name_liquid
 
-        self.flow_rate_chen_pui
-        self.alpha_chen_pui
-        self.I_emitted_chen_pui
-        self.I_hartman
-        self.sjaak_std_mean_array = []
-        self.sjaak_mean_median_array = []
-        self.med_value_array = []
-        self.mean_value_array
         self.sjaak_verified = []
         self.sjaak_verified_false = []
         self.sjaak_verified_true = []
@@ -70,22 +62,22 @@ class ElectrosprayValidation:
     def calculate_scaling_laws_cone_jet(self, data, mean, flow_rate):
         ki = 6.46
 
-        print("\nprocessing_mean:", mean)
-        self.data_points_list = data.tolist()
-        print("\nmeasurements list:", self.data_points_list)
+        # print("\nprocessing_mean:", mean)
         self.mean_value_array = mean
-
-        self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui[i] / self.dieletric_const) ** (.5)
-
-        self.I_emitted_chen_pui = ki * self.dieletric_const ** (.25) * self.alpha_chen_pui[i] ** (.5)
-        i_actual = data
-
-        b_hartman = i_actual / ((self.surface_tension * self.electrical_conductivity * flow_rate) ** .5)
-        self.I_hartman = b_hartman * ((self.surface_tension * self.electrical_conductivity * flow_rate) ** .5)
 
         if self.electrical_conductivity == 0.0 or self.rho == 0.0:
             self.flow_rate_chen_pui = 0.0
         else:
             self.flow_rate_chen_pui =  (self.dieletric_const ** 0.5) * self.permitivity * self.surface_tension / (self.rho * self.electrical_conductivity)
+
+        self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui / self.dieletric_const) ** (.5)
+
+        self.I_emitted_chen_pui = ki * self.dieletric_const ** (.25) * self.alpha_chen_pui ** (.5)
+        # i_actual = data
+        #
+        # b_hartman = i_actual / ((self.surface_tension * self.electrical_conductivity * flow_rate) ** .5)
+        # self.I_hartman = b_hartman * ((self.surface_tension * self.electrical_conductivity * flow_rate) ** .5)
+
+        self.I_hartman = "Unknown"
 
 

### 2023-04-05 Documentation/WT group/NHL/Results/Results.tex
Documentation

@@
     \resizebox{170mm}{!}{\includegraphics{Figuras/19:03/axs2.png}}
-    \caption{Cone Jet Classification}
+    \caption{Printscreen during an experiment.
+At this moment we are in Multi Jet spraying mode.
+At the left we can see the current signal has a smoth and constant curve.
+We can also see the automatic classification at the right side.}
     \label{fig:multi_class_exp}
@@
 
+The results of the classification using the statistical values are illustrated in figures \ref{fig:step_voltage}, \ref{fig:raw_data} and \ref{fig:class_step_data}.
+
 \begin{figure}[H]
@@
     \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
-    \caption{ exp-26-01-2 (V x Q)}
+    \caption{Input voltage step graph. The range is beetween 3K-10K Volts. Step size of 50V and steo time of 5 seconds.}
+    \label{fig:step_voltage}
 \end{figure}
@@
     \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
-    \caption{ exp-26-01-2 (V x Q)}
+    \caption{Output raw data collected in the voltage range experiment showed in \ref{fig:step_voltage}. The sampling rate of the oscilloscope is 10KHz. This graph has 1.5 Million data points.}
+    \label{fig:raw_data}
 \end{figure}
+
+Notice that is even possible to a visual classification.
+The Dripping mode has a current mean of 0V.
+The Intermittent state has a high variation of values that can be seen by the thickness of the graph.
+The Cone jet is a thiner graph because the signal is more constant.
+The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet.
 
@@
     \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
-    \caption{ exp-26-01-2 (V x Q)}
+    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colours are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
+    \label{fig:class_step_data}
 \end{figure}

### 2023-04-12 Documentation/UFMG/PFCII/Apendices/ApendiceB.tex
documentation

\chapter{O que mais faltou}

Inclua aqui informações que não sejam tão relevantes para o entendimento do projeto mas que ainda sejam importantes para documentá-lo.

\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/naked_eyes.png}}
    \caption{EHDA physical concept }
\end{figure}

### 2023-04-12 Documentation/UFMG/PFCII/Capa/capa.tex
documentation

--- 2023-03-03 Documentation/WT group/NHL/Capa/capa.tex
@@
 
-    \begin{figure}
+    \vspace{2cm}
+    \begin{figure}[h]
         \centering
-            % \subfigure{\includegraphics[width=5cm]{Capa/Figuras/wac.png}}
-            \hspace{0.1\textwidth}
-            \subfigure{\includegraphics[width=6cm]{Capa/Figuras/nhl-stenden.png}}
-            \vspace{3cm} 
+        \includegraphics[scale=0.5]{Figuras/brasao_ufmg.png}
     \end{figure}
+    \vspace{2cm}
 
     {\bf\Large EHDA closed loop control system based on real time non-visual spray mode classification\\}
-    \vspace{1cm} 
-    {\Large Report}
+    \vspace{2cm} 
+    {\Large Monography}
     \vspace{2cm}
@@
     \vspace{2cm}
-    {\large Supervisor: Luewton L F Agostinho}
+    {\large Supervisors:\\ Luewton L F Agostinho\\
+            Klaus Glanzer \\
+            Antônio C. Munoz\\
+            Vitor Angelo}
     \vspace{2cm}
@@
 
+    \newpage
+\clearpage
+\thispagestyle{empty}
+
+\begin{titlepage}
+
+\centering
+\vspace{2cm}
+\textbf{Monography}\\
+\vspace{2cm}
+\centering
+\textbf{EHDA closed loop control system based on real time non-visual spray mode classification.}\\
+\vspace{5cm}
+
+\parbox{1.0\textwidth} 
+{\large 
+Document submitted to the examining board designated by the Lectoraat Watertechnology at the NHL Stenden University of Applied Sciences and the Colegiado de Engenharia de Controle e Automação at the Universidade Federal de Minas Gerais as part of the requirements for approval in the subject Final Course Project II.}
+
+\vspace{7cm}
+
+\end{titlepage}
+
 \title{
     EHDA closed loop control system based on real time non-visual spray mode classification \\
-    \large Relatório de Atividades}
+    \large Monography}

### 2023-04-12 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

--- 2023-03-30 Documentation/WT group/NHL/Introduction/Introduction.tex
@@
 \chapter{Introduction}
-\label{chap:intro} %este label será usado para referenciar este capítulo
+\label{chap:intro} 
+%este label será usado para referenciar este capítulo
 
@@
 \label{sec:motivacao}
+
 % Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes.
@@
 
-As pesquisas de EHDA têm contribuído como uma importante ferramenta para
-o desenvolvimento da tecnologia . Embora existam aplicações de EHDA em
-indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.
-A corrente elétrica que flui transportada pelo spray revela formas características para diferentes modos de atomização.
-Essas formas não podem ser simplesmente resumidas por seu valor médio. Na figura um podemos ver um exemplo de cone-jet
-modo eletrospray.
+EHDA research has contributed as an important tool for the development of technology. 
+Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is done empirically and based on average current measurements.
+The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
+These forms cannot simply be summarized by their average value. In figure one we can see an example of cone-jet electrospray mode.
 
-Figura 1: exemplo de EHDA
+Figure 1: example of EHDA
 
-As técnicas de processamento de sinal podem permitir uma classificação não visual do modo de pulverização com base no elétrico
-forma atual. O processo de pulverização impõe ruídos e sequências aleatórias no sinal medido tornando-o
-classificação não é uma tarefa trivial.
-Aplicações industriais exigem estabilização automatizada de um modo de pulverização. Isso pode ser obtido por um sistema fechado
-sistema de controle de circuito. A classificação automatizada do modo de pulverização é uma parte crucial de um sistema de controle, assim como
-o desenvolvimento de um algoritmo de controle apropriado.
+Signal processing techniques may allow non-visual classification of spray mode based on electrical current form. 
+The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
+Industrial applications require automated stabilization of a spray mode. 
+This can be achieved by a closed system loop control system. 
+Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.
 
 \section{Project Goals}
-\label{sec:objetivos}
+\label{sec:goals}
 
-Tendo em vista o exposto acima, este projeto tem por objetivos:
-
-multipurpose applications
-both scientific and industrial application
+In view of the above, this project aims to:
 
 \begin{enumerate}[a)]
+\item multipurpose applications both scientific and industrial application.
 \item Fully automated and intuitive system for EHDA research and industrial application.
@@
 
-O conteúdo desta seção pode se sobrepor um pouco com o da seção anterior, podendo ela ser um sumário dos pontos expostos anteriormente.
-A escolha do título da seção talvez seja mais apropriada para a fase de proposta do projeto.
-Afinal, nesta fase se conhecem os objetivos e não os resultados.
-Por outro lado, fará pouco sentido discutir objetivos quando o projeto está finalizado, especialmente se tais objetivos não foram alcançados.
+% The content of this section may overlap somewhat with that of the previous section, and it may be a summary of the points made above. 
+% The choice of section title may be more appropriate for the project proposal phase. 
+% After all, at this stage the objectives are known and not the results. 
+% On the other hand, it makes little sense to discuss objectives when the project is finished, especially if those objectives have not been achieved.
 
 \section{People envolved}
-\label{sec:empresa}
+\label{sec:companies}
 
@@
 Descreva também o seu vínculo com a empresa.
-Implementações de processamento de sinal de projetos anteriores
-do grupo NHL Stenden Water Technology estão mostrando bons resultados de classificação. Mais pesquisas são
-necessário para melhorar a precisão da classificação e pesquisa e implementação de uma classificação adequada
-algoritmo. Por causa disso, o trabalho será feito pelo Water Technology Group da NHL Stenden University
-de Ciências Aplicadas e em combinação com empresas holandesas para combinar possibilidades de análise com conhecimento
-e disponibilidade de infraestrutura.
+
+Signal processing implementations from previous projects from the NHL Stenden Water Technology group are showing good ranking results. 
+More research is necessary to improve classification accuracy and research and implementation of proper classification algorithm. 
+Because of this, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to combine analysis possibilities with knowledge and availability of infrastructure.

### 2023-04-12 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

--- 2023-04-01 Documentation/WT group/NHL/Metodology/Metodology.tex
@@
 This chapter is about describing the metodology and developments to achieve the project goals. 
-The python routine which this project is about was developed by the previous student working on it.\cite{Monica}
-The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to industries application or research.
+The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
+The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
 
-From the optimizations made, it highlights the following:
+About the activities made to reach our goals, it highlights the following:
 
-- Integrate high speed camera to the experiment routine.
+- Integrate high speed camera and liquid pump to the peripherals connected to the software.
 
-- Remodel the software to support threads in order to separate the sensoring and controlling routines.
+- Develop of a control model to automatic stabilize the electrospraying mode.
 
-- Reduce the data collected size.
+- Remodel the software to support threads in order to separate each subsystem and exchange data beetween them with use of queues data structures.
 
-- Synchronize the power supply step commands and voltage sensoring.
+- Reduce the data collected size and optimize the saving to a real time streamming.
 
-- Reestructure the setup file in order to make it more intuitive to use the experiment.
+- Develop new automatic experiment routines such as mapping and control routines.
 
-- Improvements in code organization and readability.
+- Reestructure the setup file and the algorithm usability in order to make it more intuitive.
+
+- Integration with many computer architectures to be able to run in a portable computer such as a \emph{Raspberry Pi}.
 
@@
 
+During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window.
+The operational window, seen in Figure \ref{fig:ganan_calvo_fig} can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.
+
     \begin{figure}[H]
@@
         \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
-        \caption{Domains of existence (stability) of Taylor cone-jets. \cite{gananCalvo} }
+        \caption{Domains of existence (stability) of Taylor Cone Jets.
+\cite{gananCalvo} .
+The window formed by these points is where the system operated in the stable cone-jet.
+Operational windows depend of the liquid and configuration setup.
+Different windows are represented for different liquid conductivity.
+The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
         \label{fig:ganan_calvo_fig}
@@
 
-    In the figures 5 and 6 we can see the results of this mapping experiments. The liquid used is pure ethanol. 
-    Each figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
-    The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
-    The third graph shows the current mean value of each data sample.
+    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
     Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.
@@
         \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
-        \caption{Mapping Experiment example 1}
+        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
+        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
+        The third graph shows the current mean value of each data sample.}
         \label{fig:map2Data_fig}
     \end{figure}
+
+    With all the data collected, classified and saved in real time, we can do further analysis and studies.
+For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X FlowRate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researchs, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.
 
@@
         \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
-        \caption{Mapping Experiment example 1}
+        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capilary setup. The map shows the stability region of each electrospraying mode in the voltage and flowrate range.}
         \label{fig:map3Data_fig}

### 2023-04-12 Documentation/UFMG/PFCII/Results/Results.tex
documentation

--- 2023-04-05 Documentation/WT group/NHL/Results/Results.tex
@@
 \label{chap:Results}
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
+    \caption{Printscreen of the window shows user interface during the experiment.
+        We can see the image generated by the camera in the background.
+        The routine code running in pycharm software on the right side.
+        And also real time signal plottings of the current data on the left side.}
+\end{figure}
 
@@
         \center
-        \includegraphics[width=12cm]{Figuras/report3/exp26-01-2.png}
-        \caption{ exp-26-01-2 (V x Q)}
-    \end{figure}
-
-    \begin{figure}[H]
-        \center
         \includegraphics[width=12cm]{Figuras/regions.png}
@@
         For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.
-
-        The Figure 13 shows a printscreen of how the experiment looks like in real time.
-        We can see the image generated by the camera in the back.
-        The routine code running in pycharm software on the right.
-        And also real time signal plottings of the current data on the left.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
-            \caption{running experiment print screen}
-        \end{figure}
 
@@
 
-        Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
-
         \begin{multicols}{2}
@@
         \subsection{Non-dimensional axis}
+
+        To compare with the literature and validate the algorithm we decided to display the data using the non-dimensional numbers used in figure \ref{fig:ganan_calvo_fig}.
 
@@
 
-\section{Atividades do Projeto}
-\label{sec:metodo3}
-
-\section {Requisitos do Sistema}
-\label{sec:req}
-
 \clearpage

### 2023-04-12 Documentation/UFMG/PFCII/acknowledgment/acknowledgment.tex
documentation

\addcontentsline{toc}{chapter}{Acknowledgment}

\begin{center}
\huge{{\bf Acknowledgments}}
\vspace{4cm}
\end{center}

I wish a big thanks to my mother who always supported me and made me believe in my potential. Teaching me dedication, patience and discipline.
To my father who taught me not to be satisfied and always looking for more, that's what I call ambition and energy to always try to get out of the comfort zone.
To my dear friends from República Casassanta for making university life such a unique and unforgettable moment.

\clearpage
\thispagestyle{empty}
\cleardoublepage

### 2023-04-12 Documentation/UFMG/modelo/Agradecimentos/Agradecimentos.tex
documentation

\addcontentsline{toc}{chapter}{Agradecimentos}

\begin{center}
\huge{{\bf Agradecimentos}}
\vspace{4cm}
\end{center}

Um Agradecimento a minha mãe que sempre me apoiou e me fez acreditar no meu potencial. Me ensinando dedicacao, paciencia e disciplina.
Ao meu pai me que ensinou a não estar satisfeito e buscar sempre mais, isso que eu chamo de ambicão e energia para sempre buscar sair da zona de conforto.
Aos meus queridos amigos da República Casassanta por terem tornado a vida universitária esse momento tão único e inesquecível.

\clearpage
\thispagestyle{empty}
\cleardoublepage

### 2023-04-12 Documentation/UFMG/relatorios/Relatorio_4/Development/Development.tex
documentation

--- 2023-03-03 Documentation/UFMG/Relatorio_4/Development/Development.tex
@@
 \subsection*{2.1 Raspberry pi}
+
+As we can see in Figure 4 the plotting thread can simply be deactivated by a command in the configuration file.
+With that we are capable of running the routine in a raspberry pi with python3 installed.
+The raspberry pi offers the portable solution for the routine to be running and can be implemented in size constrained industries applications.
+The raspberry pi is also integrated with a GSM data module to connect in internet through cellphone network.

### 2023-04-13 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

\chapter{O que ficou para depois}

Inclua aqui informações que não sejam tão relevantes para o entendimento do projeto mas que ainda sejam importantes para documentá-lo.

put here the stability difficult about doing experiments

- syringe pump inclined
- pumping liquid to avoid bubbles
- mechanical noise in the pumping machine
- external electrical noise collected by antennas or connections

### 2023-04-13 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 
-The biggest motivation to use EHDA is to have a more precise and uniform size and shape of droplets creation.
+EHDA research has contributed as an important tool for the development of technology. 
+The advantage of using EHDA is precision and uniform size and shape of droplets creation. Specially in certain spraying modes.
 
-EHDA research has contributed as an important tool for the development of technology. 
-Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is done empirically and based on average current measurements.
+Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.
+
 The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
-These forms cannot simply be summarized by their average value. In figure one we can see an example of cone-jet electrospray mode.
+Signal processing techniques may allow non-visual classification of spray mode based on electrical current form.
 
-Figure 1: example of EHDA
-
-Signal processing techniques may allow non-visual classification of spray mode based on electrical current form. 
 The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
@@
 
-In view of the above, this project aims to:
+This project aims to give continuity to the previous student work\cite{Monica}, 
+Mônica, who foccused in detecting undesired discharges (sparks) in the system accusing high eletric potential. 
+For that, she developed a python software routine to connect most of the peripherals and analysed the current data.
+Her work corroborate the validation of this project motivating its development and optimization.
+
+Above is shown the main goals listed:
 
@@
 \item Fully automated and intuitive system for EHDA research and industrial application.
-\item Real Time non-visual classification.    
-\item Control and stabilization of desired spraying modes.   
-\item System Portability.
+\item Real Time non-visual classification of spraying modes.
+\item Control and stabilization on a desired spraying mode.   
+\item System Portability and versatility.
 \end{enumerate}
-
-% The content of this section may overlap somewhat with that of the previous section, and it may be a summary of the points made above. 
-% The choice of section title may be more appropriate for the project proposal phase. 
-% After all, at this stage the objectives are known and not the results. 
-% On the other hand, it makes little sense to discuss objectives when the project is finished, especially if those objectives have not been achieved.
 
@@
 
-Signal processing implementations from previous projects from the NHL Stenden Water Technology group are showing good ranking results. 
-More research is necessary to improve classification accuracy and research and implementation of proper classification algorithm. 
-Because of this, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to combine analysis possibilities with knowledge and availability of infrastructure.
+The NHL Stenden Water Technology group has been involved in previous projects that have successfully implemented automated signal processing techniques, resulting in highly ranked outcomes. 
+However, further research is required to enhance the accuracy of the classification algorithm.
+In order to achieve this, the Water Technology Group at NHL Stenden University of Applied Sciences, in collaboration with Dutch companies, is conducting extensive research and implement appropriate classification algorithms.
+The aim is to combine analytical capabilities with infrastructure knowledge and availability to achieve optimal results.
+As a student from UFMG, I am now actively involved in this research project to improve the automation usability, classification accuracy and system stabilization with signal processing techniques.
+
+\section{Document Structure}
+\label{sec:doc_struct}

### 2023-04-13 Documentation/UFMG/PFCII/acknowledgment/acknowledgment.tex
documentation

@@
 
-I wish a big thanks to my mother who always supported me and made me believe in my potential. Teaching me dedication, patience and discipline.
-To my father who taught me not to be satisfied and always looking for more, that's what I call ambition and energy to always try to get out of the comfort zone.
-To my dear friends from República Casassanta for making university life such a unique and unforgettable moment.
+I would like to express my heartfelt gratitude to the following individuals and institutions who have played a significant role in shaping me into the person I am today:
+
+First and foremost, my beloved mother, whose support and belief in my potential has been my guiding light throughout my life.
+Her invaluable lessons on dedication, patience, and discipline have helped me overcome countless challenges and achieve my goals.
+
+I also extend my gratitude to my father, whose teachings on the virtues of ambition have inspired me to strive for excellence.
+His relentless pursuit of success has been a constant source of energy for me.
+
+I would like to acknowledge the outstanding education and training that I received from the UFMG university, which has equipped me with the necessary skills and knowledge to thrive in the global marketplace.
+I am grateful for the transformative experience that has prepared me for a fulfilling career and a meaningful life.
+
+Moreover, I cannot forget my dear friends from República Casassanta, who have made my student life such a unique and unforgettable moment.
+Their camaraderie and support have been a source of joy and comfort during challenging times.
+
+Lastly, I would like to thank myself for having the courage and resilience to pursue my dreams despite my anxieties and doubts.
+Through my perseverance, I have been able to savor every moment of my journey and give my best to achieve my goals.
 

### 2023-04-14 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentacao

--- 2023-03-29 Documentation/WT group/NHL/LiteratureReview/LiteratureReview.tex
@@
 
-\section{Droplet Formation}
-\label{sec:drop_formation}
-
-In the Aerosol reasearch community there is a branch of studies about droplets formation.
-In the droplet field a very functional for applications is the atomization, which refers to breaking the liquid in small droplets.
-There is many ways of atomizing a liquid.
-Some using mechanical energy such as ultrassound, rotating disk\cite{Disk_atomization}, pressure or blowing air on the meniscus.
-But also, some of them using electric forces such as electrospray atomization.
-
-For
-
 \section{Spraying modes}
@@
 
-The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.
+The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows 3 spraying dynamics that we are most interesting in this project.
 
@@
 
-Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:
+Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate beetween 5 modes as shown above in order of growing electric potential:
 
@@
 
-In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
+Dripping mode happens when the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
 In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.
+
+\begin{figure}[H]
+  \center
+  \includegraphics[width=3cm]{Figuras/19:03/drip_example.png}
+  \label{fig:drip_example}
+  \caption{Dripping}
+\end{figure}
 
@@
 
+\begin{multicols}{3}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{Figuras/19:03/intermittent_example.png}
+      \label{fig:intermittent_example}
+      \caption{Intermittent}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=2cm]{Figuras/19:03/intermittent2_example.png}
+      \label{fig:intermittent2_example}
+      \caption{Intermittent}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=2cm]{Figuras/19:03/microdripping_example.png}
+      \label{fig:microdripping_example}
+      \caption{Microdripping}
+  \end{figure}
+
+\end{multicols}
+
 \subsection{Cone Jet}
 \label{subsec:Cone Jet}
+
+Taylor (1964) was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
 

### 2023-04-14 software/validation_electrospray.py
correct flowrate in m^3/s

@@ -64,11 +64,7 @@ class ElectrosprayValidation:
 
         # print("\nprocessing_mean:", mean)
         self.mean_value_array = mean
-
-        if self.electrical_conductivity == 0.0 or self.rho == 0.0:
-            self.flow_rate_chen_pui = 0.0
-        else:
-            self.flow_rate_chen_pui =  (self.dieletric_const ** 0.5) * self.permitivity * self.surface_tension / (self.rho * self.electrical_conductivity)
+        self.flow_rate_chen_pui = flow_rate * 16e-12 # converting uL/min to m^3/s
 
         self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui / self.dieletric_const) ** (.5)
 

### 2023-04-14 software/data_processing.py
validation dictionary

@@ -131,6 +131,7 @@ def data_processing(data_queue,
 
             # Validation through the Chen_Pui Article
             electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data, electrospray_processing.mean_value, electrospray_data.flow_rate)
+            print(electrospray_validation.get_validation_dictionary())
 
         except Exception as e:
             print("ERROR: ", str(e)) 

### 2023-04-14 software/save_data.py

@@ -75,17 +75,18 @@ def save_data(
                 # print("[SAVING] before get, queue size:", save_data_queue.qsize())
                 data_measurement, data_processing = save_data_queue.get() # block=True, timeout=None)  # expecting a list with two dictionary objects
                 # print("[SAVING] after get, queue size:", save_data_queue.qsize())
+                data_validation = electrospray_validation.get_validation_dictionary()
 
                 try:
                     if electrospray_config_setup["save_data"]:
-                        if electrospray_config_setup["save_processing"]:
+                        if electrospray_config_setup["save_validation"]:
+                            s.write('sample '+str(sample), {**data_measurement, **data_processing, **data_validation})  
+                        elif electrospray_config_setup["save_processing"]:
                             s.write('sample '+str(sample), {**data_measurement, **data_processing})  #taking values inside the two dicts and creating one dict
                         else:
                             s.write('sample '+str(sample), data_measurement)
 
                         print("[SAVING] saved electrospray sample:", sample)
-
-                        print(electrospray_validation.get_validation_dictionary())
                         
 
 

### 2023-04-14 software/validation_electrospray.py
scaling laws test

@@ -64,7 +64,7 @@ class ElectrosprayValidation:
 
         # print("\nprocessing_mean:", mean)
         self.mean_value_array = mean
-        self.flow_rate_chen_pui = flow_rate * 16e-12 # converting uL/min to m^3/s
+        self.flow_rate_chen_pui = float(flow_rate) * 16e-12 # converting uL/min to m^3/s
 
         self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui / self.dieletric_const) ** (.5)
 

### 2023-04-18 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 Taylor (1964) was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
+Taylor cone-jets naturally occurs under relatively limited circumstances: when the applied field and flow rate are in the appropriate range, and the electrosprayed liquid exhibits the adequate physical properties.
+
+\begin{multicols}{3}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=2cm]{Figuras/april/conjet1.png}
+      \label{fig:conjt1}
+      \caption{Cone Jet}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=2cm]{Figuras/april/conjet2.png}
+      \label{fig:conjt2}
+      \caption{Cone Jet}
+  \end{figure}
+
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=2cm]{Figuras/april/conjet3.png}
+      \label{fig:conjt3}
+      \caption{Cone Jet}
+  \end{figure}
+
+\end{multicols}
 
@@
 
-Since the beginning of EHDA until today the researchs are being conducted manually with visual classification of the spraying mode using a camera or even by naked eyes.
-It is recommended to use a high speed (HS) camera because some dripping or intermittent states can be in a high frequency and be wrongly noticed as a stable condition.
-The setup in \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
+From the inception of EHDA until the present day, research has been carried out through manual means, involving the use of visual classification to determine the spraying mode either through cameras or by direct observation.
+It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
+The setup in figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
 
@@
   \centering
-  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
+  \resizebox{90mm}{!}{\includegraphics{Figuras/system_setup.png}}
   \caption{EHDA experiment setup \cite{Luewton}}
@@
 That current signal holds a lot o information
-about the dynamics that is happening with the liquid. In \ref{fig:microdripping_current_pic} we can see an example of that. It's clear the two droplets generated in this time frame.
+about the dynamics that is happening with the liquid.
+Figure \ref{fig:microdripping_current_pic} illustrate an example of that.
+It can be seen the signal of two droplets of charged liquid generated in this time frame.
 
@@
 
+  The existing signal contains valuable data not only about dripping but also other modes of spraying, thus it can serve as a non-visual classifier.
+  This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+
 \clearpage

### 2023-04-19 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

\chapter{Conclusion}

In conclusion, the goals of this project have been largely accomplished. The implementation of a Python routine for complete automation and integration of the system has significantly improved the precision of experiments and enabled real-time collection of extensive data without requiring the expertise and time of a specialized scientist. The success of this project underscores the potential of automation in enhancing scientific research and accelerating progress towards achieving research goals.
In addition to its potential in scientific research, the software developed in this project can also be leveraged by industrial approaches. Furthermore, the classification methods and system control implemented in this project have yielded promising results and can be further optimized in the future. Overall, this project serves as a valuable contribution towards the advancement of automated systems and the optimization of experimental processes, with broad implications for both research and industrial applications.

\clearpage

### 2023-04-19 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
-The balance beetween capilary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
+The balance between capillary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
 The electric current transported by the spray reveals characteristic shapes for different spray modes.

### 2023-04-19 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 
-The stable balance between the capilary and field forces on the liquid suggest a \emph{quasi static} dynamics.
+The stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
 For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
@@
 
-Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate beetween 5 modes as shown above in order of growing electric potential:
+Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate between 5 modes as shown above in order of growing electric potential:
 
@@
 Dripping mode happens when the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
-In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.
+In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.
 
@@
 
+\section{Scalling Laws}
+\label{sec:scalling-laws}
+
 \clearpage

### 2023-04-19 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
 
-- Remodel the software to support threads in order to separate each subsystem and exchange data beetween them with use of queues data structures.
+- Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.
 
@@
     model was developed as a separate Thread.
-    For cuncurrency on flux of data beetween threads was used queues structures.
+    For cuncurrency on flux of data between threads was used queues structures.
     A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.
@@
     The software was previously developed as a electrospray multipurpose library\cite{Monica}. 
-    Continuing this methodology, in the setup json file there is a "sequence" atribute which can chosen beetween "ramp", "step", "map" or "control".
+    Continuing this methodology, in the setup json file there is a "sequence" atribute which can chosen between "ramp", "step", "map" or "control".
     The controller thread will manage what the algorithm must do for each sequence.
@@
         \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
-        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capilary setup. The map shows the stability region of each electrospraying mode in the voltage and flowrate range.}
+        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capillary setup. The map shows the stability region of each electrospraying mode in the voltage and flowrate range.}
         \label{fig:map3Data_fig}

### 2023-04-19 Documentation/UFMG/relatorios/Relatorio_2/Development/Development.tex
documentation

--- 2022-12-07 Documentation/Relatorio_2/Development/Development.tex
@@
 
-    2 - Voltage step sequency in order to evaluate the dynamics in each high voltage level.
+    2 - Voltage step sequence in order to evaluate the dynamics in each high voltage level.
 
@@
     In Figure 11, the data is well classified but it also have a noise in the system that can been seen in the peak current values.
-    Those peaks can be seen in all the voltage ranges in this experiment and also have similar distances in beetween the peaks. This is probably caused by
+    Those peaks can be seen in all the voltage ranges in this experiment and also have similar distances in between the peaks. This is probably caused by
     external interference but it is still not certain what is it about.

### 2023-04-19 Documentation/UFMG/relatorios/Relatorio_3/Development/Development.tex
documentation

--- 2023-01-30 Documentation/UFMG/Relatorio_3/Development/Development.tex
@@
 
-    During this time it was noticed that breaks in beetween the experiments was getting different results for the same setup. This can be caused by the temperature and humidity effects on the system.
+    During this time it was noticed that breaks in between the experiments was getting different results for the same setup. This can be caused by the temperature and humidity effects on the system.
     For that I included the sensor DHT11 in the system setup and software routine to collect data of this two variables.
-Also closed the system chamber and sprayed pure oxygen O2 to decrease the humidity inside.
+Also closed the system chamber and sprayed purified air to decrease the humidity inside.

### 2023-04-21 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
-The balance between capillary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
+The balance between capillary forces and the electric field on the charged liquid defines the spraying dynamics and droplet size.
 The electric current transported by the spray reveals characteristic shapes for different spray modes.
@@
 This project aims to give continuity to the previous student work\cite{Monica}, 
-Mônica, who foccused in detecting undesired discharges (sparks) in the system accusing high eletric potential. 
-For that, she developed a python software routine to connect most of the peripherals and analysed the current data.
-Her work corroborate the validation of this project motivating its development and optimization.
+Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
+For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
+Her work corroborates the validation of this project motivating its development and optimization.
 
@@
 
-\begin{enumerate}[a)]
-\item multipurpose applications both scientific and industrial application.
-\item Fully automated and intuitive system for EHDA research and industrial application.
+\begin{enumerate}[]
+\item Multipurpose applications for both scientific and industrial approaches.
+\item Fully automated and intuitive system for EHDA.
 \item Real Time non-visual classification of spraying modes.
-\item Control and stabilization on a desired spraying mode.   
-\item System Portability and versatility.
+\item Control and stabilization on a desired dynamic. 
+\item System portability and versatility.
 \end{enumerate}
 
-\section{People envolved}
+\section{People involved}
 \label{sec:companies}

### 2023-04-21 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
-That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}
+That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
 
@@
 
-Dripping mode happens when the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
+Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
 In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.
@@
 
-Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
+Intermittent mode is defined when the electric field forces starts to have a considerable effect in the meniscus and droplet formation. 
 In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.

### 2023-04-21 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 \label{chap:Results}
+
+In this chapter, we will present the results obtained from our project.
+Firstly, we will demonstrate how the automation routine enhanced the research experiments.
+Next, we will discuss the validation of the classification results.
+Finally, we will showcase the performance of the implemented controller algorithms.
+
+\section{Automation routine}
+\label{sec:automation_routine}
+
+The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human.
+Most power supplies available in the market rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person.
+Moreover, manual adjustment takes some time to achieve the desired voltage.
+By running a computer routine that automatically sends commands to the power supply, we can achieve faster and more reliable experiment data.
+We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment.
+All the important data of EHDA experiments are showed in the same screen and referring to each 0.5 seconds sampling time.
 
@@
     \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
-    \caption{Printscreen of the window shows user interface during the experiment.
+    \caption{Print screen of the window shows user interface during the experiment.
         We can see the image generated by the camera in the background.
@@
         And also real time signal plottings of the current data on the left side.}
+        \label{fig:multi_class_exp1}
 \end{figure}
@@
 \begin{figure}[H]
-    \centering
-    \resizebox{170mm}{!}{\includegraphics{Figuras/19:03/axs2.png}}
-    \caption{Printscreen during an experiment.
+    \center
+    {\includegraphics[width=17cm]{Figuras/19:03/axs2.png}}
+    \caption{Print screen during an experiment.
 At this moment we are in Multi Jet spraying mode.
-At the left we can see the current signal has a smoth and constant curve.
-We can also see the automatic classification at the right side.}
+At the left we can see the current signal has a smooth and constant curve.
+We can also see the automatic classification on the right side.}
     \label{fig:multi_class_exp}
@@
 
-The results of the classification using the statistical values are illustrated in figures \ref{fig:step_voltage}, \ref{fig:raw_data} and \ref{fig:class_step_data}.
+\subsection{Step Sequence}
+\label{subsec:step_results}
+
+Our first classification results were made exploring just the voltage ranges. For that we tried to stabilize all the other parameters such as humidity, temperature and external noise.
+First, we fixed a flow rate to 0.7 uL/min.
+and ran a step routine as defined in \ref{subsec:step_routine}.
+The figure \ref{fig:step_voltage} shows the step voltages during the experiment and figure \ref{fig:raw_data} illustrates the raw data acquired with it.
+In figure \ref{fig:class_step_data} we see the same experiment data classified by spraying mode and separated by color.
 
@@
     \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
-    \caption{Input voltage step graph. The range is beetween 3K-10K Volts. Step size of 50V and steo time of 5 seconds.}
+    \caption{Input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.}
     \label{fig:step_voltage}
@@
 
-Notice that is even possible to a visual classification.
-The Dripping mode has a current mean of 0V.
-The Intermittent state has a high variation of values that can be seen by the thickness of the graph.
-The Cone jet is a thiner graph because the signal is more constant.
-The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet.
-
 \begin{figure}[H]
@@
     \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
-    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colours are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
+    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colors are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
     \label{fig:class_step_data}
@@
 
-\section{Map Sequence}
-\label{sec:map_results}
+The graph of voltage scan as showed in \ref{fig:raw_data} has a common shape for different liquids and parameters.
+After having familiarity with it is even possible to classify the spraying modes by visual analysis.
+For example:
+Dripping mode has a current mean of 0V.
+The Intermittent state has a high variation of values that can be seen by the thickness of the graph.
+The Cone jet is a thinner graph because the signal is more constant.
+The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet.
+Corona sparks are not showed in the graph because the discharges has a high current value and will be above the axis limits.
 
-    \subsection{Manual experiments}
+\subsection{Map Sequence}
+\label{subsec:map_results}
 
-    For better understand the effects of both voltage and flowrate in the spraying dinamycs manual experiments were made.
+For validation purposes and also to expose the benefits of the automated routine and classification
+
+    For better understand the effects of both voltage and flow rate in the spraying dynamics manual experiments were made.
     Also in order to find the stability region of cone jet mode for the liquid and setup used.
@@
 
-    \subsection{Manual x Automatic Cone Jet stability island maps}
-
     For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.
@@
     In Figure 14 we can see a result of the map generated by the automatic classification in this experiment.
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=10cm]{Figuras/report3/map-exp-26-01.png}
-            \caption{ exp-26-01-23 }
-        \end{figure}
 
@@
             \center
-                \includegraphics[width=9cm]{Figuras/report3/manual-mapping.png}
+            \includegraphics[width=8cm]{Figuras/report3/manual-mapping.png}
             \caption{ exp-26-01 manual classification}
@@
             \center
-                \includegraphics[width=9cm]{Figuras/report3/map4-stabilityIsland.png}
+            \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
             \caption{ exp-26-01 automatic classification}
@@
             \center
-                \includegraphics[width=7cm]{Figuras/report4/map7-manual.png}
+            \includegraphics[width=8cm]{Figuras/april/map5.png}
             \caption{ exp-26-01 manual classification}
@@
             \center
-                \includegraphics[width=9cm]{Figuras/report4/map7-automatic-line.png}
+            \includegraphics[width=10cm]{Figuras/april/map2.png}
             \caption{ exp-26-01 automatic classification}
@@
 
-        \subsection{Non-dimensional axis}
+    \subsubsection{Non-dimensional axis}
 
@@
 
-        Flowrate perturbation robustness test
+        Flow rate perturbation robustness test
 
@@
         The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
-        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzified.
+        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
         Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.
 
-        For that, I tried to fuzzyfi the controller input by the data acquired in the step routine.
+        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine.
 With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.
@@
         \begin{multicols}{2}
+
             \begin{figure}[H]
@@
             \end{figure}
+
         \end{multicols}

### 2023-04-21 Documentation/UFMG/relatorios/literature review/main.tex
documentation

--- 2022-12-02 Documentation/literature review/main.tex
@@
 
-Another project is the \emph{experimental investigation of scaling laws for electrospraying: dieletric constant effect}\cite*[]{Chen_Pui}.
+Another project is the \emph{experimental investigation of scaling laws for electrospraying: dielectric constant effect}\cite*[]{Chen_Pui}.
 Where the author study about the quemical properties of the liquid being sprayed that can actually interfere in the dynamics of the process. 
-In the paper the author emphasised about the liquid dieletric constant. For us this paper is interesting because we can understand better which liquid
+In the paper the author emphasised about the liquid dielectric constant. For us this paper is interesting because we can understand better which liquid
 has a better margin of operation in cone jet mode for example. What is missing in his article is that it is not mentioning all the variables that can interfere in the 

### 2023-04-21 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
 The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
+The software was previously developed as a electrospray multipurpose library\cite{Monica}.
+
 The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
@@
     \subsection{Data Acquisition Thread}
+    \label{subsec:data_aquisition}
 
@@
 
-    The software was previously developed as a electrospray multipurpose library\cite{Monica}. 
-    Continuing this methodology, in the setup json file there is a "sequence" atribute which can chosen between "ramp", "step", "map" or "control".
+    The program developed is capable of running different types of routines. The code is also easy to implement new routines.
+    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
     The controller thread will manage what the algorithm must do for each sequence.
+    Following our control model\ref{fig:control_model_fig}, the controller outputs are the actuators signal.
+    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton thread\ref{subsec:data_aquisition}.
 
@@
 \subsection{Step}
+\label{subsec:step_routine}
 
@@
 
-During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window.
-The operational window, seen in Figure \ref{fig:ganan_calvo_fig} can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.
+The map that will be explained bellow is the most relevant sequence in this work.
+This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
+The purpose is to map the operational window, seen in Figure \ref{fig:ganan_calvo_fig}, that can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.
 
@@
     \end{figure}
+
+To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
+The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
+The algorithm for this sequence is a copy of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is illustrated in the algorithm \ref{alg:mapping_algorithm}.
 
@@
 
-\section{System Portability}
-\label{sec:portability}
-
-    Raspberry Pi
-
 \clearpage

### 2023-04-22 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 
+\section{Proposal for continuing}
+
+\subsection{Fuzzy Controller}
+
+        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
+        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
+        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.
+
+        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine.
+With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.
+
+        \begin{multicols}{2}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
+                \caption{Fuzzyfication}
+                \label{fig:fuzzy_input}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
+                \caption{Defuzzyfication}
+                \label{fig:fuzzy_output}
+            \end{figure}
+
+        \end{multicols}
+
+        \begin{figure}[H]
+            \centering
+            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
+            \caption{Fuzzy Rules}
+            \label{fig:fuzzy_rules}
+        \end{figure}
+
+        \begin{multicols}{2}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
+                \caption{Test 1: fuzzy controller}
+                \label{fig:fuzzy_test1}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
+                \caption{Test 2: fuzzy controller}
+                \label{fig:fuzzy_test2}
+            \end{figure}
+
+        \end{multicols}
+
 \clearpage

### 2023-04-22 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 \end{figure}
+
+\section{Non-visual classification}
+\label{sec:non-visual-classification}
+
+From the inception of EHDA until the present day, research has been carried out through manual means, involving the use of visual classification to determine the spraying mode either through cameras or by direct observation.
+It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
+The setup in figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
+
+\begin{figure}[H]
+  \centering
+  \resizebox{90mm}{!}{\includegraphics{Figuras/system_setup.png}}
+  \caption{EHDA experiment setup \cite{Luewton}}
+  \label{fig:ehda_setup}
+\end{figure}
+
+Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}.
+That current signal holds a lot o information
+about the dynamics that is happening with the liquid.
+Figure \ref{fig:microdripping_current_pic} illustrate an example of that.
+It can be seen the signal of two droplets of charged liquid generated in this time frame.
+
+\begin{figure}[H]
+    \centering
+    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
+    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
+    \label{fig:microdripping_current_pic}
+  \end{figure}
+
+  The existing signal contains valuable data not only about dripping but also other modes of spraying, thus it can serve as a non-visual classifier.
+  This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+
+\section{Scaling Laws}
+\label{sec:scalling-laws}
 
@@
 
-Taylor (1964) was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
+Taylor (1964)\cite{taylor} was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
 Taylor cone-jets naturally occurs under relatively limited circumstances: when the applied field and flow rate are in the appropriate range, and the electrosprayed liquid exhibits the adequate physical properties.
+
+During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window.
 
@@
 
-\subsection{Corona sparks}
-\label{subsec:Corona sparks}
+Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet phenomena. In his experiments was observed:
+\emph{"for voltages well above that for which the steady conical surface changed into a blurred agitated one, the appearance became a number of fine points with their attendant dark streaks arranged along the circumference of the raised edge".}
 
-\section{Non-visual classification}
-\label{sec:non-visual-classification}
+In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics.
+Because of that, some authors can divide what we call multi jet in more classifications.
+The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.
+Figures \ref{fig:multijt1}, \ref{fig:multijt2} and \ref{fig:multijt3} shows three different variations of multi jet spraying mode.
 
-From the inception of EHDA until the present day, research has been carried out through manual means, involving the use of visual classification to determine the spraying mode either through cameras or by direct observation.
-It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
-The setup in figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
+C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
+For this work it highlights the detection that for a low number of jets emitted, seen in figure \ref{fig:multijt1} and \ref{fig:multijt2}, the meniscus is not bound to the rim of the capillary. 
+This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
+
+As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray, seen in figure \ref{fig:multijt3}. In this work it will also be classified as multi jet.
+
+\begin{multicols}{3}
 
   \begin{figure}[H]
-  \centering
-  \resizebox{90mm}{!}{\includegraphics{Figuras/system_setup.png}}
-  \caption{EHDA experiment setup \cite{Luewton}}
-  \label{fig:ehda_setup}
+      \center
+      \includegraphics[width=3cm]{Figuras/april/multi2.png}
+      \label{fig:multijt1}
+      \caption{Multi Jet - double jet}
   \end{figure}
 
-Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}.
-That current signal holds a lot o information
-about the dynamics that is happening with the liquid.
-Figure \ref{fig:microdripping_current_pic} illustrate an example of that.
-It can be seen the signal of two droplets of charged liquid generated in this time frame.
+  \begin{figure}[H]
+      \center
+      \includegraphics[width=3cm]{Figuras/april/multi1.png}
+      \label{fig:multijt2}
+      \caption{Multi Jet - low number of jets}
+  \end{figure}
 
   \begin{figure}[H]
-    \centering
-    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
-    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
-    \label{fig:microdripping_current_pic}
+      \center
+      \includegraphics[width=3cm]{Figuras/april/multi3.png}
+      \label{fig:multijt3}
+      \caption{Multi Jet - rim spraying mode}
   \end{figure}
 
-  The existing signal contains valuable data not only about dripping but also other modes of spraying, thus it can serve as a non-visual classifier.
-  This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+\end{multicols}
 
-\section{Scalling Laws}
-\label{sec:scalling-laws}
+\subsection{Corona}
+\label{subsec:Corona}
+
+At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown and we achieve a phenomenon of discharge.
+Those can be easily classified because of its high current value.
+
+This mode is also divided by other classes such as streamer corona or transient sparks discharges, but it's not in the scope of this work. 
+Mônicas\cite{Monica} work was focused on how to predict that mode with the current analysis for safety in industrial applications.
 

### 2023-04-22 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 
-    \subsection{Fuzzy Controller}
+    \section{System Portability}
+    \label{sec:portability}
 
-        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
-        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
-        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.
-
-        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine.
-With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.
-
-        \begin{multicols}{2}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
-                \caption{Fuzzyfication}
-                \label{fig:fuzzy_input}
-            \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
-                \caption{Defuzzyfication}
-                \label{fig:fuzzy_output}
-            \end{figure}
-
-        \end{multicols}
-
-        \begin{figure}[H]
-            \centering
-            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
-            \caption{Fuzzy Rules}
-            \label{fig:fuzzy_rules}
-        \end{figure}
-
-        \begin{multicols}{2}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
-                \caption{Test 1: fuzzy controller}
-                \label{fig:fuzzy_test1}
-            \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
-                \caption{Test 2: fuzzy controller}
-                \label{fig:fuzzy_test2}
-            \end{figure}
-
-        \end{multicols}
+        Raspberry Pi
 

### 2023-04-22 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 
+The electric spray current is a critical variable that has been extensively researched by multiple authors\cite{prunet}\cite{Chen_Pui}\cite{gananCalvo}, resulting in scaling laws that express the relationship between liquid flow rate, conductivity, surface tension, density, and droplet diameter.
+These scaling laws can predict the size and charge of emitted droplets, making them useful tools for electrospraying practitioners. 
+Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms.
+
+\[ I = (\frac{\gamma K Q}{\kappa})^{1/2}\]
+
 \section{Spraying modes}
@@
 
-Since 1915 with his pioneering work in EHDA, Zeleny observed several functioning modes with very different characteristics.
-Years later the same phenomena was noticed by other scientists but the classification of these modes were still not well defined by the community.
-For that Cloupeau and Prunet-Foch proposed spray mode classifications based in what they have seen experimentally and it's still being used as basis for EHDA researchs.\cite{prunet}
+Since 1915 with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
+Years later the same phenomena was noticed by other scientists, but the classification of these modes were still not well-defined by the community.
+For that Cloupeau and Prunet-Foch\cite{prunet} proposed spray mode classifications based in what they have seen experimentally, and it's still being used as basis for EHDA researches.
 
@@
 \label{subsec:Cone Jet}
+
+The electrified meniscus can take on a conical shape within a certain range of applied voltage and injected liquid flow rate.
 

### 2023-04-22 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

@@
-\chapter{O que ficou para depois}
+\chapter{Trials and failures}
 
-Inclua aqui informações que não sejam tão relevantes para o entendimento do projeto mas que ainda sejam importantes para documentá-lo.
+\section{Machine Learn}
 
-put here the stability difficult about doing experiments
+I've tried to create a database with the samples of current. Each sample was a vector with 50k values corresponding a 0.5s of data collected in a 100KHz oscilloscope. And in a second column its
 
-- syringe pump inclined
-- pumping liquid to avoid bubbles
-- mechanical noise in the pumping machine
-- external electrical noise collected by antennas or connections
+\subsection{Spectogram analysis}

### 2023-04-22 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 Overall, this project serves as a valuable contribution towards the advancement of automated systems and the optimization of experimental processes, with broad implications for both research and industrial applications.
+
+The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
+The previous student work was more focused on detecting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
+From the work I've done it highlights:
+
+- Integrate liquid pump to the software and developed a routine with it.
+
+- Modeled the software to fit a control model turning it easy to implement new control algorithms or experiment routines.
+
+- Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.
+
+- Developed a classification for multi jet spraying mode.
+
+- Developed a simple controller to proof the concept.
+
+- Optimize the saving of data to a real time streaming together with more sensors' data.
+
+- Restructured algorithm usability in order to make it more intuitive with the setup file.
 

### 2023-04-22 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
 The software was previously developed as a electrospray multipurpose library\cite{Monica}.
-
-The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
-
-About the activities made to reach our goals, it highlights the following:
-
-- Integrate high speed camera and liquid pump to the peripherals connected to the software.
-
-- Develop of a control model to automatic stabilize the electrospraying mode.
-
-- Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.
-
-- Reduce the data collected size and optimize the saving to a real time streamming.
-
-- Develop new automatic experiment routines such as mapping and control routines.
-
-- Reestructure the setup file and the algorithm usability in order to make it more intuitive.
-
-- Integration with many computer architectures to be able to run in a portable computer such as a \emph{Raspberry Pi}.
-
-    \begin{figure}[H]
-        \centering
-        \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
-        \caption{EHDA automation system setup}
-        \label{fig:metodology_example1}
-    \end{figure}
-
-\section{System Model}
-\label{sec:control_model}
-
-ilustramos o processo com a Figura \ref{fig:control_model_fig}.
-
-\begin{figure}[H]
-  \centering
-  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
-  \caption{EHDA automation system setup}
-  \label{fig:control_model_fig}
-\end{figure}
-
-\subsection{Threading and Queues}
-\label{subsec:concurrency}
-
-    In order to implement this system model to the software and explore parallel processing each system in the
-    model was developed as a separate Thread.
-    For cuncurrency on flux of data between threads was used queues structures.
-    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.
-
-    \subsection{Controller Thread}
-
-        It is responsible of sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
-        Also responsible of sending the finish event command that end the routine and trigger the threads to close their routines.
-        As input we have the setup config file and the \emph{feedback\_queue}. As output we have the values in the emph{controller\_output\_queue()}.
-
-    \subsection{Data Acquisition Thread}
-    \label{subsec:data_aquisition}
-
-        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the powersupply, flowrate from the pump and concatenate into one sample data.
-        As output we have the values in the emph{data\_queue()}.
-
-    \subsection{Data Processing Thread}
-
-        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
-        As output we have the values in the emph{save\_data\_queue()}, emph{plotting\_queue()} and emph{feedback\_queue()}.
-
-        \subsection{Save Data Thread}
-
-        After the processing the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
-
-        With the new streamming model of saving a new structure of the collected data were created.
-        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
-        The structure of the
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
-            \caption{Output data json structure}
-        \end{figure}
-
-        To work with this data I'm using pandas Dataframe.
-        With the command:
-
-        pandas.read\_json('PATH', orient='index').
-
-        The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
-        type of file called feather is much faster to work with the data.
-
-    \subsection{Video Thread}
-
-        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.
-
-    \subsection{Plot}
-
-        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilites of running outside of the main function. 
-        It is responsible of plotting in real time the current sample acquired and it respective fast fourier transform to evaluate the sample frequency spectrum.
-
-    - plotting data queue
 
@@
  By the processing thread we take this sample and evaluate the followings statistical values.
+
+To classify the multijet I searched \cite{Ryan} The data thus obtained shows that in all cases the relationship between current and flow rate observed in single cone-jet mode is maintained in multi-jet mode when the current and flow rate is normalized by the number of jets.
 
@@
 \subsection{Machine Learning}
+
+For the machine learning
 

### 2023-04-22 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

--- 2023-04-01 Documentation/WT group/NHL/systemDescription/systemDescription.tex
@@
 
-\section{Instrumentation}
-\label{sec:instrumentation}
+This chapter is about to describe the equipment used and its integration explaining how it was modeled and implemented in both hardware and software sides.
+
+\section{System Description}
+\label{sec:system_description}
+
+\subsection{Instrumentation}
+\label{subsec:instrumentation}
 
@@
 
-    The iterface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
+    The interface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
 Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.
@@
 
-\section{Setup Validation}
-\label{sec:setup_validation}
+\subsection{Setup Validation}
+\label{subsec:setup_validation}
 
@@
 
+    \begin{figure}[H]
+        \centering
+        \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
+        \caption{EHDA automation system setup}
+        \label{fig:metodology_example1}
+    \end{figure}
+
+\section{System Model}
+\label{sec:control_model}
+
+ilustramos o processo com a Figura \ref{fig:control_model_fig}.
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
+  \caption{EHDA automation system setup}
+  \label{fig:control_model_fig}
+\end{figure}
+
+\subsection{Threading and Queues}
+\label{subsec:concurrency}
+
+    In order to implement this system model to the software and explore parallel processing each system in the
+    model was developed as a separate Thread.
+    For cuncurrency on flux of data between threads was used queues structures.
+    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.
+
+    \subsection{Controller Thread}
+
+        It is responsible of sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
+        Also responsible of sending the finish event command that end the routine and trigger the threads to close their routines.
+        As input we have the setup config file and the \emph{feedback\_queue}. As output we have the values in the emph{controller\_output\_queue()}.
+
+    \subsection{Data Acquisition Thread}
+    \label{subsec:data_aquisition}
+
+        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the powersupply, flowrate from the pump and concatenate into one sample data.
+        As output we have the values in the emph{data\_queue()}.
+
+    \subsection{Data Processing Thread}
+
+        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
+        As output we have the values in the emph{save\_data\_queue()}, emph{plotting\_queue()} and emph{feedback\_queue()}.
+
+        \subsection{Save Data Thread}
+
+        After the processing the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
+
+        With the new streamming model of saving a new structure of the collected data were created.
+        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
+        The structure of the
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
+            \caption{Output data json structure}
+        \end{figure}
+
+        To work with this data I'm using pandas Dataframe.
+        With the command:
+
+        pandas.read\_json('PATH', orient='index').
+
+        The json file is good to store the data and to read the file. But as it is getting a lot of data working with pandas Dataframe is being way faster. Also saving the dataframe in a compressed
+        type of file called feather is much faster to work with the data.
+
+    \subsection{Video Thread}
+
+        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.
+
+    \subsection{Plot}
+
+        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilites of running outside of the main function. 
+        It is responsible of plotting in real time the current sample acquired and it respective fast fourier transform to evaluate the sample frequency spectrum.
+
+    - plotting data queue
+
 \clearpage

### 2023-04-22 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
   This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+
+  According to Sjaaks\cite{Sjaaks}, evaluating the current data flowing through the nozzle to the plate can give us valuable information about the spraying behaviour.
+  Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
+  It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
 

### 2023-04-22 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
 This chapter is about describing the metodology and developments to achieve the project goals.
-The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
-The software was previously developed as a electrospray multipurpose library\cite{Monica}.
 
@@
 Which means it must be fast and automatic classification.
-Our goal is to improve and apply in our routine different approachs of non-visual spraying classification using the current data collected from the system.
+Our goal is to improve and apply in our routine different approaches of non-visual spraying classification using the current data collected from the system.
 
-\subsection{Statistical Analisys}
-
- According to Sjaaks\cite{Sjaaks}, evaluating the current data flowing through the nozzle to the plate can give us valuable information about the spraying behaviour.
- Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
- It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
-In this work, the author also exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.
-
-From those analysis we are appliying in our automatic classification system the relative standard deviation. Which is refered as the sample standart deviation divided by the sample mean values.
+\subsection{Statistical Analysis}
+In Sjaaks\cite{Sjaaks} work, the author exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.
+We acquire the current data frame of 0.5s and through statistical analysis in the signal such as mean value and standard deviation we apply in our automatic classification the relative standard deviation.
+Which is referred as the sample standard deviation divided by the sample mean values.
+Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.
 
@@
     \centering
-    \resizebox{50mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
-    \caption{EHDA automation system setup}
+    \resizebox{80mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
+    \caption{Sample classification using statistical values. Colors: Green = Dripping; Blue = Intermittent; Red = Cone Jet}
     \label{fig:sjaaks_statistical_class}
@@
 
- through statistical analysis in the signal such as mean value and standart deviation.
- Our classification by statistical analysis was implemented in the automation library made by the previous student \cite{Monica}.
+This classification by statistical analysis was already implemented in the software library made by the previous student \cite{Monica}.
+This method was capable of only classifying dripping, intermittent and cone jet modes. Also in her work, Monica extended the classification to corona or discharge detection.
+My contribution was to integrate her work on my control loop model and extend the classification for the multi jet.
 
- Each current sample is 0.5s of current data in 10kHz sampling frequency.
- By the processing thread we take this sample and evaluate the followings statistical values.
+To classify the multi jet, after running many steps experiments as shown in figure \ref{fig:raw_data} I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean.
+I also noticed that the cone jet current was almost fixed all its spectrum. 
+This effect was cited by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
 
-To classify the multijet I searched \cite{Ryan} The data thus obtained shows that in all cases the relationship between current and flow rate observed in single cone-jet mode is maintained in multi-jet mode when the current and flow rate is normalized by the number of jets.
+With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
+The cone jet current can be calculated by the scaling laws\ref{sec:scalling-laws} formula.
+The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flowrate and the voltage.
+This means this value is just defined for pure ethanol, the liquid used in all those experiments.
+The classification in the algorithm was divided in three steps as shown bellow. The algorithm is shown in \ref{alg:statistical_class}.
 
@@
     \end{algorithm}
-
-\subsection{Machine Learning}
-
-For the machine learning
 

### 2023-04-22 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
 This chapter is about to describe the equipment used and its integration explaining how it was modeled and implemented in both hardware and software sides.
+The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
+The software was previously developed as a electrospray multipurpose library\cite{Monica}.
 
@@
 Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could unterstand in practise how electrospray works.
-I noticed that we need a large set of variables in the range to produce the desired dynamics of electrospray, which most of the time is cone-jet mode.
+I noticed that we need a large set of variables in the correct range to produce the desired dynamics of electrospray, which most of the time is cone-jet mode.
  Those variables can be the liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permitivity. 

### 2023-04-23 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
 
-This chapter is about describing the metodology and developments to achieve the project goals.
+This chapter is about describing the methodology and developments to achieve the project goals. 
+Firstly, let me begin by elaborating on the workings of the classification process in the processing thread.
+Moving on, I will then delve into the operational sequences of the controller thread.
+Lastly, I will provide an explanation on the implementation of the controller.
 

### 2023-04-23 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 \label{sec:classification_results}
+
+The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
+The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes difficult the controller development.
 
@@
 
+    Of particular interest in applications is the cone-jet mode, where the meniscus emits a steady microscopic jet, resulting in uniformly sized droplets.
+
     \subsection{Simple Controller}

### 2023-04-24 software/classification_electrospray.py
scaling laws test

@@ -171,6 +171,16 @@ class ElectrosprayClassification:
         #     print("ERROR: ", str(e)) 
         #     print("Error on João classification")
 
+        try:
+            if(classification_txt == "Cone Jet") and cone_jet_mean != 0:
+                if(mean > 1.14 * cone_jet_mean):
+                    classification_txt = "Multi Jet"
+
+            print("Multi jet treshold mean value: ", cone_jet_mean * 1.14)
+
+        except Exception as e:
+            print("ERROR: ", str(e))
+            print("Error on João classification")
 
         #
         #       Correcting some wrongly classified modes by the system knowledge and memory

### 2023-04-24 software/controller.py

@@ -101,6 +101,7 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
                 controller_output_queue.put(controller_output)
                 # print("[FUG THREAD] put values in controller_output_queue")
                 # EXIT CONTROL SEQUENCE
+
                 if keyboard.is_pressed("q"):
                     print("You pressed q")
                     finish_event.set()
@@ -123,7 +124,6 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
 
 
         FUG_sendcommands(obj_fug_com, ['>S1B 0', 'I 600e-6', '>S0B 0', '>S0R ' + str(typeofmeasurement['slope']), 'U ' + str(typeofmeasurement['voltage_start']), 'F1'])
-        current_state = "Dripping"
 
         set_pump_direction(obj_pump_com, "INF")
         set_inner_diameter(obj_pump_com, syringe_diameter)
@@ -137,6 +137,8 @@ def controller(typeofmeasurement, finish_event, controller_output_queue, fug_COM
 
         controller_output = [get_voltage_from_PS(obj_fug_com), get_current_from_PS(obj_fug_com), voltage, flow_rate]
         controller_output_queue.put(controller_output)
+
+        current_state = "Dripping"
 
         while not finish_event.is_set():
 

### 2023-04-24 software/data_acquisition.py

@@ -94,7 +94,6 @@ def data_acquisition(data_queue,
         except Exception as e:
             print("ERROR: ", str(e))
             print("[DATA_ACQUISITION THREAD] Failed to get tiePie values!")
-            sys.exit(1)
 
         try:
 
@@ -151,4 +150,4 @@ def data_acquisition(data_queue,
             print("[DATA_ACQUISITION THREAD] Failed to put values on data_queue")
             sys.exit(1)
 
-    print("[DATA_ACQUISITION THREAD] Finish acquirind data")
+    print("[DATA_ACQUISITION THREAD] Finish acquiring data")

### 2023-04-24 software/data_processing.py

@@ -75,6 +75,24 @@ def data_processing(data_queue,
 
         try:
 
+            # Validation through the Chen_Pui Article
+            electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data,
+                                                                    electrospray_processing.mean_value,
+                                                                    electrospray_data.flow_rate)
+            print("I:", electrospray_validation.I_emitted_chen_pui * 10e5)
+            print("alpha:", electrospray_validation.alpha_chen_pui * 10e10)
+            cone_jet_mean = electrospray_validation.I_emitted_chen_pui  * 10e5
+
+        except Exception as e:
+            print("ERROR: ", str(e))
+            print("[DATA_PROCESSING THREAD] Failed to electrospray_validation")
+            cone_jet_mean = 1000 # just if fail doesnt mess the classification of cone jet
+
+
+
+
+        try:
+
             # if change flowrate restart conejet mean values
             if(electrospray_data.flow_rate != previous_flowrate):
                 cone_jet_mean = 0
@@ -127,15 +145,6 @@ def data_processing(data_queue,
             print("ERROR: ", str(e)) 
             print("[DATA_PROCESSING THREAD] Failed to put value in save_data_queue")
 
-        try:
-
-            # Validation through the Chen_Pui Article
-            electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data, electrospray_processing.mean_value, electrospray_data.flow_rate)
-            print(electrospray_validation.get_validation_dictionary())
-
-        except Exception as e:
-            print("ERROR: ", str(e)) 
-            print("[DATA_PROCESSING THREAD] Failed to electrospray_validation")
 
         try: 
 

### 2023-04-24 software/save_data.py

@@ -75,13 +75,15 @@ def save_data(
                 # print("[SAVING] before get, queue size:", save_data_queue.qsize())
                 data_measurement, data_processing = save_data_queue.get() # block=True, timeout=None)  # expecting a list with two dictionary objects
                 # print("[SAVING] after get, queue size:", save_data_queue.qsize())
-                data_validation = electrospray_validation.get_validation_dictionary()
+
 
                 try:
                     if electrospray_config_setup["save_data"]:
-                        if electrospray_config_setup["save_validation"]:
-                            s.write('sample '+str(sample), {**data_measurement, **data_processing, **data_validation})  
-                        elif electrospray_config_setup["save_processing"]:
+                        # if electrospray_config_setup["save_validation"]:
+                        #     data_validation = electrospray_validation.get_validation_dictionary()
+                        #     s.write('sample '+str(sample), {**data_measurement, **data_processing, **data_validation})
+                        # el
+                        if electrospray_config_setup["save_processing"]:
                             s.write('sample '+str(sample), {**data_measurement, **data_processing})  #taking values inside the two dicts and creating one dict
                         else:
                             s.write('sample '+str(sample), data_measurement)

### 2023-04-24 software/validation_electrospray.py

@@ -60,7 +60,8 @@ class ElectrosprayValidation:
             self.rho = self.data_dict['config']['liquid']['rho density']
         """
     def calculate_scaling_laws_cone_jet(self, data, mean, flow_rate):
-        ki = 6.46
+        # ki = 6.46
+        ki = 1
 
         # print("\nprocessing_mean:", mean)
         self.mean_value_array = mean

### 2023-04-24 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

@@
 
-\section{Machine Learn}
+\section{Machine Learning}
 
@@
 
+\subsection{Neural Network with raw data}
+
 \subsection{Spectogram analysis}
+
+\begin{multicols}{2}
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=7cm]{Figuras/spectogram/308_Dripping.png}
+    \label{fig:spectrogram1}
+    \caption{Dripping}
+  \end{figure}
+
+  \begin{figure}[H]
+    \center
+    \includegraphics[width=7cm]{Figuras/spectogram/486_Intermittent.png}
+    \label{fig:spectrogram5}
+    \caption{Dripping}
+  \end{figure}
+
+  \begin{figure}[H]
+    \center
+    \includegraphics[width=7cm]{Figuras/spectogram/94_Cone Jet.png}
+    \label{fig:spectrogram2}
+    \caption{Dripping}
+  \end{figure}
+
+  \begin{figure}[H]
+    \center
+    \includegraphics[width=7cm]{Figuras/spectogram/166_Multi Jet.png}
+    \label{fig:spectrogram3}
+    \caption{Dripping}
+  \end{figure}
+
+  \begin{figure}[H]
+    \center
+    \includegraphics[width=7cm]{Figuras/spectogram/276_Corona.png}
+    \label{fig:spectrogram4}
+    \caption{Dripping}
+  \end{figure}
+
+\end{multicols}

### 2023-04-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
             \center
-            \includegraphics[width=8cm]{Figuras/report3/manual-mapping.png}
+            \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
             \caption{ exp-26-01 manual classification}
@@
             \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
+            \caption{ exp-26-01 automatic classification}
+        \end{figure}
+
+    \end{multicols}
+
+    \begin{multicols}{2}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=8cm]{Figuras/april/results_map_1.png}
+            \caption{ exp-26-01 manual classification}
+        \end{figure}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=9cm]{Figuras/april/results_map_2.png}
             \caption{ exp-26-01 automatic classification}
@@
 
+    \begin{multicols}{2}
+
         \begin{figure}[H]
             \center
-            \includegraphics[width=12cm]{Figuras/19:03/non-dimensional-1.png}
+            \includegraphics[width=7cm]{Figuras/april/manual_non_dim_exp.png}
+            \caption{ exp-qw-01-2 (V x Q)}
+        \end{figure}
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=10cm]{Figuras/19:03/non-dimensional-1.png}
             \caption{ exp-26-01-2 (V x Q)}
         \end{figure}
+
+    \end{multicols}
 
@@
 
-    \subsection{Simple Controller}
-
-        \begin{algorithm}
-            \caption{simple controller}\label{alg:simple_controller}
-            \begin{algorithmic}
-            \Function{controller}{$spray\_mode$}
-
-                \If{$spray\_mode$ = $'Intermittent'$ or $spray\_mode$ = $'Dripping'$}
-                    \State \Call{send\_voltage\_command}{$voltage$ + 100}
-                \ElsIf{$spray\_mode$ = $'Multi Jet'$ or $spray\_mode$ = $'Corona'$}
-                    \State \Call{send\_voltage\_command}{$voltage$ - 100}
-                \ElsIf{ $spray\_mode$ = $"Cone Jet"$}
-                    \Comment{Keep Stable}
-                \EndIf
-
-            \EndFunction
-            \end{algorithmic}
-        \end{algorithm}
-
         Flow rate perturbation robustness test
@@
             \center
-            \includegraphics[width=15cm]{Figuras/19:03/control_first_results.png}
+            \includegraphics[width=17cm]{Figuras/19:03/control_first_results.png}
             \caption{ exp-26-01-2 (V x Q)}

### 2023-04-24 data_analysis/data_analysis_1.py

@@ -16,9 +16,9 @@ from scipy.signal import butter, lfilter
 # warnings.filterwarnings('ignore')
 sampling_frequency = 1e5
 
-file_path = "joaoData/mapping/"
+file_path = "Data/control/"
 
-file_name = "map2"
+file_name = "data3"
 
 
 with open(file_path + file_name + ".json", 'r') as data_file:    
@@ -31,11 +31,13 @@ with open(file_path + file_name + ".json", 'r') as data_file:
 
 
 print("\ndata_sample\n")
+
+
 data_sample = pd.json_normalize(
     data['measurements'], 
-    record_path = ["current"], 
-    record_prefix ='data-',
-    meta = ["name", "flow_rate", "voltage", "current_PS", "temperature", "humidity", "target_voltage"]
+    record_path = ["data [nA]"], 
+    record_prefix ='data [nA]-',
+    meta = ["name", "flow rate [m3/s]", "voltage", "current PS", "temperature", "humidity", "target voltage"]
 )
 print(data_sample.info())
 
@@ -71,51 +73,16 @@ data_window.insert(1, 'colormap', colormap)
 print(data_window.info())
 
 
-
-
-######################################
-#           fft on_cick
-######################################
-
-def onpick(event):
-    print (f'button={event.button}, x={event.x}, y={event.y}, xdata={event.xdata}, ydata={event.ydata}')
-    
-    x_value = event.xdata / 5 # round x value per multiple of five
-    x_value = round(x_value) * 5
-
-    # low pass filter to flatten out noise
-    cutoff_freq_normalized = 3000 / (0.5 * sampling_frequency)  # in Hz
-    b, a = butter(6, Wn=cutoff_freq_normalized, btype='low',
-                    analog=False)  # first argument is the order of the filter
-    datapoints = np.array(data_window['current'])[x_value]
-    datapoints_filtered = lfilter(b, a,datapoints)
-
-    
-    fig, axs = plt.subplots(2, 1)
-    axs[0].set(xlabel='time [s]', ylabel='current (nA)', title='datapoints filtered', ylim=[-1e2, 4e2])
-    axs[0].plot(datapoints_filtered)
-    axs[0].grid()
-
-    axs[1].set(xlabel='Frequency [Hz]', ylabel='mag',title='fourier transform of filtered data', ylim=[0, 1e6], xlim=[0, 300])
[…]

### 2023-04-24 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 
-In conclusion, the goals of this project have been largely accomplished.
-The implementation of a Python routine for complete automation and integration of the system has significantly improved the precision of experiments and enabled real-time collection of extensive data without requiring the expertise and time of a specialized scientist.
-The success of this project underscores the potential of automation in enhancing scientific research and accelerating progress towards achieving research goals.
+In conclusion, the implementation of a Python routine for complete automation and integration of the system has improved the precision of experiments and enabled real-time collection of extensive data without requiring the expertise and time of a specialized scientist.
+This project underscores the potential of automation in enhancing scientific research and accelerating progress towards achieving research goals.
 In addition to its potential in scientific research, the software developed in this project can also be leveraged by industrial approaches. 
 Furthermore, the classification methods and system control implemented in this project have yielded promising results and can be further optimized in the future.
-Overall, this project serves as a valuable contribution towards the advancement of automated systems and the optimization of experimental processes, with broad implications for both research and industrial applications.
+Overall, this project serves as a contribution towards the advancement of automated systems and the optimization of experimental processes.
+
+\section{Proposal for continuing}
+
+To continue, my proposal would be to prioritize the improvement of the classification step. 
+Ideally, we could use machine learning or another algorithm to ensure accurate classification of individual data samples.
+
+By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
+In this regard, I would like to present the concept of a fuzzy controller as a potential solution.
+
+To finish, I would propose a final investment in the system portability so that it can be applicable in remote applications.
+
+\subsection{Machine Learning}
+
+\subsection{Fuzzy Controller}
+
+        One challenge in implementing the controller is that we do not have continuous feedback. 
+        Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
+        As this project involves logical control, it requires a different approach.
+
+        The fuzzy approach is an attempt to quantify the classification and fit different control models.
+
+        For that, I fuzzyfied the controller input with the data acquired in an experiment of step routine\ref{subsec:step_routine}.
+With the data, I mapped the area of each spraying mode according to its potential as shown in the Figure \ref{fig:fuzzy_input}.
+        Figures \ref{fig:Fuzzyfication} and \ref{fig:defuzzyfication} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.
+
+        \begin{multicols}{2}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
+                \caption{Fuzzyfication of the voltage input}
+                \label{fig:fuzzy_input}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
+                \caption{Defuzzyfication of output}
+                \label{fig:fuzzy_output}
+            \end{figure}
+
+        \end{multicols}
+
+        Our controller is a machine that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules.
+        The rules are listed bellow.
+
+        Fuzzy Rules:
+
+        -> IF dripping THEN increase
+
+        -> IF intermittent THEN increase
+
+        -> IF cone jet THEN stabilize
+
+        -> IF multi jet THEN decrease
+
+        -> IF corona THEN decrease
+
+        % \begin{figure}[H]
+        %     \centering
+        %     \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
+        %     \caption{Fuzzy Rules}
+        %     \label{fig:fuzzy_rules}
+        % \end{figure}
+
+        For testing the concept I've showed two possible states where the voltage is bellow the necessary to stabilize in cone jet and when is above that voltage.
+We can see in figures \ref{fig:fuzzy_test1} and \ref{fig:fuzzy_test2} that each test the output was either increase or decrease the actuator signal.
+
+        \begin{multicols}{2}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
+                \caption{Test 1: fuzzy controller. Input voltage 4000 V the controller output to increase the voltage.}
+                \label{fig:fuzzy_test2}
+            \end{figure}
+
+            \begin{figure}[H]
+                \centering
+                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
+                \caption{Test 2: fuzzy controller. Input voltage 7000 V the controller output to decrease the voltage.}
+                \label{fig:fuzzy_test1}
+            \end{figure}
+
+        \end{multicols}
+
+        Note that, for this method to work it is needed to run a step sequence to scan the cone jet stability island.
+With that data, create the input membership function.
+Then, run the controller routine in fuzzy mode.
+
+    \subsection{System Portability}
+    \label{subsec:portability}
+
+        Raspberry Pi
+
+    \section{Final Discussions}
 
         The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
-The previous student work was more focused on detecting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
-From the work I've done it highlights:
+        The previous student work was focused in predicting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
+        From the development done by me, it highlights the results:
 
@@
 
-\section{Proposal for continuing}
-
-\subsection{Fuzzy Controller}
-
-        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
-        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzyfied.
-        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.
-
-        For that, I tried to fuzzyfy the controller input by the data acquired in the step routine.
-With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.
-
-        \begin{multicols}{2}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
-                \caption{Fuzzyfication}
-                \label{fig:fuzzy_input}
-            \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
-                \caption{Defuzzyfication}
-                \label{fig:fuzzy_output}
-            \end{figure}
-
-        \end{multicols}
-
-        \begin{figure}[H]
-            \centering
-            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
-            \caption{Fuzzy Rules}
-            \label{fig:fuzzy_rules}
-        \end{figure}
-
-        \begin{multicols}{2}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
-                \caption{Test 1: fuzzy controller}
-                \label{fig:fuzzy_test1}
-            \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
-                \caption{Test 2: fuzzy controller}
-                \label{fig:fuzzy_test2}
-            \end{figure}
-
-        \end{multicols}
-
 \clearpage

### 2023-04-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 Moreover, manual adjustment takes some time to achieve the desired voltage.
-By running a computer routine that automatically sends commands to the power supply, we can achieve faster and more reliable experiment data.
+By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data.
 We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment.
@@
     \center
-    \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
+    \includegraphics[width=16cm]{Figuras/19:03/axs1.png}
     \caption{Print screen of the window shows user interface during the experiment.
@@
     \center
-    {\includegraphics[width=17cm]{Figuras/19:03/axs2.png}}
+    {\includegraphics[width=16cm]{Figuras/19:03/axs2.png}}
     \caption{Print screen during an experiment.
@@
 The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
-The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes difficult the controller development.
+The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes it hard to control this process.
 
@@
 
-For validation purposes and also to expose the benefits of the automated routine and classification
+For validation purposes and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.
 
-    For better understand the effects of both voltage and flow rate in the spraying dynamics manual experiments were made.
-    Also in order to find the stability region of cone jet mode for the liquid and setup used.
+    Firstly, for better understand the spraying dynamics, manual experiments were done.
+    Figure \ref{fig:stability_1} shows the stability region of different spraying mode for pure ethanol in the range of voltage and flow rate.
 
@@
         \includegraphics[width=12cm]{Figuras/regions.png}
-        \caption{ exp-26-01-2 (V x Q)}
+        \label{fig:stability_1}
+        \caption{Spraying modes regions of pure ethanol}
     \end{figure}
 
-    For validation of the automatic system and classification some experiments were made having both manual and automatic data collecting.
-
-    In Figure 14 we can see a result of the map generated by the automatic classification in this experiment.
-
-    Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
+    For validation of the automatic classification experiments were made comparing both manual and automatic classification.
+    In figures \ref{fig:stability_2} and \ref{fig:stability_3} we can see that the cone jet stability island has a similar shape in both manual (fig.
+\ref{fig:stability_2}) and automatic (fig.
+\ref{fig:stability_3}).
+This
 
@@
             \caption{ exp-26-01 manual classification}
+            \label{fig:stability_2}
         \end{figure}
@@
             \caption{ exp-26-01 automatic classification}
+            \label{fig:stability_3}
         \end{figure}
@@
 
-    \section{System Portability}
-    \label{sec:portability}
-
-        Raspberry Pi
-
 \clearpage

### 2023-04-27 Documentation/UFMG/PFCII/Apendices/ApendiceB.tex
documentacao
documentation

@@
-\chapter{O que mais faltou}
+\chapter{Details}
 
 Inclua aqui informações que não sejam tão relevantes para o entendimento do projeto mas que ainda sejam importantes para documentá-lo.
+
+put here the stability difficult about doing experiments
+
+- syringe pump inclined
+- pumping liquid to avoid bubbles
+- mechanical noise in the pumping machine
+- external electrical noise collected by antennas or connections
+
+Foto e detalhes dos instrumentos
 
@@
 \end{figure}
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup_pic}
+\end{figure}
+
+\section{Setup Validation}
+\label{sec:setup_validation}
+
+Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could understand in practice how electrospray works.
+It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
+Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
+ And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
+
+ About the setup, integrate was changed the liquid, nozzle diameter and distance to the plate in order to
+make the experiment the most stable and easy to reach cone-jet mode as possible.
+For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
+Therefore compromising the stabilization in cone jet mode.
+A solution for that was to increasethe flowrate wich smooths this pumping noise.
+For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.

### 2023-04-27 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
         Our controller is a machine that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules.
-        The rules are listed bellow.
+        The rules are listed below.
 
@@
 
-        For testing the concept I've showed two possible states where the voltage is bellow the necessary to stabilize in cone jet and when is above that voltage.
+        For testing the concept I've showed two possible states where the voltage is below the necessary to stabilize in cone jet and when is above that voltage.
 We can see in figures \ref{fig:fuzzy_test1} and \ref{fig:fuzzy_test2} that each test the output was either increase or decrease the actuator signal.

### 2023-04-27 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

--- 2023-04-22 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
@@
 That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
-
-The stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
-For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
+A stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
+The feeding liquid is pulled through a small orifice by means of the applied voltage.
+The droplets are accelerated towards the grounded electrode by the electric field.
+The resulting spray is electrically charged, and the droplets repel one another.
+For this reason, with a controlled environment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
 
@@
 
-Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}.
-That current signal holds a lot o information
-about the dynamics that is happening with the liquid.
-Figure \ref{fig:microdripping_current_pic} illustrate an example of that.
-It can be seen the signal of two droplets of charged liquid generated in this time frame.
+Therefore, researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
+Evaluating the current data can give us valuable information about the spraying behavior.
+Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in our system during a dripping of a charged liquid. 
+We can visually identify the signal of two droplets generated in this time frame.
 
@@
     \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
-    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
+    \caption{Current measurement sample of dripping spraying mode. This graph represents 0.5s sample.}
     \label{fig:microdripping_current_pic}
@@
   This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+  A profound use of his method will be explained in section \ref{sec:section_classification}.
+  Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
 
@@
 Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
+In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid.
 
-\[ I = (\frac{\gamma K Q}{\kappa})^{1/2}\]
+\begin{equation}\label{eq:i_chenpui}
+	I = (\frac{\gamma K Q}{\kappa})^{1/2}
+\end{equation}
 
@@
 
-The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows 3 spraying dynamics that we are most interesting in this project.
+Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows 3 spraying dynamics that we are most interesting in this project.
 
@@
 
-Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate between 5 modes as shown above in order of growing electric potential:
+Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate between 5 modes as reffered below in order of growing electric potential:
 
@@
 
-Intermittent mode is defined when the electric field forces starts to have a considerable effect in the meniscus and droplet formation. 
+Intermittent mode is defined when the electric field forces start to have a considerable effect in the meniscus and droplet formation. 
+This mode can be identified by its pulsating manner.
 In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
+Figures \ref{fig:intermittent_example}, \ref{fig:intermittent2_example} and \ref{fig:microdripping_example} illustrates 3 different dynamics herein considered as intermittent.
 
@@
 
+Taylor (1964)\cite{taylor} was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
 The electrified meniscus can take on a conical shape within a certain range of applied voltage and injected liquid flow rate.
 
-Taylor (1964)\cite{taylor} was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
-Taylor cone-jets naturally occurs under relatively limited circumstances: when the applied field and flow rate are in the appropriate range, and the electrosprayed liquid exhibits the adequate physical properties.
+In Taylor cone, here referred as Cone Jet, the direction of the cone apex also varies depending on the balance of forces. 
+With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume as we increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.
 
-During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window.
+Figures \ref{fig:conjt1}, \ref{fig:conjt2} and \ref{fig:conjt3} shows three cone jets in different circunstances.
 
@@
 C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
-For this work it highlights the detection that for a low number of jets emitted, seen in figure \ref{fig:multijt1} and \ref{fig:multijt2}, the meniscus is not bound to the rim of the capillary. 
+He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt1} and \ref{fig:multijt2}, the meniscus is not bound to the rim of the capillary. 
 This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
 
-As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray, seen in figure \ref{fig:multijt3}. In this work it will also be classified as multi jet.
+As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray, seen in figure \ref{fig:multijt3}. 
+In this work, all modes with more than one stable jet will be classified as multi jet.
 
@@
 
-At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown and we achieve a phenomenon of discharge.
+At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown, and we achieve a phenomenon of discharge.
 Those can be easily classified because of its high current value.

### 2023-04-27 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

@@
-\chapter{Metodology}
+\chapter{Methodology}
 \label{chap:Metodology}
@@
 This means this value is just defined for pure ethanol, the liquid used in all those experiments.
-The classification in the algorithm was divided in three steps as shown bellow. The algorithm is shown in \ref{alg:statistical_class}.
+The classification in the algorithm was divided in three steps as shown below. The algorithm is shown in \ref{alg:statistical_class}.
 
@@
 
-The map that will be explained bellow is the most relevant sequence in this work.
+The map that will be explained below is the most relevant sequence in this work.
 This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
@@
 
+    \subsection{Simple Controller}
+
+        \begin{algorithm}
+            \caption{simple controller}\label{alg:simple_controller}
+            \begin{algorithmic}
+            \Function{controller}{$spray\_mode$}
+
+                \If{$spray\_mode$ = $'Intermittent'$ or $spray\_mode$ = $'Dripping'$}
+                    \State \Call{send\_voltage\_command}{$voltage$ + 100}
+                \ElsIf{$spray\_mode$ = $'Multi Jet'$ or $spray\_mode$ = $'Corona'$}
+                    \State \Call{send\_voltage\_command}{$voltage$ - 100}
+                \ElsIf{ $spray\_mode$ = $"Cone Jet"$}
+                    \Comment{Keep Stable}
+                \EndIf
+
+            \EndFunction
+            \end{algorithmic}
+        \end{algorithm}
+
 \clearpage

### 2023-04-27 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
-Most power supplies available in the market rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person.
+With the save data by streaming in saving thread\ref{subsec:save_thread}, we achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
+
+Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person. 
 Moreover, manual adjustment takes some time to achieve the desired voltage. 
-By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data.
-We can see in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp} the visual interface that the operator have during an experiment.
-All the important data of EHDA experiments are showed in the same screen and referring to each 0.5 seconds sampling time.
+By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data points.
+
+The visual interface for the user, seen in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp}, shows all the important sensor data and signal analysis that can be interesting to the operator in real time.
 

### 2023-04-27 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

--- 2023-04-01 Documentation/WT group/NHL/systemDescription/systemDescription.tex
@@
 
-\section{Instrumentation}
-\label{sec:instrumentation}
+In this chapter, we will discuss the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
+The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library \cite{Monica}.
 
-The main instruments used for this project are listed above:
+\section{Hardware model}
+\label{sec:hardware_model}
+
+\subsection{Instrumentation}
+\label{subsec:instrumentation}
+
+The main instruments used for this project are listed below:
 
@@
 
-    HVPS provides the electrical potential to the liquid, which can be applied by connecting the HVPS directly to the liquid feeding capillary or needle to a grounded electrode (usually a plate or a ring) located downstream.\cite{Monica}
+    The HVPS provides the electrical potential to the liquid, which can be applied by connecting the HVPS directly to the liquid feeding capillary or needle to a grounded electrode (usually a plate or a ring) located downstream.\cite{Monica}
     The setup has the USB serial interface for controlling and polling measurements.
@@
 This interface can be found in \emph{FUG\_function.py} file where is located the functions used to control and collect data from this instrument.
-    In case of future change of equipment brand a new interface must be created within this file to match another manufacturer specifications.
+    In case of change of equipment, a new interface must be created within this file to match another manufacturer specifications.
 
@@
     Wireless communication allows us to make measurements disconnected to an external power supply, which gives us more safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
-    The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 M%Ω).
+    The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
     TiePie WifiScope WS6 has a resolution of up to 16 bit at a minimal input range of 200 mV, sufficient to measure currents down to 1 nA.
 
-    The iterface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
+    The interface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
 Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.
@@
 
-  The stability of the system is aftected by many physical effects. Evidently having the more parameters analysed favours the system control.
-  The surface tension force is dependant of the liquid-gas interface on the meniscus. Hence, the gas around it must be constantly the same and so its humidity.
-  Also, temperature is a variable that interfere in many phenomenas in the system. Specially the liquid properties such as viscosity.
+  The stability of the system is affected by many physical effects. Evidently having the more parameters analyzed favors the system control.
+  The surface tension force is dependent of the liquid-gas interface on the meniscus. Hence, the surrounding gas must be constantly the same and so its humidity.
+  Also, temperature is a variable that interfere in many phenomena in the system. Specially the liquid properties such as viscosity.
 
-  For that, a standart microcontroler development board (\emph{Arduino Uno}) with a temperature and humidity sensor (DHT11) was configured to add that data in real time in the routine.
+  For that, a standard microcontroller development board (\emph{Arduino Uno}) with a temperature and humidity sensor (DHT11) was configured to add that data in real time in the routine.
   The Arduino code can be found in the \emph{/peripherals} folder.
@@
 
-  The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
-    two main variables that afect the system. 
+  The pump integration in the automation algorithm brings us a new controllable variable, the Flow rate. Now we can control the spraying mode with the
+  two main variables that affect the system. 
   It will bring more complexity for the system since now we are dealing with multivariable control.
-    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.
-    % Our control model is now a MISO \footcite{MISO: Multiple Inputs Single Output} system. The crossover (couple) between the controlled variables will be evaluated in further reports.
+  Controlling also the flow rate gives to this project a new dimension in the system giving us freedom to explore the flow rate properties.
+  With this new input variable our control is a MISO (Multiple Inputs Single Output) system.
 
-    About the pump interface. As I could not find a good ready-to-use library for this pump I developed an simple and intuitive interface to be our software routine.
+  About the pump interface. As I could not find a good ready-to-use library for this pump I developed a simple and intuitive interface to be our software routine.
   The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
 
-  Also, the supply of constant pressure can also 
-    \cite{prunet}
-  The supply at constant pressure sometimes favours the stability of the spray.
+  % The supply at constant pressure can also favor the stability of the spray\cite{prunet}.
 However, the flow rate depends on the applied pressure and pressure losses between the tank and the end of the capillary, which themselves are dependent on the liquid chosen and on its temperature.
@@
 
-\subsection{Setup Organization}
-\label{subsec:setup_organization}
-
-\begin{figure}[H]
-  \centering
-  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
-  \caption{EHDA automation system setup}
-  \label{fig:setup_pic}
-\end{figure}
-
-The peripherals automation routine was already developed by another student.
-In order to continue the research I took some time to understand the physical concept behind EHDA experiments and the project knowledge.
-I made upgrades in the routine to include the high speed camera with a hardware triggering routine using an arduino microcontroler.
-This will be usefull to validate the further classification of the spray dynamics.
-
-% ilustramos o processo com a Figura \ref{fig:setup}.
+In figure \ref{fig:setup} we illustrate a diagram with all the key components of our system. The peripherals are connected to a computer running the software routine via serial communication. 
+This diagram encapsulates our process system and will be used as a sub-system in our control model.
+The input of our process system are power supply voltage and pump machine flow rate, referred here as the controller values.
+The output is the oscilloscope current sample.
 
@@
 
-\section{Setup Validation}
-\label{sec:setup_validation}
+There are also many minor variables that affects the experiment stability. More details are explained in \ref{sec:setup_validation}.
 
-Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could unterstand in practise how electrospray works.
-I noticed that we need a large set of variables in the range to produce the desired dynamics of electrospray, which most of the time is cone-jet mode.
- Those variables can be the liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permitivity. 
- And also physical variables such as flowrate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
+\section{Software Model}
+\label{sec:control_model}
 
- About the setup,integrate was changed the liquid, nozzle diameter and distance to the plate in order to
-make the experiment the most stable and easy to reach cone-jet mode as possible.
-For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
-Therefore compromising the stabilization in cone jet mode.
-A solution for that was to increasethe flowrate wich smooths this pumping noise.
-For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
+The software was reformulated on top of the control model represented in figure \ref{fig:control_model_fig}. The process of the control loop is the same as represented in \ref{fig:setup}. 
+Each other subsystem in the control loop is a separate thread that will be explained bellow.
 
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/april/control_model.png}}
+  \caption{EHDA automation system setup}
+  \label{fig:control_model_fig}
+\end{figure}
+
+\subsection{Threading and Queues}
+\label{subsec:concurrency}
+
+    In order to implement this closed loop control model to the software and explore parallel processing, each sub-system was implemented as a separate Thread.
+    For concurrency on flux of data between threads was used queues structures.
+    A queue is an abstract data type that holds an ordered, linear sequence of items. You can describe it as a first in, first out (FIFO) structure.
+
+    \subsection{Controller Thread}
+
+        It is responsible for sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
+        Also, responsible for sending the finish event command that end the routine and trigger the threads to close their routines.
+        As input, we have the setup config file and the \emph{feedback\_queue}. As output, we have the values in the \emph{controller\_output\_queue()}.
+
+    \subsection{Data Acquisition Thread}
+    \label{subsec:data_aquisition}
+
+        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the power supply, flow rate from the pump and concatenate into one sample data.
+        As output, we have the values in the \emph{data\_queue()}.
+
+    \subsection{Data Processing Thread}
+
+        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
+        As output, we have the values in the \emph{save\_data\_queue()}, \emph{plotting\_queue()} and \emph{feedback\_queue()}.
+
+    \subsection{Save Data Thread}
+    \label{subsec:save_thread}
+
+        After processing, the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
+        With the new streaming model of saving a new structure of the collected data were created.
+        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
+        The data acquired in each sample of 0.5s is shown in figure \ref{fig:data_sample}.
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
+            \caption{Output data json structure}
+            \label{fig:data_sample}
+        \end{figure}
+
+        This new way of saving the measurement and processing data altogether separate by enumerated samples prevents loss of data in case of error during experiments and, specially improve in the usability of the data for further deep analysis.
+One experiment of around 1 hour collects around 6 GB of data.
+Organizing that amount of data to make it fast and easy to use was an important improvement in the software.
+        To work and analyze the data we can use  pandas Data frame. A python widely used framework for data analysis.
+        With the command:
+
+        pandas.read\_json('PATH', orient='index').
+
+        It will construct a Data frame with all data organized by samples.
+
+        To conclude, json files are good as a system output because of its human readability.
+But as the database gets bigger json becomes to be a slow to read and heavy way to store the data.
+For that, saving the data frame in a compressed type of file called feather is much faster to work with the data.
+
+    \subsection{Video Thread}
+
+        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.
+
+    \subsection{Plot}
+
+        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilities of running outside the main function. 
+        It is responsible for plotting in real time the current sample acquired, and its respective fast Fourier transform to evaluate the sample frequency spectrum.
+        It takes as input the \emph{plot\_data\_queue} from the \emph{processing\_thread()} and displays three graphs updated in real time on the screen during the experiment.
+
+  \section{Chapter conclusion}
+
+    In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software.
+Figure \ref{fig:metodology_example1} shows a print screen of the user interface during an experiment.
+
+    \begin{figure}[H]
+      \centering
+      \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
+      \caption{EHDA automation system setup}
+      \label{fig:metodology_example1}
+  \end{figure}
 \clearpage

### 2023-04-27 Documentation/UFMG/relatorios/Relatorio_3/Development/Development.tex
documentation

@@
     This procedure was implemented in the controller thread routine as a new sequence that can be configured in the setup file before an experiment.
-    The algorithm of this sequence in the controller thread is shown bellow.
+    The algorithm of this sequence in the controller thread is shown below.
 
@@
     As a conclusion of this discussion we got that with voltage steps under 250V the system does not show a transition dynamic. 
-    For steps above this value we can see a capacitance curve in the current data. This is explained by the system capacitance which resists to fast changes in eletric potential.
+    For steps above this value we can see a capacitance curve in the current data. This is explained by the system capacitance which resists to fast changes in electric potential.
     This treshold value of 250V will vary depending on the resultant capacitance of setup used.

### 2023-04-27 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

--- 2023-04-27 Documentation/UFMG/PFCII/Metodology/Metodology.tex
@@
 \chapter{Methodology}
-\label{chap:Metodology}
+\label{chap:Methodology}
 
 This chapter is about describing the methodology and developments to achieve the project goals. 
-Firstly, let me begin by elaborating on the workings of the classification process in the processing thread.
+Firstly, I begin by elaborating on the workings of the classification process in the processing thread.
 Moving on, I will then delve into the operational sequences of the controller thread.
@@
 \subsection{Statistical Analysis}
-In Sjaaks\cite{Sjaaks} work, the author exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.
-We acquire the current data frame of 0.5s and through statistical analysis in the signal such as mean value and standard deviation we apply in our automatic classification the relative standard deviation.
+In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
+We acquire the current data frame of 0.5s with 100 KHz as sampling frequency.
+With that each current sample as 50 thousand current values.
+Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation.
 Which is referred as the sample standard deviation divided by the sample mean values.
@@
 I also noticed that the cone jet current was almost fixed all its spectrum. 
-This effect was cited by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
+These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
 
@@
 The cone jet current can be calculated by the scaling laws\ref{sec:scalling-laws} formula.
-The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flowrate and the voltage.
+The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flow rate and the voltage.
 This means this value is just defined for pure ethanol, the liquid used in all those experiments.
@@
 
+The ramp sequence is simply done by sending one command to the power supply to perform a ramp in the voltage with initial, final and slope values.
+The flow rate for this sequence is constant, and the experiment consists in a voltage range scan.
+
 \subsection{Step}
 \label{subsec:step_routine}
+
+The step sequence is done by the same command send to the power supply but with the maximum slope value in order to proximate of a step signal.
+By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage. This algorithm is represented in \ref{alg:stepping_algorithm}.
 
@@
 This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
-The purpose is to map the operational window, seen in Figure \ref{fig:ganan_calvo_fig}, that can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.
-
-    \begin{figure}[H]
-        \center
-        \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
-        \caption{Domains of existence (stability) of Taylor Cone Jets.
-\cite{gananCalvo} .
-The window formed by these points is where the system operated in the stable cone-jet.
-Operational windows depend of the liquid and configuration setup.
-Different windows are represented for different liquid conductivity.
-The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
-        \label{fig:ganan_calvo_fig}
-    \end{figure}
+The purpose is to map the operational window, seen in Figure \ref{fig:map3Data_fig}, that can be defined where the spraying mode can be stabilized based on the flow rate, voltage and the setup configuration.
 
@@
 The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
-The algorithm for this sequence is a copy of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is illustrated in the algorithm \ref{alg:mapping_algorithm}.
+The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is represented in the algorithm \ref{alg:mapping_algorithm}.
 

### 2023-04-27 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 For validation purposes and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
+    \caption{Domains of existence (stability) of Taylor Cone Jets.
+\cite{gananCalvo} .
+The window formed by these points is where the system operated in the stable cone-jet.
+Operational windows depend of the liquid and configuration setup.
+Different windows are represented for different liquid conductivity.
+The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
+    \label{fig:ganan_calvo_fig}
+\end{figure}
 

### 2023-04-27 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
     In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
-    Note that the experiment is composed of loops that increase voltage, change flowrate and repeat.
+    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.
 
@@
     With all the data collected, classified and saved in real time, we can do further analysis and studies.
-For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X FlowRate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researchs, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.
+For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researches, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.
 
@@
 
-    The control sequence is the only from our list of sequences that actually uses the feedback value. 
+    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
     As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
+    A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.
 
@@
 
+    \section{Chapter conclusion}
+
 \clearpage

### 2023-04-28 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 
+The map was inspired in Gañan-Calvo\cite{gananCalvo} work where he points how liquid conductivity influences the cone jet stability island.
+
+\begin{figure}[H]
+    \center
+    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
+    \caption{Domains of existence (stability) of Taylor Cone Jets.
+\cite{gananCalvo} .
+The window formed by these points is where the system operated in the stable cone-jet.
+Operational windows depend of the liquid and configuration setup.
+Different windows are represented for different liquid conductivity.
+The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
+    \label{fig:ganan_calvo_fig}
+\end{figure}
+
 To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.

### 2023-04-28 Documentation/UFMG/PFCII/Results/Results.tex
documentation

--- 2023-04-27 Documentation/UFMG/PFCII/Results/Results.tex
@@
 
-The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
-The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes it hard to control this process.
+The classification results in our algorithm implemented as described in section \ref{sec:section_classification} showed good accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
+Nevertheless, the multi jet classification made by a current value factor of 1.14 above the cone jet is just effective for pure ethanol, liquid used in all this project.
+
+Even if the multi jet classification just works for pure ethanol, the data saved with correct classification in ethanol can be used to extract any other signal information about the multi jet or to train a black box classification algorithm.
 
@@
 
-Our first classification results were made exploring just the voltage ranges. For that we tried to stabilize all the other parameters such as humidity, temperature and external noise.
-First, we fixed a flow rate to 0.7 uL/min.
-and ran a step routine as defined in \ref{subsec:step_routine}.
+Our first classification results were made exploring just the voltage ranges. For that stabilized all the other parameters such as humidity, temperature and external noise.
+First, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
 The figure \ref{fig:step_voltage} shows the step voltages during the experiment and figure \ref{fig:raw_data} illustrates the raw data acquired with it. 
@@
 
-For validation purposes and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.
+For validation with literature and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.
 
@@
         \center
-        \includegraphics[width=12cm]{Figuras/regions.png}
+        \includegraphics[width=8cm]{Figuras/regions.png}
         \label{fig:stability_1}
@@
 \ref{fig:stability_2}) and automatic (fig.
-\ref{fig:stability_3}).
-This
+\ref{fig:stability_3}) data collected in the same experiment.
 
@@
             \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
-            \caption{ exp-26-01 manual classification}
+            \caption{Cone jet island manual experiment 1}
             \label{fig:stability_2}
@@
             \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
-            \caption{ exp-26-01 automatic classification}
+            \caption{Cone jet island automatic experiment 1}
             \label{fig:stability_3}
@@
     \end{multicols}
+
+    We can see in figures \ref{fig:stability_4} and \ref{fig:stability_5} another experiment with the same liquid and a comparison on manual (visually by the high speed camera) and automatic classification.
 
@@
             \includegraphics[width=8cm]{Figuras/april/results_map_1.png}
-            \caption{ exp-26-01 manual classification}
+            \caption{Cone jet island manual experiment 2}
+            \label{fig:stability_4}
         \end{figure}
@@
             \includegraphics[width=9cm]{Figuras/april/results_map_2.png}
-            \caption{ exp-26-01 automatic classification}
+            \caption{Cone jet island automatic experiment 2}
+            \label{fig:stability_5}
         \end{figure}
@@
 
-    Figures 15 and 16 shows that we could achieve a stable cone jet region map with similar shape and values in both manual and automatic classification of the same experiment.
+    We can see in figures \ref{fig:stability_6} and \ref{fig:stability_7} the same experiment and results as above, but with the Multi Jet classification that was a new feature in the software.
 
@@
             \includegraphics[width=8cm]{Figuras/april/map5.png}
-            \caption{ exp-26-01 manual classification}
+            \caption{Cone jet island manual experiment 3}
+            \label{fig:stability_6}
         \end{figure}
@@
             \includegraphics[width=10cm]{Figuras/april/map2.png}
-            \caption{ exp-26-01 automatic classification}
+            \caption{Cone jet island automatic experiment 3}
+            \label{fig:stability_7}
         \end{figure}
@@
             \includegraphics[width=7cm]{Figuras/april/manual_non_dim_exp.png}
-            \caption{ exp-qw-01-2 (V x Q)}
+            \caption{Cone jet island manual experiment 4}
         \end{figure}
@@
             \includegraphics[width=10cm]{Figuras/19:03/non-dimensional-1.png}
-            \caption{ exp-26-01-2 (V x Q)}
+            \caption{Cone jet island automatic experiment 4}
         \end{figure}
@@
 \label{sec:controller_results}
+
+    The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
+    The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes it hard to control this process.
 
@@
             \includegraphics[width=17cm]{Figuras/19:03/control_first_results.png}
-            \caption{ exp-26-01-2 (V x Q)}
+            \caption{Simple controller validation experiment.
+For this experiment we waited the system to stabilize in the desired spraying mode.
+After that we made a perturbation robustness test changing the flow rate.}
         \end{figure}

### 2023-05-02 Documentation/UFMG/PFCII/Abstract/Abstract.tex
documentation

--- 2023-03-01 Documentation/UFMG/modelo_PFC_latex/Resumo/Abstract.tex
@@
     Electrohydrodynamic Atomization (EHDA), also called electrospray, is a liquid atomization technique that
-    produces micro- and nanometric charged droplets within a narrow size distribution by using high electric fields (kV/cm).
+    produces micro and nanometric charged droplets within a narrow size distribution by using high electric fields (kV/cm).
     According to Cloupeau and Prunet-Foch\cite{prunet} (1994), electrosprays can generate droplets in different ways, which the authors
@@
     but also depend on liquid properties and system geometry. In their work, the authors proposed four possible EHDA
-    modes: dripping, intermittent, cone-jet and multi-jet, which are generally distinguished visually. Verdoold et al.\cite{Sjaaks} (2014)
-    recently suggested a classification approach based on the behavior of the electric current of the electrospray process.
+    modes: dripping, intermittent, cone-jet and multi-jet, which are generally distinguished visually.
 
@@
     The system classifies spray mode dynamics using real-time current data and changes EHDA operating parameters such
-    as liquid flowrate and applied voltage to achieve and maintain the chosen spray mode. The electrospray modes are
+    as liquid flow rate and applied voltage to achieve and maintain the chosen spray mode. The electrospray modes are
     validated in real time by using a high-speed camera.
-    As compared to conventional manual approaches, the implemented control algorithm achieves higher
+    As compared to conventional manual approaches, the control algorithm promises higher
     accuracy and lower transient time. Therefore, a completely autonomous EHDA system opens the door to potential
-    industrial applications. In addition, the use of the electric current signal will be useful to further study electrospray
-    processes, leading to better control on droplet generation (frequency, size and charge). The incorporation of Machine
-    Learning to improve mode categorization will be a future development.
-
-\clearpage
-\thispagestyle{empty}
-\cleardoublepage
+    industrial applications. In addition, the use of the electric current signal can be useful to further research in electrospray
+    processes, leading to better control on droplet generation (frequency, size and charge).

### 2023-05-02 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 This can be achieved by a closed system loop control system. 
-Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.
+An automated spray mode classification is a crucial part of the control system to work, as well as the development of an appropriate control algorithm.
 
@@
 For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
-Her work corroborates the validation of this project motivating its development and optimization.
+Her work corroborates the validation of this project motivating its continuation on development and optimization.
 
-Above is shown the main goals listed:
+Bellow are shown the main goals listed:
 
@@
 \item Fully automated and intuitive system for EHDA.
-\item Real Time non-visual classification of spraying modes.
+\item Real time non-visual classification of spraying modes.
 \item Control and stabilization on a desired dynamic. 
@@
 \label{sec:doc_struct}
+
+This document is divided in 6 chapters. 
+This chapter \ref{chap:intro} shows an introduction about EHDA and what inspired the project. 
+Chapter \ref{chap:lit_review} have a more deep explanation about the literature concepts and knowledge used in this project. 
+Chapter \ref{chap:system_description} will describe all the system implemented to make this project work with the instruments and models used to apply our methodology.
+Chapter \ref{chap:Methodology} we present the methodology applied in our experiments in order to validate our system.
+Chapter \ref{chap:Results} presents our results and discussions comparing the knowledge acquired in literature review.
+Finally, chapter \ref{chap:conclusion} will conclude our document with discussions about what goals were achieved and what can be optimized.

### 2023-05-02 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 
-Therefore, researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
+Therefore, many researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
 Evaluating the current data can give us valuable information about the spraying behavior.

### 2023-05-03 Documentation/UFMG/PFCII/Apendices/ApendiceB.tex
documentation

@@
 For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
+
+\section{Oscilloscope Impedance}
+\label{sec:osc_impedance}
+
+The current is being measured by the Oscilloscope using its internal impedance. 
+This oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
+Selecting one or other can multiply or divide your current measurement by 2. 
+By default we are using the 2Mohm differential input. But it was noticed that using the 1Mohm resistance might reduce the noise. 
+A proposal of optimization is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-03 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
-In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid.
+In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.
 
@@
 \end{equation}
+
+\vspace{2cm}
 
@@
       \center
-      \includegraphics[width=3cm]{Figuras/drippingexample.png}
+      \includegraphics[width=2.9cm]{Figuras/drippingexample.png}
       \label{fig:dripping_camera_example}
@@
       \center
-      \includegraphics[width=3cm]{Figuras/19:03/intermittent_example.png}
+      \includegraphics[width=2.5cm]{Figuras/19:03/intermittent_example.png}
       \label{fig:intermittent_example}
-      \caption{Intermittent}
+      \caption{Intermittent 1}
   \end{figure}
@@
       \label{fig:intermittent2_example}
-      \caption{Intermittent}
+      \caption{Intermittent 2}
   \end{figure}
@@
       \label{fig:microdripping_example}
-      \caption{Microdripping}
+      \caption{Microdripping / Intermittent 3}
   \end{figure}
@@
       \label{fig:conjt1}
-      \caption{Cone Jet}
+      \caption{Cone Jet 1}
   \end{figure}
@@
       \label{fig:conjt2}
-      \caption{Cone Jet}
+      \caption{Cone Jet 2}
   \end{figure}
@@
       \center
-      \includegraphics[width=2cm]{Figuras/april/conjet3.png}
+      \includegraphics[width=2.2cm]{Figuras/april/conjet3.png}
       \label{fig:conjt3}
-      \caption{Cone Jet}
+      \caption{Cone Jet 3}
   \end{figure}
@@
 
+\section{Chapter conclusion}
+
+In this chapter we exhibit some electrospray theory that was important for the development of this project. 
+Firstly, with a brief review about the physical concept behind the experiment. 
+Then, I introduce how current analysis can be useful for our application citing works already done with this approach.
+Finally, I end up the chapter defining what spraying modes classification will be considered and its properties.
+
 \clearpage

### 2023-05-03 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
     A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.
-
-    \subsection{Simple Controller}
+    Its results can be seen in results section \ref{sec:controller_results}.
 
@@
 
+This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was applied with a control and automation engineering approach in order to achieve our goals. 
+Next chapter \ref{chap:Results}, we will discuss the results reached.
+
 \clearpage

### 2023-05-03 data_analysis/reprocessing/classification_electrospray.py

@@ -1,325 +1,0 @@
-import itertools
-import os
-import re
-from typing import TextIO
-import numpy as np
-import json
-import math
-
-
-class ElectrosprayClassification:
-    
-    def __init__(self, name_liquid):
-        self.name_liquid = name_liquid
-        self.all_data = []
-        self.sjaak_std_mean_array = []
-        self.sjaak_mean_median_array = []
-        self.med_value_array = []
-        self.mean_value_array = []
-        self.sjaak_verified = []
-        self.sjaak_verified_false = []
-        self.sjaak_verified_true = []
-        self.previous_state = "Dripping"
-
-        self.data_points_list = 0
-        self.electrical_conductivity = 0
-        self.surface_tension = 0
-        self.dieletric_const = 0
-        self.electrical_conductivity = 0
-        self.permitivity = 0
-        self.rho = 0
-        self.density = 0
-
-
-
-
-    def do_classification(
-            self,
-            mean,
-            median,
-            stddeviation,
-            psd_values,
-            variance,
-            max_value_of_the_data,
-            quantity_max_data,
-            percentage_max,
-            flow_rate,
-            fft_max_peaks_array,
-            cont_fft_max_peaks):
-
-        self.med_value_array.append(median)
-        classification_txt = "Undefined"
-
-
-        #
-        #       SJAAKS  -> Is capable of classifiying Dripping, Intermittent and Cone Jet
-        #
-
-        try:
-                
-            if mean != 0:
-                self.sjaak_std_mean = (stddeviation / mean)
-                # print("std/mean = %f ;" % (self.sjaak_std_mean))
-            else:
-                self.sjaak_std_mean = 0
-            self.sjaak_std_mean_array.append(self.sjaak_std_mean)
-
-            if median != 0:
-                self.sjaak_mean_median = (mean / median)
-                # print('sjaak_mean_median: ', self.sjaak_mean_median)
-            else:
-                self.sjaak_mean_median = 0
-            self.sjaak_mean_median_array.append(self.sjaak_mean_median)
-
-            # classification for dripping
-            # if mean <= 5:
-            if self.sjaak_std_mean > 2.5:
-                classification_txt = "Dripping"
-                if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
[…]

### 2023-05-03 data_analysis/reprocessing/processing.py

@@ -1,176 +1,0 @@
-'''
-	Non Real Time Processing the data
-	AUTHOR: 乔昂 - jueta
-	DATE: 19/01/2023
-'''
-
-import pandas as pd
-from pandas.io.json import json_normalize
-import json
-import matplotlib.pyplot as plt
-from sklearn.utils import column_or_1d
-import numpy as np
-from scipy.signal import butter, lfilter
-from electrospray import ElectrosprayDataProcessing, ElectrosprayConfig
-from classification_electrospray import ElectrosprayClassification
-
-# tiepie params
-sampling_frequency = 1e5  # 100 KHz
-multiplier_for_nA = 500
-
-append_array_data = True
-append_array_processing = True
-
-
-# warnings.filterwarnings('ignore')
-sampling_frequency = 1e5
-
-file_path = "../Data/mapping/"
-
-file_name = "map3"
-
-electrospray_processing = ElectrosprayDataProcessing(sampling_frequency)
-electrospray_classification = ElectrosprayClassification("name_liquid")
-
-array_values = []
-
-
-data = pd.read_feather("map3.feather")
-
-
-
-#
-#
-#
-#
-#
-
-# time_step = 1 / sampling_frequency
-
-# # THREAD LOOP
-# for data_queue in data['data [nA]']:
-
-
-#     electrospray_data  = data_queue 
-
-#     try:
-
-#         # low pass filter to flatten out noise
-#         cutoff_freq_normalized = 3000 / (0.5 * sampling_frequency)  # in Hz
-#         b, a = butter(6, Wn=cutoff_freq_normalized, btype='low', analog=False)  # first argument is the order of the filter
-#         datapoints_filtered = lfilter(b, a, electrospray_data)
-
-#     except Exception as e:
-            print("ERROR: ", str(e)) 
-#         print("[DATA_PROCESSING THREAD] Failed to filter points!")
-
-#     try:
-
-#         electrospray_processing.calculate_filter(a, b, electrospray_data)
-        
-#         electrospray_processing.calculate_fft_raw(electrospray_data)
-
-#         electrospray_processing.calculate_statistics( electrospray_data)
-        
-#         electrospray_processing_freq, electrospray_processing_psd = electrospray_processing.calculate_power_spectral_density(electrospray_data)
-
-#         max_data, quantity_max_data, percentage_max = electrospray_processing.calculate_peaks_signal(electrospray_data)
-
[…]

### 2023-05-03 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 First, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
-The figure \ref{fig:step_voltage} shows the step voltages during the experiment and figure \ref{fig:raw_data} illustrates the raw data acquired with it. 
-In figure \ref{fig:class_step_data} we see the same experiment data classified by spraying mode and separated by color.
+The figure \ref{fig:step_class} shows three graphs.
+
+The first is the input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.
+
+The second is the output raw data collected in the voltage range. The sampling rate of the oscilloscope is 10KHz. Therefore, this graph has 1.5 Million data points.
+
+The Third graph is the same the second but after the classification procedure.
+
+% \begin{figure}[H]
+%     \center
+%     \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
+%     \caption{Input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.}
+%     \label{fig:step_voltage}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \center
+%     \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
+%     \caption{Output raw data collected in the voltage range experiment showed in \ref{fig:step_voltage}. The sampling rate of the oscilloscope is 10KHz. This graph has 1.5 Million data points.}
+%     \label{fig:raw_data}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \center
+%     \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
+%     \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colors are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
+%     \label{fig:class_step_data}
+% \end{figure}
 
@@
     \center
-    \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
-    \caption{Input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.}
-    \label{fig:step_voltage}
+    \includegraphics[width=18cm]{Figuras/may/step_class.png}
+    \caption{Automatic electrospray classification through the step routine.}
+    \label{fig:step_class}
 \end{figure}
 
-\begin{figure}[H]
-    \center
-    \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
-    \caption{Output raw data collected in the voltage range experiment showed in \ref{fig:step_voltage}. The sampling rate of the oscilloscope is 10KHz. This graph has 1.5 Million data points.}
-    \label{fig:raw_data}
-\end{figure}
+The graph of voltage scan has a common shape for different liquids and parameters. After having familiarity with it is even possible to classify the spraying modes by visual analysis.
 
-\begin{figure}[H]
-    \center
-    \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
-    \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colors are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
-    \label{fig:class_step_data}
-\end{figure}
-
-The graph of voltage scan as showed in \ref{fig:raw_data} has a common shape for different liquids and parameters.
-After having familiarity with it is even possible to classify the spraying modes by visual analysis.
-For example:
-Dripping mode has a current mean of 0V.
+For example, dripping mode has a current mean of 0V.
 The Intermittent state has a high variation of values that can be seen by the thickness of the graph.
@@
 
-    For validation of the automatic classification experiments were made comparing both manual and automatic classification.
+    For validation of the automatic classification, experiments were made comparing both manual and automatic classification.
     In figures \ref{fig:stability_2} and \ref{fig:stability_3} we can see that the cone jet stability island has a similar shape in both manual (fig.
@@
 
+    \vspace{2cm}
     \begin{multicols}{2}
@@
 
+    \vspace{2cm}
     \subsubsection{Non-dimensional axis}
 
-    To compare with the literature and validate the algorithm we decided to display the data using the non-dimensional numbers used in figure \ref{fig:ganan_calvo_fig}.
+    To compare with the literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, and validate the algorithm, we displayed the data using the non-dimensional numbers.
+    Figures \ref{fig:stability_8} and \ref{fig:stability_9} shows the same data from experiment in figures above with the axis adjusted.
 
@@
             \caption{Cone jet island manual experiment 4}
+            \label{fig:stability_8}
         \end{figure}
@@
             \caption{Cone jet island automatic experiment 4}
+            \label{fig:stability_9}
         \end{figure}
@@
 
-    \subsection{Robust Controller}
+\section{Chapter conclusion}
+
+In this chapter we exposed the results of this project.
+The automatic routine, real time classification and control were all achieved and implemented.
+However, they can all be improved.
+In the next Chapter I will conclude this document with discussions about the results and proposal of continuation.
 

### 2023-05-04 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

--- 2023-04-21 Documentation/UFMG/PFCII/Introduction/Introduction.tex
@@
 \label{chap:intro}
-%este label será usado para referenciar este capítulo
 
 Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
-The balance between capillary forces and the electric field on the charged liquid defines the spraying dynamics and droplet size.
+The balance between forces on the charged liquid meniscus defines the electrospraying dynamics and droplet size.
 The electric current transported by the spray reveals characteristic shapes for different spray modes.
 Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
-The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
+The spray process imposes noise and random sequences on the measured signal making its classification a non-trivial task. 
 Industrial applications demand automated stabilization of a spray mode. 
 This can be achieved by a closed-loop control system. 
-This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.
+This project targets the development of a system which allows real time acquisition of the electrospray current, treat and process its values, define in which specific mode the electrospray is running and control the necessary hardware to change and/or stabilize the spray at a desired mode.
 
 \section{Motivation and Justify}
-\label{sec:motivacao}
-
-% Argumente sobre a importância do projeto desenvolvido usando uma visão de alto nível, sem entrar em detalhes.
-Contextualize seu projeto dentro do local de execução ou da literatura e explique como ele é necessário ou inovador.
-É possível fazer uma breve revisão bibliográfica, confrontando seu trabalho com outras referências bibliográficas para mostrar a sua contribuição.
-No quesito contribuição, é muito importante deixar claro o tempo todo que partes do projetos foram executadas por outros e que partes foram executadas por você.
-Caso contrário, corre-se o risco de inadvertidademente tomar crédito pelo trabalho de outrem, o que pode ter implicações legais.
+\label{sec:motivation}
 
 EHDA research has contributed as an important tool for the development of technology. 
-The advantage of using EHDA is precision and uniform size and shape of droplets creation. Specially in certain spraying modes.
+The advantage of using electrospray is precision and uniform size and shape of droplets creation. 
+Specially in certain spraying modes.
 
@@
 
-The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
-Signal processing techniques may allow non-visual classification of spray mode based on electrical current form.
-
-The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
-Industrial applications require automated stabilization of a spray mode. 
+Many applications such as gas odorization, spray coating and pharmaceutical industries require automated stabilization of a spray mode. 
 This can be achieved by a closed system loop control system. 
-Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.
+An automated spray mode classification is a crucial part of the control system to work, as well as the development of an appropriate control algorithm.
 
@@
 \item Fully automated and intuitive system for EHDA.
-\item Real Time non-visual classification of spraying modes.
-\item Control and stabilization on a desired dynamic. 
+\item Real time non-visual classification of electrospraying modes.
+\item Control and stabilization on a desired spray. 
 \item System portability and versatility.
@@
 However, further research is required to enhance the accuracy of the classification algorithm.
+
 In order to achieve this, the Water Technology Group at NHL Stenden University of Applied Sciences, in collaboration with Dutch companies, is conducting extensive research and implement appropriate classification algorithms.
 The aim is to combine analytical capabilities with infrastructure knowledge and availability to achieve optimal results.
+
 As a student from UFMG, I am now actively involved in this research project to improve the automation usability, classification accuracy and system stabilization with signal processing techniques.
@@
 \label{sec:doc_struct}
+
+This document is divided in 6 chapters.
+
+Chapter \ref{chap:intro} provides an introduction to EHDA and explains the inspiration behind the project.
+
+Chapter \ref{chap:lit_review} delves into the literature concepts and knowledge that were utilized in this project.
+
+Chapter \ref{chap:system_description} describes the system that was implemented to make this project work, along with the instruments and models used to apply our methodology.
+
+Chapter \ref{chap:Methodology} presents the methodology applied in our experiments to validate our system.
+
+In Chapter \ref{chap:Results}, we present our results and engage in discussions comparing the knowledge acquired through literature review.
+
+Finally, in Chapter \ref{chap:conclusion}, we conclude our document with discussions about the goals achieved and areas for potential optimization.

### 2023-05-04 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
   \centering
-  \resizebox{90mm}{!}{\includegraphics{Figuras/system_setup.png}}
+  \resizebox{100mm}{!}{\includegraphics{Figuras/system_setup.png}}
   \caption{EHDA experiment setup \cite{Luewton}}
@@
   The existing signal contains valuable data not only about dripping but also other modes of spraying, thus it can serve as a non-visual classifier.
-  This report draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
+  This project draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
   A profound use of his method will be explained in section \ref{sec:section_classification}.

### 2023-05-04 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
-With the save data by streaming in saving thread\ref{subsec:save_thread}, we achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
+With the save data by streaming in saving thread \ref{subsec:save_thread}, we achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
 
-Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person. 
-Moreover, manual adjustment takes some time to achieve the desired voltage. 
+Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person and takes some time to achieve the desired voltage.
+Moreover, the electrospray phenomena has a known hysteresis, that can be seen in figure \ref{fig:ganan_calvo_fig}, and can perform different results depending on the previous electric potential.
 By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data points.
 
-The visual interface for the user, seen in figures \ref{fig:multi_class_exp1} and \ref{fig:multi_class_exp}, shows all the important sensor data and signal analysis that can be interesting to the operator in real time.
+The visual interface for the user, seen in figure \ref{fig:multi_class_exp1}, shows all the important sensor data and signal analysis that can be interesting to the operator in real time, serving as a supervisory system.
 
@@
 
-\begin{figure}[H]
-    \center
-    {\includegraphics[width=16cm]{Figuras/19:03/axs2.png}}
-    \caption{Print screen during an experiment.
-At this moment we are in Multi Jet spraying mode.
-At the left we can see the current signal has a smooth and constant curve.
-We can also see the automatic classification on the right side.}
-    \label{fig:multi_class_exp}
-\end{figure}
-
 \section{Classification}
@@
 
+We will categorize our classification results into two main groups - the step routine and the map routine.
+These two routines have showed valuable insights and comprehensible results of the electrospraying process.
+
 \subsection{Step Sequence}
@@
 
-Our first classification results were made exploring just the voltage ranges. For that stabilized all the other parameters such as humidity, temperature and external noise.
-First, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
+Our first classification results were made exploring the voltage ranges. 
+For that, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
 The figure \ref{fig:step_class} shows three graphs.
 
-The first is the input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.
+The first shows the controller output signal as an input voltage of the process.
+As it is a step routine we implemented a increasing voltage with steps of sizes 50V and time between each step of 5 seconds.
+The voltage range is between 3K~10K Volts.
 
-The second is the output raw data collected in the voltage range. The sampling rate of the oscilloscope is 10KHz. Therefore, this graph has 1.5 Million data points.
+The second is the raw output data collected by the oscilloscope in \emph{data\_acquisition\_thread()}. 
+The sampling rate is 10KHz. Therefore, this experiment of 700s has 7 Million data points just of current data. 
+This is an example of how scalable the data collected can be depending on the experiment time. This will be even more noticeable in mapping experiments.
 
-The Third graph is the same the second but after the classification procedure.
-
-% \begin{figure}[H]
-%     \center
-%     \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
-%     \caption{Input voltage step graph. The range is between 3K-10K Volts. Step size of 50V and step time of 5 seconds.}
-%     \label{fig:step_voltage}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \center
-%     \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
-%     \caption{Output raw data collected in the voltage range experiment showed in \ref{fig:step_voltage}. The sampling rate of the oscilloscope is 10KHz. This graph has 1.5 Million data points.}
-%     \label{fig:raw_data}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \center
-%     \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
-%     \caption{The same graph as \ref{fig:raw_data} but after the classification procedure. The colors are green: Dripping, Blue: Intermittent, Red: Cone Jet, Purple: Multi Jet and Black: Undefined.}
-%     \label{fig:class_step_data}
-% \end{figure}
+The Third graph is the same data as the second after the classification procedure done by \emph{data\_processing\_thread()}.
 
@@
     \center
-    \includegraphics[width=18cm]{Figuras/may/step_class.png}
+    \includegraphics[width=15cm]{Figuras/may/step_class.png}
     \caption{Automatic electrospray classification through the step routine.}
@@
         \label{fig:stability_1}
-        \caption{Spraying modes regions of pure ethanol}
+        \caption{Experimental spraying modes regions of pure ethanol}
     \end{figure}
@@
 After that we made a perturbation robustness test changing the flow rate.}
+            \label{fig:control_results}
         \end{figure}

### 2023-05-04 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
   \centering
-  \resizebox{150mm}{!}{\includegraphics{Figuras/april/control_model.png}}
+  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
   \caption{EHDA automation system setup}
@@
 
-    \subsection{Video Thread}
+    \subsection{Plotting}
 
-        Normally deactivated, that thread is responsible for triggering the camera in case we want to save a video of that sample.
-
-    \subsection{Plot}
-
-        The only running function that is not a thread because of the plotting library \emph{matplotlib} incompatibilities of running outside the main function. 
+        The only running function that should run in the main thread because the plotting library \emph{matplotlib} incompatibilities of running outside the main function. 
         It is responsible for plotting in real time the current sample acquired, and its respective fast Fourier transform to evaluate the sample frequency spectrum.
@@
     In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software. 
-Figure \ref{fig:metodology_example1} shows a print screen of the user interface during an experiment.
+    Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.
 
@@
       \caption{EHDA automation system setup}
-      \label{fig:metodology_example1}
+      \label{fig:Methodology_example1}
   \end{figure}

### 2023-05-04 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 \chapter{Conclusion}
+\label{chap:conclusion}
 
@@
 
-\section{Proposal for continuing}
+\section{Proposal for continuation}
 
@@
 With the data, I mapped the area of each spraying mode according to its potential as shown in the Figure \ref{fig:fuzzy_input}.
-        Figures \ref{fig:Fuzzyfication} and \ref{fig:defuzzyfication} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.
-
-        \begin{multicols}{2}
+        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.
 
@@
                 \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
-                \caption{Fuzzyfication of the voltage input}
-                \label{fig:fuzzy_input}
+                \includegraphics[width=17cm]{Figuras/fuzzy/Fuzzyy.png}
+                \caption{fuzzyfication of input and defuzzyfication of output}
+                \label{fig:fuzzyy}
             \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
-                \caption{Defuzzyfication of output}
-                \label{fig:fuzzy_output}
-            \end{figure}
-
-        \end{multicols}
 
@@
 
-        % \begin{figure}[H]
-        %     \centering
-        %     \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
-        %     \caption{Fuzzy Rules}
-        %     \label{fig:fuzzy_rules}
-        % \end{figure}
-
-        For testing the concept I've showed two possible states where the voltage is below the necessary to stabilize in cone jet and when is above that voltage.
-We can see in figures \ref{fig:fuzzy_test1} and \ref{fig:fuzzy_test2} that each test the output was either increase or decrease the actuator signal.
-
-        \begin{multicols}{2}
-
     \begin{figure}[H]
         \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
-                \caption{Test 1: fuzzy controller. Input voltage 4000 V the controller output to increase the voltage.}
-                \label{fig:fuzzy_test2}
+        \includegraphics[width=17cm]{Figuras/fuzzy/test3.png}
+        \caption{fuzzyfication of input and defuzzyfication of output}
+        \label{fig:fuzzyy1}
     \end{figure}
-
-            \begin{figure}[H]
-                \centering
-                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
-                \caption{Test 2: fuzzy controller. Input voltage 7000 V the controller output to decrease the voltage.}
-                \label{fig:fuzzy_test1}
-            \end{figure}
-
-        \end{multicols}
 

### 2023-05-04 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 
-\vspace{2cm}
-
 \section{Spraying modes}
@@
 
-Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows 3 spraying dynamics that we are most interesting in this project.
-
-\begin{multicols}{3}
+Figure \ref{fig:spraying_modes} shows 3 spraying dynamics that we are most interesting in this project.
 
@@
       \center
-      \includegraphics[width=2.9cm]{Figuras/drippingexample.png}
-      \label{fig:dripping_camera_example}
-      \caption{Dripping}
+      \includegraphics[width=15cm]{Figuras/spraying_modes.png}
+      \label{fig:spraying_modes}
+      \caption{Fundamental electrospraying modes.}
   \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/conejetexample.png}
-      \label{fig:cone_camera_jet_example}
-      \caption{Cone Jet}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/multijetexample.png}
-      \label{fig:multi_camera_jet_example}
-      \caption{Multi Jet}
-  \end{figure}
-
-\end{multicols}
 
@@
 In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
-Figures \ref{fig:intermittent_example}, \ref{fig:intermittent2_example} and \ref{fig:microdripping_example} illustrates 3 different dynamics herein considered as intermittent.
-
-\begin{multicols}{3}
+Figure \ref{fig:intermittent_example} illustrates 3 different dynamics herein considered as intermittent.
 
@@
       \center
-      \includegraphics[width=2.5cm]{Figuras/19:03/intermittent_example.png}
+      \includegraphics[width=15cm]{Figuras/19:03/intermittent_example.png}
       \label{fig:intermittent_example}
-      \caption{Intermittent 1}
+      \caption{Intermittent examples}
   \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=2cm]{Figuras/19:03/intermittent2_example.png}
-      \label{fig:intermittent2_example}
-      \caption{Intermittent 2}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=2cm]{Figuras/19:03/microdripping_example.png}
-      \label{fig:microdripping_example}
-      \caption{Microdripping / Intermittent 3}
-  \end{figure}
-
-\end{multicols}
 
@@
 
+The Cone jet mode is a particular interest in applications, where the meniscus emits a steady microscopic jet, resulting in uniformly sized droplets. 
 Taylor (1964)\cite{taylor} was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
@@
 
-Figures \ref{fig:conjt1}, \ref{fig:conjt2} and \ref{fig:conjt3} shows three cone jets in different circunstances.
-
-\begin{multicols}{3}
+Figures \ref{fig:conjt} shows three cone jets in different circumstances.
 
@@
       \center
-      \includegraphics[width=2cm]{Figuras/april/conjet1.png}
-      \label{fig:conjt1}
-      \caption{Cone Jet 1}
+      \includegraphics[width=15cm]{Figuras/april/conjet.png}
+      \label{fig:conjt}
+      \caption{Cone Jet}
   \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=2cm]{Figuras/april/conjet2.png}
-      \label{fig:conjt2}
-      \caption{Cone Jet 2}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=2.2cm]{Figuras/april/conjet3.png}
-      \label{fig:conjt3}
-      \caption{Cone Jet 3}
-  \end{figure}
-
-\end{multicols}
 
@@
 
-\begin{multicols}{3}
-
   \begin{figure}[H]
       \center
-      \includegraphics[width=3cm]{Figuras/april/multi2.png}
-      \label{fig:multijt1}
-      \caption{Multi Jet - double jet}
+      \includegraphics[width=15cm]{Figuras/april/multjt.png}
+      \label{fig:multijt}
+      \caption{Multi Jet}
   \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/april/multi1.png}
-      \label{fig:multijt2}
-      \caption{Multi Jet - low number of jets}
-  \end{figure}
-
-  \begin{figure}[H]
-      \center
-      \includegraphics[width=3cm]{Figuras/april/multi3.png}
-      \label{fig:multijt3}
-      \caption{Multi Jet - rim spraying mode}
-  \end{figure}
-
-\end{multicols}
 

### 2023-05-04 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
     \center
-    \includegraphics[width=15cm]{Figuras/may/step_class.png}
+    \includegraphics[width=16cm]{Figuras/may/step_class.png}
     \caption{Automatic electrospray classification through the step routine.}
@@
 
-The graph of voltage scan has a common shape for different liquids and parameters. After having familiarity with it is even possible to classify the spraying modes by visual analysis.
+The graph of voltage scan has a common shape for different liquids and parameters. After having familiarity with it, is even possible to classify the spraying modes by visual analysis.
 
 For example, dripping mode has a current mean of 0V.
-The Intermittent state has a high variation of values that can be seen by the thickness of the graph.
-The Cone jet is a thinner graph because the signal is more constant.
-The Multi Jet is the same as Cone jet graph but with a higher mean value than cone Jet.
-Corona sparks are not showed in the graph because the discharges has a high current value and will be above the axis limits.
+The Intermittent state has a high variation of values that can be seen by the increased thickness on the graph.
+The Cone jet is a thinner graph because of its constant signal.
+Multi Jet  has the same shape as Cone jet but with a higher mean value.
+Corona sparks are not showed in the graph because its discharges has a high current value above the axis limits.
 
@@
 
-For validation with literature and also to expose the benefits of the automated routine and classification the map sequence proof itself the best result of this work.
+For validation with literature and also to expose the benefits of the automated routine and classification, the map sequence proof itself the best result of this work.
 
-    Firstly, for better understand the spraying dynamics, manual experiments were done.
-    Figure \ref{fig:stability_1} shows the stability region of different spraying mode for pure ethanol in the range of voltage and flow rate.
+    Initially, for better understand pure ethanol classification regions through voltage and flow rate ranges, I made a manual map seen in figure \ref{fig:stability_1}.
 
@@
         \center
-        \includegraphics[width=8cm]{Figuras/regions.png}
+        \includegraphics[width=12cm]{Figuras/regions.png}
         \label{fig:stability_1}
@@
 
-    For validation of the automatic classification, experiments were made comparing both manual and automatic classification.
-    In figures \ref{fig:stability_2} and \ref{fig:stability_3} we can see that the cone jet stability island has a similar shape in both manual (fig.
-\ref{fig:stability_2}) and automatic (fig.
-\ref{fig:stability_3}) data collected in the same experiment.
-
-    \begin{multicols}{2}
+    In order to validate our automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
+    Figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).
 
@@
             \center
-            \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
-            \caption{Cone jet island manual experiment 1}
+            \includegraphics[width=16cm]{Figuras/april/manual_stability_island.png}
+            \caption{Cone jet stability region for pure ethanol experiment 1}
             \label{fig:stability_2}
@@
 
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=9cm]{Figuras/report3/map-exp-26-01.png}
-            \caption{Cone jet island automatic experiment 1}
-            \label{fig:stability_3}
-        \end{figure}
-
-    \end{multicols}
-
-    We can see in figures \ref{fig:stability_4} and \ref{fig:stability_5} another experiment with the same liquid and a comparison on manual (visually by the high speed camera) and automatic classification.
-
-    \vspace{2cm}
-    \begin{multicols}{2}
+    With the development of a Multi Jet classification using the logic explained in section \ref{sec:section_classification}, I repeated the same experiment as shown in Figure \ref{fig:stability_6}.
 
@@
             \center
-            \includegraphics[width=8cm]{Figuras/april/results_map_1.png}
-            \caption{Cone jet island manual experiment 2}
-            \label{fig:stability_4}
+            \includegraphics[width=18cm]{Figuras/april/map_third.png}
+            \caption{Cone jet stability region for pure ethanol experiment 2}
+            \label{fig:stability_6}
         \end{figure}
+
+    \subsubsection{Non-dimensional axis}
+
+    To have a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, with a visual juxtaposition of the shapes, we displayed in figure \ref{fig:stability_8} the data using the non-dimensional numbers used in his work\cite{gananCalvo}.
 
@@
             \center
-            \includegraphics[width=9cm]{Figuras/april/results_map_2.png}
-            \caption{Cone jet island automatic experiment 2}
-            \label{fig:stability_5}
-        \end{figure}
-
-    \end{multicols}
-
-    We can see in figures \ref{fig:stability_6} and \ref{fig:stability_7} the same experiment and results as above, but with the Multi Jet classification that was a new feature in the software.
-
-    \begin{multicols}{2}
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=8cm]{Figuras/april/map5.png}
-            \caption{Cone jet island manual experiment 3}
-            \label{fig:stability_6}
-        \end{figure}
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=10cm]{Figuras/april/map2.png}
-            \caption{Cone jet island automatic experiment 3}
-            \label{fig:stability_7}
-        \end{figure}
-
-    \end{multicols}
-
-    \vspace{2cm}
-    \subsubsection{Non-dimensional axis}
-
-    To compare with the literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, and validate the algorithm, we displayed the data using the non-dimensional numbers.
-    Figures \ref{fig:stability_8} and \ref{fig:stability_9} shows the same data from experiment in figures above with the axis adjusted.
-
-    \begin{multicols}{2}
-
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=7cm]{Figuras/april/manual_non_dim_exp.png}
+            \includegraphics[width=18cm]{Figuras/april/manual_au_1.png}
             \caption{Cone jet island manual experiment 4}
@@
 
-        \begin{figure}[H]
-            \center
-            \includegraphics[width=10cm]{Figuras/19:03/non-dimensional-1.png}
-            \caption{Cone jet island automatic experiment 4}
-            \label{fig:stability_9}
-        \end{figure}
-
-    \end{multicols}
+    The results of mapping experiment corresponded visual, literature and automatic regions of classification, giving authentication to our method.
 
@@
 
-    The results of the classification process were favorable for experiment automation, however, they may not be as effective for optimal performance of the controller.
-    The inaccuracy of the classification by statistical method in addition with the amount of variables that need to be syntonized for stabilize in cone jet or multi jet makes it hard to control this process.
+    The results of the classification process were favorable for experiment automation, however, the inaccuracy of the classification by statistical methods, specially the Multi Jet\ref{subsec:Multi Jet}, limited the development of a complete control project.
+    Together with the amount of variables that need to be syntonized makes it hard to stabilize in a desired mode.
 
-    Of particular interest in applications is the cone-jet mode, where the meniscus emits a steady microscopic jet, resulting in uniformly sized droplets.
+    Even with all those problems we could implement a simple controller project, described in \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.
 
-        Flow rate perturbation robustness test
-
+    The controller not only stabilized in Cone Jet mode, but also could reject perturbation, as seen in Figure \ref{fig:control_results}, where I manually changed the flow rate.
+    First graph shows current acquired.
+It starts as intermittent state, with an oscillating signal.
+We can validate this with the blue colored sample on the third graph representing its automatic classification.
+    The second graph shows the controller actuating increasing the voltage to achieve a stable cone jet mode.
+    After a period of time in cone jet, I manually increased the flow rate, serving as a perturbation of the system, and we can see that the effect of that was to return to intermittent state with the oscillating signal.
+The controller again, actuate increasing the voltage to reach the cone jet stability island.
+    This procedure was repeated after some seconds of stabilization in cone jet, increasing again the flow rate manually, and we can see the system automatically adjusting the voltage.
         \begin{figure}[H]
             \center
-            \includegraphics[width=17cm]{Figuras/19:03/control_first_results.png}
+            \includegraphics[width=16cm]{Figuras/19:03/control_first_results.png}
             \caption{Simple controller validation experiment.
 For this experiment we waited the system to stabilize in the desired spraying mode.
-After that we made a perturbation robustness test changing the flow rate.}
+After that we made a perturbation test changing the flow rate.
+The classification legend follows the same color reference in all project.}
             \label{fig:control_results}
         \end{figure}
+
+    After 200s of experiment we had some breaks up of the cone jet into a droplet and stabilized again.
+This is represented by the peak values in current signal.
+The classification correctly identified as intermittent, seen as blue dots in the third graph, and the controller reacted increasing the voltage, in a situation that can be considered as noise.
+A filter can be applied in a more complex controller project to avoid this.
 

### 2023-05-04 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

--- 2023-04-28 Documentation/UFMG/PFCII/Methodology/Methodology.tex
@@
 
-The classification is a key step in our routine.
-For being able to be used in multipurpose applications our classification routine must be able to run in real-time.
-Which means it must be fast and automatic classification.
-Our goal is to improve and apply in our routine different approaches of non-visual spraying classification using the current data collected from the system.
+The classification is a key step in our routine and for being able to be used in multipurpose applications our classification routine must be able to run in real-time, which means it must be fast and automatic.
+Our goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.
 
@@
 
-To classify the multi jet, after running many steps experiments as shown in figure \ref{fig:raw_data} I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean.
-I also noticed that the cone jet current was almost fixed all its spectrum. 
+To classify the multi jet, after running many steps experiments I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range.
 These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
@@
 With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
-The cone jet current can be calculated by the scaling laws\ref{sec:scalling-laws} formula.
-The value 1.14 was found by repeating a lot of experiments with the same liquid, but varying the flow rate and the voltage.
-This means this value is just defined for pure ethanol, the liquid used in all those experiments.
-The classification in the algorithm was divided in three steps as shown below. The algorithm is shown in \ref{alg:statistical_class}.
+The cone jet current can be calculated by the scaling laws \ref{sec:scalling-laws} formula.
+The factor value of 1.14 was found by repeating a lot of experiments with the same liquid (pure ethanol), but varying the flow rate and the voltage.
+This factor value is just applied for pure ethanol, the liquid used in all experiments in this work.
+The classification in the algorithm was divided in three steps as shown below.
 
@@
 
-	The algorithm implemented works in the following way:
+	The algorithm \ref{alg:statistical_class} shows the implemented classification and works in the following way:
+
 	\begin{algorithm}
@@
 
-    The program developed is capable of running different types of routines. The code is also easy to implement new routines.
+    The program developed is capable of running different types of routines and with an easy way to implement new strategies.
     Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
     The controller thread will manage what the algorithm must do for each sequence.
-    Following our control model\ref{fig:control_model_fig}, the controller outputs are the actuators signal.
-    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton thread\ref{subsec:data_aquisition}.
+    Following our control model\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
+    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread\ref{subsec:data_aquisition}.
 
@@
 The step sequence is done by the same command send to the power supply but with the maximum slope value in order to proximate of a step signal.
-By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage. This algorithm is represented in \ref{alg:stepping_algorithm}.
+By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage, as represented in algorithm \ref{alg:stepping_algorithm}.
 
@@
 This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
-The purpose is to map the operational window, seen in Figure \ref{fig:map3Data_fig}, that can be defined where the spraying mode can be stabilized based on the flow rate, voltage and the setup configuration.
+The purpose is to map the operational window, seen in Figure \ref{fig:map3Data_fig}, that can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration.
 
@@
 The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
-The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is represented in the algorithm \ref{alg:mapping_algorithm}.
+The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen, and it is represented in the algorithm \ref{alg:mapping_algorithm}.
 
@@
     The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
-    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
-    A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.
-
-    \subsection{Simple Controller}
+    As it is a closed loop control, the controller must be able to stabilize the system in the desired conditions.
+    A simple controller algorithm is represented in algorithm \ref{alg:simple_controller}, and it was used as a proof of concept.
+    Its results can be seen in results section \ref{sec:controller_results}.
 
@@
 
+This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve our goals. 
+Next chapter \ref{chap:Results}, we will discuss the results reached.
+
 \clearpage

### 2023-05-04 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
-\chapter[System Description]{System Description}
+\chapter{System Description}
 \label{chap:system_description}
@@
 In this chapter, we will discuss the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
-The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library \cite{Monica}.
+The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library.
 
@@
 
-    Wireless communication allows us to make measurements disconnected to an external power supply, which gives us more safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
+    Wireless communication allows us to make measurements disconnected to an external power supply, which increase safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
     The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
@@
 
-  The pump integration in the automation algorithm brings us a new controllable variable, the Flow rate. Now we can control the spraying mode with the
+  The pump integration in the automation algorithm was done in this work, bringing us a new controllable variable, the flow rate. We can control the spraying mode with the
   two main variables that affect the system. 
-  It will bring more complexity for the system since now we are dealing with multivariable control.
+  It brings more complexity for the system since now we are dealing with multivariable control.
   Controlling also the flow rate gives to this project a new dimension in the system giving us freedom to explore the flow rate properties.
@@
 
-  About the pump interface. As I could not find a good ready-to-use library for this pump I developed a simple and intuitive interface to be our software routine.
-  The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.
-
-  % The supply at constant pressure can also favor the stability of the spray\cite{prunet}.
-However, the flow rate depends on the applied pressure and pressure losses between the tank and the end of the capillary, which themselves are dependent on the liquid chosen and on its temperature.
-This volume flow rate may also depend on the applied voltage, since the electrostatic pressure on the meniscus produces a suction effect.
+  About the pump interface, as there was no good ready-to-use library, I developed a simple and intuitive interface to be used in our software routine.
+  The communication protocol used is RS-232 and the pump commands list were found in the user manual.
 
@@
         To conclude, json files are good as a system output because of its human readability.
-But as the database gets bigger json becomes to be a slow to read and heavy way to store the data.
-For that, saving the data frame in a compressed type of file called feather is much faster to work with the data.
+But as the database gets bigger json becomes to be a slow to read and heavy to store data.
+For that, saving the data frame in a compressed type of file called feather is much faster to work with it.
 
@@
     In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software. 
-    Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.
+  %   Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.
 
-    \begin{figure}[H]
-      \centering
-      \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
-      \caption{EHDA automation system setup}
-      \label{fig:Methodology_example1}
-  \end{figure}
+  %   \begin{figure}[H]
+  %     \centering
+  %     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
+  %     \caption{EHDA automation system setup}
+  %     \label{fig:Methodology_example1}
+  % \end{figure}
+
 \clearpage

### 2023-05-08 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
Documentation

--- 2023-04-22 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
@@
-\chapter{Trials and failures}
+\chapter{System Details}
 
-\section{Machine Learn}
+The electroplating system itself is a marginally stable system, depending on various parameters in the correct range to achieve a desired mode.
+The tips bellow were used and can help avoid noise and stabilize the system.
 
-I've tried to create a database with the samples of current. Each sample was a vector with 50k values corresponding a 0.5s of data collected in a 100KHz oscilloscope. And in a second column its
+- Don't use the oscilloscope with the charger. The charger brings noise from the power line.
+- To aviod mechanical noise in the pumping machine use the syringe pump inclined with a bubble.
+- external electrical noise collected by antennas or connections.
+- To stabilize internal humidity you can turn on the gas pipeline with air into the chamber.
 
-\subsection{Spectogram analysis}
+The picture in figure \ref{fig:setup_pic}
+
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup_pic}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \resizebox{100mm}{!}{\includegraphics{Figuras/naked_eyes.png}}
+    \caption{EHDA picture of the electrified syringe.}
+\end{figure}
+
+\section{Setup Validation}
+\label{sec:setup_validation}
+
+Initial tests were made to verify the setup assembly and the automation routine integration. In this step I could understand in practice how electrospray works.
+It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
+Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
+ And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
+
+ About the setup, integrate was changed the liquid, nozzle diameter and distance to the plate in order to
+make the experiment the most stable and easy to reach cone-jet mode as possible.
+For example, while doing experiments we discovered that the frequency of the pump machine internal motors was creating an interference in the flowrate.
+Therefore compromising the stabilization in cone jet mode.
+A solution for that was to increasethe flowrate wich smooths this pumping noise.
+For that was also necessary to increase the nozzle diameter to balance with all other variables from the experiment.
+
+\section{Oscilloscope Impedance}
+\label{sec:osc_impedance}
+
+The current is being measured by the Oscilloscope using its internal impedance. 
+This oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
+Selecting one or other can multiply or divide your current measurement by 2. 
+By default we are using the 2Mohm differential input. But it was noticed that using the 1Mohm resistance might reduce the noise. 
+A proposal of optimization is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-08 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
Documentation

@@
 To continue, my proposal would be to prioritize the improvement of the classification step. 
-Ideally, we could use machine learning or another algorithm to ensure accurate classification of individual data samples.
-
+Ideally, we could use machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
 By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
@@
 
-To finish, I would propose a final investment in the system portability so that it can be applicable in remote applications.
+\subsection{Machine Learning}
 
-\subsection{Machine Learning}
+    When it comes to classifying spraying modes, machine learning represents a sophisticated and trendy approach.
+    This project was designed in order to substitute our statistical classifier for a more general and accurate algorithm.
+
+    The data collected in this project was saved in 0.5s samples together with its classification allowing it to be used for supervised learning.
+    Experimental trials were conducted to explore machine learning algorithms to classify the data.
+Unfortunately, despite efforts, an accurate method of distinguishing between classifications could not be identified.
 
@@
 
-        One challenge in implementing the controller is that we do not have continuous feedback. 
-        Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
+        One challenge in implementing the controller in this project is that we don't have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control.
         As this project involves logical control, it requires a different approach.
 
-        The fuzzy approach is an attempt to quantify the classification and fit different control models.
+        The controller project that will be presented is an attempt to quantify the classification and fit it in a fuzzy control model.
+        That approach is for an open loop control system and the input and outputs of the controller must be fuzzyfied.
 
-        For that, I fuzzyfied the controller input with the data acquired in an experiment of step routine\ref{subsec:step_routine}.
-With the data, I mapped the area of each spraying mode according to its potential as shown in the Figure \ref{fig:fuzzy_input}.
-        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication between the input and output of the controller.
+        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine\ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
+        Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication within the input and output of the controller.
 
@@
 
-        Our controller is a machine that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules.
-        The rules are listed below.
+        Our controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules listed below.
 
@@
 
+        In figure \ref{fig:fuzzyy1}, two tests were made.
+Test 1 with a higher voltage of 7000V accusing it to be 100\% in multi jet and the output of decrease voltage.
+Test 2 shows the opposite case when the voltage is lower than expected.
+
     \begin{figure}[H]
@@
 
-        Note that, for this method to work it is needed to run a step sequence to scan the cone jet stability island.
-With that data, create the input membership function.
-Then, run the controller routine in fuzzy mode.
-
-    \subsection{System Portability}
-    \label{subsec:portability}
-
-        Raspberry Pi
-
     \section{Final Discussions}
 
-        The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.
-        The previous student work was focused in predicting corona streamers or spark discharges, therefore her automation routine was a first version concept that proved to be valuable.
-        From the development done by me, it highlights the results:
+        The works presented in this report represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.
 
-        - Integrate liquid pump to the software and developed a routine with it.
+        The previous student work focused on predicting corona streamers or spark discharges\cite{Monica} and her automation routine provided a valuable proof-of-concept.
 
-        - Modeled the software to fit a control model turning it easy to implement new control algorithms or experiment routines.
-
-        - Remodel the software to support threads in order to separate each subsystem and exchange data between them with use of queues data structures.
-
-        - Developed a classification for multi jet spraying mode.
-
-        - Developed a simple controller to proof the concept.
-
-        - Optimize the saving of data to a real time streaming together with more sensors' data.
-
-        - Restructured algorithm usability in order to make it more intuitive with the setup file.
+        The current project builds on this foundation and highlights several key results, including the integration of a liquid pump into the software and the development of a routine that can be easily modeled to fit a control model, making it straightforward to implement new control algorithms or experiment routines.
+        The software was also remodeled to support threads, allowing for the separation of each subsystem and the exchange of data between them using queue data structures.
+A classification for multi-jet spraying mode was developed, along with a simple controller to demonstrate proof of concept.
+        Additionally, the saving of data was optimized to a real-time streaming format and expanded to include more sensor data.
+Finally, the algorithm usability was restructured to make it more intuitive for users through the use of a setup file.
 

### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
Documentation

@@
 C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
-He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt1} and \ref{fig:multijt2}, the meniscus is not bound to the rim of the capillary. 
+He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt}, the meniscus is not bound to the rim of the capillary. 
 This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
-
-As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray, seen in figure \ref{fig:multijt3}. 
+As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
 In this work, all modes with more than one stable jet will be classified as multi jet.

### 2023-05-08 Documentation/UFMG/PFCII/Methodology/Methodology.tex
Documentation

@@
 This chapter is about describing the methodology and developments to achieve the project goals. 
-Firstly, I begin by elaborating on the workings of the classification process in the processing thread.
-Moving on, I will then delve into the operational sequences of the controller thread.
-Lastly, I will provide an explanation on the implementation of the controller.
+Firstly, by elaborating on the workings of classification process in the processing thread.
+Moving on, delving into the operational sequences of the controller thread.
+Lastly, providing an explanation on the implementation of the controller.
 
@@
 
-The classification is a key step in our routine and for being able to be used in multipurpose applications our classification routine must be able to run in real-time, which means it must be fast and automatic.
-Our goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.
+The classification is a key step in our routine and for being able to be used in multipurpose applications our classification must be able to run in real-time, which means it must be fast and automatic.
+The goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.
 
@@
 In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
-We acquire the current data frame of 0.5s with 100 KHz as sampling frequency.
-With that each current sample as 50 thousand current values.
+We acquire the current data frame of 0.5s with 100 KHz as sampling frequency, with each current sample as 50 thousand current values.
 Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation.

### 2023-05-08 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

--- 2023-04-22 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
@@
-\chapter{Trials and failures}
+\chapter{System Details}
 
-\section{Machine Learn}
+The electroplating system is an unstable system that relies on multiple parameters being within their respective optimal ranges to achieve a desired mode. 
+Several tips can help reduce noise and stabilize the system, such as avoiding the use of an oscilloscope with the charger to avoid power line noise. 
+Mechanical noise in the pumping machine can be minimized by using a syringe pump tilted with a bubble inside. 
+External electrical noise can be picked up by antennas or connections in the circuit. 
+To stabilize internal humidity, turn on the gas pipeline with air into the chamber.
 
-I've tried to create a database with the samples of current. Each sample was a vector with 50k values corresponding a 0.5s of data collected in a 100KHz oscilloscope. And in a second column its
+The picture in figure \ref{fig:setup_pic} shows the setup used in all this project.
+Figure \ref{fig:nozzleElectr} shows the nozzle and plate with the charged liquid being electrosprayed in cone jet mode.
 
-\subsection{Spectogram analysis}
+\begin{figure}[H]
+  \centering
+  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
+  \caption{EHDA automation system setup}
+  \label{fig:setup_pic}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \resizebox{80mm}{!}{\includegraphics{Figuras/naked_eyes.png}}
+    \label{fig:nozzleElectr}
+    \caption{EHDA picture of the electrified syringe.}
+\end{figure}
+
+\section{Setup Validation}
+\label{sec:setup_validation}
+
+It is recommended to do initial tests in order to verify the setup assembly and the automation routine integration. 
+This is an important step to understand in practice how electrospray works.
+Factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
+Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
+And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
+
+\section{Oscilloscope Impedance}
+\label{sec:osc_impedance}
+
+The current being measured by the Oscilloscope use its internal impedance. 
+The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
+Selecting one or other can multiply or divide your current measurement by 2. 
+By default, we are using the 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
+A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-08 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
-We acquire the current data frame of 0.5s with 100 KHz as sampling frequency, with each current sample as 50 thousand current values.
+We acquire the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values.
 Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation.
@@
     \resizebox{80mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
-    \caption{Sample classification using statistical values. Colors: Green = Dripping; Blue = Intermittent; Red = Cone Jet}
+    \caption{Sample classification using statistical values. Colors: Green = Dripping; Blue = Intermittent; Red = Cone Jet.}
     \label{fig:sjaaks_statistical_class}
@@
 The window formed by these points is where the system operated in the stable cone-jet.
-Operational windows depend of the liquid and configuration setup.
+Operational windows depend on the liquid and configuration setup.
 Different windows are represented for different liquid conductivity.
@@
         \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
-        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x axis representing the samples collected. The first is the current values collected through all the experiment.
+        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
         The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
@@
         \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
-        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capillary setup. The map shows the stability region of each electrospraying mode in the voltage and flowrate range.}
+        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capillary setup.
+The map shows the stability region of each electrospraying mode in the voltage and flow rate range.}
         \label{fig:map3Data_fig}

### 2023-05-08 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
         \label{fig:stability_1}
-        \caption{Experimental spraying modes regions of pure ethanol}
+        \caption{Experimental spraying modes regions of pure ethanol.}
     \end{figure}
@@
             \includegraphics[width=16cm]{Figuras/april/manual_stability_island.png}
-            \caption{Cone jet stability region for pure ethanol experiment 1}
+            \caption{Cone jet stability region for pure ethanol experiment 1.}
             \label{fig:stability_2}
@@
             \includegraphics[width=18cm]{Figuras/april/map_third.png}
-            \caption{Cone jet stability region for pure ethanol experiment 2}
+            \caption{Cone jet stability region for pure ethanol experiment 2.}
             \label{fig:stability_6}
@@
             \includegraphics[width=18cm]{Figuras/april/manual_au_1.png}
-            \caption{Cone jet island manual experiment 4}
+            \caption{Cone jet island manual experiment 4.}
             \label{fig:stability_8}

### 2023-05-08 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
 
-    The signal analysis with an oscilloscope using WiFi technology allows an in-depth case study of the electric current signal.
-    The current is measured via a TiePie WifiScope WS6 from TiePie engineering that is a battery powered oscilloscope capable of transmitting data via a WiFi connection allowing it to be placed in the high voltage or ground path.
+    The signal analysis with an oscilloscope using Wi-Fi technology allows an in-depth case study of the electric current signal.
+    The current is measured via a TiePie WifiScope WS6 from TiePie engineering that is a battery powered oscilloscope capable of transmitting data via a Wi-Fi connection allowing it to be placed in the high voltage or ground path.
 
@@
   - model: Photron fastcam mini
+
+  The High Speed Camera (HSC) was just used in this project for validation purposes.
 
@@
   \resizebox{150mm}{!}{\includegraphics{Figuras/new_system_setup.png}}
-  \caption{EHDA automation system setup}
+  \caption{EHDA automation system setup.}
   \label{fig:setup}
@@
   \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
-  \caption{EHDA automation system setup}
+  \caption{EHDA automation closed loop control system model implemented.}
   \label{fig:control_model_fig}
@@
             \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
-            \caption{Output data json structure}
+            \caption{Output data json structure.}
             \label{fig:data_sample}
@@
     In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software.
-  %   Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.
-
-  %   \begin{figure}[H]
-  %     \centering
-  %     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
-  %     \caption{EHDA automation system setup}
-  %     \label{fig:Methodology_example1}
-  % \end{figure}
 

### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
   \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
-  \caption{EHDA physical concept \cite{Gabriel}}
+  \caption{EHDA physical concept\cite{Gabriel}.}
   \label{fig:ehda_setup_ex2}
@@
   \resizebox{100mm}{!}{\includegraphics{Figuras/system_setup.png}}
-  \caption{EHDA experiment setup \cite{Luewton}}
+  \caption{EHDA experiment setup\cite{Luewton}.}
   \label{fig:ehda_setup}
@@
   \label{fig:drip_example}
-  \caption{Dripping}
+  \caption{Dripping examples.}
 \end{figure}
@@
       \label{fig:intermittent_example}
-      \caption{Intermittent examples}
+      \caption{Intermittent examples.}
   \end{figure}
@@
       \label{fig:conjt}
-      \caption{Cone Jet}
+      \caption{Cone Jet examples.}
   \end{figure}
@@
 The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.
-Figures \ref{fig:multijt1}, \ref{fig:multijt2} and \ref{fig:multijt3} shows three different variations of multi jet spraying mode.
 
 C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
-He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt}, the meniscus is not bound to the rim of the capillary. 
+He detected that for a low number of jets emitted the meniscus is not bound to the rim of the capillary. 
 This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
 As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
-In this work, all modes with more than one stable jet will be classified as multi jet.
+In this work, all modes with more than one stable jet will be classified as multi jet. Figure \ref{fig:multijt} shows three different variations of multi jet spraying mode.
 
@@
       \label{fig:multijt}
-      \caption{Multi Jet}
+      \caption{Multi Jet examples.}
   \end{figure}

### 2023-05-08 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

@@
   \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
-  \caption{EHDA automation system setup}
+  \caption{EHDA automation system setup used for experiments.}
   \label{fig:setup_pic}
@@
 The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
-Selecting one or other can multiply or divide your current measurement by 2. 
-By default, we are using the 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
+Selecting one or other will multiply or divide your current measurement by 2. 
+By default, it is being used 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
 A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-08 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 
-To continue, my proposal would be to prioritize the improvement of the classification step. 
-Ideally, we could use machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
-By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
-In this regard, I would like to present the concept of a fuzzy controller as a potential solution.
+To continue, a proposal is to prioritize the improvement of the classification step. 
+Ideally using machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
+By achieving a reliable classification, a more effective controller logic or approaches can be implemented. 
+In this regard, a concept of a fuzzy controller will be presented as a potential solution.
 
@@
     When it comes to classifying spraying modes, machine learning represents a sophisticated and trendy approach.
-    This project was designed in order to substitute our statistical classifier for a more general and accurate algorithm.
+    This project was designed in order to substitute the statistical classifier for a more general and accurate algorithm.
 
@@
 
-        One challenge in implementing the controller in this project is that we don't have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control.
+        One challenge in implementing the controller in this project is that it does not have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control.
         As this project involves logical control, it requires a different approach.
@@
                 \includegraphics[width=17cm]{Figuras/fuzzy/Fuzzyy.png}
-                \caption{fuzzyfication of input and defuzzyfication of output}
+                \caption{fuzzyfication of input and defuzzyfication of output.}
                 \label{fig:fuzzyy}
@@
 
-        Our controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules listed below.
+        The controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.
 
@@
         \includegraphics[width=17cm]{Figuras/fuzzy/test3.png}
-        \caption{fuzzyfication of input and defuzzyfication of output}
+        \caption{Test implemented to validate the concept of fuzzy controller in this project.}
         \label{fig:fuzzyy1}
@@
         The current project builds on this foundation and highlights several key results, including the integration of a liquid pump into the software and the development of a routine that can be easily modeled to fit a control model, making it straightforward to implement new control algorithms or experiment routines.
+
         The software was also remodeled to support threads, allowing for the separation of each subsystem and the exchange of data between them using queue data structures.

### 2023-05-08 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 EHDA research has contributed as an important tool for the development of technology. 
-The advantage of using electrospray is precision and uniform size and shape of droplets creation. 
-Specially in certain spraying modes.
-
-Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.
+The advantage of using electrospray is precision and uniform size and shape of droplets creation, specially in certain spraying modes. 
+Although there are many applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.
 
@@
 
-This project aims to give continuity to the previous student work\cite{Monica}, 
-Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
-For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
+This project aims to give continuity to the previous student work\cite{Monica}, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
+For that, it was developed a python software routine to connect most of the peripherals and analyzed the current data.
 Her work corroborates the validation of this project motivating its continuation on development and optimization.
@@
 \label{sec:companies}
-
-% Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido.
-Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc.
-Descreva também o seu vínculo com a empresa.
 
@@
 
-Chapter \ref{chap:system_description} describes the system that was implemented to make this project work, along with the instruments and models used to apply our methodology.
+Chapter \ref{chap:system_description} describes the system that was implemented to make this project work, along with the instruments and models used to apply the methodology.
 
-Chapter \ref{chap:Methodology} presents the methodology applied in our experiments to validate our system.
+Chapter \ref{chap:Methodology} presents the methodology applied in experiments to validate the system.
 
-In Chapter \ref{chap:Results}, we present our results and engage in discussions comparing the knowledge acquired through literature review.
+In Chapter \ref{chap:Results}, it is presented results and engage in discussions comparing the knowledge acquired through literature review.
 
-Finally, in Chapter \ref{chap:conclusion}, we conclude our document with discussions about the goals achieved and areas for potential optimization.
+Finally, in Chapter \ref{chap:conclusion}, this document is concluded with discussions about the goals achieved and areas for potential optimization.

### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA).
-The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
+The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomenon.\cite{Grace}
 That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
@@
 The resulting spray is electrically charged, and the droplets repel one another.
-For this reason, with a controlled environment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.
+For this reason, with a controlled environment a certain stable spraying mode can be reached as seen in the Figure \ref{fig:ehda_setup_ex2}.
 
@@
 It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
-The setup in figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
+The setup in Figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.
 
@@
 Therefore, many researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
-Evaluating the current data can give us valuable information about the spraying behavior.
-Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in our system during a dripping of a charged liquid. 
-We can visually identify the signal of two droplets generated in this time frame.
+Evaluating the current data gives valuable information about the spraying behavior.
+Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in the system during a dripping of a charged liquid. 
+It can be visually identified the signal of two droplets generated in this time frame.
 
@@
 Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
-In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.
+Equation \ref{eq:i_chenpui} calculates the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.
 
@@
 Since 1915 with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
-Years later the same phenomena was noticed by other scientists, but the classification of these modes were still not well-defined by the community.
-For that Cloupeau and Prunet-Foch\cite{prunet} proposed spray mode classifications based in what they have seen experimentally, and it's still being used as basis for EHDA researches.
+Years later the same circumstance was noticed by other scientists, but the classification of these modes were still not well-defined by the community.
+For that Cloupeau and Prunet-Foch\cite{prunet} proposed spray mode classifications based on what they have seen experimentally, and it is still being used as basis for EHDA researches.
 
-Figure \ref{fig:spraying_modes} shows 3 spraying dynamics that we are most interesting in this project.
+Figure \ref{fig:spraying_modes} shows 3 spraying dynamics that are most interesting in this project.
 
@@
 
-Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate between 5 modes as reffered below in order of growing electric potential:
+Through the various classifications and subclassifications of spraying defined in literature it will be aggregated some of them and separated between 5 modes as explained below in order of growing electric potential.
 
@@
 
-Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
+Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomenon called field enhanced dripping.
 In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.
@@
 This mode can be identified by its pulsating manner.
-In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
+In this mode the droplet size is smaller than the nozzle, situation called electric microdripping, and the dripping frequency increases with the increasing of the field applied.
 Figure \ref{fig:intermittent_example} illustrates 3 different dynamics herein considered as intermittent.
@@
 In Taylor cone, here referred as Cone Jet, the direction of the cone apex also varies depending on the balance of forces. 
-With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume as we increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.
+With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume when increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.
 
@@
 
-Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet phenomena. In his experiments was observed:
+Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet mode. In his experiments was observed:
 \emph{"for voltages well above that for which the steady conical surface changed into a blurred agitated one, the appearance became a number of fine points with their attendant dark streaks arranged along the circumference of the raised edge".}
@@
 In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics.
-Because of that, some authors can divide what we call multi jet in more classifications.
+Because of that, some authors can divide what it is called multi jet in more classifications.
 The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.
@@
 
-At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown, and we achieve a phenomenon of discharge.
+At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown, achieving an event of discharge, referred in this work as corona.
 Those can be easily classified because of its high current value.
@@
 This mode is also divided by other classes such as streamer corona or transient sparks discharges, but it's not in the scope of this work. 
-Mônicas\cite{Monica} work was focused on how to predict that mode with the current analysis for safety in industrial applications.
+The previous student work was focused on how to predict that mode with the current analysis for safety in industrial applications.
 
@@
 
-In this chapter we exhibit some electrospray theory that was important for the development of this project. 
+In this chapter it was exhibited some electrospray theory that was important for the development of this project. 
 Firstly, with a brief review about the physical concept behind the experiment. 
-Then, I introduce how current analysis can be useful for our application citing works already done with this approach.
-Finally, I end up the chapter defining what spraying modes classification will be considered and its properties.
+Then, introduced how current analysis can be useful for applications citing works already done with this approach.
+Finally, ending up the chapter defining what spraying modes classification will be considered and its properties.
 

### 2023-05-08 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 
-The classification is a key step in our routine and for being able to be used in multipurpose applications our classification must be able to run in real-time, which means it must be fast and automatic.
+The classification is a key step in this routine and for being able to be used in multipurpose applications the classification must be able to run in real-time, which means it must be fast and automatic.
 The goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.
@@
 In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
-We acquire the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values.
-Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation.
-Which is referred as the sample standard deviation divided by the sample mean values.
-Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.
+It is acquired the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values.
+Through statistical analysis in these values such as mean, median and standard deviation the classification is done.
+Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks\cite{Sjaaks} method.
 
@@
 
-To classify the multi jet, after running many steps experiments I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range.
+To classify the multi jet, after running many steps experiments it was noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range.
 These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
 
-With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
+With that, it was implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
 The cone jet current can be calculated by the scaling laws \ref{sec:scalling-laws} formula.
@@
     The controller thread will manage what the algorithm must do for each sequence.
-    Following our control model\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
+    Following the control model in Figure\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
     The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread\ref{subsec:data_aquisition}.
@@
 
-    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
+    In Figure \ref{fig:map2Data_fig} it can be seen the data acquired in this mapping experiments. The liquid used is pure ethanol. 
     Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.
@@
         \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
-        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
-        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
+        \caption{Mapping Experiment data collected. The Figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
+        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined in the routine.
         The third graph shows the current mean value of each data sample.}
@@
 
-    With all the data collected, classified and saved in real time, we can do further analysis and studies.
-For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researches, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.
+    With all the data collected, classified and saved in real time, further analysis and studies can be done.
+For example, Figure \ref{fig:map3Data_fig} illustrate the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison on automatic results with previous researches can be done, such as showed in Figure \ref{fig:ganan_calvo_fig}, validating the algorithm.
 
@@
         \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
-        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capillary setup.
-The map shows the stability region of each electrospraying mode in the voltage and flow rate range.}
+        \caption{Mapping Experiment for pure ethanol in ambient conditions. The map shows the stability region of each electrospraying mode in the voltage and flow rate range.}
         \label{fig:map3Data_fig}
@@
 
-    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
+    The control sequence is the only from the list of sequences that actually uses the feedback classification value. 
     As it is a closed loop control, the controller must be able to stabilize the system in the desired conditions.
@@
 
-This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve our goals. 
-Next chapter \ref{chap:Results}, we will discuss the results reached.
+This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve the project goals.
+Next chapter \ref{chap:Results}, it will be discussed the results reached.
 

### 2023-05-08 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 
-In this chapter, we will present the results obtained from our project. 
-Firstly, we will demonstrate how the automation routine enhanced the research experiments. 
-Next, we will discuss the validation of the classification results. 
-Finally, we will showcase the performance of the implemented controller algorithms.
+This chapter will present the results obtained from this project. 
+Firstly, it will be demonstrated how the automation routine enhanced the research experiments. 
+Next, a discussion on the validation of the classification results. 
+Finally, a showcase of performance on the implemented controller algorithms.
 
@@
 The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
-With the save data by streaming in saving thread \ref{subsec:save_thread}, we achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
+With the save data by streaming in saving thread \ref{subsec:save_thread}, it was achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
 
@@
 Moreover, the electrospray phenomena has a known hysteresis, that can be seen in figure \ref{fig:ganan_calvo_fig}, and can perform different results depending on the previous electric potential.
-By running a computer routine that automatically sends commands to the power supply and pump machine we can achieve faster and more reliable experiment data points.
+Running a computer routine that automatically sends commands to the power supply and pump machine allowed obtaining faster and more reliable experiment data points.
 
@@
     \caption{Print screen of the window shows user interface during the experiment.
-        We can see the image generated by the camera in the background.
+        The image generated by the high speed camera can be seen in the background.
         The routine code running in pycharm software on the right side.
-        And also real time signal plottings of the current data on the left side.}
+        And also real time signal plotting of the current data on the left side.}
         \label{fig:multi_class_exp1}
@@
 
-The classification results in our algorithm implemented as described in section \ref{sec:section_classification} showed good accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
+The classification results in the algorithm implemented as described in section \ref{sec:section_classification} showed good accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
 Nevertheless, the multi jet classification made by a current value factor of 1.14 above the cone jet is just effective for pure ethanol, liquid used in all this project.
@@
 
-We will categorize our classification results into two main groups - the step routine and the map routine.
+The classification result will be categorized into two main groups - the step routine and the map routine.
 These two routines have showed valuable insights and comprehensible results of the electrospraying process.
@@
 
-Our first classification results were made exploring the voltage ranges. 
-For that, we fixed a flow rate to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
+The first classification results were made exploring the voltage ranges. 
+For that, a flow rate was fixed to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
 The figure \ref{fig:step_class} shows three graphs.
@@
 The first shows the controller output signal as an input voltage of the process.
-As it is a step routine we implemented a increasing voltage with steps of sizes 50V and time between each step of 5 seconds.
-The voltage range is between 3K~10K Volts.
+As it is a step routine, an increasing voltage with steps of sizes 50V and time between each step of 5 seconds was implemented.
+The voltage range is between 3k-10k Volts.
 
 The second is the raw output data collected by the oscilloscope in \emph{data\_acquisition\_thread()}. 
-The sampling rate is 10KHz. Therefore, this experiment of 700s has 7 Million data points just of current data. 
+The sampling rate is 100kHz. Therefore, this experiment of 700s has 70 Million data points just of current data. 
 This is an example of how scalable the data collected can be depending on the experiment time. This will be even more noticeable in mapping experiments.
@@
 The Intermittent state has a high variation of values that can be seen by the increased thickness on the graph.
-The Cone jet is a thinner graph because of its constant signal.
-Multi Jet  has the same shape as Cone jet but with a higher mean value.
+The cone jet is a thinner graph because of its constant signal.
+Multi Jet  has the same shape as cone jet but with a higher mean value.
 Corona sparks are not showed in the graph because its discharges has a high current value above the axis limits.
@@
 For validation with literature and also to expose the benefits of the automated routine and classification, the map sequence proof itself the best result of this work. 
-
-    Initially, for better understand pure ethanol classification regions through voltage and flow rate ranges, I made a manual map seen in figure \ref{fig:stability_1}.
+Initially, for better understand pure ethanol classification regions through voltage and flow rate ranges, it was made a manual map seen in figure \ref{fig:stability_1}.
 
@@
 
-    In order to validate our automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
+    In order to validate the automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
     Figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).
@@
 
-    With the development of a Multi Jet classification using the logic explained in section \ref{sec:section_classification}, I repeated the same experiment as shown in Figure \ref{fig:stability_6}.
+    With the development of a multi jet classification using the logic explained in section \ref{sec:section_classification}, the same experiment was repeated, as shown in Figure \ref{fig:stability_6}.
 
@@
 
-    To have a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, with a visual juxtaposition of the shapes, we displayed in figure \ref{fig:stability_8} the data using the non-dimensional numbers used in his work\cite{gananCalvo}.
+    To have a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, with a visual juxtaposition of the shapes, the data displayed in Figure \ref{fig:stability_8} using the non-dimensional numbers used in his work\cite{gananCalvo}.
 
@@
 
-    The results of mapping experiment corresponded visual, literature and automatic regions of classification, giving authentication to our method.
+    The results of mapping experiment corresponded visual, literature and automatic regions of classification, giving authentication to the method.
 
@@
     Together with the amount of variables that need to be syntonized makes it hard to stabilize in a desired mode.
+    Even with all those problems, a simple controller project could be implemented, as described in section \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.
 
-    Even with all those problems we could implement a simple controller project, described in \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.
-
-    The controller not only stabilized in Cone Jet mode, but also could reject perturbation, as seen in Figure \ref{fig:control_results}, where I manually changed the flow rate.
+    The controller not only stabilized in cone jet mode, but also could reject perturbation, as seen in Figure \ref{fig:control_results}, where the flow rate was manually changed.
     First graph shows current acquired.
 It starts as intermittent state, with an oscillating signal.
-We can validate this with the blue colored sample on the third graph representing its automatic classification.
+This can be validated with the blue colored sample on the third graph representing its automatic classification.
     The second graph shows the controller actuating increasing the voltage to achieve a stable cone jet mode.
-    After a period of time in cone jet, I manually increased the flow rate, serving as a perturbation of the system, and we can see that the effect of that was to return to intermittent state with the oscillating signal.
+    After a period of time in cone jet, a manual increase in the flow rate was done, serving as a perturbation of the system, and it can be seen that the effect of that was to return to intermittent state with the oscillating signal.
 The controller again, actuate increasing the voltage to reach the cone jet stability island.
-    This procedure was repeated after some seconds of stabilization in cone jet, increasing again the flow rate manually, and we can see the system automatically adjusting the voltage.
+    This procedure was repeated after some seconds of stabilization in cone jet, increasing once more the flow rate manually, and again the system automatically adjusting the voltage.
         \begin{figure}[H]
@@
             \caption{Simple controller validation experiment.
-For this experiment we waited the system to stabilize in the desired spraying mode.
-After that we made a perturbation test changing the flow rate.
+For this experiment, after waiting the system to stabilize in the desired spraying mode it was made a perturbation test changing the flow rate.
 The classification legend follows the same color reference in all project.}
@@
 
-    After 200s of experiment we had some breaks up of the cone jet into a droplet and stabilized again.
+    After 200s of experiment the system had some breaks up of the cone jet into a droplet and stabilized again.
 This is represented by the peak values in current signal.
@@
 
-In this chapter we exposed the results of this project.
+In this chapter the results of this project were exposed.
 The automatic routine, real time classification and control were all achieved and implemented.
 However, they can all be improved.
-In the next Chapter I will conclude this document with discussions about the results and proposal of continuation.
+Next Chapter will conclude this document with discussions about the results and proposal of continuation.
 

### 2023-05-08 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
 
-In this chapter, we will discuss the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
+In this chapter, will be discussed the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
 The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library.
@@
 
-    The software has an interface to integrate the HVPS to our routine.
+    The software has an interface to integrate the HVPS to the routine.
 This interface can be found in \emph{FUG\_function.py} file where is located the functions used to control and collect data from this instrument.
@@
 
-    Wireless communication allows us to make measurements disconnected to an external power supply, which increase safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
+    Wireless communication allows measurements disconnected to an external power supply, which increase safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
     The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
@@
 
-  The pump integration in the automation algorithm was done in this work, bringing us a new controllable variable, the flow rate. We can control the spraying mode with the
-  two main variables that affect the system. 
-  It brings more complexity for the system since now we are dealing with multivariable control.
-  Controlling also the flow rate gives to this project a new dimension in the system giving us freedom to explore the flow rate properties.
-  With this new input variable our control is a MISO (Multiple Inputs Single Output) system.
+  The pump integration in the automation algorithm was done in this work, bringing a new controllable variable, the flow rate.
+The spraying mode can be controlled using the two main variables that affect the system.
+  It brings more complexity for the system since now it is a multivariable control.
+  Controlling also the flow rate provide this project a new dimension in the system giving freedom to explore the flow rate properties.
+  With this new input variable the control system is MISO (Multiple Inputs Single Output).
 
-  About the pump interface, as there was no good ready-to-use library, I developed a simple and intuitive interface to be used in our software routine.
+  About the pump interface, as there was no good ready-to-use library, it was developed a simple and intuitive interface to be used in the software routine.
   The communication protocol used is RS-232 and the pump commands list were found in the user manual.
@@
 
-In figure \ref{fig:setup} we illustrate a diagram with all the key components of our system. The peripherals are connected to a computer running the software routine via serial communication. 
-This diagram encapsulates our process system and will be used as a sub-system in our control model.
-The input of our process system are power supply voltage and pump machine flow rate, referred here as the controller values.
+Figure \ref{fig:setup} illustrate a diagram with all the key components in the system. The peripherals are connected to a computer running the software routine via serial communication. 
+This diagram encapsulates the process system and will be used as a sub-system of the control model.
+The input in the process are power supply voltage and pump machine flow rate, referred here as the controller values.
 The output is the oscilloscope current sample.
@@
 
-There are also many minor variables that affects the experiment stability. More details are explained in \ref{sec:setup_validation}.
+There are also many minor variables that affects the experiment stability. More details are explained in appendix \ref{sec:setup_validation}.
 
@@
 
-The software was reformulated on top of the control model represented in figure \ref{fig:control_model_fig}. The process of the control loop is the same as represented in \ref{fig:setup}. 
+The software was reformulated on top of the control model represented in Figure \ref{fig:control_model_fig}. The process of the control loop is the same as represented in Figure \ref{fig:setup}. 
 Each other subsystem in the control loop is a separate thread that will be explained bellow.
@@
 
-    In order to implement this closed loop control model to the software and explore parallel processing, each sub-system was implemented as a separate Thread.
+    In order to implement this closed loop control model to the software and explore parallel processing, each sub-system was implemented as a separate thread.
     For concurrency on flux of data between threads was used queues structures.
@@
 
-        It is responsible for sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
+        The controller thread is responsible for sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
         Also, responsible for sending the finish event command that end the routine and trigger the threads to close their routines.
-        As input, we have the setup config file and the \emph{feedback\_queue}. As output, we have the values in the \emph{controller\_output\_queue()}.
+        As input, there is the setup config file and the \emph{feedback\_queue}. As output, the values in the \emph{controller\_output\_queue()}.
 
@@
 
-        It is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the power supply, flow rate from the pump and concatenate into one sample data.
-        As output, we have the values in the \emph{data\_queue()}.
+        The data acquisition thread is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the power supply, flow rate from the pump and concatenate into one sample data.
+        As output, the values in the \emph{data\_queue()}.
 
@@
 
-        It is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
-        As output, we have the values in the \emph{save\_data\_queue()}, \emph{plotting\_queue()} and \emph{feedback\_queue()}.
+        The data processing is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
+        As output, the values in the \emph{save\_data\_queue()}, \emph{plotting\_queue()} and \emph{feedback\_queue()}.
 
@@
         After processing, the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
-        With the new streaming model of saving a new structure of the collected data were created.
-        Instead of having all data measurements values and after all data processing values we now are saving for each sample the measurements and processing values.
-        The data acquired in each sample of 0.5s is shown in figure \ref{fig:data_sample}.
+        With the new streaming model of saving, instead of having all data together in program memory to be saved in the end, it is saving each sample in real time during the experiment.
+        The data acquired in each sample of 0.5s is shown in Figure \ref{fig:data_sample}.
 
@@
 Organizing that amount of data to make it fast and easy to use was an important improvement in the software.
-        To work and analyze the data we can use  pandas Data frame. A python widely used framework for data analysis.
+        To work and analyze the data it can be used pandas Data frame. A python widely used framework for data analysis.
         With the command:
@@
         The only running function that should run in the main thread because the plotting library \emph{matplotlib} incompatibilities of running outside the main function. 
-        It is responsible for plotting in real time the current sample acquired, and its respective fast Fourier transform to evaluate the sample frequency spectrum.
+        The plotting function is responsible for plotting in real time the current sample acquired, and its respective fast Fourier transform to evaluate the sample frequency spectrum.
         It takes as input the \emph{plot\_data\_queue} from the \emph{processing\_thread()} and displays three graphs updated in real time on the screen during the experiment.
@@
 
-    In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software.
+    In this chapter it is described the system description detailing the hardware instruments, how it was modelled and its implementation in the software.
 

### 2023-05-17 software/classification_electrospray.py
version 17 may 2023

@@ -171,16 +171,16 @@ class ElectrosprayClassification:
         #     print("ERROR: ", str(e)) 
         #     print("Error on João classification")
 
-        try:
-            if(classification_txt == "Cone Jet") and cone_jet_mean != 0:
-                if(mean > 1.14 * cone_jet_mean):
-                    classification_txt = "Multi Jet"
-
-            print("Multi jet treshold mean value: ", cone_jet_mean * 1.14)
-
-        except Exception as e:
-            print("ERROR: ", str(e))
-            print("Error on João classification")
+        # try:
+        #     if(classification_txt == "Cone Jet") and cone_jet_mean != 0:
+        #         if(mean > 1.14 * cone_jet_mean):
+        #             classification_txt = "Multi Jet"
+        #
+        #     print("Multi jet treshold mean value: ", cone_jet_mean * 1.14)
+        #
+        # except Exception as e:
+        #     print("ERROR: ", str(e))
+        #     print("Error on João classification")
 
         #
         #       Correcting some wrongly classified modes by the system knowledge and memory

### 2023-05-17 software/data_processing.py

@@ -71,7 +71,6 @@ def data_processing(data_queue,
         except Exception as e:
             print("ERROR: ", str(e)) 
             print("[DATA_PROCESSING THREAD] Failed to process data")
-            sys.exit(1)
 
         try:
 
@@ -79,8 +78,8 @@ def data_processing(data_queue,
             electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data,
                                                                     electrospray_processing.mean_value,
                                                                     electrospray_data.flow_rate)
-            print("I:", electrospray_validation.I_emitted_chen_pui * 10e5)
-            print("alpha:", electrospray_validation.alpha_chen_pui * 10e10)
+            # print("I:", electrospray_validation.I_emitted_chen_pui * 10e5)
+            # print("alpha:", electrospray_validation.alpha_chen_pui * 10e10)
             cone_jet_mean = electrospray_validation.I_emitted_chen_pui  * 10e5
 
         except Exception as e:

### 2023-05-17 Documentation/UFMG/PFCII/Abstract/Abstract.tex
documentation

@@
     accuracy and lower transient time. Therefore, a completely autonomous EHDA system opens the door to potential
-    industrial applications. In addition, the use of the electric current signal can be useful to further research in electrospray
+    industrial applications. In addition, the use of the electric current signal can be helpful to further research in electrospray
     processes, leading to better control on droplet generation (frequency, size and charge).

### 2023-05-17 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

@@
 The spray process imposes noise and random sequences on the measured signal making its classification a non-trivial task. 
-Industrial applications demand automated stabilization of a spray mode. 
-This can be achieved by a closed-loop control system. 
-This project targets the development of a system which allows real time acquisition of the electrospray current, treat and process its values, define in which specific mode the electrospray is running and control the necessary hardware to change and/or stabilize the spray at a desired mode.
+Industrial applications demand automated stabilization of a spray mode which can be achieved by a closed-loop control system. 
+This project targets the development of a system that allows real time acquisition of the electrospray current, treat and process its values, define in which specific mode the electrospray is running and control the necessary hardware to change and/or stabilize the spray at a desired mode.
 
-\section{Motivation and Justify}
+\section{Motivation}
 \label{sec:motivation}
@@
 
-This project aims to give continuity to the previous student work\cite{Monica}, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
-For that, it was developed a python software routine to connect most of the peripherals and analyzed the current data.
-Her work corroborates the validation of this project motivating its continuation on development and optimization.
+This project aims to give continuity to the previous student work\cite{Monica}, who focused on predicting undesired discharges (sparks) in the system occurred when the electric potential is too high. 
+For that, a python software routine was developed to connect most of the peripherals and analyze the current data.
+The success of her work in applying statistical classifications corroborates the validation of this project motivating its continuation on development and optimization.
 
-Bellow are shown the main goals listed:
+The main goals are shown:
 
@@
 
-In order to achieve this, the Water Technology Group at NHL Stenden University of Applied Sciences, in collaboration with Dutch companies, is conducting extensive research and implement appropriate classification algorithms.
+In order to achieve this, the Water Technology Group at NHL Stenden University of Applied Sciences, in collaboration with Dutch companies, is conducting extensive research to implement appropriate classification algorithms.
 The aim is to combine analytical capabilities with infrastructure knowledge and availability to achieve optimal results.
@@
 
-In Chapter \ref{chap:Results}, it is presented results and engage in discussions comparing the knowledge acquired through literature review.
+In Chapter \ref{chap:Results}, presents results and engages in discussions comparing the knowledge acquired through literature review.
 

### 2023-05-17 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
-A stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
+A stable balance between the capillary and field forces on the liquid suggests a \emph{quasi static} dynamics.
 The feeding liquid is pulled through a small orifice by means of the applied voltage.
@@
 The resulting spray is electrically charged, and the droplets repel one another.
-For this reason, with a controlled environment a certain stable spraying mode can be reached as seen in the Figure \ref{fig:ehda_setup_ex2}.
+For this reason, with a controlled environment a certain stable spraying mode can be reached, as seen in the Figure \ref{fig:ehda_setup_ex2}.
 
@@
 Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in the system during a dripping of a charged liquid. 
-It can be visually identified the signal of two droplets generated in this time frame.
+The signal of two droplets generated in this time frame can be visually identified by the perturbation.
 
@@
   This project draws significant inspiration from Sjaak's\cite{Sjaaks} work, which identifies distinct statistical characteristics of electrical current for various spraying modes.
-  A profound use of his method will be explained in section \ref{sec:section_classification}.
-  Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
+  A profound of his method will be explained in section \ref{sec:section_classification}.
+  Together with the current characteristics, visual observations and results from literature, it was investigated whether generic trends are present that can be related to the actual spraying modes.
 
@@
 
+Where,
+\[I : current \: emitted \: [A] \] 
+\[Q : flow \: rate \: [m^3/s] \]    
+\[ \gamma : surface \: tension \: [N/m]  \]   
+\[\kappa : relative \: dieletric \: constant \] 
+\[K : electric \: conductivity \: [S/m] \]
+
 \section{Spraying modes}
@@
 
-Since 1915 with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
+Since 1915, with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
 Years later the same circumstance was noticed by other scientists, but the classification of these modes were still not well-defined by the community.

### 2023-05-17 Documentation/UFMG/PFCII/acknowledgment/acknowledgment.tex
documentation

@@
 
-I would like to acknowledge the outstanding education and training that I received from the UFMG university, which has equipped me with the necessary skills and knowledge to thrive in the global marketplace.
+I would like to acknowledge the outstanding education and training that I received from UFMG, which has equipped me with the necessary skills and knowledge to thrive in the global marketplace.
 I am grateful for the transformative experience that has prepared me for a fulfilling career and a meaningful life.

### 2023-05-17 software/classification_electrospray.py
verdoold ranges for classification

@@ -46,7 +46,7 @@ class ElectrosprayClassification:
             flow_rate,
             fft_max_peaks_array,
             cont_fft_max_peaks,
-            cone_jet_mean):
+            I_chen_pui):
 
         self.med_value_array.append(median)
         classification_txt = "Undefined"
@@ -73,26 +73,26 @@ class ElectrosprayClassification:
             self.sjaak_mean_median_array.append(self.sjaak_mean_median)
 
             # classification for dripping
-            # if mean <= 5:
-            if self.sjaak_std_mean > 2.5:
-                classification_txt = "Dripping"
-                if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
-                    # print("classification dripping confirmed!")
-                    classification_txt = "Dripping"
+            if mean <= 5:
+                if self.sjaak_std_mean > 2.5:
+                    #classification_txt = "Dripping"
+                    if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
+                        # print("classification dripping confirmed!")
+                        classification_txt = "Dripping"
 
             # classification for intermittent
-            # if mean > 5:
-            if (self.sjaak_std_mean) < 2.5 and self.sjaak_std_mean > 0.5:
-                # print("intermittent Sjaak!")
-                classification_txt = "Intermittent"
-                if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
-                    classification_txt = "Intermittent"
+            if mean > 5:
+                if (self.sjaak_std_mean) < 2.5 and self.sjaak_std_mean > 0.5:
+                    # print("intermittent Sjaak!")
+                    #classification_txt = "Intermittent"
+                    if (self.sjaak_mean_median) < 0.9 or (self.sjaak_mean_median) > 1.1:
+                        classification_txt = "Intermittent"
 
             # classification for cone-jet
-            if mean > 10:  # replace absolut value with cone-jet current estimation by laMora/Calvo
-                if self.sjaak_std_mean < 0.3:
-                    classification_txt = "Cone Jet"
-                    if (self.sjaak_mean_median) > 0.9 or (self.sjaak_mean_median) < 1.1:
[…]

### 2023-05-17 software/data_processing.py

@@ -78,7 +78,6 @@ def data_processing(data_queue,
             electrospray_validation.calculate_scaling_laws_cone_jet(electrospray_data.data,
                                                                     electrospray_processing.mean_value,
                                                                     electrospray_data.flow_rate)
-            # print("I:", electrospray_validation.I_emitted_chen_pui * 10e5)
             # print("alpha:", electrospray_validation.alpha_chen_pui * 10e10)
             cone_jet_mean = electrospray_validation.I_emitted_chen_pui  * 10e5
 
@@ -98,7 +97,7 @@ def data_processing(data_queue,
                 previous_flowrate = electrospray_data.flow_rate
 
 
-            classification_txt, cone_jet_mean = electrospray_classification.do_classification(
+            classification_txt = electrospray_classification.do_classification(
                                                                         electrospray_processing.mean_value,
                                                                         electrospray_processing.med,
                                                                         electrospray_processing.stddev,
@@ -110,7 +109,7 @@ def data_processing(data_queue,
                                                                         electrospray_data.flow_rate,
                                                                         max_fft_peaks,
                                                                         cont_max_fft_peaks,
-                                                                        cone_jet_mean
+                                                                        electrospray_validation.I_emitted_chen_pui
 
             )
         except Exception as e:

### 2023-05-17 software/validation_electrospray.py

@@ -70,6 +70,7 @@ class ElectrosprayValidation:
         self.alpha_chen_pui =  (self.surface_tension * self.electrical_conductivity * self.flow_rate_chen_pui / self.dieletric_const) ** (.5)
 
         self.I_emitted_chen_pui = ki * self.dieletric_const ** (.25) * self.alpha_chen_pui ** (.5)
+        self.I_emitted_chen_pui = self.I_emitted_chen_pui*10e5 / 2  # divided by two because of oscilloscope internal impedance
         # i_actual = data
         #
         # b_hartman = i_actual / ((self.surface_tension * self.electrical_conductivity * flow_rate) ** .5)

### 2023-05-20 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

@@
 
-Through the various classifications and subclassifications of spraying defined in literature it will be aggregated some of them and separated between 5 modes as explained below in order of growing electric potential.
+About the classification, there is not a convention in literature.
+Some authors can describe more classifications than others, hence this work will focus on 5 electrospraying modes as will be explained below.
 
@@
 
-Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomenon called field enhanced dripping.
-In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.
+When the applied electric field is insufficient to alter the shape of the meniscus, the liquid droplet typically has a size larger than that of the capillary.
+Additionally, there are low-frequency intervals between each drop, indicating that the droplet is in a dripping mode.
+With the increase of electric field, starts a phenomenon called field enhanced dripping, where droplet size decrease and frequency starts to increase in order to keep the same volume of liquid flowing.
 
@@
 Taylor (1964)\cite{taylor} was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
-The electrified meniscus can take on a conical shape within a certain range of applied voltage and injected liquid flow rate.
+The electrified meniscus can assume a conical shape within a certain range of applied voltage and injected liquid flow rate.
 
 In Taylor cone, here referred as Cone Jet, the direction of the cone apex also varies depending on the balance of forces. 
-With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume when increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.
+With a fixed flow of liquid, it is noticeable that the pointing direction curves and the meniscus reduce volume when the electric potential increase, until the moment the jet breaks into two or more jets going to the next classification.
 
@@
 
-Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet mode. In his experiments was observed:
+Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet mode. In his experiments it was observed:
 \emph{"for voltages well above that for which the steady conical surface changed into a blurred agitated one, the appearance became a number of fine points with their attendant dark streaks arranged along the circumference of the raised edge".}
@@
 C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
-He detected that for a low number of jets emitted the meniscus is not bound to the rim of the capillary. 
+It was detected that for a low number of jets emitted the meniscus is not bound to the rim of the capillary. 
 This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
-As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
+As the number of jets increases the mode becomes what Ryan refers to as rim-mode electrospray. 
 In this work, all modes with more than one stable jet will be classified as multi jet. Figure \ref{fig:multijt} shows three different variations of multi jet spraying mode.
@@
 
-In this chapter it was exhibited some electrospray theory that was important for the development of this project. 
-Firstly, with a brief review about the physical concept behind the experiment. 
-Then, introduced how current analysis can be useful for applications citing works already done with this approach.
+This chapter presents some electrospray theory that was important for the development of this project:
+Firstly, a brief review about the physical concept behind the experiment. 
+Then, it is introduced how current analysis can be useful for applications, citing works already done with this approach.
 Finally, ending up the chapter defining what spraying modes classification will be considered and its properties.

### 2023-05-20 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
-It is acquired the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values.
-Through statistical analysis in these values such as mean, median and standard deviation the classification is done.
-Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks\cite{Sjaaks} method.
+A current data frame of 0.5s is acquired with 100 kHz as sampling frequency. Therefore, each current sample holds 50 thousand current values.
+
+Through statistical analysis in these signal such as mean, median and standard deviation the classification is done. 
+Figure \ref{fig:sjaaks_statistical_class} illustrates data samples being classified using Sjaaks\cite{Sjaaks} method.
 
@@
     Following the control model in Figure\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
-    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread\ref{subsec:data_aquisition}.
+    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread.
 

### 2023-05-20 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
-With the save data by streaming in saving thread \ref{subsec:save_thread}, it was achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
+With the save data by streaming in saving thread, it was achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
 

### 2023-05-20 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

@@
 
-In this chapter, will be discussed the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
+In this chapter, the equipment used will be discussed in detail, including its integration and how it was modeled and implemented in both hardware and software. 
 The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library.
@@
 
-    Wireless communication allows measurements disconnected to an external power supply, which increase safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
+    Wireless communication allows measurements disconnected from an external power supply, which increases safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
     The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
     TiePie WifiScope WS6 has a resolution of up to 16 bit at a minimal input range of 200 mV, sufficient to measure currents down to 1 nA.
-
-    The interface with the software was made using the TiePie Library\cite{TiePieLib} and can be found in \emph{configuration\_tiepie.py}.
-Note that is also important to have the \emph{printinfo.py} file in the project folder in order to work.
+In addition the WifiScope has an open source interface library for python, \cite{TiePieLib}, making it easier to integrate with the automation routine.
 
@@
 
-  The stability of the system is affected by many physical effects. Evidently having the more parameters analyzed favors the system control.
-  The surface tension force is dependent of the liquid-gas interface on the meniscus. Hence, the surrounding gas must be constantly the same and so its humidity.
-  Also, temperature is a variable that interfere in many phenomena in the system. Specially the liquid properties such as viscosity.
+  The stability of the system is affected by many physical effects. Evidently, it favors the system control having more parameters analyzed.
+  The surface tension force, for example, is dependent of the liquid-gas interface on the meniscus, hence, the surrounding gas must be constant and so its humidity.
+  Also, temperature is a variable that interferes in many phenomena in the system, specially the liquid properties such as viscosity.
 
-  For that, a standard microcontroller development board (\emph{Arduino Uno}) with a temperature and humidity sensor (DHT11) was configured to add that data in real time in the routine.
-  The Arduino code can be found in the \emph{/peripherals} folder.
+  For that, a standard microcontroller development board (\emph{Arduino Uno}) with a temperature and humidity sensor (DHT11) was configured to add that data in real time to the routine.
 
@@
   It brings more complexity for the system since now it is a multivariable control.
-  Controlling also the flow rate provide this project a new dimension in the system giving freedom to explore the flow rate properties.
+  Controlling also the flow rate provides this project a new dimension in the system giving freedom to explore the flow rate properties.
   With this new input variable the control system is MISO (Multiple Inputs Single Output).
 
-  About the pump interface, as there was no good ready-to-use library, it was developed a simple and intuitive interface to be used in the software routine.
+  About the pump interface, as there was no good ready-to-use library, a simple and intuitive interface was developed to be used in the software routine.
   The communication protocol used is RS-232 and the pump commands list were found in the user manual.
@@
 
-Figure \ref{fig:setup} illustrate a diagram with all the key components in the system. The peripherals are connected to a computer running the software routine via serial communication. 
+Figure \ref{fig:setup} illustrates a diagram with all the key components in the system. The peripherals are connected to a computer running the software routine via serial communication. 
 This diagram encapsulates the process system and will be used as a sub-system of the control model.
-The input in the process are power supply voltage and pump machine flow rate, referred here as the controller values.
-The output is the oscilloscope current sample.
+The inputs in the process are power supply voltage and pump machine flow rate, referred here as the controller values.
+The output is the oscilloscope current measurement.
 
@@
 
-There are also many minor variables that affects the experiment stability. More details are explained in appendix \ref{sec:setup_validation}.
+There are also many minor variables that affect the experiment stability. More details are explained in appendix \ref{sec:setup_validation}.
 
@@
 The software was reformulated on top of the control model represented in Figure \ref{fig:control_model_fig}. The process of the control loop is the same as represented in Figure \ref{fig:setup}. 
-Each other subsystem in the control loop is a separate thread that will be explained bellow.
+Each other subsystem in the control loop is a separate thread that will be explained below.
 
@@
 
-    In order to implement this closed loop control model to the software and explore parallel processing, each sub-system was implemented as a separate thread.
+    In order to implement this closed loop control model in the software and explore parallel processing, each sub-system was implemented as a separate thread.
     For concurrency on flux of data between threads was used queues structures.
@@
 
-    \subsection{Controller Thread}
+    The controller thread is responsible for sending to the power supply the set voltage values and to syringe pump the flow rate set values according to the sequence selected.
+    Also, responsible for sending the finish event command that end the routine and trigger the threads to close their routines.
+    As input, the setup config file with information about the liquid and the setup used such as geometric parameters of the nozzle to plate system. As output, the commands to the actuators.
 
-        The controller thread is responsible for sending the power supply set voltage values and the syringe pump the flow rate set values according to the sequence selected.
-        Also, responsible for sending the finish event command that end the routine and trigger the threads to close their routines.
-        As input, there is the setup config file and the \emph{feedback\_queue}. As output, the values in the \emph{controller\_output\_queue()}.
-
-    \subsection{Data Acquisition Thread}
-    \label{subsec:data_aquisition}
-
-        The data acquisition thread is responsible for reading the current data from the oscilloscope, humidity and temperature data from the DHT11 sensor, voltage from the power supply, flow rate from the pump and concatenate into one sample data.
-        As output, the values in the \emph{data\_queue()}.
-
-    \subsection{Data Processing Thread}
-
+    The data acquisition thread is responsible for concatenating the current, voltage, flow rate, humidity and temperature data and concatenate it into one sample.
     The data processing is responsible for calculating the statistical values from the raw data and classify it in the respective spray mode for that sample.
-        As output, the values in the \emph{save\_data\_queue()}, \emph{plotting\_queue()} and \emph{feedback\_queue()}.
-
-    \subsection{Save Data Thread}
-    \label{subsec:save_thread}
-
     After processing, the data is saved in real time in a json file using \emph{jsonstreams} library to save one sample structure at a time.
@@
 
-        This new way of saving the measurement and processing data altogether separate by enumerated samples prevents loss of data in case of error during experiments and, specially improve in the usability of the data for further deep analysis.
-One experiment of around 1 hour collects around 6 GB of data.
-Organizing that amount of data to make it fast and easy to use was an important improvement in the software.
-        To work and analyze the data it can be used pandas Data frame. A python widely used framework for data analysis.
-        With the command:
+    This new way of saving the measurement and processing ensures that the data is stored separately in enumerated samples.
+    This prevents any loss of data in the event of errors during experiments and significantly enhances the usability of the data for in-depth analysis.
+Each hour-long experiment generates approximately 6 GB of data, and effectively organizing such a substantial amount of data was a crucial enhancement in the software.
+To efficiently work with and analyze the data, the widely-used Python framework, pandas Dataframe, can be utilized with the following command:
 
@@
     To conclude, json files are good as a system output because of its human readability.
-But as the database gets bigger json becomes to be a slow to read and heavy to store data.
+But as the database gets bigger json becomes slow to read and large to store.
 For that, saving the data frame in a compressed type of file called feather is much faster to work with it.
 
-    \subsection{Plotting}
-
-        The only running function that should run in the main thread because the plotting library \emph{matplotlib} incompatibilities of running outside the main function. 
+    This is only running function that should run in the main thread because of the plotting library \emph{matplotlib} incompatibilities with running outside the main function. 
     The plotting function is responsible for plotting in real time the current sample acquired, and its respective fast Fourier transform to evaluate the sample frequency spectrum.
@@
 
-    In this chapter it is described the system description detailing the hardware instruments, how it was modelled and its implementation in the software.
+    In this chapter it is explained the system description, detailing the hardware instruments, how it was modelled and its implementation in the software.
 

### 2023-05-21 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 Through statistical analysis in these signal such as mean, median and standard deviation the classification is done. 
-Figure \ref{fig:sjaaks_statistical_class} illustrates data samples being classified using Sjaaks\cite{Sjaaks} method.
+Figure \ref{fig:sjaaks_statistical_class} illustrates data samples separated by statistical method, depending on the range in mean, mean/median and deviation/mean.
 
@@
     \centering
-    \resizebox{80mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
+    \resizebox{150mm}{!}{\includegraphics{Figuras/may/classificators.png}}
     \caption{Sample classification using statistical values. Colors: Green = Dripping; Blue = Intermittent; Red = Cone Jet.}
@@
 
-With that, it was implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
+With that, the classification of the multi jet was implemented  when the current mean is 14\% above the expected cone jet current mean. 
 The cone jet current can be calculated by the scaling laws \ref{sec:scalling-laws} formula.
@@
             \State $mean \gets sample.mean$; 
-            \State $std\_deviation \gets sample.std\_deviation$;
-            \State $median \gets sample.median$;
+            \State $deviation\_mean \gets sample.std\_deviation / sample.mean$;
+            \State $mean\_median \gets sample.mean / sample.median$;
 
-            \If{ $mean / std\_deviation$ > 2.5}
+            \If{ $mean > 5$}
                 \Comment{Sjaak classification \cite{Sjaaks}} 
                 \State $spray\_mode \gets "Dripping"$;
-            \ElsIf{$ 2.5 < mean / std\_deviation < 2.5 \And mean / std\_deviation > 0.3 $}
+                \If{$ 2.5 < mean / std\_deviation < 2.5 \And mean / std\_deviation > 0.3 $}
                 \State $spray\_ mode \gets "Intermittent"$;
+                \EndIf
             \ElsIf{ $mean / std\_deviation$ < 0.3}

### 2023-05-24 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

@@
 The electroplating system is an unstable system that relies on multiple parameters being within their respective optimal ranges to achieve a desired mode. 
-Several tips can help reduce noise and stabilize the system, such as avoiding the use of an oscilloscope with the charger to avoid power line noise. 
+Several tips can help reduce noise and stabilize the system, such as avoiding the use of an oscilloscope with the charger to reduce power line noise. 
 Mechanical noise in the pumping machine can be minimized by using a syringe pump tilted with a bubble inside. 
 External electrical noise can be picked up by antennas or connections in the circuit. 
-To stabilize internal humidity, turn on the gas pipeline with air into the chamber.
+And gas pipeline with air into the chamber can be used to stabilize internal humidity and temperature.
 
@@
 \end{figure}
-
-\section{Setup Validation}
-\label{sec:setup_validation}
-
-It is recommended to do initial tests in order to verify the setup assembly and the automation routine integration. 
-This is an important step to understand in practice how electrospray works.
-Factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
-Also, liquid properties such as surface tension, dielectric constant, viscosity, density, electrical conductivity and vacuum permittivity. 
-And also physical variables such as flow rate, system impedance, system temperature, system humidity, nozzle to plate distance, nozzle dimensions and applied voltage.
-
-\section{Oscilloscope Impedance}
-\label{sec:osc_impedance}
-
-The current being measured by the Oscilloscope use its internal impedance. 
-The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
-Selecting one or other will multiply or divide your current measurement by 2. 
-By default, it is being used 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
-A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-24 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

@@
 To continue, a proposal is to prioritize the improvement of the classification step. 
-Ideally using machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
-By achieving a reliable classification, a more effective controller logic or approaches can be implemented. 
+Ideally, using machine learning or another classification algorithm to improve accuracy with a broad range of liquids.
+By achieving a reliable classification, a more effective controller logic can be implemented. 
 In this regard, a concept of a fuzzy controller will be presented as a potential solution.
@@
 
-        One challenge in implementing the controller in this project is that it does not have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control.
+        One challenge in implementing the controller in this project is that it does not have a real value as feedback.
+Instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control.
         As this project involves logical control, it requires a different approach.
@@
 
-        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine\ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
+        Firstly, the fuzzyfication and defuzzyfication machines were implemented using the data acquired in the experiment of step routine \ref{subsec:step_routine}, mapping the area of each spraying mode according to its potential.
         Figure \ref{fig:fuzzyy} shows the steps of fuzzyfication and defuzzyfication within the input and output of the controller.
@@
 
-        The controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.
+        The controller is an algorithm that calculates the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.
 
@@
 
-        The works presented in this report represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.
+        The works presented in this project represent a continuation and refinement of previous efforts to develop a more precise and versatile automation routine that can be effectively applied in both industrial and research applications.
 

### 2023-05-24 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 This classification by statistical analysis was already implemented in the software library made by the previous student \cite{Monica}.
-This method was capable of only classifying dripping, intermittent and cone jet modes. Also in her work, Monica extended the classification to corona or discharge detection.
-My contribution was to integrate her work on my control loop model and extend the classification for the multi jet.
+This method was capable of only classifying dripping, intermittent and cone jet modes using the rules defined in figure \ref{fig:statis_ranges}. 
+\begin{figure}[H]
+    \centering
+    \resizebox{150mm}{!}{\includegraphics{Figuras/may/statistical_analysis.png}}
+    \caption{Statistical classification modes ranges.}
+    \label{fig:statis_ranges}
+\end{figure}
+
+Also in her work, Monica extended the classification to corona or discharge detection.
+My contribution was to integrate her work on a classic closed loop control model using parallel computing and extend the classification for the multi jet.
 
 To classify the multi jet, after running many steps experiments it was noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range.
-These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.
+These effects were exposed by Ryan\cite{Ryan}. In his work the relation between current per jet is defined in both cone jet and multi jet modes.
 
@@
             \State $spray\_mode \gets "Undefined"$;
-            \State $mean \gets sample.mean$; 
-            \State $deviation\_mean \gets sample.std\_deviation / sample.mean$;
-            \State $mean\_median \gets sample.mean / sample.median$;
 
-            \If{ $mean > 5$}
-                \Comment{Sjaak classification \cite{Sjaaks}} 
-                \State $spray\_mode \gets "Dripping"$;
-                \If{$ 2.5 < mean / std\_deviation < 2.5 \And mean / std\_deviation > 0.3 $}
-                \State $spray\_ mode \gets "Intermittent"$;
-                \EndIf
-            \ElsIf{ $mean / std\_deviation$ < 0.3}
-                \State $spray\_ mode \gets "Cone Jet"$;
-                \State $cone\_jet\_mean \gets mean$;
-            \EndIf
+            \State $spray\_mode$ = \Call{sjaaks\_classification}{$sample$} \Comment{Sjaak classification \cite{Sjaaks}}
 
-            \If{ $mean / std\_deviation$ > 2.5}
+            \If{ $mean > 1000$}
             \Comment{Monica classification \cite{Monica}} 
+                \State $spray\_mode \gets "Corona"$;
             \EndIf
@@
             \Comment{João classification} 
-                \If{ $cone\_jet\_mean > 1.14 \times mean$}
+                \If{ $mean > 1.14  \times cone\_jet\_mean$}
                     \State $spray\_ mode \gets "Multi Jet"$;
@@
     The controller thread will manage what the algorithm must do for each sequence.
-    Following the control model in Figure\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
+    Following the control model in Figure \ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
     The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread.
 
-\subsection{Ramp}
+\subsection{Ramp or Step}
+\label{subsec:step_routine}
 
@@
 
-\subsection{Step}
-\label{subsec:step_routine}
+The step sequence is done by the same command sent to the power supply but with the maximum slope value in order to proximate of a step signal.
+By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage.
 
-The step sequence is done by the same command send to the power supply but with the maximum slope value in order to proximate of a step signal.
-By waiting a certain defined \emph{step\_time} and repeating the command in a loop until it gets into the final voltage, as represented in algorithm \ref{alg:stepping_algorithm}.
+% \begin{algorithm}
+%     \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
+%     \begin{algorithmic}
+%     \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
+%         \State $voltage \gets voltage\_start$
+%         \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
+%             \State \Call{send\_voltage\_command}{voltage}
+%             \State \Call{sleep}{step \_time}
+%             \State $voltage \gets voltage + step\_size$
+%         \EndWhile
+%     \EndProcedure
 
-\begin{algorithm}
-    \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
-    \begin{algorithmic}
-    \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
-        \State $voltage \gets voltage\_start$
-        \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
-            \State \Call{send\_voltage\_command}{voltage}
-            \State \Call{sleep}{step \_time}
-            \State $voltage \gets voltage + step\_size$
-        \EndWhile
-    \EndProcedure
-
-    \end{algorithmic}
-\end{algorithm}
+%     \end{algorithmic}
+% \end{algorithm}
 
@@
 The map was inspired in Gañan-Calvo\cite{gananCalvo} work where he points how liquid conductivity influences the cone jet stability island. 
+The window formed by these points is where the system operated in the stable cone-jet.
+Operational windows depend on the liquid and configuration setup.
+Different windows are represented for different liquid conductivity.
+The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.
 
@@
     \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
-    \caption{Domains of existence (stability) of Taylor Cone Jets.
-\cite{gananCalvo} .
-The window formed by these points is where the system operated in the stable cone-jet.
-Operational windows depend on the liquid and configuration setup.
-Different windows are represented for different liquid conductivity.
-The X and Y axis are non-dimensional representation of electric potential and liquid flow rate, respectively.}
+    \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} .}
     \label{fig:ganan_calvo_fig}
@@
 
-To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
-The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
-The algorithm for this sequence is a loop of the step sequence\ref{subsec:step_routine} for each flow rate chosen, and it is represented in the algorithm \ref{alg:mapping_algorithm}.
-
-    \begin{algorithm}
-        \caption{MAP sequence in controller thread}\label{alg:mapping_algorithm}
-        \begin{algorithmic}
-        \Procedure{MAP}{$flowrate\_values$} 
-            \ForAll{flowrate\_values}  \Comment{scanning in the flowrate range}
-                \State \Call{send\_flowrate\_command}{flowrate}
-                \State $voltage \gets voltage\_start$
-                \While{$voltage \leq voltage\_stop$} \Comment{scanning in the voltage range}
-                    \State \Call{send\_voltage\_command}{voltage}
-                    \State \Call{sleep}{step \_time}
-                    \State $voltage \gets voltage + step\_size$
-                \EndWhile
-            \EndFor
-        \EndProcedure
-
-        \end{algorithmic}
-    \end{algorithm}
-
-    In Figure \ref{fig:map2Data_fig} it can be seen the data acquired in this mapping experiments. The liquid used is pure ethanol. 
+    To reach certain map it is necessary to traverse flow rate (X axis) and voltage (Y axis) values acquiring samples.
+    In Figure \ref{fig:map2Data_fig} it can be seen how the mapping procedure works. The liquid used is pure ethanol. 
     Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.
@@
         \center
-        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
+        \includegraphics[width=16cm]{Figuras/report2/map2Data.png}
         \caption{Mapping Experiment data collected. The Figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
@@
     With all the data collected, classified and saved in real time, further analysis and studies can be done. 
-For example, Figure \ref{fig:map3Data_fig} illustrate the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison on automatic results with previous researches can be done, such as showed in Figure \ref{fig:ganan_calvo_fig}, validating the algorithm.
+    For example, Figure \ref{fig:map3Data_fig} illustrates the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison between manual and automatic results can be done, validating the algorithm, as will be shown in section \ref{subsec:map_results}.
 
@@
 This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve the project goals.
-Next chapter \ref{chap:Results}, it will be discussed the results reached.
+Next chapter \ref{chap:Results}, the results reached will be discussed.
 

### 2023-05-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

@@
 The automated experiment routine is capable of acquiring a significantly more precise and extensive amount of data than what can be achieved by a human. 
-With the save data by streaming in saving thread, it was achieved less program memory during the experiment and, specially, safety for not losing the data in case the program fail during an experiment.
+It was achieved less program memory during the experiment and, specially, safety for not losing data in case the program fail during an experiment with the usage of json streams in the saving thread.
 
-Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person and takes some time to achieve the desired voltage.
+Also, most power supplies rely on manual potentiometer adjustment to select the set point, which results in imprecise potential selection by a person, and it takes some time to achieve the desired voltage.
 Moreover, the electrospray phenomena has a known hysteresis, that can be seen in figure \ref{fig:ganan_calvo_fig}, and can perform different results depending on the previous electric potential.
@@
 
-The classification results in the algorithm implemented as described in section \ref{sec:section_classification} showed good accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
+The classification results in the algorithm implemented as described in section \ref{sec:section_classification} showed high accuracy for all the classifications described in section \ref{sec:spraying_modes_subsec}.
 Nevertheless, the multi jet classification made by a current value factor of 1.14 above the cone jet is just effective for pure ethanol, liquid used in all this project.
 
-Even if the multi jet classification just works for pure ethanol, the data saved with correct classification in ethanol can be used to extract any other signal information about the multi jet or to train a black box classification algorithm.
+Even if the multi jet classification just works for pure ethanol, the data saved with correct classification for ethanol can be used to extract any other signal information about the multi jet or to train a black box classification algorithm.
 
@@
 The first classification results were made exploring the voltage ranges. 
-For that, a flow rate was fixed to 0.7 uL/min. and ran a step routine as defined in \ref{subsec:step_routine}. 
+For that the setup file was configured to run a step routine with a fixed flow rate of 0.7 uL/min., as defined in \ref{subsec:step_routine}.
+
 The figure \ref{fig:step_class} shows three graphs. 
-
-The first shows the controller output signal as an input voltage of the process.
-As it is a step routine, an increasing voltage with steps of sizes 50V and time between each step of 5 seconds was implemented.
+The first is about the controller output signal as an input voltage of the process.
+As it is a step routine, an increasing voltage with steps sizes of 50V and time between each step of 5 seconds was implemented.
 The voltage range is between 3k-10k Volts.
@@
 For example, dripping mode has a current mean of 0V.
-The Intermittent state has a high variation of values that can be seen by the increased thickness on the graph.
+The Intermittent state have a high variation of values that can be seen by the increased thickness on the graph.
 The cone jet is a thinner graph because of its constant signal.
@@
 For validation with literature and also to expose the benefits of the automated routine and classification, the map sequence proof itself the best result of this work. 
-Initially, for better understand pure ethanol classification regions through voltage and flow rate ranges, it was made a manual map seen in figure \ref{fig:stability_1}.
+Initially, for better understanding of pure ethanol classification regions through voltage and flow rate ranges, a manual map was made, as seen in figure \ref{fig:stability_1}.
 
@@
     In order to validate the automatic classification, experiments were made comparing both visual and automatic stability island on the same experiment.
-    Figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).
+    figure \ref{fig:stability_2} shows that automatic stable cone jet region could be identified in the same region as visually seen by the high speed camera (data acquired manually).
 
@@
 
-    With the development of a multi jet classification using the logic explained in section \ref{sec:section_classification}, the same experiment was repeated, as shown in Figure \ref{fig:stability_6}.
+    With the development of a multi jet classification using the logic explained in section \ref{sec:section_classification}, the same experiment was repeated, as shown in figure \ref{fig:stability_6}.
 
@@
 
-    \subsubsection{Non-dimensional axis}
-
-    To have a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands showed in figure \ref{fig:ganan_calvo_fig}, with a visual juxtaposition of the shapes, the data displayed in Figure \ref{fig:stability_8} using the non-dimensional numbers used in his work\cite{gananCalvo}.
+    For a better comparison with literature, specifically the Gañán-Calvo\cite{gananCalvo} stability islands shapes showed in figure \ref{fig:ganan_calvo_fig}, a visual juxtaposition of the same data in figure \ref{fig:stability_6} was displayed in figure \ref{fig:stability_8} using the non-dimensional numbers of potential and flow rate on the axis.
 
@@
 
-    The results of mapping experiment corresponded visual, literature and automatic regions of classification, giving authentication to the method.
+        The holes of data in figure \ref{fig:stability_8} is because of the logarithmic scale in the x-axis. 
+        To fill the graph and compare with literature the behavior of the cone jet island while increasing the conductivity, other 3 experiments with different conductivities solutions of ethanol were done with help of a PhD in chemical engineering, L.
+P.
+Di Bonito.
+        Each graph in figure \ref{fig:conductivity_test} took around 5 hours of experiment and 20 GB of data stored.
+
+        While increasing conductivity, the cone jet stability region changes its shape and slightly moves to the right, as demonstrated by Gañán-Calvo in figure \ref{fig:ganan_calvo_fig}.
+        The multi jet classification was not considered in these experiments and were classified as 'Undefined' because the classification rule defined in this project works just for pure ethanol.
+
+        \begin{figure}[H]
+            \center
+            \includegraphics[width=18cm]{Figuras/may/conductivity_test.png}
+            \caption{Mapping experiment for different conductivities of ethanol solution.}
+            \label{fig:conductivity_test}
+        \end{figure}
+
+    The results of automatic mapping experiment corresponded manually and with literature the regions of classification, validating the method.
 
@@
 
-    The results of the classification process were favorable for experiment automation, however, the inaccuracy of the classification by statistical methods, specially the Multi Jet\ref{subsec:Multi Jet}, limited the development of a complete control project.
-    Together with the amount of variables that need to be syntonized makes it hard to stabilize in a desired mode.
+    The results of the classification process were favorable for experiment automation, however, the inaccuracy of the classification by statistical methods, specially the Multi Jet \ref{subsec:Multi Jet}, limited the development of a complete control project.
+    Together with the amount of variables that need to be adjusted it is hard to stabilize in a desired mode.
     Even with all those problems, a simple controller project could be implemented, as described in section \ref{sec:control_model}, that validated the efforts of remodeling all software into a closed loop control model.
 
-    The controller not only stabilized in cone jet mode, but also could reject perturbation, as seen in Figure \ref{fig:control_results}, where the flow rate was manually changed.
-    First graph shows current acquired.
-It starts as intermittent state, with an oscillating signal.
-This can be validated with the blue colored sample on the third graph representing its automatic classification.
-    The second graph shows the controller actuating increasing the voltage to achieve a stable cone jet mode.
-    After a period of time in cone jet, a manual increase in the flow rate was done, serving as a perturbation of the system, and it can be seen that the effect of that was to return to intermittent state with the oscillating signal.
-The controller again, actuate increasing the voltage to reach the cone jet stability island.
-    This procedure was repeated after some seconds of stabilization in cone jet, increasing once more the flow rate manually, and again the system automatically adjusting the voltage.
+    The controller not only stabilized in cone jet mode, but also could reject perturbation, as seen in figure \ref{fig:control_results}, where the flow rate was manually changed.
+    First graph shows the raw current acquired during this experiment.
+    The second graph shows a voltage graph where it can be seen the controller actuating increasing the voltage to achieve a stable cone jet mode.
+    The third graph shows the mean value of each sample colored representing its automatic classification.
+
+    At the beginning, the system starts up with initial voltage of 4500 V, being classified as intermittent state, defined by an oscillating signal in first graph and blue samples in third graph. 
+    The controller then, automatically actuates increasing the voltage to reach the stable cone jet. 
+    After a period of stability, it was done a manual increase in the flow rate, serving as a perturbation of the system, and it can be seen that the effect of that was to return to intermittent state with the oscillating signal.
+    The controller again, actuates by increasing the voltage to reach the cone jet stability island. 
+    This procedure was repeated after some seconds of stabilization in cone jet, increasing once more the flow rate manually, and again the system automatically adjusted the voltage.
+
     \begin{figure}[H]
@@
             \includegraphics[width=16cm]{Figuras/19:03/control_first_results.png}
-            \caption{Simple controller validation experiment.
-For this experiment, after waiting the system to stabilize in the desired spraying mode it was made a perturbation test changing the flow rate.
-The classification legend follows the same color reference in all project.}
+            \caption{Simple controller validation with manual perturbations in flow rate.}
             \label{fig:control_results}
@@
 
-    After 200s of experiment the system had some breaks up of the cone jet into a droplet and stabilized again.
-This is represented by the peak values in current signal.
-The classification correctly identified as intermittent, seen as blue dots in the third graph, and the controller reacted increasing the voltage, in a situation that can be considered as noise.
+    After 200 seconds of experiment the system had some breaks up of the cone jet into a droplet and stabilized again, represented by the peak values in current signal.
+In this case the classification correctly identified as intermittent because of its signal shape, seen as blue dots in the third graph, but the controller reacted increasing the voltage in a situation that can be considered as noise because it was a small period of instability inside the stability region that could be a result of other external perturbation such as a bubble in the liquid line.
 A filter can be applied in a more complex controller project to avoid this.

### 2023-05-24 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

@@
 
-% \begin{algorithm}
-%     \caption{STEP sequence in controller thread}\label{alg:stepping_algorithm}
-%     \begin{algorithmic}
-%     \Procedure{STEP}{$voltage\_start,voltage\_stop$} 
-%         \State $voltage \gets voltage\_start$
-%         \While{$voltage \leq voltage\_stop$} \Comment{scanning voltage range}
-%             \State \Call{send\_voltage\_command}{voltage}
-%             \State \Call{sleep}{step \_time}
-%             \State $voltage \gets voltage + step\_size$
-%         \EndWhile
-%     \EndProcedure
-
-%     \end{algorithmic}
-% \end{algorithm}
-
 \subsection{Map}
@@
     \center
-    \includegraphics[width=13cm]{Figuras/ganan_calvo_map.png}
+    \includegraphics[width=15cm]{Figuras/ganan_calvo_map.png}
     \caption{Domains of existence (stability) of Taylor Cone Jets. \cite{gananCalvo} .}
@@
 
+    \vspace{2cm}
     To reach certain map it is necessary to traverse flow rate (X axis) and voltage (Y axis) values acquiring samples.
